\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


\usepackage{unicode-math}
\setmathfont{LatinModernMath-Regular}
\AtBeginDocument{\grelatexsimpledefbarredsymbol{V}{0.1em}{0.12em}{0.14em}{0.18em}}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Everything]{Graduale O.P.}
\section{Everything}


 

%%Combination

\newpage


 \subsection{Officium}  \greannotation{VIII} \index[Officium]{Ad te levavi} \label{Ad te levavi (Officium)} \grecommentary[7pt]{Ps 24:1–3; \Vbar. 4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--ad_te_levavi--dominican--id_5367}  \vspace{5pt} \par{To You have I lifted up my soul; my God, in you I put my trust, let me not be ashamed; neither let my enemies laugh at me, for no one who waits for You shall be confounded. \Vbar. Show, O Lord, Your ways to me, and teach me Your paths.}  

 \subsection{Responsorium}  \greannotation{I} \index[Responsorium]{Universi} \label{Universi (Responsorium)} \grecommentary[0pt]{Ps 24:3; \Vbar. 4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--universi--dominican--id_5146}  \vspace{5pt} \par{No one who waits for You shall be confounded, O Lord. \Vbar. Show, O Lord, Your ways to me, and teach me Your paths.}  

 \subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Ostende nobis} \label{Ostende nobis (Alleluia)} \grecommentary[0pt]{Ps 84:8} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--ostende_nobis--dominican--id_4904}  \vspace{5pt} \par{Show us, O Lord, Your mercy, and grant us Your salvation.}  
 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Ad te Domine levavi} \label{Ad te Domine levavi (Offertorium)} \grecommentary[0pt]{Ps 24:1–3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--ad_te_domine_levavi--dominican--id_4301}  \vspace{5pt} \par{To You, O Lord, have I lifted up my soul; my God, in You I put my trust, let me not be ashamed; neither let my enemies laugh at me: for no one who waits for Yon shall be confounded.}  
 \subsection{Communio}  \greannotation{I} \index[Communio]{Dominus dabit} \label{Dominus dabit (Communio)} \grecommentary[5pt]{Ps 84:13} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--dominus_dabit--dominican--id_6204}  \vspace{5pt} \par{The Lord will bestow His goodness, and our earth shall yield its fruit.}  


 \subsection{Officium}  \greannotation{VII} \index[Officium]{Populus Sion} \label{Populus Sion (Officium)} \grecommentary[5pt]{Cf. Is 30:19, 30; \Vbar. Ps 79:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--populus_sion--dominican--id_4278}  \vspace{5pt} \par{People of Zion, behold the Lord shall come to save the nations; and the Lord shall make the glory of His voice to be heard in the joy of your hearts. \Vbar. Take heed, O you who rule Israel, you who lead Joseph like a sheep.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Ex Sion} \label{Ex Sion (Responsorium)} \grecommentary[0pt]{Ps 49:2, 3; \Vbar. 5} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--ex_sion_species--dominican--id_6456}  \vspace{5pt} \par{Out of Zion, the loveliness of His beauty, God shall come revealed. \Vbar. Gather together His saints before Him, who have set His covenant before sacrifices.}  
 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Lætatus sum} \label{Lætatus sum (Alleluia)} \grecommentary[0pt]{Ps 121:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--laetatus_sum--dominican--id_6365}  \vspace{5pt} \par{I rejoiced at the things that were said to me: ``We shall go into the house of the Lord."}  


 \subsection{Offertorium}  \greannotation{III} \index[Offertorium]{Deus tu convertens} \label{Deus tu convertens (Offertorium)} \grecommentary[5pt]{Ps 84:7–8} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--deus_tu_convertens--dominican--id_4305}  \vspace{5pt} \par{You will tum, O God, and bring us to life, and Your people shall rejoice in You. Show us, O Lord, Your mercy, and grant us Your salvation.}  

 \subsection{Communio}  \greannotation{II} \index[Communio]{Ierusalem surge} \label{Ierusalem surge (Communio)} \grecommentary[0pt]{Bar 5:5; 4:36} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--ierusalem_surge--dominican--id_6773}  \vspace{5pt} \par{Arise, O Jerusalem, and stand on high; and behold the joy that comes to you from your God.}  



 \subsection{Officium}  \greannotation{I} \index[Officium]{Gaudete in Domino} \label{Gaudete in Domino (Officium)} \grecommentary[0pt]{Phil 4:4, 5; \Vbar. 7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--gaudete_in_domino--dominican--id_4287}  \vspace{5pt} \par{Rejoice in the Lord always; again, I say, rejoice. Let your moderation be known to all men. The Lord is near. Have no anxiety, but in every prayer let your petitions be made known to God. \Vbar. And may the peace of God, which surpasses all understanding, keep your hearts and minds.}  

 \subsection{Responsorium} Dom. annis A et C: \greannotation{VII} \index[Responsorium]{Qui sedes, Domine} \label{Qui sedes, Domine (Responsorium)} \grecommentary[5pt]{Ps 79:2, 3; \Vbar. 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--qui_sedes_domine--dominican--id_6651}  \vspace{5pt} \par{You, O Lord, who sit upon the cherubim, stir up Your might, and come. \Vbar. Take heed, O you who rule Israel, you who lead Joseph like a sheep.}  
 \subsection{Responsorium} Dom. anno B: \greannotation{V} \index[Responsorium]{Fuit homo} \label{Fuit homo (Responsorium)} \grecommentary[5pt]{Io 1:6; \Vbar. 7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--fuit_homo--dominican}  \vspace{5pt} \par{There was a man sent from God whose name was John; he came. \Vbar. To bear witness to the light, to prepare an upright people for the Lord.}  

 \subsection{Alleluia}  \greannotation{IV} \index[Alleluia]{Excita Domine} \label{Excita Domine (Alleluia)} \grecommentary[0pt]{Ps 79:3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--excita_domine--dominican--id_5097}  \vspace{5pt} \par{Stir up Your might, O Lord, and come, that You may save us.}  
 \subsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Benedixisti Domine} \label{Benedixisti Domine (Offertorium)} \grecommentary[0pt]{Ps 84:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--benedixisti_domine--dominican--id_4304}  \vspace{5pt} \par{You have blessed Your land, O Lord; You have turned away the captivity of Jacob; You have forgiven the iniquity of Your people.}  
 \subsection{Communio}  \greannotation{VII} \index[Communio]{Dicite: Pusillanimes} \label{Dicite: Pusillanimes (Communio)} \grecommentary[10pt]{Cf. Is 35:4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--dicite_pusillanimes--dominican--id_5719}  \vspace{5pt} \par{Say to the faint-hearted: ``Take courage and fear not; behold, our God will come and save us."}  


































 \subsection{Officium}  \greannotation{I} \index[Officium]{Rorate cæli} \label{Rorate cæli (Officium)} \grecommentary[5pt]{Is 45:8} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--rorate--dominican--id_5489}  \vspace{5pt} \par{Drop down dew, you heavens, from above, and let the clouds rain the just; let the earth be opened and bud forth a Savior. \Vbar. And let justice spring up together: I the Lord have created him.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Prope est Dominus} \label{Prope est Dominus (Responsorium)} \grecommentary[0pt]{Ps 144:18; \Vbar. 21} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--prope_est_dominus--dominican--id_6717}  \vspace{5pt} \par{The Lord is near to all who call upon Him; to all who call upon Him in truth. \Vbar. My mouth shall speak the praise of the Lord; and let all flesh bless His holy name.}  
 \subsection{Alleluia}  \greannotation{III} \index[Alleluia]{Veni Domine} \label{Veni Domine (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--veni_domine--dominican--id_4958}  \vspace{5pt} \par{Come, O Lord, and do not delay: forgive the sins of Your people.}  
 \subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Ave Maria [Dominica quarta Adventus]} \label{Ave Maria [Dominica quarta Adventus] (Offertorium)} \grecommentary[0pt]{Lc 1:28, 42} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--ave_maria_et_benedictus--dominican--id_4781}  \vspace{5pt} \par{Hail Mary, full of grace, the Lord is with you. Blessed are you among women, and blessed is the fruit of your womb.}  
 \subsection{Communio}  \greannotation{I} \index[Communio]{Ecce virgo} \label{Ecce virgo (Communio)} \grecommentary[3pt]{Is 7:14} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--ecce_virgo--dominican--id_6887}  \vspace{5pt} \par{Behold, a virgin shall conceive and bring forth a son, and His name shall be called Emmanuel.}  










 \subsection{Communio}  \greannotation{I} \index[Communio]{Revelabitur} \label{Revelabitur (Communio)} \grecommentary[0pt]{Cf. Is 40:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--revelabitur--dominican--id_7068} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The glory of the Lord shall be revealed, and all flesh shall see the salvation of our God.} 

 \subsection{Officium}  \greannotation{II} \index[Officium]{Dominus dixit} \label{Dominus dixit (Officium)} \grecommentary[0pt]{Ps 2:7; \Vbar. 1, 2, 8} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--dominus_dixit--dominican--id_6135-antiphon-only}  \vspace{5pt} \par{The Lord said to me: ``You are my Son, this day have I begotten you.'' \par \Vbar.\textsuperscript{1} Why have the Gentiles raged, and the people devised vain things? \par \Vbar.\textsuperscript{2} The kings of the earth stand by, and the princes come together as one against the Lord, and against his Christ. \par \Vbar.\textsuperscript{8} Ask of me, and I will give you the nations as your inheritance, and the ends of the earth as your possession.}  
 \subsection{Versus Officii}  \greannotation{II} \index[Versus Officii]{Dominus dixit (Verses)} \label{Dominus dixit (Verses) (Versus Officii)} \grecommentary[0pt]{Ps 2:7; \Vbar. 1, 2, 8} \gresetinitiallines{0}  \gregorioscore{graduale-chants/in--dominus_dixit--dominican--id_6135-verses-only}  \vspace{5pt} \par{}  
 \subsection{Responsorium}  \greannotation{II} \index[Responsorium]{Tecum principium} \label{Tecum principium (Responsorium)} \grecommentary[0pt]{Ps 109:3; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--tecum_principium--dominican--id_6602}  \vspace{5pt} \par{Yours is princely power in the day of Your strength. In the brightness of the saints, from the womb before the day-star I begot You. \Vbar. The Lord said to my Lord: ``Sit at my right hand until I make Your enemies Your footstool.''}  
 \subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Dominus dixit} \label{Dominus dixit (Alleluia)} \grecommentary[0pt]{Ps 2:7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--dominus_dixit--dominican--id_6629}  \vspace{5pt} \par{The Lord said to me: ``You are my son, this day have I begotten You. Alleluia!''}  
 \subsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Lætentur cæli} \label{Lætentur cæli (Offertorium)} \grecommentary[0pt]{Ps 95:11} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--laetentur_caeli--dominican--id_7062}  \vspace{5pt} \par{Let the heavens rejoice, and let the earth be glad before the face of the Lord, because He comes.}  
 \subsection{Communio}  \greannotation{VI} \index[Communio]{In splendoribus} \label{In splendoribus (Communio)} \grecommentary[0pt]{Ps 109:3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--in_splendoribus--dominican--id_7236}  \vspace{5pt} \par{In the brightness of the saints, from the womb before the day-star I begot You.} \vspace{10pt}

 \subsection{Officium}  \greannotation{VIII} \index[Officium]{Lux fulgebit} \label{Lux fulgebit (Officium)} \grecommentary[7pt]{Cf. Is 9:2, 6; Lc 1:33; Ps 92:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--lux_fulgebit--dominican--id_6395}  \vspace{5pt} \par{A light shall shine upon us this day, for our Lord is born to us; and He shall be called Wonderful, God, the Prince of peace, the Father of the world to come: of whose reign there shall be no end. \Vbar. The Lord has reigned, He is clothed with beauty; the Lord is clothed with strength, and has girded Himself with power.} \vspace{10pt}





 \subsection{Officium}  \greannotation{VII} \index[Officium]{Puer natus est} \label{Puer natus est (Officium)} \grecommentary[3pt]{Is 9:6; Ps 97:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--puer_natus_est--dominican--id_5324}  \vspace{5pt} \par{A child is born to us and a son is given to us, whose government is upon His shoulders; and His name shall be called the angel of great counsel. \Vbar. Sing to the Lord a new canticle, for He has done wonderful things.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Viderunt omnes} \label{Viderunt omnes (Responsorium)} \grecommentary[3pt]{Ps 97:3, 4; \Vbar. 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--viderunt_omnes--dominican--id_5602}  \vspace{5pt} \par{All the ends of the earth have seen the salvation of our God. Sing joyfully to God, all the earth. \Vbar. The Lord has made known His salvation; He has revealed His justice in the sight of the Gentiles.}  
 \subsection{Alleluia}  \greannotation{II} \index[Alleluia]{Dies sanctificatus} \label{Dies sanctificatus (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--dies_sanctificatus--dominican--id_6593}  \vspace{5pt} \par{A sanctified day has shone upon us; come you Gentiles, and adore the Lord; for this day a great light has descended upon the earth.}  
 \subsection{Sequentia}  \greannotation{VI} \index[Sequentia]{Laetabundus} \label{Laetabundus (Sequentia)} \grecommentary[7pt]{Ecclesia [Proprium 1985]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/se--laetabundus_1985_version--dominican--id_4215}  \vspace{5pt} \par{Let the faithful choir joyfully rejoice, alleluia! The womb of the undefiled one has brought forth the King of Kings: a thing of wonder. The Angel of the counsel is born of the Virgin; the Sun of the Star. The Sun knows no setting, the Star is ever shining, ever bright. As the star brings forth its ray, in like manner the Virgin brings forth her Son. Neither the Star by its ray, nor the Mother by her Son becomes defiled. \par The lofty cedar of Lebanon is conformed to the hyssop in our Valley; The Word, the Being of the Most High, has deigned to become incarnate, having assumed our flesh. Isaias foretold it, the Synagogue remembers it, yet never does it cease to be bound. If not her own prophets, let her at least believe the Gentiles; in the sibylline verses these things were predicted. O Unhappy one, hasten, believe even the ancient legends. Why be cast away, O Chosen Race? Behold the Child whom the Scriptures proclaim. A Maid has borne Him. Alleluia!}  
 \subsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Tui sunt cæli} \label{Tui sunt cæli (Offertorium)} \grecommentary[0pt]{Ps 88:12, 15} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--tui_sunt_caeli--dominican}  \vspace{5pt} \par{Yours are the heavens, and Yours is the earth. The world and the fullness thereof You have founded. Justice and judgement are the preparation of Your throne.}  
 \subsection{Communio}  \greannotation{I} \index[Communio]{Viderunt omnes} \label{Viderunt omnes (Communio)} \grecommentary[5pt]{Ps 97:3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--viderunt_omnes--dominican--id_5158}  \vspace{5pt} \par{All the ends of the earth have seen the salvation of our God.}  















 \subsection{Officium}  \greannotation{II} \index[Officium]{Salve sancta Parens} \label{Salve sancta Parens (Officium)} \grecommentary[4pt]{Sedulius, \emph{Carmen Paschale}; \Vbar. Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--salve_sancta_parens--dominican--id_6966}  \vspace{5pt} \par{Hail holy Mother, the Child-Bearer who has brought forth the King, the ruler of heaven and earth for ever. \Vbar. After giving birth, O Virgin, you remained inviolate: Mother of God, intercede for us.}  
 \subsection{Officium} Vel: \greannotation{VIII} \index[Officium]{Lux fulgebit} \label{Lux fulgebit (Officium)} \grecommentary[7pt]{Cf. Is 9:2, 6; Lc 1:33; Ps 92:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--lux_fulgebit--dominican--id_6395}  \vspace{5pt} \par{A light shall shine upon us this day, for our Lord is born to us; and He shall be called Wonderful, God, the Prince of peace, the Father of the world to come: of whose reign there shall be no end. \Vbar. The Lord has reigned, He is clothed with beauty; the Lord is clothed with strength, and has girded Himself with power.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Diffusa est} \label{Diffusa est (Responsorium)} \grecommentary[3pt]{Ps 44:3; \Vbar. 5 [GR]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--diffusa_est--vatican}  \vspace{5pt} \par{Grace is poured out upon your lips; therefore has God blessed you for ever. \Vbar. For the cause of truth and goodness and righteousness, your right hand shall lead you wonderfully.}  
 \subsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Multifarie} \label{Multifarie (Alleluia)} \grecommentary[4pt]{Hebr 1:1, 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--multifarie--dominican--id_4775}  \vspace{5pt} \par{In many ways in the past, God spoke through the prophets; at long last, in these present days, he has spoken to us through his Son.}  
 \subsection{Offertorium}  \greannotation{I} \index[Offertorium]{Felix namque} \label{Felix namque (Offertorium)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--felix_namque--dominican}  \vspace{5pt} \par{For you are happy, O holy virgin Mary, and most worthy of all praise, because from you arose the sun of justice, Christ our God.}  
 \subsection{Communio}  \greannotation{IV} \index[Communio]{Exsulta filia Sion} \label{Exsulta filia Sion (Communio)} \grecommentary[0pt]{Zach 9:9} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--exsulta_filia--dominican--id_6171}  \vspace{5pt} \par{Rejoice greatly, O daughter of Zion, shout for joy, O daughter of Jerusalem; behold your King comes, the holy one, and the Savior of the world.}  



















 \subsection{Officium}  \greannotation{II} \index[Officium]{Ecce advenit} \label{Ecce advenit (Officium)} \grecommentary[0pt]{Cf. Mal 3:1; 1 Chron 29:12; \Vbar. Ps 71:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--ecce_advenit--dominican--id_5006}  \vspace{5pt} \par{Behold the Lord the ruler is come, and a kingdom is in His hand, and power and dominion. \Vbar. Give to the king Your judgement, O God, and to the king's son Your justice.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Omnes de Saba} \label{Omnes de Saba (Responsorium)} \grecommentary[0pt]{Is 60:6; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--omnes_de_saba--dominican--id_7014}  \vspace{5pt} \par{All those from Sheba shall come, bringing gold and frankincense, and showing forth praise to the Lord. \Vbar. Arise, and be enlightened, O Jerusalem, for the glory of the Lord is risen upon you.}  
 \subsection{Alleluia}  \greannotation{II} \index[Alleluia]{Vidimus stellam} \label{Vidimus stellam (Alleluia)} \grecommentary[0pt]{Cf. Mt 2:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--vidimus_stellam--dominican--id_6342}  \vspace{5pt} \par{We have seen His star in the east, and have come with gifts to adore Him.}  
 \subsection{Offertorium}  \greannotation{V} \index[Offertorium]{Reges Tharsis} \label{Reges Tharsis (Offertorium)} \grecommentary[0pt]{Ps 71:10, 11} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--reges_tharsis--dominican--id_6426}  \vspace{5pt} \par{The kings of Tharsis and the islands shall offer gifts; the kings of the Arabians and of Sheba shall bring presents; and all the kings of the earth shall adore Him, all nations shall serve Him.}  
 \subsection{Communio}  \greannotation{IV} \index[Communio]{Vidimus stellam} \label{Vidimus stellam (Communio)} \grecommentary[0pt]{Cf. Mt 2:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--vidimus_stellam--dominican--id_5896}  \vspace{5pt} \par{We have seen His star in the east, and have come with gifts to adore Him.}  




















 \section{Ad ritus initiales et liturgiam verbi}           
 \subsection{Officium}  \greannotation{I} \index[Officium]{Misereris omnium} \label{Misereris omnium (Officium)} \grecommentary[2pt]{Sap 11:24–25, 27; \Vbar. Ps 56:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--misereris_omnium--dominican--id_4279}  \vspace{5pt} \par{You have mercy upon all, O Lord, and hate none of the things which You have made, overlooking the sins of men for the sake of repentance and sparing them: for You are the Lord our God. \Vbar. Have mercy on me, O God, have mercy on me, for my soul trusts in You.}  
 \subsection{Responsorium}  \greannotation{I} \index[Responsorium]{Miserere mei} \label{Miserere mei (Responsorium)} \grecommentary[0pt]{Ps 56:2; \Vbar. 4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--miserere_mei_deus--dominican--id_5398}  \vspace{5pt} \par{Have mercy on me; O God, have mercy on me, for my soul trusts in You. \Vbar. He has sent forth from heaven and delivered me; He has made them a reproach who trod upon me.}  
 \subsection{Tractus}  \greannotation{II} \index[Tractus]{Domine non secundum} \label{Domine non secundum (Tractus)} \grecommentary[0pt]{Ps 102:10; Ps 78:8–9} \gresetinitiallines{1}  \gregorioscore{graduale-chants/tr--domine_non_secundum--dominican--id_6453}  \vspace{5pt} \par{Deal not with us, O Lord, according to our sins; nor reward us according to our iniquities. \Vbar. Remember not, O Lord, our former iniquities; let Your mercies speedily prevent us, for we are becoming very poor. \Vbar. Help us, O God our Savior, and for the glory of Your name, O Lord, deliver us, and forgive us our sins for Your name's sake.}  
 \section{Ad benedictionem et impositionem cinerum}           
  \emph{Dum celebrans principalis imponit cineres, cantantur:}          
 \subsection{Antiphona}  \greannotation{I} \index[Antiphona]{Immutemur habitu} \label{Immutemur habitu (Antiphona)} \grecommentary[0pt]{Cf. Ioel 2:13} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/an--immutemur_habitu--dominican--id_5601} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{Let us change our garments for ashes and sackcloth; let us fast and lament before the Lord; for plenteous in mercy to forgive our sins is our God.}  
 \subsection{Antiphona}  \greannotation{II} \index[Antiphona]{Iuxta vestibulum} \label{Iuxta vestibulum (Antiphona)} \grecommentary[4pt]{Ioel 2:7; Est 13:17} \gresetinitiallines{1}  \gregorioscore{graduale-chants/an--iuxta_vestibulum--dominican}  \vspace{5pt} \par{Between the porch and the altar the priests and the Levites, the ministers of the Lord, shall weep and shall say: ``Spare, O Lord, spare Your people, and shut not the mouths of those who cry to You, O Lord."}  
 \subsection{Responsorium} \emph{Vel:} \greannotation{II} \index[Responsorium]{Emendemus in melius} \label{Emendemus in melius (Responsorium)} \grecommentary[0pt]{Cf. Bar 3:2; \Vbar. Ps 106:6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/re--emendemus_in_melius--dominican--id_5915}  \vspace{5pt} \par{Let us make amends for the sins we have committed in ignorance, lest death's day come upon us suddenly, when we might seek more time for repentance and find none. $\star$ Hearken, O Lord, and have mercy, for we have sinned against you. \Vbar. We have sinned like our fathers; we have acted unjustly, we have performed iniquities. $\star$ Hearken, O Lord.}  
 \subsection{Antiphona} \emph{Vel, simpliciore forma:} \greannotation{VII} \index[Antiphona]{Exaudi nos Domine} \label{Exaudi nos Domine (Antiphona)} \grecommentary[7pt]{Ps 68:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/an--exaudi_nos--dominican--id_4802}  \vspace{5pt} \par{Hear us, O Lord, for Your mercy is kind; look upon us, O Lord, according to the multitude of Your tender mercies. \Vbar. Save me, O God, for the waters have come in even unto my soul.}  
 \section{Ad liturgiam Eucharisticam}           
 \subsection{Offertorium}  \greannotation{III} \index[Offertorium]{Exaltabo te} \label{Exaltabo te (Offertorium)} \grecommentary[0pt]{Ps 29:2, 3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--exaltabo_te--dominican--id_7207}  \vspace{5pt} \par{I will extol You, O Lord, for You have upheld me and have not made my enemies rejoice over me. O Lord, I have cried to You and You have healed me.}  
 \subsection{Communio}  \greannotation{III} \index[Communio]{Qui meditabitur} \label{Qui meditabitur (Communio)} \grecommentary[0pt]{Ps 1:2–3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--qui_meditabitur--dominican--id_6589}  \vspace{5pt} \par{He who shall meditate upon the law of the Lord, day and night, shall bring forth his fruit in due season.}  

















 \subsection{Officium}  \greannotation{VIII} \index[Officium]{Invocabit me} \label{Invocabit me (Officium)} \grecommentary[0pt]{Ps 90:15–16, 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--invocavit_me--dominican--id_5614}  \vspace{5pt} \par{He called upon Me, and I will hear him; I will deliver him, and glorify him; I will fill him with length of days. \Vbar. He who dwells in the shelter of the Most High, shall abide under the protection of the God of Heaven.}  
 \subsection{Responsorium}  \greannotation{II} \index[Responsorium]{Angelis suis} \label{Angelis suis (Responsorium)} \grecommentary[0pt]{Ps 90:11–12} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--angelis_suis--dominican--id_5301}  \vspace{5pt} \par{God has given His angels charge over you, to keep you in all your ways. \Vbar. In their hands they shall bear you up, lest at any time you dash your foot against a stone.}  
 \subsection{Tractus}  \greannotation{II} \index[Tractus]{Qui habitat} \label{Qui habitat (Tractus)} \grecommentary[0pt]{Ps 90:1–7, 11–16} \gresetinitiallines{1} \renewcommand{\headsep}{12pt} \gregorioscore{graduale-chants/tr--qui_habitat--dominican--id_5592}  \vspace{5pt} \par{He who dwells in the shelter of the Most High, shall abide under the protection of the God of heaven. \par \Vbar. He shall say to the Lord: You are my protector, and my refuge: my God, in Him will I trust. \par \Vbar. For He has delivered me from the snare of the hunters and from the sharp word. \par \Vbar. He will overshadow you with His shoulders, and under His wings you shall trust. \par \Vbar. His truth shall compass you with a shield; you shall not be afraid of the terror of the night. \par \Vbar. Of the arrow that flies in the day; of the business that walks in the dark; of ruin, or of the noonday devil. \par \Vbar. A thousand shall fall at your side, and ten thousand at your right hand; but it shall not come near to you. \par \Vbar. For He has given His angels charge over you to keep you in all your ways. \par \Vbar. In their hands they  shall bear you up lest you dash your foot against a stone. \par \Vbar. You shall walk upon the asp and the basilisk, and you shall trample underfoot the lion and the dragon. \par \Vbar. Because he has hoped in Me, I will deliver him; I will protect him, because he has known My name. \par \Vbar. He shall call upon Me, and I will hear him; I am with him in tribulation. \par \Vbar. I will deliver him, and I will glorify him; I will fill him with length of days, and I will show him My salvation.}   \renewcommand{\headsep}{5pt}
 \subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Scapulis suis} \label{Scapulis suis (Offertorium)} \grecommentary[0pt]{Ps 90:4–5} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--scapulis_suis--dominican--id_5204}  \vspace{5pt} \par{The Lord will overshadow you with His shoulders, and under His wings you shall trust; His truth shall compass you with a shield.}  
 \subsection{Communio}  \greannotation{III} \index[Communio]{Scapulis suis} \label{Scapulis suis (Communio)} \grecommentary[0pt]{Ps 90:4–5} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--scapulis_suis--dominican--id_6971}  \vspace{5pt} \par{He will overshadow you with His shoulders, and under His wings you shall trust; His truth shall compass you with a shield.}  
































 \subsection{Officium}  \greannotation{III} \index[Officium]{Tibi dixit cor meum} \label{Tibi dixit cor meum (Officium)} \grecommentary[7pt]{Ps 26:8, 9; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--tibi_dixit--dominican--id_5182}  \vspace{5pt} \par{My heart has said to You: I have sought Your face; Your face, O Lord, will I seek: turn not away Your face from me. \Vbar. The Lord is my light and my salvation; whom shall I fear?}  
 \subsection{Officium} Vel: \greannotation{IV} \index[Officium]{Reminiscere} \label{Reminiscere (Officium)} \grecommentary[4pt]{Ps 24:6, 3, 22; \Vbar. 1-2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--reminiscere--dominican--id_5181}  \vspace{5pt} \par{Remember, O Lord, Your compassion and Your mercies that are from the beginning of the world, lest at any time our enemies rule over us. Deliver us, O God of Israel, from all our tribulations. \Vbar. To you, O Lord, have I lifted up my soul: my God, in you have I put my trust, let me not be ashamed.}  


 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Meditabor in mandatis} \label{Meditabor in mandatis (Offertorium)} \grecommentary[5pt]{Ps 118:47, 48} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--meditabor--dominican--id_6142}  \vspace{5pt} \par{I will meditate on Your commandments, which I have loved exceedingly, and I will lift up my hands to Your commandments, which I have loved.} 
 \subsection{Communio}  \greannotation{I} \index[Communio]{Visionem quam vidistis} \label{Visionem quam vidistis (Communio)} \grecommentary[0pt]{Mt 17:9 [GR]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--visionem--vatican}  \vspace{5pt} \par{Of the vision you have seen, tell no one until the Son of Man has risen from the dead.}  
































 \subsection{Officium}  \greannotation{VII} \index[Officium]{Oculi mei} \label{Oculi mei (Officium)} \grecommentary[0pt]{Ps 24:15, 16; \Vbar. 1-2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--oculi_mei--dominican--id_7217}  \vspace{5pt} \par{My eyes are always on the Lord, for He shall pluck my feet out of the snare. Look upon me, and have mercy on me, for I am alone and poor. \Vbar. To You, O Lord, have I lifted up my soul; my God, in You have I put my trust, let me not be ashamed.}  



 \subsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Iustitiæ Domini} \label{Iustitiæ Domini (Offertorium)} \grecommentary[0pt]{Ps 18:9, 11, 12} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--iustitiae_domini--dominican--id_6109}  \vspace{5pt} \par{The precepts of the Lord are right, rejoicing hearts, and His judgments are sweeter than honey and the honeycomb, for Your servant will keep them.}  

 \subsection{Communio} Anno A (Quando legitur Evangelium de Samaritana): \greannotation{VII} \index[Communio]{Qui biberit aquam} \label{Qui biberit aquam (Communio)} \grecommentary[0pt]{Io 4:13, 14} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--qui_biberit--dominican--id_4868}  \vspace{5pt} \par{``Whosoever drinks the water that I shall offer," said the Lord (to the Samaritan woman), ``shall have within him a spring of water welling up unto eternal life."} 


 \subsection{Communio} Annis B et C (Quando legitur aliud Evangelium): \greannotation{I} \index[Communio]{Passer invenit} \label{Passer invenit (Communio)} \grecommentary[0pt]{Ps 83:4, 5} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--passer_invenit--dominican--id_6674}  \vspace{5pt} \par{The sparrow has found herself a house, and the turtledove a nest where she may lay her young ones: Your altars, O Lord of Hosts, my King, and my God. Blessed are they who dwell in Your house; for ever and ever shall they sing your praise.}  
































 \subsection{Officium}  \greannotation{V} \index[Officium]{Lætare Ierusalem} \label{Lætare Ierusalem (Officium)} \grecommentary[5pt]{Cf. Is 66:10, 11; \Vbar. Ps 121:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--laetare_ierusalem--dominican--id_5261}  \vspace{5pt} \par{Rejoice, O Jerusalem, and come together all you who love her; rejoice with joy, you who have been in sorrow, that you may exult, and be filled from the breasts of your consolation. \Vbar. I rejoiced because they said to me, ``We will go into the house of the Lord."}  


 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Laudate Dominum} \label{Laudate Dominum (Offertorium)} \grecommentary[0pt]{Ps 134:3, 6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--laudate_dominum--dominican--id_5285}  \vspace{5pt} \par{Praise the Lord, for He is good; sing to His name, for He is sweet; whatsoever He pleased He has done in heaven and in earth.}  

 \subsection{Offertorium} Anno A (\emph{ad libitum}): \greannotation{IV} \index[Offertorium]{Illumina oculos meos} \label{Illumina oculos meos (Offertorium)} \grecommentary[5pt]{Ps 12:4, 5} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--illumina--dominican--id_5998}  \vspace{5pt} \par{Enlighten my eyes lest I fall into the sleep of death; lest my enemy say: ``I have prevailed against him."}  

 \subsection{Communio} Anno A (Quando legitur Evangelium de cæco nato): \greannotation{VI} \index[Communio]{Lutum fecit} \label{Lutum fecit (Communio)} \grecommentary[5pt]{Cf. Io 9:6, 11, 38} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--lutum_fecit--dominican--id_6341}  \vspace{5pt} \par{The Lord made clay of spittle, and anointed my eyes, and I went, and washed, and I saw; and I believed in God.}  
 \subsection{Communio} Anno B: \greannotation{IV} \index[Communio]{Ierusalem quæ ædificatur} \label{Ierusalem quæ ædificatur (Communio)} \grecommentary[0pt]{Ps 121:3, 4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--ierusalem_quae--dominican--id_5394}  \vspace{5pt} \par{Jerusalem, which is built as a city, which is compact together; for there did the tribes go up, the tribes of the Lord, to praise Your name, O Lord.}  

 \subsection{Communio} Anno C (Quando legitur Evangelium de filio prodigo): \greannotation{VIII} \index[Communio]{Oportet te} \label{Oportet te (Communio)} \grecommentary[3pt]{Lc 15:32} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--oportet_te_fili--dominican--id_6842}  \vspace{5pt} \par{You ought to rejoice, my son, because Your brother was dead, and has come to life; he was lost, and is found.}  
































 \subsection{Officium}  \greannotation{III} \index[Officium]{Iudica me Deus} \label{Iudica me Deus (Officium)} \grecommentary[5pt]{Ps 42:1, 2, 3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--iudica_me--dominican--id_6158}  \vspace{5pt} \par{Judge me, O God, and distinguish my cause from the nation that is not holy. From the unjust and deceitful man deliver me, for You are my God and my strength. \Vbar. Send forth Your light and Your truth; they have conducted me, and brought me to Your holy hill, and into Your tabernacles.}  


 \subsection{Offertorium}  \greannotation{I} \index[Offertorium]{Confitebor tibi} \label{Confitebor tibi (Offertorium)} \grecommentary[3pt]{Ps 118:7, 10, 17, 25} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--confitebor_tibi__in_toto--dominican}  \vspace{5pt} \par{I will confess to You, O Lord, with my whole heart. Render to Your servant; I shall live and keep Your words; enliven me according to Your word, O Lord.}  

 \subsection{Communio} Anno A (Quando legitur Evangelium de Lazaro): \greannotation{I} \index[Communio]{Videns Dominus flentes} \label{Videns Dominus flentes (Communio)} \grecommentary[3pt]{Io 11:33, 35, 43, 44, 39} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--videns_dominus--dominican--id_7057}  \vspace{5pt} \par{When the Lord saw the sisters of Lazarus in tears near the tomb, He wept in the presence of the Jews, and cried out: ``Lazarus, come forth!" And he came forth, with bound feet and hands, he who had been dead four days.}  

 \subsection{Communio} Anno B (Quando legitur aliud Evangelium): \greannotation{V} \index[Communio]{Qui mihi ministrat} \label{Qui mihi ministrat (Communio)} \grecommentary[5pt]{Io 12:26} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--qui_mihi_ministrat--dominican--id_6620}  \vspace{5pt} \par{If anyone serves Me, let him follow Me: and where I am, there also shall my servant be.}  

 \subsection{Communio} Anno C (Quando legitur Evangelium de muliere adultera): \greannotation{VIII} \index[Communio]{Nemo te condemnavit} \label{Nemo te condemnavit (Communio)} \grecommentary[3pt]{Io 8:10, 11} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--nemo_te_condemnavit--dominican--id_7175}  \vspace{5pt} \par{``Has no one condemned you, woman?" ``No one, Lord." ``Neither will I condemn you; now sin no more."}  












 \subsection{Communio}  \greannotation{VII} \index[Communio]{Redime me Deus} \label{Redime me Deus (Communio)} \grecommentary[0pt]{Ps 24:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--redime_me--dominican--id_6994} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Redeem me, O God of Israel, from all my tribulations.} 
















 \subsection{Officium}  \greannotation{VIII} \index[Officium]{Domine ne longe} \label{Domine ne longe (Officium)} \grecommentary[0pt]{Ps 21:20, 22 et 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{} 









 \subsection{Antiphona}  \greannotation{VII} \index[Antiphona]{Hosanna filio David} \label{Hosanna filio David (Antiphona)} \grecommentary[0pt]{Mt 21:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--hosanna_filio_david--dominican--id_5587} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Hosanna to the Son of David: Blessed is he who comes in the Name of the Lord! }  









 \subsection{Antiphona}  \greannotation{I f} \index[Antiphona]{Pueri Hebræorum tollentes} \label{Pueri Hebræorum tollentes (Antiphona)} \grecommentary[0pt]{Cf. Jn 12:13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--pueri_hebraeorum_tollentes--dominican--id_6640} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Hebrew children, taking up olive branches, met the Lord, crying out and saying: ``Hosanna in the highest."} 



 \subsection{Antiphona}  \greannotation{I f} \index[Antiphona]{Pueri Hebræorum vestimenta} \label{Pueri Hebræorum vestimenta (Antiphona)} \grecommentary[0pt]{Cf. Mt 21:15, 8, 9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--pueri_hebraeorum_vestimenta--dominican--id_6173} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Hebrew children spread their garments in the way, and cried out, saying: ``Hosanna to the son of David; Blessed is He who comes in the name of the Lord."}  






 \subsection{Responsorium}  \greannotation{II} \index[Responsorium]{Ingrediente Domino} \label{Ingrediente Domino (Responsorium)} \grecommentary[0pt]{Ecclesia [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/re--ingrediente_domino--vatican-op} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{As the Lord entered the Holy City, the children of the Hebrews proclaimed the resurrection of life, $\star$ and, waving olive branches, they loudly praised the Lord: ``Hosanna in the highest." \Vbar. When the people heard that Jesus was entering Jerusalem, they went to meet him $\star$ and, waving olive branches, they loudly praised the Lord: ``Hosanna in the highest."}  

 \subsection{Officium}  \greannotation{VIII} \index[Officium]{Domine ne longe} \label{Domine ne longe (Officium)} \grecommentary[5pt]{Ps 21:20, 22 et 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--domine_ne_longe--dominican--id_6256} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Lord, let not Your help be far from me. Look to my defence; deliver me from the lion's mouth, and my lowliness from the horns of the unicorns. \Vbar. O God, my God, look on me! Why have You forsaken me? The voice of my sins keeps salvation far from me.}  






 \subsection{Communio}  \greannotation{VIII} \index[Communio]{Pater si non potest} \label{Pater si non potest (Communio)} \grecommentary[0pt]{Mt 26:42} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--pater_si_non_potest--dominican--id_4841} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Father, if this cup cannot pass away unless I drink it, Your will be done.}  



























 \subsection{Officium}  \greannotation{IV} \index[Officium]{Nos autem gloriari} \label{Nos autem gloriari (Officium)} \grecommentary[3pt]{Cf. Gal 6:14; Ps 66:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--nos_autem--dominican--id_6834} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{We ought to glory in the cross of our Lord Jesus Christ, in whom is our salvation, life and resurrection; by whom we are saved and delivered. \Vbar. May God have mercy on us, and bless us; may He let His face shine upon us, and have mercy on us.}  




 \subsection{Antiphona I}  \greannotation{II} \index[Antiphona I]{Dominus Iesus postquam} \label{Dominus Iesus postquam (Antiphona I)} \grecommentary[2pt]{Io 13:12, 13, 15; \Vbar. Ps 66:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--dominus_iesus--dominican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Lord Jesus, after eating supper with His disciples, washed their feet and said to them, ``Do you know what I, your Lord and Master, have done to you? I have given you an example, that so you also should do." \Vbar. May God have mercy on us, and bless us; may He let His face shine upon us, and have mercy on us.}  
 \subsection{Antiphona II}  \greannotation{IV} \index[Antiphona II]{Postquam surrexit} \label{Postquam surrexit (Antiphona II)} \grecommentary[7pt]{Cf. Io 13:4, 5, 15; \Vbar. Ps 48:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--postquam_surrexit--dominican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{After the Lord from supper, he poured water into a basin, and began to wash the feet of the disciples. Such is the example that he left them. \Vbar. Hear this, all you peoples; perceive with your ears you who dwell in the world.}  


 \subsection{Antiphona V}  \greannotation{III} \index[Antiphona V]{Mandatum novum} \label{Mandatum novum (Antiphona V)} \grecommentary[3pt]{Io 13:34; \Vbar. Ps 118:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--mandatum_novum--dominican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{A new commandment I give you: that you love one another, just as I have loved you, says the Lord. \Vbar. Blessed are the undefiled in the way, who walk in the law of the Lord.}  








 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Dextera Domini} \label{Dextera Domini (Offertorium)} \grecommentary[5pt]{Ps 117:16, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--dextera_domini--dominican--id_4758} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The right hand of the Lord has wrought strength; the right hand of the Lord has exalted me. I shall not die, but live, and shall declare the works of the Lord.}  



 \subsection{Communio}  \greannotation{VIII} \index[Communio]{Hoc corpus} \label{Hoc corpus (Communio)} \grecommentary[3pt]{I Cor 11:24, 25} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--hoc_corpus--dominican--id_5947} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{``This is my body which is given up for you; this is the chalice of the new covenant in my blood," says the Lord. ``Do this, as often as your receive it, in memory of me."}  











 \subsection{Improperia}  \input{graduale-chants/improperia--popule_meus}          


 \subsection{Antiphona}  \greannotation{VI} \index[Antiphona]{Ecce lignum Crucis} \label{Ecce lignum Crucis (Antiphona)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--ecce_lignum--dominican--id_6369} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Behold the wood of the Cross, on which the savior of the world hung; come, let us adore.} 
 \subsection{Antiphona}  \greannotation{IV} \index[Antiphona]{Tuam Crucem} \label{Tuam Crucem (Antiphona)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--tuam_crucem--dominican--id_6093} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{We adore your Christ, O Lord, we recall your glorious passion; have mercy on us, you who suffered for us.}  
 \subsection{Antiphona}  \greannotation{IV} \index[Antiphona]{Crucem tuam} \label{Crucem tuam (Antiphona)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--crucem_tuam--dominican--id_5371} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{We adore your Cross, O Lord, and we praise and glorify your holy Resurrection; for behold, on account of the Cross joy has come to the whole world.} 
 \subsection{Antiphona}  \greannotation{IV} \index[Antiphona]{Adoremus Crucis} \label{Adoremus Crucis (Antiphona)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--adoremus--dominican--id_6069} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{We adore the sign of the Cross, through which we have received the sacrament of salvation.}  
 \subsection{Hymnus}  \greannotation{I} \index[Hymnus]{Crux fidelis} \label{Crux fidelis (Hymnus)} \grecommentary[10pt]{Venantius Fortunatus} \gresetinitiallines{1} \gresetlyriccentering{syllable} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/hy--crux_fidelis--dominican--english} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0cm}{scalable} \vspace{5pt} \par{} 
 \subsection{Antiphona}  \greannotation{II} \index[Antiphona]{Super omnia ligna} \label{Super omnia ligna (Antiphona)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/an--super_omnia--dominican--id_6407} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{You alone are above all the cedars, you on which hung the life of the world; on which Christ triumphed, and death overcame death forever.} 

 \subsection{Communio}  \greannotation{I} \index[Communio]{Adoramus te} \label{Adoramus te (Communio)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--adoramus_te--dominican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{We adore you, O Christ, and we bless you, because by your Cross you have redeemed the world.}  
 \subsection{Communio}  \greannotation{VIII} \index[Communio]{Per lignum} \label{Per lignum (Communio)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--per_lignum--dominican--id_4990--good-friday} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{By the tree we became slaves, and by the holy cross we have been set free; the fruit of the tree enslaved us, the Son of God redeemed us. Alleluia!} 
 \subsection{Communio}  \greannotation{VII} \index[Communio]{Salvator mundi} \label{Salvator mundi (Communio)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--salvator_mundi--dominican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Savior of the world, save us, you have redeemed us by your Cross and Blood; help us, we beseech you, our God.} 























 \subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Confitemini Domino (+ Laudate Dominum)} \label{Confitemini Domino (+ Laudate Dominum) (Alleluia)} \grecommentary[3pt]{Ps 106:1-2; Ps 116:1-2} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/al--confitemini_quoniam_sab_sancto--dominican--id_5407--with--laudate_dominum-tract} \grechangedim{spaceabovelines}{0cm}{scalable} \vspace{5pt} \par{Praise the Lord, for He is good; for His mercy endures forever. \Vbar. Praise the Lord all you Gentiles, and praise Him all you people. \Vbar. For His mercy is established on us, and the truth of the Lord remains forever.}  







 \subsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam (Haec est dies)} \label{Vidi aquam (Haec est dies) (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348--haec_est_dies} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia; and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \Vbar. This is the day the Lord has made; let us exult and rejoice in it.}  

 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Dextera Domini} \label{Dextera Domini (Offertorium)} \grecommentary[5pt]{Ps 117:16, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--dextera_domini--dominican--id_4758} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The right hand of the Lord has wrought strength; the right hand of the Lord has exalted me. I shall not die, but live, and shall declare the works of the Lord.}  
 \subsection{Communio}  \greannotation{VI} \index[Communio]{Pascha nostrum} \label{Pascha nostrum (Communio)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--pascha_nostrum--dominican--id_6187} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Christ our Passover is sacrificed, alleluia; therefore, let us feast with the unleavened bread of sincerity and truth, alleluia, alleluia, alleluia.}  









 \subsection{Officium}  \greannotation{IV} \index[Officium]{Resurrexi} \label{Resurrexi (Officium)} \grecommentary[0pt]{Ps 138:18, 5, 6 et 1-2} \gresetinitiallines{2} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--resurrexi--dominican--id_6541} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{I have risen, and I am with you still, alleluia. You have laid your hand upon me, alleluia; Your knowledge is become wonderful, alleluia, alleluia. \Vbar. Lord, You have proved me, and known me; You have known when I sit and when I stand.}  

 \subsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Pascha nostrum} \label{Pascha nostrum (Alleluia)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--pascha_nostrum--dominican--id_7076} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Christ our Pasch is sacrificed.}  
 \subsection{Sequentia}  \greannotation{I} \index[Sequentia]{Victimæ paschali laudes} \label{Victimæ paschali laudes (Sequentia)} \grecommentary[5pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.3cm}{scalable} \gregorioscore{graduale-chants/se--victimae_paschali_laudes--dominican} \grechangedim{spaceabovelines}{0.0cm}{scalable} \vspace{5pt} \par{To the Paschal Victim let Christians offer their praises. The Lamb has redeemed the sheep, the sinless One has reconciled the sinners to His Father. \Vbar. Death and life contend in a wondrous conflict. The Prince of life died, yet living, reigns. \Vbar. Tell us, Mary, what did you see on the way? \Vbar. I saw the sepulcher of the living Christ and the glory of the Risen Savior; the angelic witnesses, the linen cloth and the clothing. \Vbar. Christ my hope has risen and goes before you into Galilee. \Vbar. We know that Christ is truly risen from the dead. O victorious King, have mercy on us. Alleluia.}  
 \subsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam (Haec est dies)} \label{Vidi aquam (Haec est dies) (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348--haec_est_dies} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia; and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \Vbar. This is the day the Lord has made; let us exult and rejoice in it.}  
 \subsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Terra tremuit} \label{Terra tremuit (Offertorium)} \grecommentary[0pt]{Ps 75:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--terra_tremuit--dominican--id_5651} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The earth trembled and was still, when God arose in judgment, alleluia.}  
 \subsection{Communio}  \greannotation{VI} \index[Communio]{Pascha nostrum} \label{Pascha nostrum (Communio)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--pascha_nostrum--dominican--id_6187} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Christ our Passover is sacrificed, alleluia; therefore, let us feast with the unleavened bread of sincerity and truth, alleluia, alleluia, alleluia.}  








































 \subsection{Officium}  \greannotation{VI} \index[Officium]{Quasi modo} \label{Quasi modo (Officium)} \grecommentary[0pt]{1 Petr. 2:2; \Vbar. Ps 80:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--quasi_modo--dominican--id_5508} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{As newborn babes, alleluia; desire the spiritual milk without guile, alleluia, alleluia, alleluia. \Vbar. Rejoice to God our helper; sing aloud to the God of Jacob.}  



 \subsection{Alleluia}  \greannotation{VII} \index[Alleluia]{In die resurrectionis} \label{In die resurrectionis (Alleluia)} \grecommentary[5pt]{Mt 28:7} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{graduale-chants/al--in_die--dominican--id_5632} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{``On the day of My Resurrection," says the Lord, ``I will go before you into Galilee."}  
 \subsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Post dies octo} \label{Post dies octo (Alleluia)} \grecommentary[0pt]{Io 20:26} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{graduale-chants/al--post_dies_octo--dominican--id_5461} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{After eight days, the doors being shut, Jesus stood in the midst of His disciples, and said, ``Peace be with you."}  



 \subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Angelus Domini} \label{Angelus Domini (Offertorium)} \grecommentary[5pt]{Mt 28:2, 5, 6} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.7 cm}{scalable} \gregorioscore{graduale-chants/of--angelus_domini--dominican--id_4302} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{An angel of the Lord descended from heaven and said to the women: ``He whom you seek is risen, as He said, alleluia."}  
 \subsection{Communio}  \greannotation{VI} \index[Communio]{Mitte manum tuam} \label{Mitte manum tuam (Communio)} \grecommentary[0pt]{Io 20:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--mitte_manum_alleluia--dominican--id_4846} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Put in your hand, and know the place of the nails, alleluia, and be not unbelieving, but believing, alleluia, alleluia.}  




 \subsection{Officium}  \greannotation{VIII} \index[Officium]{Iubilate Deo omnis terra alleluia} \label{Iubilate Deo omnis terra alleluia (Officium)} \grecommentary[5pt]{Ps 65:1, 2, 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--iubilate_deo--dominican--id_6146} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Sing joyfully to God, all the earth, alleluia. Sing a psalm to His name, alleluia. Give glory to His praise, alleluia, alleluia, alleluia. \Vbar. Say to God: ``How terrible are Your works, O Lord! because of Your great strength."}  

 \subsection{Alleluia}  \greannotation{III} \index[Alleluia]{Cognoverunt discipuli} \label{Cognoverunt discipuli (Alleluia)} \grecommentary[5pt]{Lc 24:35 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--cognoverunt--vatican-op} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The disciples recognized the Lord Jesus at the breaking of the bread.}  
 \subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Oportebat pati} \label{Oportebat pati (Alleluia)} \grecommentary[0pt]{Lc 24:46} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--oportebat_pati--dominican--id_6843} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{It behooved Christ to suffer, and rise again from the dead, and so enter into the glory of God.}  




 \subsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Lauda anima mea} \label{Lauda anima mea (Offertorium)} \grecommentary[0pt]{Ps 145:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--lauda_anima_mea--dominican--id_6999} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Praise the Lord, O my soul, in my life I will praise the Lord; I will sing to my God as long as I shall be, alleluia.}  
 \subsection{Communio} Dom. anno A: \greannotation{VI} \index[Communio]{Surrexit Dominus} \label{Surrexit Dominus (Communio)} \grecommentary[3pt]{Lc 24:34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--surrexit_dominus--dominican--id_7481} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Lord has risen, and has appeared to Peter, alleluia.}  
 \subsection{Communio} Dom. anno B: \greannotation{I} \index[Communio]{Cantate Domino} \label{Cantate Domino (Communio)} \grecommentary[5pt]{Ps 95:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--cantate_domino--dominican--id_5304} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Sing to the Lord, alleluia. Sing to the Lord, and bless His name. Show forth His salvation from day to day, alleluia, alleluia.}  
 \subsection{Communio} Dom. anno C: \greannotation{VI} \index[Communio]{Simon Ioannis} \label{Simon Ioannis (Communio)} \grecommentary[3pt]{Io 21:15, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--simon_ioannis--dominican--id_5102} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{``Simon, son of John, do you love Me more than these do?" ``Lord, You know all things, You know, Lord, that I love You."}  




 \subsection{Officium}  \greannotation{IV} \index[Officium]{Misericordia Domini} \label{Misericordia Domini (Officium)} \grecommentary[0pt]{Ps 32:5, 6 et 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--misericordia_domini--dominican--id_7213} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The earth is full of the mercy of the Lord, alleluia! By the word of God the heavens were established, alleluia, alleluia. \Vbar. Rejoice in the Lord, you just; praise becomes the upright.}  


 \subsection{Alleluia}  \greannotation{II} \index[Alleluia]{Redemptionem misit} \label{Redemptionem misit (Alleluia)} \grecommentary[0pt]{Ps 110:9 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--redemptionem--vatican-op} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Lord has sent deliverance to his people.}  
 \subsection{Alleluia} GR gives this rubric: "Pro dominica tantum:" \greannotation{I} \index[Alleluia]{Ego sum pastor} \label{Ego sum pastor (Alleluia)} \grecommentary[0pt]{Io 10:14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--ego_sum_pastor--dominican--id_7120} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I am the good shepherd, and I know My sheep, and Mine know Me.}  


 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Deus Deus meus} \label{Deus Deus meus (Offertorium)} \grecommentary[5pt]{Ps 62:2, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--deus_deus_meus--dominican--id_5884} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{O God, my God, to You do I watch at break of day; and in Your name I will lift up my hands, alleluia.}  
 \subsection{Communio}  \greannotation{VIII} \index[Communio]{Ego sum pastor} \label{Ego sum pastor (Communio)} \grecommentary[5pt]{Io 10:14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--ego_sum_pastor--dominican--id_6143} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I am the Good Shepherd, alleluia, and I know My sheep, and Mine know Me, alleluia, alleluia.}  



 \subsection{Officium}  \greannotation{VI} \index[Officium]{Cantate Domino} \label{Cantate Domino (Officium)} \grecommentary[0pt]{Ps 97:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--cantate_domino--dominican--id_6037} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Sing to the Lord a new song, alleluia, for the Lord has done wonderful things, alleluia. He has revealed His justice in the sight of the Gentiles, alleluia, alleluia. \Vbar. His right hand has wrought for Him salvation; and His arm is holy.}  

 \subsection{Alleluia}  \greannotation{IV} \index[Alleluia]{Dextera Dei} \label{Dextera Dei (Alleluia)} \grecommentary[3pt]{Ps 117:16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--dextera_dei--dominican--id_6041} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The right hand of God has done mightily; the right hand of the Lord has exalted me.}  
 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Christus resurgens} \label{Christus resurgens (Alleluia)} \grecommentary[0pt]{Rom 6:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--christus_resurgens--dominican--id_6484} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Christ, rising again from the dead, dies now no more; death shall no longer have dominion over Him, alleluia.}  






 \subsection{Offertorium}  \greannotation{I} \index[Offertorium]{Iubilate Deo universa} \label{Iubilate Deo universa (Offertorium)} \grecommentary[5pt]{Ps 65:1, 2, 16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--iubilate_deo_universa--dominican--id_4862} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Sing joyfully to God, all the earth; sing a psalm to His name; come and hear, and I will tell you, all you that fear God, what things the Lord has done for my soul, alleluia.}  
 \subsection{Communio} Dom. anno A: \greannotation{IV} \index[Communio]{Tanto tempore} \label{Tanto tempore (Communio)} \grecommentary[0pt]{Io 14:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--tanto_tempore--dominican--id_6774} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Have I been so long a time with you, and have you not known Me? Philip, he who sees Me, sees the Father also, alleluia. Do you not believe that I am in the Father, and the Father in Me? Alleluia, alleluia.}  
 \subsection{Communio} Dom. annis B et C: \greannotation{VIII} \index[Communio]{Ego sum vitis vera} \label{Ego sum vitis vera (Communio)} \grecommentary[5pt]{Io 15:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--ego_sum_vitis--dominican--id_7015} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I am the true vine, you the branches. He who abides in Me, and I in him, he bears much fruit, alleluia.}  





 \subsection{Officium}  \greannotation{III} \index[Officium]{Vocem iucunditatis} \label{Vocem iucunditatis (Officium)} \grecommentary[10pt]{Cf. Is 48:20; Ps 65} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--vocem_iucunditatis--dominican--id_6200} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Declare the voice of joy, and let it be heard, alleluia; declare it even to the ends of the earth: the Lord has delivered His people, alleluia, alleluia. \Vbar. Shout with joy to God, all the earth: sing a psalm to His name, give glory to His praise.}  
 \subsection{Alleluia} Dom. anno A (I): \greannotation{I} \index[Alleluia]{Surrexit Christus et illuxit} \label{Surrexit Christus et illuxit (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--surrexit_christus_et_illuxit--dominican--id_6350} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Christ is risen, and has shone upon His people whom He redeemed with His blood.}  
 \subsection{Alleluia} Dom. anno A (II): \greannotation{I} \index[Alleluia]{Non vos relinquam} \label{Non vos relinquam (Alleluia)} \grecommentary[0pt]{Io 14:18, 28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--non_vos_relinquam--dominican--id_6071} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I will not leave you orphans: I go away, and I come to you; and your heart shall rejoice.}  
 \subsection{Alleluia} Dom. anno B (I): \greannotation{VII} \index[Alleluia]{Exivi a Patre} \label{Exivi a Patre (Alleluia)} \grecommentary[0pt]{Io 16:28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--exivi_a_patre--dominican--id_6244} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I came forth from the Father, and have come into the world: again I leave the world, and I go to the Father.}  
 \subsection{Alleluia} Dom. anno B (II): \greannotation{I} \index[Alleluia]{Ego vos elegi} \label{Ego vos elegi (Alleluia)} \grecommentary[0pt]{Io 15:16 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--ego_vos_elegi--vatican-op} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I have chosen you from the world, in order that you might go, and bear fruit, and that your fruit should last.}  
 \subsection{Alleluia} Dom. anno C (I): Surrexit Christus \emph{vel} Exivi a Patre, \emph{ut supra.} \par \vspace{5pt} Dom. Anno C (II): \greannotation{VIII} \index[Alleluia]{Spritus Sanctus docebit vos} \label{Spritus Sanctus docebit vos (Alleluia)} \grecommentary[0pt]{Io 14:26 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--spiritus_sanctus_docebit--vatican-op} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Holy Spirit will teach you all the things which I have said unto you.}  

 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Benedicite gentes} \label{Benedicite gentes (Offertorium)} \grecommentary[0pt]{Ps 65:8, 9, 20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--benedicite_gentes--dominican--id_6100} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{O bless the Lord our God, you Gentiles, and make the voice of His praise to be heard who has set my soul to live, and has not suffered my feet to be moved. Blessed be the Lord, who has not turned away my prayer and His mercy from me, alleluia.}  
 \subsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Non vos relinquam} \label{Non vos relinquam (Communio)} \grecommentary[0pt]{Io 14:18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--non_vos_relinquam--dominican--id_6454} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I will not leave you orphans; I will come to you again, alleluia, and your heart shall rejoice, alleluia, alleluia.}  
 \subsection{Communio} Dom. anno B: \greannotation{I} \index[Communio]{Ego vos elegi} \label{Ego vos elegi (Communio)} \grecommentary[0pt]{Io 15:16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--ego_vos_elegi_alleluia--dominican--id_5178} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I have chosen you out of the world that you may go and bring forth fruit; and that your fruit may remain.}  
 \subsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Spiritus Sanctus docebit vos} \label{Spiritus Sanctus docebit vos (Communio)} \grecommentary[5pt]{Io 14:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--spiritus_sanctus--dominican--id_4850} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Holy Spirit shall teach you, alleluia, whatsoever I have said to you, alleluia, alleluia.}  










































































































































































































































 \subsection{Officium}  \greannotation{VI} \index[Officium]{Omnes gentes} \label{Omnes gentes (Officium)} \grecommentary[0pt]{Ps 46:2; \Vbar. 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--omnes_gentes--dominican--id_5326} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Clap your hands, all you nations; shout to God with the voice of joy, alleluia, alleluia, alleluia! \Vbar. He has subdued the people under us; and the nations under our feet.} 




























 \subsection{Communio}  \greannotation{I} \index[Communio]{Passer invenit} \label{Passer invenit (Communio)} \grecommentary[0pt]{Ps 83:4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--passer_invenit--dominican--id_6674} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The sparrow has found herself a house, and the turtle a nest where she may lay her young ones: Your altars, O Lord of Hosts, my King, and my God. Blessed are they who dwell in Your house; they shall praise You forever and ever.} 






















































 \subsection{Communio}  \greannotation{VIII} \index[Communio]{Primum quærite} \label{Primum quærite (Communio)} \grecommentary[0pt]{Mt 6:33} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--primum_quaerite--dominican--id_5473} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Seek first the kingdom of God, and all things shall be added unto you, says the Lord.} 










































































\section{Hebdomada vigesima septima}            
 \subsection{Officium}  \greannotation{IV} \index[Officium]{In voluntate tua} \label{In voluntate tua (Officium)} \grecommentary[0pt]{Esth 13:9, 10, 11; \Vbar. Ps 118:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--in_voluntate_tua--dominican--id_6357}  \vspace{5pt} \par{All things are in Your will, O Lord; and there is none that can resist Your will; for You have made all things, heaven and earth, and all things that are under the cope of heaven; You are Lord of all. \Vbar. Blessed are the undefiled in the way, who walk in the law of the Lord.} 
 \subsection{}  \greannotation{} \index[]{Ad libitum:} \label{Ad libitum: ()} \grecommentary[0pt]{} \gresetinitiallines{1}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}
 \subsection{}  \greannotation{} \index[]{De ventre matris meæ} \label{De ventre matris meæ ()} \grecommentary[0pt]{} \gresetinitiallines{1}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}
 \subsection{Responsorium}  \greannotation{II} \index[Responsorium]{Domine refugium} \label{Domine refugium (Responsorium)} \grecommentary[0pt]{Ps 89:1; \Vbar. 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--domine_refugium--dominican--id_6881}  \vspace{5pt} \par{Lord, You have been our refuge from generation to generation. \Vbar. Before the mountains were made, or the earth and the world was formed, from eternity and to eternity You are God.} 
 \subsection{}  \greannotation{} \index[]{Qui operatus est Petro} \label{Qui operatus est Petro ()} \grecommentary[0pt]{} \gresetinitiallines{1}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{} 
 \subsection{Alleluia}  \greannotation{II} \index[Alleluia]{In exitu Isræl} \label{In exitu Isræl (Alleluia)} \grecommentary[0pt]{Ps 113:1 [GR]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--in_exitu_israel--vatican--id_3493}  \vspace{5pt} \par{When Israel went out of Egypt; the house of Jacob from a barbarous nation.} 
 \subsection{}  \greannotation{} \index[]{Laudate Dominum} \label{Laudate Dominum ()} \grecommentary[0pt]{} \gresetinitiallines{1}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{} 
 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Vir erat} \label{Vir erat (Offertorium)} \grecommentary[0pt]{Iob 1:1, 2:7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--vir_erat--dominican--id_7582}  \vspace{5pt} \par{There was a man in the land, whose name was Job, simple, and upright, and fearing God, whom Satan besought that he might tempt. And power was given him from the Lord over his possessions and his flesh; and he destroyed all his substance and his children; and wounded his flesh also with a grievous ulcer.} 
 \subsection{Communio}  \greannotation{I} \index[Communio]{In salutari tuo} \label{In salutari tuo (Communio)} \grecommentary[0pt]{Ps 118:81, 84, 86} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--in_salutari_tuo--dominican--id_6778}  \vspace{5pt} \par{My soul is in Your salvation, and in Your word have I hoped. When will You execute judgment on those who persecute me? The wicked have persecuted me; help me, O Lord my God.} 




 \subsection{Officium}  \greannotation{III} \index[Officium]{Si iniquitates} \label{Si iniquitates (Officium)} \grecommentary[7pt]{Ps 129:3, 4; \Vbar. 1, 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--si_iniquitates--dominican--id_6130}  \vspace{5pt} \par{If You shall observe iniquities, O Lord, Lord, who shall endure it? For with You is propitiation, O God of Israel. \Vbar. Out of the depths I have cried to You, O Lord; Lord, hear my voice.}  
 \subsection{Responsorium} Dom. anno A: \greannotation{I} \index[Responsorium]{Si ambulem} \label{Si ambulem (Responsorium)} \grecommentary[0pt]{Ps 22:4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--si_ambulem--dominican--id_6258}  \vspace{5pt} \par{If I should walk in the midst of the shadow of death, I will fear no evils, for You are with me, O Lord. \Vbar. Your rod and Your staff have comforted me.}  
 \subsection{Responsorium} Dom. annis B et C: \greannotation{I} \index[Responsorium]{Ecce quam bonum} \label{Ecce quam bonum (Responsorium)} \grecommentary[0pt]{Ps 132:1; \Vbar. 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--ecce_quam_bonum_v_sicut--dominican--id_6309}  \vspace{5pt} \par{Behold how good and how pleasant it is for brethren to dwell together in unity. \Vbar. It is like the precious ointment on the head, that ran down over the beard, the beard of Aaron.}  




 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Qui timent Dominum} \label{Qui timent Dominum (Alleluia)} \grecommentary[0pt]{Ps 113:11} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--qui_timent_dominum--dominican--id_6493}  \vspace{5pt} \par{They who fear the Lord, let them hope in Him; He is their helper and protector.}  
 \subsection{Offertorium}  \greannotation{I} \index[Offertorium]{Recordare mei} \label{Recordare mei (Offertorium)} \grecommentary[0pt]{Esth 14:12, 13} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--recordare_mei--dominican--id_5756}  \vspace{5pt} \par{Remember me, O Lord, You who rule above all power; give a well-ordered speech in my mouth, that my words may be pleasing in the sight of the prince.}  
 \subsection{Communio}  \greannotation{II} \index[Communio]{Aufer a me} \label{Aufer a me (Communio)} \grecommentary[0pt]{Ps 118:22, 24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--aufer_a_me--dominican--id_6054} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Remove from me reproach and contempt, because I have sought out Your commandments, O Lord; for Your testimonies are my meditation.} 


 \subsection{Officium}  \greannotation{III} \index[Officium]{Ego clamavi} \label{Ego clamavi (Officium)} \grecommentary[2pt]{Ps 16:6, 8; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--ego_clamavi--dominican--id_6294}  \vspace{5pt} \par{I have cried, for You, O God, have heard me. Incline Your ear and hear my words; keep me, O Lord, as the apple of Your eye; protect me under the shadow of Your wings. \Vbar. Hear, O Lord, my justice: attend to my supplication.}  
 \subsection{Responsorium}  \greannotation{VII} \index[Responsorium]{Salvum fac populum} \label{Salvum fac populum (Responsorium)} \grecommentary[7pt]{Ps 27:9; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--salvum_fac_populum--dominican--id_5230}  \vspace{5pt} \par{Save Your people, O Lord, and bless Your inheritance. \Vbar. Unto You have I cried, O Lord my God; be not silent unto me, lest I become like them who go down into the pit.}  
 \subsection{}  \greannotation{} \index[]{Lætatus sum} \label{Lætatus sum ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Lauda anima mea} \label{Lauda anima mea (Alleluia)} \grecommentary[5pt]{Ps 145:2 [GR]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--lauda_anima_mea--solesmes}  \vspace{5pt} \par{Praise the Lord, O my soul; I will praise the Lord throughout my life; I will sing in honor of my God as long as I have being.}  
 \subsection{}  \greannotation{} \index[]{Lætatus sum} \label{Lætatus sum ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Meditabor in mandatis} \label{Meditabor in mandatis (Offertorium)} \grecommentary[5pt]{Ps 118:47, 48} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--meditabor--dominican--id_6142}  \vspace{5pt} \par{I will meditate on Your commandments, which I have loved exceedingly, and I will lift up my hands to Your commandments, which I have loved.}  
 \subsection{Communio}  \greannotation{II} \index[Communio]{Domine Dominus noster} \label{Domine Dominus noster (Communio)} \grecommentary[4pt]{Ps 8:2 ab} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--domine_dominus_noster--dominican--id_4994}  \vspace{5pt} \par{O Lord, our Lord, how wonderful is Your name in all the earth.} 



 \subsection{Officium}  \greannotation{II} \index[Officium]{Lætetur cor} \label{Lætetur cor (Officium)} \grecommentary[0pt]{Ps 104:3, 4; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--laetetur_cor--dominican--id_6129}  \vspace{5pt} \par{Let the hearts of those who seek the Lord rejoice. Seek the Lord, and be strengthened; seek His face evermore. \Vbar. Give glory to the Lord, and call upon His name; declare His deeds among the Gentiles.}  
 \subsection{Responsorium} Dom. annis A et B: \greannotation{V} \index[Responsorium]{Unam petii} \label{Unam petii (Responsorium)} \grecommentary[0pt]{Ps 26:4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--unam_petii_v_ut_videam--protegar--dominican--id_5760}  \vspace{5pt} \par{One thing I have asked of the Lord, this will I seek after: that I may dwell in the house of the Lord. \Vbar. That I may see the will of the Lord, and be protected by His holy temple.}  
 \subsection{Responsorium} Dom. anno C: \greannotation{VII} \index[Responsorium]{Clamaverunt iusti} \label{Clamaverunt iusti (Responsorium)} \grecommentary[3pt]{Ps 33:18; \Vbar. 19 [GR]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--clamaverunt--vatican}  \vspace{5pt} \par{The righteous cried out for help, and the Lord heard them; and he delivered them out of all their troubles. \Vbar. The Lord is near to the broken-hearted and he shall save the contrite in spirit.}  
 \subsection{}  \greannotation{} \index[]{Clamaverunt iusti} \label{Clamaverunt iusti ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Alleluia}  \greannotation{IV} \index[Alleluia]{Lauda Ierusalem} \label{Lauda Ierusalem (Alleluia)} \grecommentary[0pt]{Ps 147:1 [GR]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--lauda_ierusalem--vatican}  \vspace{5pt} \par{Praise the Lord, O Jerusalem; praise your God, O Zion.}  
 \subsection{Offertorium}  \greannotation{III} \index[Offertorium]{Domine, vivifica me} \label{Domine, vivifica me (Offertorium)} \grecommentary[3pt]{Ps 118:107, 125} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--domine_vivifica--dominican--id_4306}  \vspace{5pt} \par{O Lord, give me life according to Your word, that I may know Your testimonies.}  
 \subsection{Communio}  \greannotation{II} \index[Communio]{Lætabimur} \label{Lætabimur (Communio)} \grecommentary[0pt]{Ps 19:6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--laetabimur--dominican--id_6160}  \vspace{5pt} \par{We will rejoice in Your salvation, and in the name of the Lord our God we shall be exalted.} 

 \subsection{Officium} Dom. annis A et B: \greannotation{VII} \index[Officium]{Ne derelinquas me} \label{Ne derelinquas me (Officium)} \grecommentary[5pt]{Ps 37:22, 23; \Vbar. 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--ne_derelinquas_me--dominican--id_6841}  \vspace{5pt} \par{Forsake me not, O Lord my God, do not depart from me; attend to my help, O Lord, the power of my salvation. \Vbar. Rebuke me not, O Lord, in Your indignation; nor chastise me in Your wrath.}  
 \subsection{Officium} Dom. anno C: \greannotation{I} \index[Officium]{Misereris omnium} \label{Misereris omnium (Officium)} \grecommentary[2pt]{Sap 11:24–25, 27; \Vbar. Ps 56} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--misereris_omnium--dominican--id_4279}  \vspace{5pt} \par{You have mercy upon all, O Lord, and hate none of the things which You have made, and overlook the sins of men for the sake of repentance and spare them for You are the Lord our God. \Vbar. Have mercy on me; O God, have mercy on me, for my soul trusts in You.}  
 \subsection{}  \greannotation{} \index[]{Misereris omnium} \label{Misereris omnium ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Suscepimus} \label{Suscepimus (Responsorium)} \grecommentary[1pt]{Ps 47:10, 11; \Vbar. 9} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--suscepimus_deus--dominican--id_6094}  \vspace{5pt} \par{We have received Your mercy, O God, in the midst of Your temple; according to Your name, O Lord, so also is Your praise to the ends of the earth. \Vbar. As we have heard, so have we seen, in the city of our God.}  
 \subsection{}  \greannotation{} \index[]{Lætatus sum} \label{Lætatus sum ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{}  \greannotation{} \index[]{Beatus vir} \label{Beatus vir ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Alleluia} Dom. annis A et B: \greannotation{VIII} \index[Alleluia]{Verbo Domini} \label{Verbo Domini (Alleluia)} \grecommentary[2pt]{Ps 32:6 [GR]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--verbo_domini--vatican}  \vspace{5pt} \par{By the Word of the Lord, the heavens were established, and all the power therein by the Spirit of his mouth.}  
 \subsection{Alleluia} Dom. anno C: \greannotation{I} \index[Alleluia]{O quam bonus} \label{O quam bonus (Alleluia)} \grecommentary[2pt]{Sap 12:1 [GR]} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--o_quam_bonus--vatican}  \vspace{5pt} \par{O Lord, how good and delightful your Spirit is in us.}  
 \subsection{}  \greannotation{} \index[]{O quam bonus} \label{O quam bonus ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{}  \greannotation{} \index[]{Lætatus sum} \label{Lætatus sum ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{}  \greannotation{} \index[]{Beatus vir qui timet} \label{Beatus vir qui timet ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Offertorium}  \greannotation{V} \index[Offertorium]{Benedic anima mea} \label{Benedic anima mea (Offertorium)} \grecommentary[1pt]{Ps 102:2, 5} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--benedic_anima_mea--dominican--id_4303}  \vspace{5pt} \par{Bless the Lord, O my soul, and never forget all He has done for you, and your youth shall be renewed like the eagle's.}  
 \subsection{Communio}  \greannotation{VII} \index[Communio]{Notas mihi} \label{Notas mihi (Communio)} \grecommentary[0pt]{Ps 15:11} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--notas_mihi--dominican--id_6934}  \vspace{5pt} \par{You have made known to me the ways of life; You shall fill me with joy with Your countenance, O Lord.} 


 \subsection{Officium}  \greannotation{III} \index[Officium]{Intret oratio mea} \label{Intret oratio mea (Officium)} \grecommentary[0pt]{Ps 87:3; \Vbar. 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--intret_oratio--dominican--id_5682}  \vspace{5pt} \par{Let my prayer come before You; incline Your ear to my petition, O Lord. \Vbar. O Lord, the God of my salvation, I have cried in the day, and in the night before You.}  
 \subsection{Responsorium}  \greannotation{VII} \index[Responsorium]{Dirigatur} \label{Dirigatur (Responsorium)} \grecommentary[0pt]{Ps 140:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{}  \greannotation{} \index[]{Benedicam Dominum} \label{Benedicam Dominum ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{}  \greannotation{} \index[]{In omnem terram} \label{In omnem terram ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{}  \greannotation{} \index[]{Beatus vir} \label{Beatus vir ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Alleluia} Dom. anno A: \greannotation{VII} \index[Alleluia]{Quinque prudentes virgines} \label{Quinque prudentes virgines (Alleluia)} \grecommentary[0pt]{Mt 25:4, 6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Alleluia} Dom. annis B et C: \greannotation{IV} \index[Alleluia]{Qui posuit fines} \label{Qui posuit fines (Alleluia)} \grecommentary[0pt]{Ps 147:3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--qui_posuit_fines--dominican--id_6791}  \vspace{5pt} \par{Who has made peace in your borders; and filled you with the fat of corn.}  
 \subsection{}  \greannotation{} \index[]{Quinque prudentes virgines} \label{Quinque prudentes virgines ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{}  \greannotation{} \index[]{Fulgebunt iusti} \label{Fulgebunt iusti ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{}  \greannotation{} \index[]{Beatus vir qui timet} \label{Beatus vir qui timet ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Gressus meos} \label{Gressus meos (Offertorium)} \grecommentary[0pt]{Ps 118:133} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--gressus_meos--dominican--id_5995}  \vspace{5pt} \par{Direct my steps according to Your word, that no iniquity may have dominion over me, O Lord.}  
 \subsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Quinque prudentes virgines} \label{Quinque prudentes virgines (Communio)} \grecommentary[0pt]{Mt 25:4, 6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{}  
 \subsection{Communio} Dom. annis B et C: \greannotation{II} \index[Communio]{Dominus regit me} \label{Dominus regit me (Communio)} \grecommentary[0pt]{Ps 22:1, 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--dominus_regit_me--dominican--id_5335}  \vspace{5pt} \par{The Lord rules me, and I shall want for nothing; He has set me in a place of pasture; He has led me to refreshing waters.} 



 \subsection{Officium}  \greannotation{VI} \index[Officium]{Dicit Dominius Ego} \label{Dicit Dominius Ego (Officium)} \grecommentary[0pt]{Ier 29:11, 12, 14; Ps 84:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--dicit_dominus_ego--dominican--id_7204}  \vspace{5pt} \par{The Lord says: ``I think thoughts of peace, and not of affliction. You shall call upon Me, and I will hear you; and I will bring back your captivity from all places.” \Vbar. Lord, You have blessed Your land; You have turned away the captivity of Jacob.}  
 \subsection{Responsorium}  \greannotation{VII} \index[Responsorium]{Liberasti nos} \label{Liberasti nos (Responsorium)} \grecommentary[2pt]{Ps 43:8; \Vbar. 9} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--liberasti_nos--dominican--id_7116}  \vspace{5pt} \par{You have delivered us, O Lord, from those who afflict us; and have put them to shame who hate us. \Vbar. In God we will glory all the day; and to Your name we will give praise forever.}  
 \subsection{Alleluia}  \greannotation{VII} \index[Alleluia]{De profundis} \label{De profundis (Alleluia)} \grecommentary[0pt]{Ps 129:1, 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--de_profundis--dominican--id_6472}  \vspace{5pt} \par{Out of the depths I have cried out to You, O Lord; Lord, hear my prayer.}  
 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{De profundis} \label{De profundis (Offertorium)} \grecommentary[0pt]{Ps 129:1, 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--de_profundis--dominican--id_6740}  \vspace{5pt} \par{Out of the depths I have cried out to You, O Lord; Lord, hear my prayer.}  
 \subsection{Communio} Dom. anno A: \greannotation{VII} \index[Communio]{Domine quinque talenta} \label{Domine quinque talenta (Communio)} \grecommentary[0pt]{Mt 25:20, 21} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--domine_quinque_talenta--dominican--id_5425}  \vspace{5pt} \par{Master, you did hand over to me five talents; behold, I have gained five others in addition. Well done, faithful servant, because you have been faithful over a few things I will set you over many things; enter into the joy of your master.}  
 \subsection{Communio} Dom. annis B et C: \greannotation{I} \index[Communio]{Amen dico vobis, quidquid} \label{Amen dico vobis, quidquid (Communio)} \grecommentary[0pt]{Mc 11:24} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quidquid--dominican--id_5918}  \vspace{5pt} \par{Amen I say to you, all things whatever you ask for in prayer, believe that you shall receive, and it shall be done to you.} 



















































\section{D. N. Iesu Christi Universorum Regis}            
 \subsection{}  \greannotation{} \index[]{Antiphona ad introitum III} \label{Antiphona ad introitum III ()} \grecommentary[]{} \gresetinitiallines{}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{} 
 \subsection{Officium}  \greannotation{III} \index[Officium]{Dignus est Agnus} \label{Dignus est Agnus (Officium)} \grecommentary[7pt]{Apoc 5:12 et 1:6; Ps 71:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--dignus_est_agnus--dominican--id_7395}  \vspace{5pt} \par{Worthy is the Lamb who was slain to receive power, and divinity, and wisdom, and strength, and honor. To Him belong glory and dominion forever and ever. \Vbar. O God, with Your judgment endow the King, and with Your justice, the King's son.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Dominabitur} \label{Dominabitur (Responsorium)} \grecommentary[0pt]{Ps 71:8; \Vbar. 11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/gr--dominabitur--dominican--id_7398} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{He shall rule from sea to sea, and from the river to the ends of the earth. \Vbar. And all kings of the earth shall adore Him; all nations shall serve Him.}  
 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Potestas eius} \label{Potestas eius (Alleluia)} \grecommentary[0pt]{Dan 7:14} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--potestas_ejus--dominican--id_7399}  \vspace{5pt} \par{His power is an everlasting power that shall not be taken away, and His kingdom that shall not be destroyed.}  
 \subsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Postula a me} \label{Postula a me (Offertorium)} \grecommentary[0pt]{Ps 2:8} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--postula_a_me--dominican--id_7400}  \vspace{5pt} \par{Ask of Me and I will give You the Gentiles for Your inheritance, and the ends of the earth for Your possession.}  
 \subsection{Communio}  \greannotation{VI} \index[Communio]{Sedebit} \label{Sedebit (Communio)} \grecommentary[0pt]{Ps 28:10b, 11b} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--sedebit_dominus--dominican--id_7401}  \vspace{5pt} \par{The Lord shall sit as a King forever; the Lord will bless His people with peace.} 



































































































 \subsection{Officium}  \greannotation{II} \index[Officium]{Mihi autem} \label{Mihi autem (Officium)} \grecommentary[0pt]{Ps 138:17; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--mihi_autem_nimis--dominican--id_4899} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{To me Your friends, O God, are made exceedingly honorable; their principality is exceedingly strengthened. \Vbar. Lord, You have proved me, and known me; You have known when I sit and when I stand.} 

















 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{In omnem terram} \label{In omnem terram (Offertorium)} \grecommentary[0pt]{Ps 18:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--in_omnem_terram--dominican--id_6618} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Their sound went forth into all the earth, and their words to the ends of the world.} 






 \subsection{Communio}  \greannotation{I} \index[Communio]{Vos qui secuti ... tribus Israel} \label{Vos qui secuti ... tribus Israel (Communio)} \grecommentary[0pt]{Mt 19:28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--vos_qui_secuti--dominican--id_5171} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{You who have followed Me shall sit on seats judging the twelve tribes of Israel.} 











































 \subsection{Officium}  \greannotation{I} \index[Officium]{Sapientiam sanctorum} \label{Sapientiam sanctorum (Officium)} \grecommentary[2pt]{Sir 44:15, 14; \Vbar. Ps 32:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--sapientiam--dominican--id_5872} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Let the people show forth the wisdom of the saints, and the Church declare their praise; and their names shall live unto generation and generation. \Vbar. Rejoice in the Lord, you just: praise becomes the upright.} 








































































































































































































































































































































































































































































































































































































































 \subsection{Officium}  \greannotation{VI} \index[Officium]{In medio Ecclesiæ (T.P. Alleluia, alleluia.)} \label{In medio Ecclesiæ (T.P. Alleluia, alleluia.) (Officium)} \grecommentary[0pt]{Sir 15:5; \Vbar. 6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--in_medio--dominican--id_6549}  \vspace{5pt} \par{In the midst of the Church he opened his mouth, and the Lord filled him with the spirit of wisdom and understanding; He clothed him with a robe of glory. \emph{T.P.} Alleluia, alleluia, alleluia. \Vbar. A treasure of joy and gladness He heaped upon him.}  
 \subsection{Responsorium}  \greannotation{I} \index[Responsorium]{Os iusti} \label{Os iusti (Responsorium)} \grecommentary[4pt]{Ps 36:30; \Vbar. 31} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--os_iusti--dominican--id_4733}  \vspace{5pt} \par{The mouth of the just man shall meditate wisdom, and his tongue shall speak judgment. \Vbar. The law of his God is in his heart, and his steps shall not be supplanted.}  
 \subsection{Tractus}  \greannotation{VII} \index[Tractus]{Quasi stella} \label{Quasi stella (Tractus)} \grecommentary[5pt]{Sir 50:6-9} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/tr--quasi_stella--dominican--id_7081} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{He shone in his days as the morning star in the midst of a cloud, and as the full moon. \par \Vbar. And as the sun when it shines, so did he shine in the temple of God. \par \Vbar. And as the rainbow appearing in the cloudy sky, and as the flower of roses in the springtime. \par \Vbar. And as the lilies that are on the brink of the water, and as the sweet-smelling frankincense in summertime. \par \Vbar. As a bright fire, and frankincense burning in the fire. \par \Vbar. As a massive vessel of gold, adorned with every precious stone.}  
 \subsection{Alleluia}  \greannotation{V} \index[Alleluia]{Gloriose pater Vincenti} \label{Gloriose pater Vincenti (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--gloriose_pater--dominican--id_5072}  \vspace{5pt} \par{O glorious father Vincent, famous son of the Order of Dominic, pour forth your prayers to the sovereign judge for all the nations who are devoted to you.}  
 \subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Oportebat pati} \label{Oportebat pati (Alleluia)} \grecommentary[0pt]{Lc 24:46} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--oportebat_pati--dominican--id_6843}  \vspace{5pt} \par{It behooved Christ to suffer, and rise again from the dead, and so enter into the glory of God.}  
 \subsection{Offertorium}  \greannotation{VI} \index[Offertorium]{Desiderium} \label{Desiderium (Offertorium)} \grecommentary[0pt]{Ps 20:2, 3, 4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--desiderium_animae--dominican--id_6021}  \vspace{5pt} \par{You have given him his heart's desire, O Lord; and the request of his lips You have not deprived from him; You have set on his head a crown of precious stones. \emph{T.P.} Alleluia.}  
 \subsection{Communio}  \greannotation{VI} \index[Communio]{Vincenti dabo} \label{Vincenti dabo (Communio)} \grecommentary[8pt]{Apoc 2:7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--vincenti_dabo--dominican--id_6089}  \vspace{5pt} \par{To Vincent I will give to eat of the tree of life, which is in the paradise of my God. \emph{T.P.} Alleluia.}  
































































 \subsection{Officium}  \greannotation{VII} \index[Officium]{Mihi adhærere} \label{Mihi adhærere (Officium)} \grecommentary[3pt]{Ps 72:28, 26; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--mihi_adhaere_deo--dominican--id_7243}  \vspace{5pt} \par{It is good for me to hold fast to my God, to put my hope in the Lord God; my flesh and my heart have failed; You are the God of my heart, and the God that is my portion forever. \emph{T.P.} Alleluia, alleluia. \Vbar. How good is God to Israel, to those who are upright of heart.}  
 \subsection{Responsorium} Extra tempus Paschale: \greannotation{VII} \index[Responsorium]{Quasi stella} \label{Quasi stella (Responsorium)} \grecommentary[3pt]{Sir 50:6-7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--quasi_stella_quasi_sol--dominican--id_7230}  \vspace{5pt} \par{As the morning star in the midst of a cloud, and as the sun when it shines, so did Catherine shine in the temple of God. \Vbar. In her days the wells of water flowed out, and they were filled as the sea above measure.}  
 \subsection{Tractus} Infra Septuagesimam: \greannotation{II} \index[Tractus]{Defecit caro mea} \label{Defecit caro mea (Tractus)} \grecommentary[0pt]{Ps 72:26; \Vbar. Ct 5:6; \Vbar. Ct 5:4; \Vbar. Ct 2:5; \Vbar. Ct 2:6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/tr--defecit_caro_mea--dominican--id_6801}  \vspace{5pt} \par{My flesh grows weak, as does my heart; the God of my heart, God is my portion forever. \par \Vbar. My soul is made like liquid, for my beloved has spoken. \par \Vbar. He brought me into his wine cellar, he ordered love within me. \par \Vbar. Support me with flowers, for evil has pressed around me, because I languish for love. \par \Vbar. With his left hand under my head, with his right hand he will embrace me.}  
 \subsection{Alleluia} Tempore Paschali et post Trinitatem: \greannotation{I} \index[Alleluia]{Sideribus} \label{Sideribus (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--sideribus_cunctis--dominican--id_5405}  \vspace{5pt} \par{Brighter than all the stars shines Catherine, and she is forever the glory of virgins.}  
 \subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Veritatem dico} \label{Veritatem dico (Offertorium)} \grecommentary[5pt]{Rom 9:1-3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--veritatem--dominican--id_5660}  \vspace{5pt} \par{I speak the truth in Christ, I do not lie; that I have great sadness, and continuous sorrow in my heart. For I could wish to be anathema myself from Christ for the sake of my brethren. \emph{T.P.} Alleluia.}  
 \subsection{Communio}  \greannotation{V} \index[Communio]{Benedicta} \label{Benedicta (Communio)} \grecommentary[0pt]{Jud 13:23, 25} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--benedicta--dominican--id_4820}  \vspace{5pt} \par{Blessed are you, O daughter, by the Lord the most high God above all women upon the earth; because He has so magnified your name that your praise shall not depart out of the mouth of men. \emph{T.P.} Alleluia.}  



































































































































































































































































































































































































































































































































































































































































































































































































































































\section{Die 1 novembris}            
\section{Omnium Sanctorum}            

 \subsection{Officium}  \greannotation{I} \index[Officium]{Gaudeamus... Sanctorum omnium} \label{Gaudeamus... Sanctorum omnium (Officium)} \grecommentary[0pt]{Ecclesia \Vbar. Ps 32:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--gaudeamus_sanctorum_omnium--dominican--id_4288}  \vspace{5pt} \par{Let us all rejoice in the Lord, celebrating a feast day in honor of all the saints, at whose solemnity the angels rejoice, and give praise to the Son of God. \par \Vbar. 1. Rejoice in the Lord, you just: praise is fitting to the upright. \par \Vbar. 2. Give praise to the Lord on the harp; sing to him with the psaltery, the ten stringed instrument. \par \Vbar. 3. Sing to him a new canticle, sing well unto him with a loud cry.}  
 \subsection{Officium}  \greannotation{I} \index[Officium]{Gaudeamus... Sanctorum omnium} \label{Gaudeamus... Sanctorum omnium (Officium)} \grecommentary[0pt]{Ecclesia; \Vbar. Ps 32:1-3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--gaudeamus_sanctorum_omnium--dominican--id_4288-antiphon-only}  \vspace{5pt} \par{Let us all rejoice in the Lord, celebrating a feast day in honor of all the saints, at whose solemnity the angels rejoice, and give praise to the Son of God.}  
 \subsection{Versus Officii}  \greannotation{I} \index[Versus Officii]{Gaudeamus... Sanctorum omnium} \label{Gaudeamus... Sanctorum omnium (Versus Officii)} \grecommentary[0pt]{Ecclesia; \Vbar. Ps 32:1-3} \gresetinitiallines{0}  \gregorioscore{graduale-chants/in--gaudeamus_sanctorum_omnium--dominican--id_4288-verses-only}  \vspace{5pt} \par{\Vbar.\textsuperscript{1} Rejoice in the Lord, you just: praise is fitting to the upright. \par \Vbar.\textsuperscript{2} Give praise to the Lord on the harp; sing to him with the psaltery, the ten stringed instrument. \par \Vbar.\textsuperscript{3} Sing to him a new canticle, sing well unto him with a loud cry.}  

 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Iudicabunt} \label{Iudicabunt (Alleluia)} \grecommentary[0pt]{Sap 3:8} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--iudicabunt_sancti--dominican}  \vspace{5pt} \par{The saints shall judge nations, and rule over people; and their king shall reign forever.}  


 \subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Mirabilis Deus} \label{Mirabilis Deus (Offertorium)} \grecommentary[5pt]{Ps 67:36} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--mirabilis_deus--dominican--id_4790}  \vspace{5pt} \par{God is wonderful in His saints. The God of Israel Himself will give power and strength to His people: blessed be God! \emph{T.P.} Alleluia.}  
 \subsection{Communio}  \greannotation{I} \index[Communio]{Gaudete iusti} \label{Gaudete iusti (Communio)} \grecommentary[0pt]{Ps 32:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--gaudete_iusti__alleluia--dominican}  \vspace{5pt} \par{Rejoice in the Lord, you just, alleluia. Praise is fitting to the upright, alleluia.} 















































































\section{In Præsentatione B. Mariæ Virginis}            
 \subsection{Officium}  \greannotation{I} \index[Officium]{Gaudeamus ... Praesentatio} \label{Gaudeamus ... Praesentatio (Officium)} \grecommentary[0pt]{Ecclesia; \Vbar. Ps 44:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--gaudeamus_praesentatio--dominican}  \vspace{5pt} \par{Let us all rejoice in the Lord, celebrating a feast day in honor of the Blessed Virgin Mary, in whose Presentation the angels rejoice and give praise to the Son of God. \Vbar. My heart has uttered a good word; I speak my works to the King.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Propter veritatem} \label{Propter veritatem (Responsorium)} \grecommentary[0pt]{Ps 44:5; \Vbar. 11, 12} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--propter_veritatem--dominican}  \vspace{5pt} \par{Because of truth and meekness, and justice; and your right hand shall conduct you wonderfully. \Vbar. Hearken, O daughter, and see, and incline your ear, for the king has greatly desired your beauty.}  
 \subsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Praesentatio gloriosæ} \label{Praesentatio gloriosæ (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--praesentatio_gloriosae_virginis--dominican}  \vspace{5pt} \par{This is the Presentation of the glorious Virgin Mary, of the seed of Abraham, of the tribe of Juda, of the noble race of David.}  
 \subsection{Offertorium}  \greannotation{I} \index[Offertorium]{Felix namque} \label{Felix namque (Offertorium)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--felix_namque--dominican}  \vspace{5pt} \par{For you are happy, O holy virgin Mary, and most worthy of all praise, because from you arose the sun of justice, Christ our Lord.}  
 \subsection{Communio}  \greannotation{I} \index[Communio]{Beata viscera} \label{Beata viscera (Communio)} \grecommentary[0pt]{Lc 11:27} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--beata_viscera--dominican}  \vspace{5pt} \par{Blessed is the womb of the virgin Mary, which bore the Son of the eternal Father.} 


































































 \subsection{Officium}  \greannotation{III} \index[Officium]{Gaudens gaudebo} \label{Gaudens gaudebo (Officium)} \grecommentary[3pt]{Is 61:10; Ps 29:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--gaudens_gaudebo--dominican}  \vspace{5pt} \par{I will greatly rejoice in the Lord, and my soul shall be joyful in my God, for He has clothed me with the garments of salvation, and with the robe of justice He has covered me, as a bride adorned with her jewels. \Vbar. I will extol You, O Lord, for You have upheld me, and have not made my enemies rejoice over me.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Benedicta es tu} \label{Benedicta es tu (Responsorium)} \grecommentary[0pt]{Iudith 13:23; \Vbar. 15:10} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--benedicta_es--dominican}  \vspace{5pt} \par{Blessed are you, O virgin Mary, by the Lord the most high God, above all women upon the earth. \Vbar. You are the glory of Jerusalem, you are the joy of Israel, you are the honor of our people.}  
 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Tota pulchra es} \label{Tota pulchra es (Alleluia)} \grecommentary[0pt]{Cant 4:7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--tota_pulchra_es--dominican}  \vspace{5pt} \par{You are all fair, O Mary, and there is in you no stain of original sin.}  
 \subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Ave Maria [In Conceptione Immaculata B.M.V.]} \label{Ave Maria [In Conceptione Immaculata B.M.V.] (Offertorium)} \grecommentary[3pt]{Lc 1:28} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--ave_maria--dominican}  \vspace{5pt} \par{Hail, Mary, full of grace, the Lord is with you. Blessed are you among women, alleluia!}  
 \subsection{Communio}  \greannotation{VIII} \index[Communio]{Gloriosa} \label{Gloriosa (Communio)} \grecommentary[0pt]{Ps 86:3; Lc 1:49} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--gloriosa--dominican}  \vspace{5pt} \par{Glorious things are told of you, O Mary, for He who is mighty has done great things to you.}  
































































 \subsection{Communio}  \greannotation{VII} \index[Communio]{Vox in Rama audita est} \label{Vox in Rama audita est (Communio)} \grecommentary[3pt]{Mt 2:18} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--vox_in_rama--dominican--id_4760}  \vspace{5pt} \par{A voice was heard in Rama, weeping and loud lamentation: Rachel weeping for her children; she would not be comforted, because they are no more.}  


















































































 \subsection{Officium}  \greannotation{I} \index[Officium]{Deus Israel} \label{Deus Israel (Officium)} \grecommentary[5pt]{Tob 7:15; 8:19; \Vbar. Ps 127:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--deus_israel--dominican--id_4300}  \vspace{5pt} \par{May the God of Israel join you together, and may He be with you, who took pity on two only children; and now, Lord, make them bless You more fully. \Vbar. Blessed are all who fear the Lord, who walk in His ways.}  
 \subsection{Responsorium}  \greannotation{II} \index[Responsorium]{Uxor tua} \label{Uxor tua (Responsorium)} \grecommentary[0pt]{Ps 127:3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--uxor_tua--dominican--id_6249}  \vspace{5pt} \par{Your wife as a fruitful vine on the sides of your house. \Vbar. Your children as olive plants round about your table.}  
 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Mittat vobis} \label{Mittat vobis (Alleluia)} \grecommentary[0pt]{Ps 19:3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--mittat_vobis--dominican--id_5742}  \vspace{5pt} \par{May the Lord send you help from the sanctuary, and defend you out of Zion.}  
 \subsection{Tractus}  \greannotation{VIII} \index[Tractus]{Ecce sic} \label{Ecce sic (Tractus)} \grecommentary[4pt]{Ps 127:4-6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/tr--ecce_sic_benedicetur--dominican--id_5644}  \vspace{5pt} \par{Behold, thus shall the man be blessed who fears the Lord. \Vbar. May the Lord bless you out of Zion; and may you see the good things of Jerusalem all the days of your life. \Vbar. And may you see your children's children: peace upon Israel.}  
 \subsection{Alleluia} \emph{Tempore Paschali dicitur II. Alleluia, sequens:} \greannotation{I} \index[Alleluia]{Benedicat vobis} \label{Benedicat vobis (Alleluia)} \grecommentary[0pt]{Ps 133:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--benedicat_vobis--dominican--id_5811}  \vspace{5pt} \par{May the Lord out of Zion bless you, who made heaven and earth.}  
 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{In te speravi} \label{In te speravi (Offertorium)} \grecommentary[0pt]{Ps 30:15, 16} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--in_te_speravi--dominican--id_6005}  \vspace{5pt} \par{In You have I hoped, O Lord. I said, ``You are my God, my times are in Your hands."}  
 \subsection{Communio}  \greannotation{VII} \index[Communio]{Ecce sic} \label{Ecce sic (Communio)} \grecommentary[5pt]{Ps 127:4, 6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--ecce_sic_benedicetur--dominican--id_5537}  \vspace{5pt} \par{Behold, thus shall every man be blessed who fears the Lord; and may you see your children's children; peace upon Israel.}  









































































































































































































































































































































































































































































































































































































 \subsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam} \label{Vidi aquam (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia! and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \par \emph{In die Paschæ:} \Vbar. This is the day the Lord has made; let us exult and rejoice in it. \par \emph{In aliis Dominicis usque ad Pentecosten:} \Vbar. Praise the Lord for He is good, for His mercy endures forever. \par \emph{In die Pentecostes:} \Vbar. Send forth your spirit, and they shall be created; and you shall renew the face of the earth.}  
 \subsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam (Haec est dies)} \label{Vidi aquam (Haec est dies) (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348--haec_est_dies} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia; and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \Vbar. This is the day the Lord has made; let us exult and rejoice in it.}  
 \subsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam (Confitemini)} \label{Vidi aquam (Confitemini) (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348--confitemini} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia; and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \Vbar. Praise the Lord for He is good, for His mercy endures forever.}  
 \subsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam (Emite Spiritum)} \label{Vidi aquam (Emite Spiritum) (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348--emite_spiritum} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia; and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \Vbar. Send forth your spirit, and they shall be created; and you shall renew the face of the earth.}  
































































































































































































\section{Common of Apostles}
  \section{Common of Martyrs}
  \section{Common of Pastors}
  \section{Common of Virgins}
  \section{Common of Holy Men and Women}



 \subsection{Officium}  \greannotation{IV} \index[Officium]{Omnis terra} \label{Omnis terra (Officium)} \grecommentary[0pt]{Ps 65:4; \Vbar. 1-2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--omnis_terra--dominican--id_5228}  \vspace{5pt} \par{All the earth shall adore you, O God, and shall sing to You: sing a psalm to Your name, O Most High. \Vbar. Sing joyfully to God, all the earth; sing a psalm to His name; make His praise glorious.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Misit Dominus} \label{Misit Dominus (Responsorium)} \grecommentary[0pt]{Ps 106:20; \Vbar. 21} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--misit_dominus--dominican--id_6504}  \vspace{5pt} \par{The Lord sent His word, and healed them, and delivered them out of their distresses. \Vbar. Let the mercies of the Lord give glory to Him, and His wonderful works to the children of men.}  
 \subsection{Alleluia}  \greannotation{IV} \index[Alleluia]{Laudate Deum} \label{Laudate Deum (Alleluia)} \grecommentary[0pt]{Ps 148:2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--laudate_deum--dominican--id_6780}  \vspace{5pt} \par{Praise the Lord, all His angels; praise Him all His hosts.}  
 \subsection{Offertorium}  \greannotation{I} \index[Offertorium]{Iubilate Deo universa} \label{Iubilate Deo universa (Offertorium)} \grecommentary[5pt]{Ps 65:1, 2, 16} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--iubilate_deo_universa--dominican--id_4862}  \vspace{5pt} \par{Sing joyfully to God, all the earth; sing a psalm to His name; come and hear, and I will tell you, all you that fear God, what things the Lord has done for my soul, alleluia.}  
 \subsection{Communio} Dom. anno A: \greannotation{II} \index[Communio]{Lætabimur} \label{Lætabimur (Communio)} \grecommentary[5pt]{Ps 19:6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--laetabimur--dominican--id_6160}  \vspace{5pt} \par{We will rejoice in Your salvation, and in the name of the Lord our God we shall be exalted.}  
 \subsection{Communio} Dom. anno B: \greannotation{VIII} \index[Communio]{Dicit Andreas} \label{Dicit Andreas (Communio)} \grecommentary[5pt]{Io 1:41, 42} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--dicit_andreas--dominican--id_6487}  \vspace{5pt} \par{Andrew said to his brother Simon: ``We have found the Messiah," which means Christ; and he led him to Jesus.}  
 \subsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Dicit Dominus} \label{Dicit Dominus (Communio)} \grecommentary[5pt]{Io 2:7, 8, 9, 10-11} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--dicit_dominus--dominican--id_5103}  \vspace{5pt} \par{The Lord said, ``Fill the jars with water and take them to the chief steward." When the chief steward had tasted the water made wine, he said to the bridegroom, ``You have kept the good wine until now." This first miracle Jesus worked in the presence of His disciples.}  


 \subsection{Officium} Dom. annis A et B: \greannotation{I} \index[Officium]{Dominus secus mare} \label{Dominus secus mare (Officium)} \grecommentary[7pt]{Mt 4:18, 19; \Vbar. 20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--dominus_secus_mare--dominican--id_4298} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Lord, walking by the sea of Galilee, saw two brothers, Peter and Andrew, and he called out to them: ``Follow me; I will make you fishers of men.'' \Vbar. At once, they left their nets and boat and followed him.}  
 \subsection{Officium} Dom. anno C: \greannotation{VII} \index[Officium]{Adorate Deum} \label{Adorate Deum (Officium)} \grecommentary[5pt]{Ps 96:7-8; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--adorate_deum--dominican--id_5980} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Adore God, all you His angels. Zion heard, and was glad; and the daughters of Judah rejoiced. \Vbar. The Lord has reigned; let the earth rejoice; let many islands be glad.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Timebunt gentes} \label{Timebunt gentes (Responsorium)} \grecommentary[5pt]{Ps 101:16; \Vbar. 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/gr--timebunt_gentes--dominican--id_4967} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Gentiles shall fear Your name, O Lord, and all the kings of the earth Your glory. \Vbar. For the Lord has built up Zion, and He shall be seen in His majesty.}  
 \subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Dominus regnavit exsultet} \label{Dominus regnavit exsultet (Alleluia)} \grecommentary[0pt]{Ps 96:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--dominus_regnavit_exsultet--dominican--id_6766} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Lord has reigned, let the earth rejoice; let many islands be glad.}  
 \subsection{Offertorium}  \greannotation{II} \index[Offertorium]{Dextera Domini} \label{Dextera Domini (Offertorium)} \grecommentary[5pt]{Ps 117:16, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--dextera_domini--dominican--id_4758} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The right hand of the Lord has wrought strength; the right hand of the Lord has exalted me. I shall not die, but live, and shall declare the works of the Lord.}  
 \subsection{Communio}  \greannotation{VII} \index[Communio]{Mirabantur omnes} \label{Mirabantur omnes (Communio)} \grecommentary[3pt]{Lc 4:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--mirabantur_omnes--dominican--id_7227} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{All marveled at these things that came from the mouth of God.} 
 \subsection{Communio} \emph{Ad libitum:} Dom. annis A et B: \greannotation{VIII} \index[Communio]{Venite post me} \label{Venite post me (Communio)} \grecommentary[5pt]{Mt 4:19-20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--venite_post_me--dominican--id_7007} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Come, follow Me, I will make you fishers of men: at that, they left the nets and boat and followed the Lord.}  
 \subsection{Communio} \emph{Ad libitum:} Dom. anno C: \greannotation{VIII} \index[Communio]{Comedite pinguia} \label{Comedite pinguia (Communio)} \grecommentary[5pt]{2 Esdr 8:10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--comedite_pinguia--dominican--id_6323} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Eat rich meats, and drink sweet wine, and send portions to them who have not prepared for themselves; because it is the holy day of the Lord; be not sad, for the joy of the Lord is our strength.}  


 \subsection{Officium}  \greannotation{II} \index[Officium]{Lætetur cor} \label{Lætetur cor (Officium)} \grecommentary[0pt]{Ps 104:3, 4; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--laetetur_cor--dominican--id_6129}  \vspace{5pt} \par{Let the hearts of those who seek the Lord rejoice. Seek the Lord, and be strengthened; seek His face evermore. \Vbar. Give glory to the Lord, and call upon His name; declare His deeds among the Gentiles.}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Quis sicut Dominus} \label{Quis sicut Dominus (Responsorium)} \grecommentary[0pt]{Ps 112:5, 6; \Vbar. 7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/gr--quis_sicut_dominus--dominican--id_5616} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Who is like the Lord our God, who dwells on high, looking down on the lowly in heaven and on earth? \Vbar. Raising up the needy from the earth, and lifting up the poor out of the dunghill.}  
 \subsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Adorabo ad templum} \label{Adorabo ad templum (Alleluia)} \grecommentary[0pt]{Ps 137:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--adorabo--dominican--id_5217} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I will bow down toward Your holy temple and give glory to Your name.}  
 \subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Bonum est confiteri} \label{Bonum est confiteri (Offertorium)} \grecommentary[0pt]{Ps 91:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--bonum_est_confiteri--dominican--id_7242} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{It is good to give praise to the Lord and to sing praise to Your name, O Most High.}  
 \subsection{Communio} Dom. anno A: \greannotation{I} \index[Communio]{Beati mundo corde} \label{Beati mundo corde (Communio)} \grecommentary[0pt]{Mt 5:8, 9, 10 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--beati_mundo_corde--vatican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Blessed are the pure in heart, for they shall see God; blessed are the peacemakers, for they shall be called sons of God; blessed are those who suffer persecution for the sake of justice, for theirs is the kingdom of heaven.}  
 \subsection{Communio} Dom. annis B et C: \greannotation{I} \index[Communio]{Illumina faciem tuam} \label{Illumina faciem tuam (Communio)} \grecommentary[0pt]{Ps 30:17, 18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--illumina_faciem--dominican--id_4792} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Let Your face shine upon Your servant, and save me in Your mercy; let me not be confounded, O Lord, for I have called upon You.}  


 \subsection{Officium}  \greannotation{II} \index[Officium]{Venite adoremus Deum} \label{Venite adoremus Deum (Officium)} \grecommentary[0pt]{Ps 94:6, 7; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--venite_adoremus--dominican--id_5307}  \vspace{5pt} \par{Come, let us adore God, and fall down before the Lord; let us weep before Him who made us; for He is the Lord our God. \Vbar. Come, let us praise the Lord with joy; let us joyfully sing to God our Savior.}  
 \subsection{Responsorium} Dom. anno A: \greannotation{II} \index[Responsorium]{Dispersit} \label{Dispersit (Responsorium)} \grecommentary[0pt]{Ps 111:9; \Vbar. 2} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--dispersit--dominican--id_5366}  \vspace{5pt} \par{He has distributed, he has given to the poor; his justice remains forever and ever. \Vbar. His seed shall he mighty upon earth; the generation of the righteous shall be blessed.}  
 \subsection{Responsorium} Dom. annis B et C: \greannotation{V} \index[Responsorium]{Tollite} \label{Tollite (Responsorium)} \grecommentary[0pt]{Ps 95:8, 9; \Vbar. Ps 28:9} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--tollite_hostias--dominican--id_6741}  \vspace{5pt} \par{Bring up sacrifices, and come into His courts; adore the Lord in His holy court. \Vbar. The Lord laid bare the thick woods; and in His temple all shall speak His glory.}  
 \subsection{Alleluia}  \greannotation{II} \index[Alleluia]{Laudate Dominum} \label{Laudate Dominum (Alleluia)} \grecommentary[0pt]{Ps 116:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--laudate_dominum--dominican--id_6552}  \vspace{5pt} \par{O praise the Lord all you nations, and praise him together all you people.}  
 \subsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Perfice} \label{Perfice (Offertorium)} \grecommentary[0pt]{Ps 16:5, 6, 7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--perfice_gressus--dominican--id_6795}  \vspace{5pt} \par{Secure my footsteps in Your paths, that my footsteps be not moved. Incline Your ear and hear my words. Show forth Your wonderful mercies, You who save those who trust in You, O Lord.}  
 \subsection{Communio} Dom. annis A et C: \greannotation{VIII} \index[Communio]{Introibo} \label{Introibo (Communio)} \grecommentary[5pt]{Ps 42:4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--introibo_ad_altare--dominican--id_4851}  \vspace{5pt} \par{I will go to the altar of God; to God who gives joy to my youth.}  
 \subsection{Communio} Dom. anno B: \greannotation{II} \index[Communio]{Multitudo languentium} \label{Multitudo languentium (Communio)} \grecommentary[3pt]{Lc 6:17, 18, 19} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--multitudo_languentium--dominican}  \vspace{5pt} \par{A multitude of the sick, and those who were troubled with unclean spirits, came to him: for power went forth from Him and healed all.}  


 \subsection{Officium}  \greannotation{VI} \index[Officium]{Esto mihi} \label{Esto mihi (Officium)} \grecommentary[0pt]{Ps 30:3, 4; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--esto_mihi--dominican--id_4916} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Be unto me a protecting God and a house of refuge, to save me; for You are my strength and my refuge; and for Your name's sake You will lead me and nourish me. \Vbar. In You, O Lord, have I hoped, let me never be confounded; in Your justice, deliver me and set me free.}  
 \subsection{Responsorium}  \greannotation{III} \index[Responsorium]{Tu es Deus} \label{Tu es Deus (Responsorium)} \grecommentary[5pt]{Ps 76:15; \Vbar. 16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/gr--tu_es_deus--dominican--id_4883} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{You are the God who alone does wonders. You have made Your power known among the nations. \Vbar. With Your arm You have redeemed Your people, the children of Israel and of Joseph.}  
 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Cantate Domino (d-a)} \label{Cantate Domino (d-a) (Alleluia)} \grecommentary[3pt]{Ps 97:1 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--cantate_domino_altera_melodia--solesmes} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Sing to the Lord a new song; for the Lord has accomplished wondrous deeds.}  
 \subsection{Offertorium}  \greannotation{III} \index[Offertorium]{Benedictus es... in labiis} \label{Benedictus es... in labiis (Offertorium)} \grecommentary[0pt]{Ps 118:12, 13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--benedictus_es_in_labiis--dominican--id_6310} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Blessed are You, O Lord; teach me Your justifications. With my lips I have pronounced all the judgments of Your mouth.}  
 \subsection{Communio}  \greannotation{I} \index[Communio]{Manducaverunt} \label{Manducaverunt (Communio)} \grecommentary[0pt]{Ps 77:29, 30} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--manducaverunt--dominican--id_5897} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{They ate and were filled exceedingly, and the Lord gave them their desire; they were not defrauded of that which they craved.}  


 \subsection{Officium}  \greannotation{V} \index[Officium]{Domine in tua} \label{Domine in tua (Officium)} \grecommentary[0pt]{Ps 12:6; \Vbar. 1 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--domine_in_tua_misericordia--vatican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{O Lord, I have hoped in your merciful love; my heart has rejoiced in your salvation; I will sing to the Lord who has granted me good things. \Vbar.  How long, O Lord, will you forget me: for ever? How long will you hide your face from me?}  
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Ego dixi} \label{Ego dixi (Responsorium)} \grecommentary[0pt]{Ps 40:5; \Vbar. 2 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/gr--ego_dixi--vatican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I said: ``Lord, have mercy on me; heal my soul because I have sinned against you." \Vbar. Blessed is he who considers the needy and the poor; the Lord will deliver him on the day of evil.}  
 \subsection{Alleluia}  \greannotation{II} \index[Alleluia]{Verba mea} \label{Verba mea (Alleluia)} \grecommentary[0pt]{Ps 5:2 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--verba_mea--vatican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Lend ear to my words, O Lord; consider my cry.}  
 \subsection{Offertorium}  \greannotation{V} \index[Offertorium]{Intende voci} \label{Intende voci (Offertorium)} \grecommentary[0pt]{Ps 5:3, 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--intende_voci--dominican--id_5467} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Attend to the voice of my prayer, O my King and my God, for to You will I pray, O Lord.}  
 \subsection{Communio}  \greannotation{II} \index[Communio]{Narrabo omnia} \label{Narrabo omnia (Communio)} \grecommentary[0pt]{Ps 9:2, 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--narrabo_omnia--dominican--id_6592} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I will declare all Your wonders; I will be glad and rejoice in You; I will sing praise to Your name, O Most High.}  


 \subsection{Officium}  \greannotation{I} \index[Officium]{Factus est Dominus} \label{Factus est Dominus (Officium)} \grecommentary[5pt]{Ps 17:19, 20; \Vbar. 2-3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/in--factus_est--dominican--id_4293} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{The Lord has become my protector, and has brought me forth into a large place; He saved me, because He was well pleased with me. \Vbar. I will love You, O Lord, my strength; the Lord is my stronghold, and my refuge, and my deliverer.}  
 \subsection{Responsorium} Dom. annis A et B: \greannotation{V} \index[Responsorium]{Ad Dominum} \label{Ad Dominum (Responsorium)} \grecommentary[10pt]{Ps 119:1; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/gr--ad_dominum--dominican--id_6295} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{In my trouble I cried to the Lord, and He heard me. \Vbar. O Lord, deliver my soul from wicked lips and a deceitful tongue.}  
 \subsection{Responsorium} Dom. anno C: \greannotation{V} \index[Responsorium]{Bonum est confiteri} \label{Bonum est confiteri (Responsorium)} \grecommentary[10pt]{Ps 91:2; \Vbar. 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/gr--bonum_est_confiteri--dominican--id_6112} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{It is good to give praise to the Lord, and to sing to Your name, O Most High. \Vbar. To show forth Your mercy in the morning, and Your truth in the night.}  
 \subsection{Alleluia}  \greannotation{I} \index[Alleluia]{Domine Deus meus} \label{Domine Deus meus (Alleluia)} \grecommentary[2pt]{Ps 7:2 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/al--domine_deus_meus_in_te--vatican} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{O Lord, my God, in you have I hoped; save me from all those who persecute me, and deliver me.}  
 \subsection{Offertorium}  \greannotation{VI} \index[Offertorium]{Domine convertere} \label{Domine convertere (Offertorium)} \grecommentary[0pt]{Ps 6:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/of--domine_convertere--dominican--id_6227} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Turn to me, O Lord, and deliver my soul; save me for Your mercy's sake.}  
 \subsection{Communio} Dom. anno A: \greannotation{VIII} \index[Communio]{Primum quærite} \label{Primum quærite (Communio)} \grecommentary[3pt]{Mt 6:33} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--primum_quaerite--dominican--id_5473} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{Seek first the kingdom of God, and all things shall be added unto you, says the Lord.}  
" \subsection{Communio} Dom. annis B et C: \greannotation{II} \index[Communio]{Cantabo Domino} \label{Cantabo Domino (Communio)} \grecommentary[0pt]{Ps 12:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \gregorioscore{graduale-chants/co--cantabo_domino--dominican--id_7094} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \vspace{5pt} \par{I will sing to the Lord, who gives me good things, and I will sing praises to the name of the Lord Most High.
}  "












































































\end{document}
