 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Ab occultis meis} \label{Ab occultis meis (Communio)} \grecommentary[0pt]{Ps 18:13, 14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.7cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ab_occultis_meis--dominican--id_5429}  \vspace{5pt} \par{From my secret sins cleanse me, O Lord, and from those of others spare Your servant.} 
 \subsubsection{Communio} Dom. annis A et B: \greannotation{IV} \index[Communio]{Acceptabis sacrificium} \label{Acceptabis sacrificium (Communio)} \grecommentary[0pt]{Ps 50:21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--acceptabilis--dominican--id_7167}  \vspace{5pt} \par{You will accept the sacrifice of justice, oblations and holocausts, upon Your altar, O Lord.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Adoramus te} \label{Adoramus te (Communio)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--adoramus_te--dominican}  \vspace{5pt} \par{We adore you, O Christ, and we bless you, because by your Cross you have redeemed the world.} 
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Adversum me} \label{Adversum me (Communio)} \grecommentary[0pt]{Ps 68:13, 14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--adversum_me--dominican--id_5409}  \vspace{5pt} \par{They who sat in the gate spoke against me; and they who drank wine made songs against me; but I made my prayer to You, O Lord; it is the time, O God, to show Your good will in the multitude of Your mercy.} 
 \subsubsection{Communio} \emph{Vel:} \greannotation{I} \index[Communio]{Amen dico vobis, quidquid} \label{Amen dico vobis, quidquid (Communio)} \grecommentary[3pt]{Mc 11:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quidquid--dominican--id_5918}  \vspace{5pt} \par{Amen, I say to you, all things whatever you ask for in prayer, believe that you shall receive, and it shall be done to you.} 
 \subsubsection{Communio} Dom. annis B et C et in feriis: \greannotation{I} \index[Communio]{Amen dico vobis, quidquid} \label{Amen dico vobis, quidquid (Communio)} \grecommentary[0pt]{Mc 11:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quidquid--dominican--id_5918}  \vspace{5pt} \par{Amen, I say to you, all things whatever you ask for in prayer, believe that you shall receive, and it shall be done to you.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Amen dico vobis: quod uni} \label{Amen dico vobis: quod uni (Communio)} \grecommentary[0pt]{Mt 25:40, 34 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quod_uni--vatican}  \vspace{5pt} \par{Amen, I say to you, that what you did to the least of mine, you did to me; come, blessed of my Father, inherit the kingdom that has been prepared for you from the beginning of the world.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Amen dico vobis: quod vos} \label{Amen dico vobis: quod vos (Communio)} \grecommentary[0pt]{Mt 19:28, 29} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quod_vos--dominican--id_4856}  \vspace{5pt} \par{Amen, I say to you, that you, who have left all things and followed Me, shall receive a hundredfold, and shall possess life everlasting. T.P. Alleluia!} 
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Aufer a me} \label{Aufer a me (Communio)} \grecommentary[0pt]{Ps 118:22, 24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--aufer_a_me--dominican--id_6054}  \vspace{5pt} \par{Remove from me reproach and contempt, because I have sought out Your commandments, O Lord; for Your testimonies are my meditation.} 

 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Beata viscera} \label{Beata viscera (Communio)} \grecommentary[0pt]{Lc 11:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beata_viscera--dominican}  \vspace{5pt} \par{Blessed is the womb of the Virgin Mary, which bore the Son of the eternal Father.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Beata viscera} \label{Beata viscera (Communio)} \grecommentary[0pt]{Lc 11:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beata_viscera--dominican}  \vspace{5pt} \par{Blessed is the womb of the virgin Mary, which bore the Son of the eternal Father.} 

 \subsubsection{Communio} Dom. anno A: \greannotation{I} \index[Communio]{Beati mundo corde} \label{Beati mundo corde (Communio)} \grecommentary[0pt]{Mt 5:8, 9, 10 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beati_mundo_corde--vatican}  \vspace{5pt} \par{Blessed are the pure in heart, for they shall see God; blessed are the peacemakers, for they shall be called sons of God; blessed are those who suffer persecution for the sake of justice, for theirs is the kingdom of heaven.} 



 \subsubsection{Communio} Annis A et C: \greannotation{IV} \index[Communio]{Benedicimus Deum} \label{Benedicimus Deum (Communio)} \grecommentary[3pt]{Tob 12:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--benedicimus_deum--dominican--id_4804}  \vspace{5pt} \par{We bless the God of heaven, and before all the living we will praise Him, because He has shown His mercy to us.} 

 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Benedicta} \label{Benedicta (Communio)} \grecommentary[0pt]{Jud 13:23, 25} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--benedicta--dominican--id_4820}  \vspace{5pt} \par{Blessed are you, O daughter, by the Lord the most high God above all women upon the earth; because He has so magnified your name that your praise shall not depart out of the mouth of men. \emph{T.P.} Alleluia.} 
" \subsubsection{Communio} Dom. annis B et C: \greannotation{II} \index[Communio]{Cantabo Domino} \label{Cantabo Domino (Communio)} \grecommentary[0pt]{Ps 12:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--cantabo_domino--dominican--id_7094}  \vspace{5pt} \par{I will sing to the Lord, who gives me good things, and I will sing praises to the name of the Lord Most High.
} "
 \subsubsection{Communio} Dom. anno B: \greannotation{I} \index[Communio]{Cantate Domino} \label{Cantate Domino (Communio)} \grecommentary[5pt]{Ps 95:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--cantate_domino--dominican--id_5304}  \vspace{5pt} \par{Sing to the Lord, alleluia. Sing to the Lord, and bless His name. Show forth His salvation from day to day, alleluia, alleluia.} 


 \subsubsection{Communio} \emph{Ad libitum:} Dom. anno C: \greannotation{VIII} \index[Communio]{Comedite pinguia} \label{Comedite pinguia (Communio)} \grecommentary[5pt]{2 Esdr 8:10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--comedite_pinguia--dominican--id_6323}  \vspace{5pt} \par{Eat rich meats, and drink sweet wine, and send portions to them who have not prepared for themselves; because it is the holy day of the Lord; be not sad, for the joy of the Lord is our strength.} 


 \subsubsection{Communio} Anno A: \greannotation{I} \index[Communio]{Data est mihi} \label{Data est mihi (Communio)} \grecommentary[5pt]{Mt 28:18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--data_est_mihi--dominican--id_7085}  \vspace{5pt} \par{All power has been given to Me in heaven and on earth, alleluia. Go, teach all nations, baptizing them in the name of the Father, and of the Son, and of the Holy Spirit, alleluia, alleluia.} 
 \subsubsection{Communio} Anno B: \greannotation{I} \index[Communio]{Data est mihi} \label{Data est mihi (Communio)} \grecommentary[5pt]{Mt 28:18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--data_est_mihi--dominican--id_7085}  \vspace{5pt} \par{All power has been given to Me in heaven and on earth, alleluia. Go, teach all nations, baptizing them in the name of the Father, and of the Son, and of the Holy Spirit, alleluia, alleluia.} 


 \subsubsection{Communio} Dom. anno B: \greannotation{VIII} \index[Communio]{Dicit Andreas} \label{Dicit Andreas (Communio)} \grecommentary[5pt]{Io 1:41, 42} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicit_andreas--dominican--id_6487}  \vspace{5pt} \par{Andrew said to his brother Simon: ``We have found the Messiah," which means Christ; and he led him to Jesus.} 
 \subsubsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Dicit Dominus} \label{Dicit Dominus (Communio)} \grecommentary[5pt]{Io 2:7, 8, 9, 10-11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicit_dominus--dominican--id_5103}  \vspace{5pt} \par{The Lord said, ``Fill the jars with water and take them to the chief steward." When the chief steward had tasted the water made wine, he said to the bridegroom, ``You have kept the good wine until now." This first miracle Jesus worked in the presence of His disciples.} 
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Dicite: Pusillanimes} \label{Dicite: Pusillanimes (Communio)} \grecommentary[10pt]{Cf. Is 35:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicite_pusillanimes--dominican--id_5719}  \vspace{5pt} \par{Say to the faint-hearted: ``Take courage and fear not; behold, our God will come and save us."} 





 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Domine Dominus noster} \label{Domine Dominus noster (Communio)} \grecommentary[4pt]{Ps 8:2 ab} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_dominus_noster--dominican--id_4994}  \vspace{5pt} \par{O Lord, our Lord, how wonderful is Your name in all the earth.} 
 \subsubsection{Communio} Dom. anno A: \greannotation{VII} \index[Communio]{Domine quinque talenta} \label{Domine quinque talenta (Communio)} \grecommentary[0pt]{Mt 25:20, 21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_quinque_talenta--dominican--id_5425}  \vspace{5pt} \par{Master, you did hand over to me five talents; behold, I have gained five others in addition. Well done, faithful servant, because you have been faithful over a few things I will set you over many things; enter into the joy of your master.} 





 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Dominus dabit} \label{Dominus dabit (Communio)} \grecommentary[5pt]{Ps 84:13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_dabit--dominican--id_6204}  \vspace{5pt} \par{The Lord will bestow His goodness, and our earth shall yield its fruit.} 

 \subsubsection{Communio} Dom. annis B et C et in feriis: \greannotation{II} \index[Communio]{Dominus regit me} \label{Dominus regit me (Communio)} \grecommentary[0pt]{Ps 22:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_regit_me--dominican--id_5335}  \vspace{5pt} \par{The Lord rules me, and I shall want for nothing; He has set me in a place of pasture; He has led me to refreshing waters.} 



 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Ecce sic} \label{Ecce sic (Communio)} \grecommentary[5pt]{Ps 127:4, 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ecce_sic_benedicetur--dominican--id_5537}  \vspace{5pt} \par{Behold, thus shall every man be blessed who fears the Lord; and may you see your children's children; peace upon Israel. \emph{T.P.} Alleluia.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Ecce virgo} \label{Ecce virgo (Communio)} \grecommentary[3pt]{Is 7:14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ecce_virgo--dominican--id_6887}  \vspace{5pt} \par{Behold, a virgin shall conceive and bring forth a son, and His name shall be called Emmanuel.} 
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Ego clamavi} \label{Ego clamavi (Communio)} \grecommentary[3pt]{Ps 16:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_clamavi--dominican}  \vspace{5pt} \par{I have cried to You for You, O God, have heard me; O incline Your ear to me, and hear my words.} 
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Ego sum pastor} \label{Ego sum pastor (Communio)} \grecommentary[5pt]{Io 10:14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_sum_pastor--dominican--id_6143}  \vspace{5pt} \par{I am the Good Shepherd, alleluia, and I know My sheep, and Mine know Me, alleluia, alleluia.} 
 \subsubsection{Communio} Dom. annis B et C: \greannotation{VIII} \index[Communio]{Ego sum vitis vera} \label{Ego sum vitis vera (Communio)} \grecommentary[5pt]{Io 15:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_sum_vitis--dominican--id_7015}  \vspace{5pt} \par{I am the true vine and you are the branches; whoever remains in me, and I in him, bears fruit in plenty, alleluia.} 
 \subsubsection{Communio} Dom. anno B: \greannotation{I} \index[Communio]{Ego vos elegi} \label{Ego vos elegi (Communio)} \grecommentary[0pt]{Io 15:16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_vos_elegi_alleluia--dominican--id_5178}  \vspace{5pt} \par{I have chosen you out of the world that you may go and bring forth fruit; and that your fruit may remain, alleluia.} 






 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Exsulta filia Sion} \label{Exsulta filia Sion (Communio)} \grecommentary[0pt]{Zach 9:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--exsulta_filia--dominican--id_6171}  \vspace{5pt} \par{Rejoice greatly, O daughter of Zion, shout for joy, O daughter of Jerusalem; behold your King comes, the holy one, and the Savior of the world.} 





 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Florete flores} \label{Florete flores (Communio)} \grecommentary[0pt]{Sir 39:19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--florete_flores}  \vspace{5pt} \par{Send forth flowers, as the lily, and yield a smell, and bring forth leaves in grace; and praise with canticles, and bless the Lord in His works.} 


 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Gaudete iusti} \label{Gaudete iusti (Communio)} \grecommentary[0pt]{Ps 32:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--gaudete_iusti__alleluia--dominican}  \vspace{5pt} \par{Rejoice in the Lord, you just, alleluia. Praise is fitting to the upright, alleluia.} 
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Gloriosa} \label{Gloriosa (Communio)} \grecommentary[0pt]{Ps 86:3; Lc 1:49} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--gloriosa--dominican}  \vspace{5pt} \par{Glorious things are told of you, O Mary, for He who is mighty has done great things to you.} 

 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Hoc corpus} \label{Hoc corpus (Communio)} \grecommentary[3pt]{I Cor 11:24, 25} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--hoc_corpus--dominican--id_5947}  \vspace{5pt} \par{``This is my body which is given up for you; this is the chalice of the new covenant in my blood," says the Lord. ``Do this, as often as your receive it, in memory of me."} 
 \subsubsection{Communio} Anno C: \greannotation{VIII} \index[Communio]{Hoc corpus} \label{Hoc corpus (Communio)} \grecommentary[3pt]{I Cor 11:24, 25} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--hoc_corpus--dominican--id_5947}  \vspace{5pt} \par{``This is my body which is given up for you; this is the chalice of the new covenant in my blood," says the Lord. ``Do this, as often as your receive it, in memory of me."} 

 \subsubsection{Communio} Anno B: \greannotation{IV} \index[Communio]{Ierusalem quæ ædificatur} \label{Ierusalem quæ ædificatur (Communio)} \grecommentary[0pt]{Ps 121:3, 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ierusalem_quae--dominican--id_5394}  \vspace{5pt} \par{Jerusalem, which is built as a city, which is compact together; for there did the tribes go up, the tribes of the Lord, to praise Your name, O Lord.} 

 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Ierusalem surge} \label{Ierusalem surge (Communio)} \grecommentary[0pt]{Bar 5:5; 4:36} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ierusalem_surge--dominican--id_6773}  \vspace{5pt} \par{Arise, O Jerusalem, and stand on high; and behold the joy that comes to you from your God.} 
 \subsubsection{Communio} Dom. annis B et C: \greannotation{I} \index[Communio]{Illumina faciem tuam} \label{Illumina faciem tuam (Communio)} \grecommentary[0pt]{Ps 30:17, 18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--illumina_faciem--dominican--id_4792}  \vspace{5pt} \par{Let Your face shine upon Your servant, and save me in Your mercy; let me not be confounded, O Lord, for I have called upon You.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{In salutari tuo} \label{In salutari tuo (Communio)} \grecommentary[0pt]{Ps 118:81, 84, 86} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--in_salutari_tuo--dominican--id_6778}  \vspace{5pt} \par{My soul is in Your salvation, and in Your word have I hoped. When will You execute judgment on those who persecute me? The wicked have persecuted me; help me, O Lord my God.} 
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{In splendoribus} \label{In splendoribus (Communio)} \grecommentary[0pt]{Ps 109:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--in_splendoribus--dominican--id_7236}  \vspace{5pt} \par{In the brightness of the saints, from the womb before the day-star I begot You.} \vspace{10pt}


 \subsubsection{Communio} Dom. annis A et C: \greannotation{VIII} \index[Communio]{Introibo} \label{Introibo (Communio)} \grecommentary[5pt]{Ps 42:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--introibo_ad_altare--dominican--id_4851}  \vspace{5pt} \par{I will go to the altar of God; to God who gives joy to my youth.} 


 \subsubsection{Communio} Dom. anno A: \greannotation{II} \index[Communio]{Lætabimur} \label{Lætabimur (Communio)} \grecommentary[5pt]{Ps 19:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--laetabimur--dominican--id_6160}  \vspace{5pt} \par{We will rejoice in Your salvation, and in the name of the Lord our God we shall be exalted.} 
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Lætabimur} \label{Lætabimur (Communio)} \grecommentary[0pt]{Ps 19:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--laetabimur--dominican--id_6160}  \vspace{5pt} \par{We will rejoice in Your salvation, and in the name of the Lord our God we shall be exalted.} 


 \subsubsection{Communio} Anno A (Quando legitur Evangelium de cæco nato): \greannotation{VI} \index[Communio]{Lutum fecit} \label{Lutum fecit (Communio)} \grecommentary[5pt]{Cf. Io 9:6, 11, 38} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--lutum_fecit--dominican--id_6341}  \vspace{5pt} \par{The Lord made clay of spittle, and anointed my eyes, and I went, and washed, and I saw; and I believed in God.} 
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Lux æterna} \label{Lux æterna (Communio)} \grecommentary[5pt]{IV Esdr 2:35; \Vbar. Ps 120:1-8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--lux_aeterna--dominican--id_6519}  \vspace{5pt} \par{May eternal light shine upon them, O Lord, with Your saints forever, because You are merciful. \par \Vbar.\textsuperscript{1} I have lifted up my eyes to the mountains, from whence help shall come to me. \par\Vbar.\textsuperscript{2} My help is from the Lord, who made heaven and earth. \par\Vbar.\textsuperscript{3} May he not suffer your foot to be moved: neither let him slumber that keepeth you. \par\Vbar.\textsuperscript{4} Behold he shall neither slumber nor sleep, that keepeth Israel. \par\Vbar.\textsuperscript{5} The Lord is your keeper, the Lord is thy protection upon thy right hand. \par\Vbar.\textsuperscript{6} The sun shall not burn you by day: nor the moon by night. \par\Vbar.\textsuperscript{7} The Lord keepeth you from all evil: may the Lord keep your soul. \par\Vbar.\textsuperscript{8} May the Lord keep your coming in and thy going out; from henceforth now and for ever.} 

 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Manducaverunt} \label{Manducaverunt (Communio)} \grecommentary[0pt]{Ps 77:29, 30} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--manducaverunt--dominican--id_5897}  \vspace{5pt} \par{They ate and were filled exceedingly, and the Lord gave them their desire; they were not defrauded of that which they craved.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Memento} \label{Memento (Communio)} \grecommentary[0pt]{Ps 118:49, 50} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--memento_verbi_tui--dominican--id_6042}  \vspace{5pt} \par{Be mindful of Your word to Your servant, O Lord, in which You have given me hope; this has comforted me in my humiliation.} 

 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Mirabantur omnes} \label{Mirabantur omnes (Communio)} \grecommentary[3pt]{Lc 4:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--mirabantur_omnes--dominican--id_7227}  \vspace{5pt} \par{All marveled at these things that came from the mouth of God.} 

 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Mitte manum tuam} \label{Mitte manum tuam (Communio)} \grecommentary[0pt]{Io 20:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--mitte_manum_alleluia--dominican--id_4846}  \vspace{5pt} \par{Put in your hand, and know the place of the nails, alleluia, and be not unbelieving, but believing, alleluia, alleluia.} 

 \subsubsection{Communio} Dom. anno B: \greannotation{II} \index[Communio]{Multitudo languentium} \label{Multitudo languentium (Communio)} \grecommentary[3pt]{Lc 6:17, 18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--multitudo_languentium--dominican}  \vspace{5pt} \par{A multitude of the sick, and those who were troubled with unclean spirits, came to him: for power went forth from Him and healed all.} 

 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Narrabo omnia} \label{Narrabo omnia (Communio)} \grecommentary[0pt]{Ps 9:2, 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--narrabo_omnia--dominican--id_6592}  \vspace{5pt} \par{I will declare all Your wonders; I will be glad and rejoice in You; I will sing praise to Your name, O Most High.} 

 \subsubsection{Communio} Anno C (Quando legitur Evangelium de muliere adultera): \greannotation{VIII} \index[Communio]{Nemo te condemnavit} \label{Nemo te condemnavit (Communio)} \grecommentary[3pt]{Io 8:10, 11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--nemo_te_condemnavit--dominican--id_7175}  \vspace{5pt} \par{``Has no one condemned you, woman?" ``No one, Lord." ``Neither will I condemn you; now sin no more."} 
 \subsubsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Non vos relinquam} \label{Non vos relinquam (Communio)} \grecommentary[0pt]{Io 14:18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--non_vos_relinquam--dominican--id_6454}  \vspace{5pt} \par{I will not leave you orphans; I will come to you again, alleluia, and your heart shall rejoice, alleluia, alleluia.} 

 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Notas mihi} \label{Notas mihi (Communio)} \grecommentary[0pt]{Ps 15:11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--notas_mihi--dominican--id_6934}  \vspace{5pt} \par{You have made known to me the ways of life; You shall fill me with joy with Your countenance, O Lord.} 


 \subsubsection{Communio} Anno C (Quando legitur Evangelium de filio prodigo): \greannotation{VIII} \index[Communio]{Oportet te} \label{Oportet te (Communio)} \grecommentary[3pt]{Lc 15:32} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--oportet_te_fili--dominican--id_6842}  \vspace{5pt} \par{You ought to rejoice, my son, because Your brother was dead, and has come to life; he was lost, and is found.} 




 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Pascha nostrum} \label{Pascha nostrum (Communio)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pascha_nostrum--dominican--id_6187}  \vspace{5pt} \par{Christ our Passover is sacrificed, alleluia; therefore, let us feast with the unleavened bread of sincerity and truth, alleluia, alleluia, alleluia.} 
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Pascha nostrum} \label{Pascha nostrum (Communio)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pascha_nostrum--dominican--id_6187}  \vspace{5pt} \par{Christ our Passover is sacrificed, alleluia; therefore, let us feast with the unleavened bread of sincerity and truth, alleluia, alleluia, alleluia.} 
 \subsubsection{Communio} Annis B et C (Quando legitur aliud Evangelium): \greannotation{I} \index[Communio]{Passer invenit} \label{Passer invenit (Communio)} \grecommentary[0pt]{Ps 83:4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--passer_invenit--dominican--id_6674}  \vspace{5pt} \par{The sparrow has found herself a house, and the turtledove a nest where she may lay her young ones: Your altars, O Lord of Hosts, my King, and my God. Blessed are they who dwell in Your house; for ever and ever shall they sing your praise.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Passer invenit} \label{Passer invenit (Communio)} \grecommentary[0pt]{Ps 83:4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--passer_invenit--dominican--id_6674}  \vspace{5pt} \par{The sparrow has found herself a house, and the turtle a nest where she may lay her young ones: Your altars, O Lord of Hosts, my King, and my God. Blessed are they who dwell in Your house; they shall praise You forever and ever.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Pater cum essem} \label{Pater cum essem (Communio)} \grecommentary[0pt]{Io 17:12, 13, 15} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pater_cum_essem--dominican--id_4810}  \vspace{5pt} \par{Father, while I was with them, I kept them whom You have given Me, alleluia. But now I come to You; I do not pray that You take them out of the world, but that You keep them from evil, alleluia, alleluia.} 
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Pater si non potest} \label{Pater si non potest (Communio)} \grecommentary[0pt]{Mt 26:42} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pater_si_non_potest--dominican--id_4841}  \vspace{5pt} \par{Father, if this cup cannot pass away unless I drink it, Your will be done.} 
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Per lignum} \label{Per lignum (Communio)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--per_lignum--dominican--id_4990--good-friday}  \vspace{5pt} \par{By the tree we became slaves, and by the holy cross we have been set free; the fruit of the tree enslaved us, the Son of God redeemed us. Alleluia!} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Per signum Crucis} \label{Per signum Crucis (Communio)} \grecommentary[3pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--per_signum_crucis--dominican}  \vspace{5pt} \par{By the sign of the cross deliver us from our enemies, O You who are our God.} 






 \subsubsection{Communio} Dom. anno A: \greannotation{VIII} \index[Communio]{Primum quærite} \label{Primum quærite (Communio)} \grecommentary[3pt]{Mt 6:33} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--primum_quaerite--dominican--id_5473}  \vspace{5pt} \par{Seek first the kingdom of God, and all things shall be added unto you, says the Lord.} 
 \subsubsection{Communio} Dom. anno C et in feriis: \greannotation{VIII} \index[Communio]{Primum quærite} \label{Primum quærite (Communio)} \grecommentary[0pt]{Mt 6:33} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--primum_quaerite--dominican--id_5473}  \vspace{5pt} \par{Seek first the kingdom of God, and all things shall be added unto you, says the Lord.} 

 \subsubsection{Communio} Anno C: \greannotation{I} \index[Communio]{Psallite Domino} \label{Psallite Domino (Communio)} \grecommentary[10pt]{Ps 67:33, 34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--psallite_domino--dominican--id_5669}  \vspace{5pt} \par{Sing to the Lord, who mounts above the heaven of heavens to the East, alleluia.} 
 \subsubsection{Communio} Anno A (Quando legitur Evangelium de Samaritana): \greannotation{VII} \index[Communio]{Qui biberit aquam} \label{Qui biberit aquam (Communio)} \grecommentary[0pt]{Io 4:13, 14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_biberit--dominican--id_4868}  \vspace{5pt} \par{``Whosoever drinks the water that I shall offer," said the Lord (to the Samaritan woman), ``shall have within him a spring of water welling up unto eternal life."} 

 \subsubsection{Communio} Annis A et B: \greannotation{VI} \index[Communio]{Qui manducat} \label{Qui manducat (Communio)} \grecommentary[3pt]{Io 6:57} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_manducat--dominican--id_6212}  \vspace{5pt} \par{He who eats My flesh, and drinks My blood, abides in Me, and I in him, says the Lord.} 
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Qui meditabitur} \label{Qui meditabitur (Communio)} \grecommentary[0pt]{Ps 1:2–3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_meditabitur--dominican--id_6589}  \vspace{5pt} \par{He who shall meditate upon the law of the Lord, day and night, shall bring forth his fruit in due season.} 
 \subsubsection{Communio} Anno B (Quando legitur aliud Evangelium): \greannotation{V} \index[Communio]{Qui mihi ministrat} \label{Qui mihi ministrat (Communio)} \grecommentary[5pt]{Io 12:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_mihi_ministrat--dominican--id_6620}  \vspace{5pt} \par{If anyone serves Me, let him follow Me: and where I am, there also shall my servant be.} 





 \subsubsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Quinque prudentes virgines} \label{Quinque prudentes virgines (Communio)} \grecommentary[0pt]{Mt 25:4, 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/}  \vspace{5pt} \par{} 



 \subsubsection{Communio} In ritu Ordinis Prædicatorum: \greannotation{VII} \index[Communio]{Quotiescumque} \label{Quotiescumque (Communio)} \grecommentary[3pt]{1 Cor 11:26-27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--quotiescumque--dominican--id_4700}  \vspace{5pt} \par{As often as you shall eat this bread, and drink the cup, you proclaim the death of the Lord, until he comes. Therefore, whoever eats this bread or drinks the cup of the Lord unworthily, will be guilty of the body and blood of the Lord, alleluia.} 
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Redime me Deus} \label{Redime me Deus (Communio)} \grecommentary[0pt]{Ps 24:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--redime_me--dominican--id_6994}  \vspace{5pt} \par{Redeem me, O God of Israel, from all my tribulations.} 

 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Revelabitur} \label{Revelabitur (Communio)} \grecommentary[0pt]{Cf. Is 40:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--revelabitur--dominican--id_7068}  \vspace{5pt} \par{The glory of the Lord shall be revealed, and all flesh shall see the salvation of our God.} 
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Salvator mundi} \label{Salvator mundi (Communio)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--salvator_mundi--dominican}  \vspace{5pt} \par{Savior of the world, save us, you have redeemed us by your Cross and Blood; help us, we beseech you, our God.} 

 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Scapulis suis} \label{Scapulis suis (Communio)} \grecommentary[0pt]{Ps 90:4–5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--scapulis_suis--dominican--id_6971}  \vspace{5pt} \par{He will overshadow you with His shoulders, and under His wings you shall trust; His truth shall compass you with a shield.} 
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Sedebit} \label{Sedebit (Communio)} \grecommentary[0pt]{Ps 28:10b, 11b} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--sedebit_dominus--dominican--id_7401}  \vspace{5pt} \par{The Lord shall sit as a King forever; the Lord will bless His people with peace.} 



 \subsubsection{Communio} Anno B: Psallite Domino, \emph{ut infra, vel:} \greannotation{VII} \index[Communio]{Signa} \label{Signa (Communio)} \grecommentary[10pt]{Mk 16:17, 18 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--signa_eos--vatican-op}  \vspace{5pt} \par{These signs will accompany those who believe: they will cast out demons; they will lay their hands upon the sick, and these will recover, alleluia.} 



 \subsubsection{Communio} Dom. anno C: \greannotation{VI} \index[Communio]{Simon Ioannis} \label{Simon Ioannis (Communio)} \grecommentary[3pt]{Io 21:15, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--simon_ioannis--dominican--id_5102}  \vspace{5pt} \par{``Simon, son of John, do you love Me more than these do?" ``Lord, You know all things; You know, Lord, that I love You."} 


 \subsubsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Spiritus Sanctus docebit vos} \label{Spiritus Sanctus docebit vos (Communio)} \grecommentary[5pt]{Io 14:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--spiritus_sanctus--dominican--id_4850}  \vspace{5pt} \par{The Holy Spirit shall teach you, alleluia, whatsoever I have said to you, alleluia, alleluia.} 


 \subsubsection{Communio} Dom. anno A: \greannotation{VI} \index[Communio]{Surrexit Dominus} \label{Surrexit Dominus (Communio)} \grecommentary[3pt]{Lc 24:34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--surrexit_dominus--dominican--id_7481}  \vspace{5pt} \par{The Lord has risen, and has appeared to Peter, alleluia.} 
 \subsubsection{Communio} Dom. anno A: \greannotation{IV} \index[Communio]{Tanto tempore} \label{Tanto tempore (Communio)} \grecommentary[0pt]{Io 14:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tanto_tempore--dominican--id_6774}  \vspace{5pt} \par{Have I been so long a time with you, and have you not known Me? Philip, he who sees Me, sees the Father also, alleluia. Do you not believe that I am in the Father, and the Father in Me? Alleluia, alleluia.} 








 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Ultimo} \label{Ultimo (Communio)} \grecommentary[0pt]{Io 7:37-39} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ultimo_festivitatis--dominican--id_5123}  \vspace{5pt} \par{On the last day of the feast, Jesus said, ``He who believes in Me, out of his stomach shall flow rivers of living water;” but this He said of the Spirit whom they should receive who believed in Him, alleluia, alleluia.} 



 \subsubsection{Communio} \emph{Ad libitum:} Dom. annis A et B: \greannotation{VIII} \index[Communio]{Venite post me} \label{Venite post me (Communio)} \grecommentary[5pt]{Mt 4:19-20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--venite_post_me--dominican--id_7007}  \vspace{5pt} \par{Come, follow Me, I will make you fishers of men: at that, they left the nets and boat and followed the Lord.} 
 \subsubsection{Communio} Anno A (Quando legitur Evangelium de Lazaro): \greannotation{I} \index[Communio]{Videns Dominus flentes} \label{Videns Dominus flentes (Communio)} \grecommentary[3pt]{Io 11:33, 35, 43, 44, 39} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--videns_dominus--dominican--id_7057}  \vspace{5pt} \par{When the Lord saw the sisters of Lazarus in tears near the tomb, He wept in the presence of the Jews, and cried out: ``Lazarus, come forth!" And he came forth, with bound feet and hands, he who had been dead four days.} 

 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Viderunt omnes} \label{Viderunt omnes (Communio)} \grecommentary[5pt]{Ps 97:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--viderunt_omnes--dominican--id_5158}  \vspace{5pt} \par{All the ends of the earth have seen the salvation of our God.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Vidimus stellam} \label{Vidimus stellam (Communio)} \grecommentary[0pt]{Cf. Mt 2:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vidimus_stellam--dominican--id_5896}  \vspace{5pt} \par{We have seen His star in the east, and have come with gifts to adore Him.} 
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Vincenti dabo} \label{Vincenti dabo (Communio)} \grecommentary[8pt]{Apoc 2:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vincenti_dabo--dominican--id_6089}  \vspace{5pt} \par{To Vincent I will give to eat of the tree of life, which is in the paradise of my God. \emph{T.P.} Alleluia.} 

 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Visionem quam vidistis} \label{Visionem quam vidistis (Communio)} \grecommentary[0pt]{Mt 17:9 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--visionem--vatican}  \vspace{5pt} \par{Of the vision you have seen, tell no one until the Son of Man has risen from the dead.} 


 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Vos qui secuti ... tribus Israel} \label{Vos qui secuti ... tribus Israel (Communio)} \grecommentary[0pt]{Mt 19:28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vos_qui_secuti--dominican--id_5171}  \vspace{5pt} \par{You who have followed Me shall sit on seats judging the twelve tribes of Israel.} 

 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Vox in Rama audita est} \label{Vox in Rama audita est (Communio)} \grecommentary[3pt]{Mt 2:18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vox_in_rama--dominican--id_4760}  \vspace{5pt} \par{A voice was heard in Rama, weeping and loud lamentation: Rachel weeping for her children; she would not be comforted, because they are no more.} 