\part{Proprium de Tempore}               
\chapter{Tempus Adventus}               
\section{Hebdomada prima Adventus}               
 \subsubsection{Officium}  \greannotation{VIII} \index[Officium]{Ad te levavi} \label{Ad te levavi (Officium)} \grecommentary[7pt]{Ps 24:1–3; \Vbar. 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--ad_te_levavi--dominican--id_5367}  \vspace{5pt} \par{To You have I lifted up my soul; my God, in you I put my trust, let me not be ashamed; neither let my enemies laugh at me, for no one who waits for You shall be confounded. \Vbar. Show, O Lord, Your ways to me, and teach me Your paths.} 
  \par \vspace{5pt} \textbf{Feria 6:} Dominus illuminatio mea, \ref{Dominus illuminatio mea}.             
 \subsubsection{Responsorium}  \greannotation{I} \index[Responsorium]{Universi} \label{Universi (Responsorium)} \grecommentary[0pt]{Ps 24:3; \Vbar. 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--universi--dominican--id_5146}  \vspace{5pt} \par{No one who waits for You shall be confounded, O Lord. \Vbar. Show, O Lord, Your ways to me, and teach me Your paths.} 
  \par \vspace{5pt} \textbf{Feria 5:} Bonum est confidere, \ref{Bonum est confidere}.             
 \subsubsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Ostende nobis} \label{Ostende nobis (Alleluia)} \grecommentary[0pt]{Ps 84:8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--ostende_nobis--dominican--id_4904}  \vspace{5pt} \par{Show us, O Lord, Your mercy, and grant us Your salvation.} 
 \subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{Ad te Domine levavi} \label{Ad te Domine levavi (Offertorium)} \grecommentary[0pt]{Ps 24:1–3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--ad_te_domine_levavi--dominican--id_4301}  \vspace{5pt} \par{To You, O Lord, have I lifted up my soul; my God, in You I put my trust, let me not be ashamed; neither let my enemies laugh at me: for no one who waits for Yon shall be confounded.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Dominus dabit} \label{Dominus dabit (Communio)} \grecommentary[5pt]{Ps 84:13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_dabit--dominican--id_6204}  \vspace{5pt} \par{The Lord will bestow His goodness, and our earth shall yield its fruit.} 
  \par \vspace{5pt} \textbf{Feria 4:} Manducaverunt, \ref{Manducaverunt}.             
\section{Hebdomada secunda Adventus}               
 \subsubsection{Officium}  \greannotation{VII} \index[Officium]{Populus Sion} \label{Populus Sion (Officium)} \grecommentary[5pt]{Cf. Is 30:19, 30; \Vbar. Ps 79:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--populus_sion--dominican--id_4278}  \vspace{5pt} \par{People of Zion, behold the Lord shall come to save the nations; and the Lord shall make the glory of His voice to be heard in the joy of your hearts. \Vbar. Take heed, O you who rule Israel, you who lead Joseph like a sheep.} 
 \subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Ex Sion} \label{Ex Sion (Responsorium)} \grecommentary[0pt]{Ps 49:2, 3; \Vbar. 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--ex_sion_species--dominican--id_6456}  \vspace{5pt} \par{Out of Zion, the loveliness of His beauty, God shall come revealed. \Vbar. Gather together His saints before Him, who have set His covenant before sacrifices.} 
 \subsubsection{Alleluia}  \greannotation{I} \index[Alleluia]{Lætatus sum} \label{Lætatus sum (Alleluia)} \grecommentary[0pt]{Ps 121:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--laetatus_sum--dominican--id_6365}  \vspace{5pt} \par{I rejoiced at the things that were said to me: ``We shall go into the house of the Lord."} 
  \par \vspace{5pt} \textbf{Feria 4:} Venite ad me, \ref{Venite ad me}.             
  \par \vspace{5pt} \textbf{Feria 6:} Qui sequitur me, \ref{Qui sequitur me}.             
 \subsubsection{Offertorium}  \greannotation{III} \index[Offertorium]{Deus tu convertens} \label{Deus tu convertens (Offertorium)} \grecommentary[5pt]{Ps 84:7–8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--deus_tu_convertens--dominican--id_4305}  \vspace{5pt} \par{You will tum, O God, and bring us to life, and Your people shall rejoice in You. Show us, O Lord, Your mercy, and grant us Your salvation.} 
  \par \vspace{5pt} \textbf{Feria 2:} Confortamini, \ref{Confortamini}.             
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Ierusalem surge} \label{Ierusalem surge (Communio)} \grecommentary[0pt]{Bar 5:5; 4:36} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ierusalem_surge--dominican--id_6773}  \vspace{5pt} \par{Arise, O Jerusalem, and stand on high; and behold the joy that comes to you from your God.} 


\section{Hebdomada tertia Adventus}               
 \subsubsection{Officium}  \greannotation{I} \index[Officium]{Gaudete in Domino} \label{Gaudete in Domino (Officium)} \grecommentary[0pt]{Phil 4:4, 5; \Vbar. 7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--gaudete_in_domino--dominican--id_4287}  \vspace{5pt} \par{Rejoice in the Lord always; again, I say, rejoice. Let your moderation be known to all men. The Lord is near. Have no anxiety, but in every prayer let your petitions be made known to God. \Vbar. And may the peace of God, which surpasses all understanding, keep your hearts and minds.} 

 \subsubsection{Responsorium} Dom. annis A et C: \greannotation{VII} \index[Responsorium]{Qui sedes, Domine} \label{Qui sedes, Domine (Responsorium)} \grecommentary[5pt]{Ps 79:2, 3; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--qui_sedes_domine--dominican--id_6651}  \vspace{5pt} \par{You, O Lord, who sit upon the cherubim, stir up Your might, and come. \Vbar. Take heed, O you who rule Israel, you who lead Joseph like a sheep.} 
 \subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Fuit homo} \label{Fuit homo (Responsorium)} \grecommentary[5pt]{Io 1:6; \Vbar. 7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--fuit_homo--dominican}  \vspace{5pt} \par{There was a man sent from God whose name was John; he came. \Vbar. To bear witness to the light, to prepare an upright people for the Lord.} 
 \subsubsection{Alleluia}  \greannotation{IV} \index[Alleluia]{Excita Domine} \label{Excita Domine (Alleluia)} \grecommentary[0pt]{Ps 79:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--excita_domine--dominican--id_5097}  \vspace{5pt} \par{Stir up Your might, O Lord, and come, that You may save us.} 
 \subsubsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Benedixisti Domine} \label{Benedixisti Domine (Offertorium)} \grecommentary[0pt]{Ps 84:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--benedixisti_domine--dominican--id_4304}  \vspace{5pt} \par{You have blessed Your land, O Lord; You have turned away the captivity of Jacob; You have forgiven the iniquity of Your people.} 
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Dicite: Pusillanimes} \label{Dicite: Pusillanimes (Communio)} \grecommentary[10pt]{Cf. Is 35:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicite_pusillanimes--dominican--id_5719}  \vspace{5pt} \par{Say to the faint-hearted: ``Take courage and fear not; behold, our God will come and save us."} 

\section{In Feriis Adventus}               
\subsection{A die 17 ad diem 24 decembris}               

\subsection{Feria Secunda}               




\subsection{Feria Tertia}               




\subsection{Feria Quarta}               




\subsection{Feria Quinta}               


\subsection{Feria Sexta}               


\subsection{Sabbato}               


\section{Cantus ad lectiones apti pro diebus 19 et 20 decembris:}               
\subsection{Die 19 decembris}               

\subsection{Die 20 decembris}               

\section{Dominica quarta Adventus}               
 \subsubsection{Officium}  \greannotation{I} \index[Officium]{Rorate cæli} \label{Rorate cæli (Officium)} \grecommentary[5pt]{Is 45:8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--rorate--dominican--id_5489}  \vspace{5pt} \par{Drop down dew, you heavens, from above, and let the clouds rain the just; let the earth be opened and bud forth a Savior. \Vbar. And let justice spring up together: I the Lord have created him.} 
 \subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Prope est Dominus} \label{Prope est Dominus (Responsorium)} \grecommentary[0pt]{Ps 144:18; \Vbar. 21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--prope_est_dominus--dominican--id_6717}  \vspace{5pt} \par{The Lord is near to all who call upon Him; to all who call upon Him in truth. \Vbar. My mouth shall speak the praise of the Lord; and let all flesh bless His holy name.} 
 \subsubsection{Alleluia}  \greannotation{III} \index[Alleluia]{Veni Domine} \label{Veni Domine (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--veni_domine--dominican--id_4958}  \vspace{5pt} \par{Come, O Lord, and do not delay: forgive the sins of Your people.} 
 \subsubsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Ave Maria [Dominica quarta Adventus]} \label{Ave Maria [Dominica quarta Adventus] (Offertorium)} \grecommentary[0pt]{Lc 1:28, 42} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--ave_maria_et_benedictus--dominican--id_4781}  \vspace{5pt} \par{Hail Mary, full of grace, the Lord is with you. Blessed are you among women, and blessed is the fruit of your womb.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Ecce virgo} \label{Ecce virgo (Communio)} \grecommentary[3pt]{Is 7:14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ecce_virgo--dominican--id_6887}  \vspace{5pt} \par{Behold, a virgin shall conceive and bring forth a son, and His name shall be called Emmanuel.} 
\section{Die 24 decembris, ad Missam matutinam}               


\chapter{Tempus Nativitatis}               
\section{In Nativitate Domini}               
\subsection{Ad Missam in vigilia}               




 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Revelabitur} \label{Revelabitur (Communio)} \grecommentary[0pt]{Cf. Is 40:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--revelabitur--dominican--id_7068}  \vspace{5pt} \par{The glory of the Lord shall be revealed, and all flesh shall see the salvation of our God.} 
\subsection{Ad Missam in nocte}               
 \subsubsection{Officium}  \greannotation{II} \index[Officium]{Dominus dixit} \label{Dominus dixit (Officium)} \grecommentary[0pt]{Ps 2:7; \Vbar. 1, 2, 8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--dominus_dixit--dominican--id_6135-antiphon-only}  \vspace{5pt} \par{The Lord said to me: ``You are my Son, this day have I begotten you.'' \par \Vbar.\textsuperscript{1} Why have the Gentiles raged, and the people devised vain things? \par \Vbar.\textsuperscript{2} The kings of the earth stand by, and the princes come together as one against the Lord, and against his Christ. \par \Vbar.\textsuperscript{8} Ask of me, and I will give you the nations as your inheritance, and the ends of the earth as your possession.} 
 \subsubsection{Versus Officii}  \greannotation{II} \index[Versus Officii]{Dominus dixit (Verses)} \label{Dominus dixit (Verses) (Versus Officii)} \grecommentary[0pt]{Ps 2:7; \Vbar. 1, 2, 8} \gresetinitiallines{0}  \grechangedim{spaceabovelines}{0pt}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--dominus_dixit--dominican--id_6135-verses-only}  \vspace{5pt} \par{} 
 \subsubsection{Responsorium}  \greannotation{II} \index[Responsorium]{Tecum principium} \label{Tecum principium (Responsorium)} \grecommentary[0pt]{Ps 109:3; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--tecum_principium--dominican--id_6602}  \vspace{5pt} \par{Yours is princely power in the day of Your strength. In the brightness of the saints, from the womb before the day-star I begot You. \Vbar. The Lord said to my Lord: ``Sit at my right hand until I make Your enemies Your footstool.''} 
 \subsubsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Dominus dixit} \label{Dominus dixit (Alleluia)} \grecommentary[0pt]{Ps 2:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--dominus_dixit--dominican--id_6629}  \vspace{5pt} \par{The Lord said to me: ``You are my son, this day have I begotten You. Alleluia!''} 
 \subsubsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Lætentur cæli} \label{Lætentur cæli (Offertorium)} \grecommentary[0pt]{Ps 95:11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--laetentur_caeli--dominican--id_7062}  \vspace{5pt} \par{Let the heavens rejoice, and let the earth be glad before the face of the Lord, because He comes.} 
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{In splendoribus} \label{In splendoribus (Communio)} \grecommentary[0pt]{Ps 109:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--in_splendoribus--dominican--id_7236}  \vspace{5pt} \par{In the brightness of the saints, from the womb before the day-star I begot You.} \vspace{10pt}
\subsection{Ad Missam in aurora}               
 \subsubsection{Officium}  \greannotation{VIII} \index[Officium]{Lux fulgebit} \label{Lux fulgebit (Officium)} \grecommentary[7pt]{Cf. Is 9:2, 6; Lc 1:33; Ps 92:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--lux_fulgebit--dominican--id_6395}  \vspace{5pt} \par{A light shall shine upon us this day, for our Lord is born to us; and He shall be called Wonderful, God, the Prince of peace, the Father of the world to come: of whose reign there shall be no end. \Vbar. The Lord has reigned, He is clothed with beauty; the Lord is clothed with strength, and has girded Himself with power.} \vspace{10pt}




\subsection{Ad Missam in die}               
 \subsubsection{Officium}  \greannotation{VII} \index[Officium]{Puer natus est} \label{Puer natus est (Officium)} \grecommentary[3pt]{Is 9:6; Ps 97:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--puer_natus_est--dominican--id_5324}  \vspace{5pt} \par{A child is born to us and a son is given to us, whose government is upon His shoulders; and His name shall be called the angel of great counsel. \Vbar. Sing to the Lord a new canticle, for He has done wonderful things.} 
 \subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Viderunt omnes} \label{Viderunt omnes (Responsorium)} \grecommentary[3pt]{Ps 97:3, 4; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--viderunt_omnes--dominican--id_5602}  \vspace{5pt} \par{All the ends of the earth have seen the salvation of our God. Sing joyfully to God, all the earth. \Vbar. The Lord has made known His salvation; He has revealed His justice in the sight of the Gentiles.} 
 \subsubsection{Alleluia}  \greannotation{II} \index[Alleluia]{Dies sanctificatus} \label{Dies sanctificatus (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--dies_sanctificatus--dominican--id_6593}  \vspace{5pt} \par{A sanctified day has shone upon us; come you Gentiles, and adore the Lord; for this day a great light has descended upon the earth.} 
 \subsubsection{Sequentia}  \greannotation{VI} \index[Sequentia]{Laetabundus} \label{Laetabundus (Sequentia)} \grecommentary[7pt]{Ecclesia [Proprium 1985]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/se--laetabundus_1985_version--dominican--id_4215}  \vspace{5pt} \par{Let the faithful choir joyfully rejoice, alleluia! The womb of the undefiled one has brought forth the King of Kings: a thing of wonder. The Angel of the counsel is born of the Virgin; the Sun of the Star. The Sun knows no setting, the Star is ever shining, ever bright. As the star brings forth its ray, in like manner the Virgin brings forth her Son. Neither the Star by its ray, nor the Mother by her Son becomes defiled. \par The lofty cedar of Lebanon is conformed to the hyssop in our Valley; The Word, the Being of the Most High, has deigned to become incarnate, having assumed our flesh. Isaias foretold it, the Synagogue remembers it, yet never does it cease to be bound. If not her own prophets, let her at least believe the Gentiles; in the sibylline verses these things were predicted. O Unhappy one, hasten, believe even the ancient legends. Why be cast away, O Chosen Race? Behold the Child whom the Scriptures proclaim. A Maid has borne Him. Alleluia!} 
 \subsubsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Tui sunt cæli} \label{Tui sunt cæli (Offertorium)} \grecommentary[0pt]{Ps 88:12, 15} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--tui_sunt_caeli--dominican}  \vspace{5pt} \par{Yours are the heavens, and Yours is the earth. The world and the fullness thereof You have founded. Justice and judgement are the preparation of Your throne.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Viderunt omnes} \label{Viderunt omnes (Communio)} \grecommentary[5pt]{Ps 97:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--viderunt_omnes--dominican--id_5158}  \vspace{5pt} \par{All the ends of the earth have seen the salvation of our God.} 

\section{Sanctæ Familiæ Iesu, Mariæ et Ioseph}               






\section{Infra octavam Nativitatis Domini}               


\subsection{Die 29 decembris}               



\section{Sollemnitas Sanctæ Dei Genetricis Mariæ}               
 \subsubsection{Officium}  \greannotation{II} \index[Officium]{Salve sancta Parens} \label{Salve sancta Parens (Officium)} \grecommentary[4pt]{Sedulius, \emph{Carmen Paschale}; \Vbar. Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--salve_sancta_parens--dominican--id_6966}  \vspace{5pt} \par{Hail holy Mother, the Child-Bearer who has brought forth the King, the ruler of heaven and earth for ever. \Vbar. After giving birth, O Virgin, you remained inviolate: Mother of God, intercede for us.} 
 \subsubsection{Officium} Vel: \greannotation{VIII} \index[Officium]{Lux fulgebit} \label{Lux fulgebit (Officium)} \grecommentary[7pt]{Cf. Is 9:2, 6; Lc 1:33; Ps 92:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--lux_fulgebit--dominican--id_6395}  \vspace{5pt} \par{A light shall shine upon us this day, for our Lord is born to us; and He shall be called Wonderful, God, the Prince of peace, the Father of the world to come: of whose reign there shall be no end. \Vbar. The Lord has reigned, He is clothed with beauty; the Lord is clothed with strength, and has girded Himself with power.} 
 \subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Diffusa est} \label{Diffusa est (Responsorium)} \grecommentary[3pt]{Ps 44:3; \Vbar. 5 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--diffusa_est--vatican}  \vspace{5pt} \par{Grace is poured out upon your lips; therefore has God blessed you for ever. \Vbar. For the cause of truth and goodness and righteousness, your right hand shall lead you wonderfully.} 
 \subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Multifarie} \label{Multifarie (Alleluia)} \grecommentary[4pt]{Hebr 1:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--multifarie--dominican--id_4775}  \vspace{5pt} \par{In many ways in the past, God spoke through the prophets; at long last, in these present days, he has spoken to us through his Son.} 
 \subsubsection{Offertorium}  \greannotation{I} \index[Offertorium]{Felix namque} \label{Felix namque (Offertorium)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--felix_namque--dominican}  \vspace{5pt} \par{For you are happy, O holy virgin Mary, and most worthy of all praise, because from you arose the sun of justice, Christ our God.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Exsulta filia Sion} \label{Exsulta filia Sion (Communio)} \grecommentary[0pt]{Zach 9:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--exsulta_filia--dominican--id_6171}  \vspace{5pt} \par{Rejoice greatly, O daughter of Zion, shout for joy, O daughter of Jerusalem; behold your King comes, the holy one, and the Savior of the world.} 
\section{Dominica Secunda Post Nativitatem}               





\subsection{In feriis temporis Nativitatis}               

\subsection{Die 4 ianuarii}               

\section{In Epiphania Domini}               
 \subsubsection{Officium}  \greannotation{II} \index[Officium]{Ecce advenit} \label{Ecce advenit (Officium)} \grecommentary[0pt]{Cf. Mal 3:1; 1 Chron 29:12; \Vbar. Ps 71:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--ecce_advenit--dominican--id_5006}  \vspace{5pt} \par{Behold the Lord the ruler is come, and a kingdom is in His hand, and power and dominion. \Vbar. Give to the king Your judgement, O God, and to the king's son Your justice.} 
 \subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Omnes de Saba} \label{Omnes de Saba (Responsorium)} \grecommentary[0pt]{Is 60:6; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--omnes_de_saba--dominican--id_7014}  \vspace{5pt} \par{All those from Sheba shall come, bringing gold and frankincense, and showing forth praise to the Lord. \Vbar. Arise, and be enlightened, O Jerusalem, for the glory of the Lord is risen upon you.} 
 \subsubsection{Alleluia}  \greannotation{II} \index[Alleluia]{Vidimus stellam} \label{Vidimus stellam (Alleluia)} \grecommentary[0pt]{Cf. Mt 2:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--vidimus_stellam--dominican--id_6342}  \vspace{5pt} \par{We have seen His star in the east, and have come with gifts to adore Him.} 
 \subsubsection{Offertorium}  \greannotation{V} \index[Offertorium]{Reges Tharsis} \label{Reges Tharsis (Offertorium)} \grecommentary[0pt]{Ps 71:10, 11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--reges_tharsis--dominican--id_6426}  \vspace{5pt} \par{The kings of Tharsis and the islands shall offer gifts; the kings of the Arabians and of Sheba shall bring presents; and all the kings of the earth shall adore Him, all nations shall serve Him.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Vidimus stellam} \label{Vidimus stellam (Communio)} \grecommentary[0pt]{Cf. Mt 2:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vidimus_stellam--dominican--id_5896}  \vspace{5pt} \par{We have seen His star in the east, and have come with gifts to adore Him.} 
\subsection{In feriis post Epiphaniam}               

\subsection{Die 7 ianuarii}               


\subsection{Die 8 ianuarii, vel feria tertia post Epiphaniam}               