\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[2\textsuperscript{nd} Sunday in Ordinary Time]{Graduale Novum\\Ordinis Prædicatorum}
\section{2\textsuperscript{nd} Sunday in Ordinary Time}

\input{001_edited}

\newpage


%%Combination
\subsubsection{Officium}  \greannotation{IV} \index[Officium]{Omnis terra} \label{Omnis terra (Officium)} \grecommentary[0pt]{Ps 65:4; \Vbar. 1-2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--omnis_terra--dominican--id_5228}  \vspace{5pt} \par{All the earth shall adore you, O God, and shall sing to You: sing a psalm to Your name, O Most High. \Vbar. Sing joyfully to God, all the earth; sing a psalm to His name; make His praise glorious.} \newpage
\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Misit Dominus} \label{Misit Dominus (Responsorium)} \grecommentary[0pt]{Ps 106:20; \Vbar. 21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--misit_dominus--dominican--id_6504}  \vspace{5pt} \par{The Lord sent His word, and healed them, and delivered them out of their distresses. \Vbar. Let the mercies of the Lord give glory to Him, and His wonderful works to the children of men.} \newpage




\subsubsection{Alleluia}  \greannotation{IV} \index[Alleluia]{Laudate Deum} \label{Laudate Deum (Alleluia)} \grecommentary[0pt]{Ps 148:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--laudate_deum--dominican--id_6780}  \vspace{5pt} \par{Praise God, all his angels; praise him, all his hosts.} \newpage







\subsubsection{Offertorium}  \greannotation{I} \index[Offertorium]{Iubilate Deo universa} \label{Iubilate Deo universa (Offertorium)} \grecommentary[5pt]{Ps 65:1, 2, 16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--iubilate_deo_universa--dominican--id_4862}  \vspace{5pt} \par{Sing joyfully to God, all the earth; sing a psalm to His name; come and hear, and I will tell you, all you who fear God, what things the Lord has done for my soul, alleluia.} \newpage
\subsubsection{Communio} Dom. anno A: \greannotation{II} \index[Communio]{Lætabimur} \label{Lætabimur (Communio)} \grecommentary[5pt]{Ps 19:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--laetabimur--dominican--id_6160}  \vspace{5pt} \par{We will rejoice in Your salvation, and in the name of the Lord our God we shall be exalted.} \newpage
\subsubsection{Communio} Dom. anno B: \greannotation{VIII} \index[Communio]{Dicit Andreas} \label{Dicit Andreas (Communio)} \grecommentary[5pt]{Io 1:41, 42} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicit_andreas--dominican--id_6487}  \vspace{5pt} \par{Andrew said to his brother Simon: ``We have found the Messiah," which means Christ; and he led him to Jesus.} \newpage
\subsubsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Dicit Dominus} \label{Dicit Dominus (Communio)} \grecommentary[5pt]{Io 2:7, 8, 9, 10-11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicit_dominus--dominican--id_5103}  \vspace{5pt} \par{The Lord said, ``Fill the jars with water and take them to the chief steward." When the chief steward had tasted the water made wine, he said to the bridegroom, ``You have kept the good wine until now." This first miracle Jesus worked in the presence of His disciples.} \newpage

\end{document}
