 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Ab occultis meis} \label{Ab occultis meis (Communio)} \grecommentary[0pt]{Ps 18:13, 14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.7cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ab_occultis_meis--dominican--id_5429}  \vspace{5pt} \par{From my secret sins cleanse me, O Lord, and from those of others spare Your servant.} 
 \subsubsection{Communio} Dom. annis A et B: \greannotation{IV} \index[Communio]{Acceptabis sacrificium} \label{Acceptabis sacrificium (Communio)} \grecommentary[0pt]{Ps 50:21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--acceptabilis--dominican--id_7167}  \vspace{5pt} \par{You will accept the sacrifice of justice, oblations and holocausts, upon Your altar, O Lord.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Adoramus te} \label{Adoramus te (Communio)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--adoramus_te--dominican}  \vspace{5pt} \par{We adore you, O Christ, and we bless you, because by your Cross you have redeemed the world.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Adversum me} \label{Adversum me (Communio)} \grecommentary[0pt]{Ps 68:13, 14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--adversum_me--dominican--id_5409}  \vspace{5pt} \par{They who sat in the gate spoke against me; and they who drank wine made songs against me; but I made my prayer to You, O Lord; it is the time, O God, to show Your good will in the multitude of Your mercy.} 
 \subsubsection{Communio} \emph{Vel:} \greannotation{I} \index[Communio]{Amen dico vobis, quidquid} \label{Amen dico vobis, quidquid (Communio)} \grecommentary[3pt]{Mc 11:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quidquid--dominican--id_5918}  \vspace{5pt} \par{Amen, I say to you, all things whatever you ask for in prayer, believe that you shall receive, and it shall be done to you.} \newpage
 \subsubsection{Communio} Dom. annis B et C et in feriis: \greannotation{I} \index[Communio]{Amen dico vobis, quidquid} \label{Amen dico vobis, quidquid (Communio)} \grecommentary[3pt]{Mc 11:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quidquid--dominican--id_5918}  \vspace{5pt} \par{Amen, I say to you, all things whatsoever you ask for in prayer, believe that you shall receive, and it shall be done to you.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Amen dico vobis: quod uni} \label{Amen dico vobis: quod uni (Communio)} \grecommentary[0pt]{Mt 25:40, 34 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quod_uni--vatican}  \vspace{5pt} \par{Amen, I say to you, that what you did to the least of mine, you did to me; come, blessed of my Father, inherit the kingdom that has been prepared for you from the beginning of the world.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Amen dico vobis: quod vos} \label{Amen dico vobis: quod vos (Communio)} \grecommentary[0pt]{Mt 19:28, 29} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quod_vos--dominican--id_4856}  \vspace{5pt} \par{Amen, I say to you, that you, who have left all things and followed Me, shall receive a hundredfold, and shall possess life everlasting. T.P. Alleluia!} 
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Aufer a me} \label{Aufer a me (Communio)} \grecommentary[0pt]{Ps 118:22, 24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--aufer_a_me--dominican--id_6054}  \vspace{5pt} \par{Remove from me reproach and contempt, because I have sought out Your commandments, O Lord; for Your testimonies are my meditation.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Beata viscera} \label{Beata viscera (Communio)} \grecommentary[0pt]{Lc 11:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beata_viscera--dominican}  \vspace{5pt} \par{Blessed is the womb of the Virgin Mary, which bore the Son of the eternal Father.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Beata viscera} \label{Beata viscera (Communio)} \grecommentary[0pt]{Lc 11:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beata_viscera--dominican}  \vspace{5pt} \par{Blessed is the womb of the Virgin Mary, which bore the Son of the eternal Father.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Beata viscera} \label{Beata viscera (Communio)} \grecommentary[0pt]{Lc 11:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beata_viscera--dominican}  \vspace{5pt} \par{Blessed is the womb of the Virgin Mary, which bore the Son of the eternal Father.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Beata viscera} \label{Beata viscera (Communio)} \grecommentary[0pt]{Lc 11:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beata_viscera--dominican}  \vspace{5pt} \par{Blessed is the womb of the Virgin Mary, which bore the Son of the eternal Father.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Beatam me dicent} \label{Beatam me dicent (Communio)} \grecommentary[0pt]{Lc 1:48, 49 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beatam_me_dicent--solesmes-op}  \vspace{5pt} \par{Blessed is the womb of the Virgin Mary, which bore the Son of the eternal Father.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Beati mundo corde} \label{Beati mundo corde (Communio)} \grecommentary[0pt]{Mt 5:8, 9, 10 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beati_mundo_corde--vatican}  \vspace{5pt} \par{Blessed are the pure in heart, for they shall see God; blessed are the peacemakers, for they shall be called sons of God; blessed are those who suffer persecution for the sake of justice, for theirs is the kingdom of heaven.} \newpage
 \subsubsection{Communio} Dom. anno A: \greannotation{I} \index[Communio]{Beati mundo corde} \label{Beati mundo corde (Communio)} \grecommentary[0pt]{Mt 5:8, 9, 10 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beati_mundo_corde--vatican}  \vspace{5pt} \par{Blessed are the pure in heart, for they shall see God; blessed are the peacemakers, for they shall be called sons of God; blessed are those who suffer persecution for the sake of justice, for theirs is the kingdom of heaven.} \newpage
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Beatus servus} \label{Beatus servus (Communio)} \grecommentary[0pt]{Mt 24:46, 47} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beatus_servus--dominican--id_5854}  \vspace{5pt} \par{Blessed is that servant whom his master, when He comes, shall find watching. Amen, I say to you, He will set him over all His goods. \emph{T.P.} Alleluia.} \newpage
 \subsubsection{Communio} Annis A et C: \greannotation{IV} \index[Communio]{Benedicimus Deum} \label{Benedicimus Deum (Communio)} \grecommentary[3pt]{Tob 12:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--benedicimus_deum--dominican--id_4804}  \vspace{5pt} \par{We bless the God of heaven, and before all the living we will praise Him, because He has shown His mercy to us.} \newpage
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Benedicite omnes angeli} \label{Benedicite omnes angeli (Communio)} \grecommentary[0pt]{Dan 3:58} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--benedicite_omnes_angeli--dominican--id_5241}  \vspace{5pt} \par{All you angels of the Lord, bless the Lord; sing a hymn, and exalt Him above all forever.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Benedicta} \label{Benedicta (Communio)} \grecommentary[0pt]{Jud 13:23, 25} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--benedicta--dominican--id_4820}  \vspace{5pt} \par{Blessed are you, O daughter, by the Lord the most high God above all women upon the earth; because He has so magnified your name that your praise shall not depart out of the mouth of men. \emph{T.P.} Alleluia.} \newpage
" \subsubsection{Communio} Dom. annis B et C: \greannotation{II} \index[Communio]{Cantabo Domino} \label{Cantabo Domino (Communio)} \grecommentary[0pt]{Ps 12:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--cantabo_domino--dominican--id_7094}  \vspace{5pt} \par{I will sing to the Lord, who gives me good things, and I will sing praises to the name of the Lord Most High.
} \newpage"
 \subsubsection{Communio} Dom. anno B: \greannotation{I} \index[Communio]{Cantate Domino} \label{Cantate Domino (Communio)} \grecommentary[5pt]{Ps 95:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--cantate_domino--dominican--id_5304}  \vspace{5pt} \par{Sing to the Lord, alleluia. Sing to the Lord, and bless His name. Show forth His salvation from day to day, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Christus resurgens} \label{Christus resurgens (Communio)} \grecommentary[0pt]{Rom 6:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--christus_resurgens--dominican--id_5045}  \vspace{5pt} \par{Christ rising again from the dead, dies now no more, alleluia. Death shall no longer have dominion over Him, alleluia, alleluia.} \newpage
 \subsubsection{Communio} Dom. anno B: \greannotation{VI} \index[Communio]{Circuibo} \label{Circuibo (Communio)} \grecommentary[0pt]{Ps 26:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--circuibo--dominican--id_5503}  \vspace{5pt} \par{I will go round, and offer up in His tabernacle a sacrifice of jubilation; I will sing, and recite a psalm to the Lord.} \newpage
 \subsubsection{Communio} \emph{Ad libitum:} Dom. anno C: \greannotation{VIII} \index[Communio]{Comedite pinguia} \label{Comedite pinguia (Communio)} \grecommentary[5pt]{2 Esdr 8:10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--comedite_pinguia--dominican--id_6323}  \vspace{5pt} \par{Eat rich meats, and drink sweet wine, and send portions to them who have not prepared for themselves; because it is the holy day of the Lord; be not sad, for the joy of the Lord is our strength.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Confundantur superbi} \label{Confundantur superbi (Communio)} \grecommentary[0pt]{Ps 118:78, 80} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--confundantur}  \vspace{5pt} \par{Let the proud be ashamed because they have been unjust to me; but I will be employed in Your commandments, in Your justifications, that Imay not be confounded.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Cum invocarem} \label{Cum invocarem (Communio)} \grecommentary[0pt]{Ps 4:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--cum_invocarem_te--dominican--id_6660}  \vspace{5pt} \par{When I called upon You, You heard me, O God of my justice; when I was in distress, You enlarged me; have mercy on me, O Lord, and hear my prayer.} \newpage
 \subsubsection{Communio} Anno A: \greannotation{I} \index[Communio]{Data est mihi} \label{Data est mihi (Communio)} \grecommentary[5pt]{Mt 28:18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--data_est_mihi--dominican--id_7085}  \vspace{5pt} \par{All power has been given to Me in heaven and on earth, alleluia. Go, teach all nations, baptizing them in the name of the Father, and of the Son, and of the Holy Spirit, alleluia, alleluia.} \newpage
 \subsubsection{Communio} Anno B: \greannotation{I} \index[Communio]{Data est mihi} \label{Data est mihi (Communio)} \grecommentary[5pt]{Mt 28:18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--data_est_mihi--dominican--id_7085}  \vspace{5pt} \par{All power has been given to Me in heaven and on earth, alleluia. Go, teach all nations, baptizing them in the name of the Father, and of the Son, and of the Holy Spirit, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Date est mihi} \label{Date est mihi (Communio)} \grecommentary[0pt]{Mt 28:18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--data_est_mihi--dominican--id_7085}  \vspace{5pt} \par{All power has been given to Me in heaven and on earth, alleluia. Go, teach all nations, baptizing them in the name of the Father, and of the Son, and of the Holy Spirit, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{De fructo operum tuorum} \label{De fructo operum tuorum (Communio)} \grecommentary[0pt]{Ps 103:13, 14, 15} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--de_fructu--dominican--id_6806}  \vspace{5pt} \par{The earth shall be filled with the fruit of Your works, O Lord, that You may bring bread out of the earth, and that wine may cheer the heart of man; that he may make the face cheerful with oil; and that bread may strengthen man's heart.} \newpage
 \subsubsection{Communio} Dom. anno B: \greannotation{VIII} \index[Communio]{Dicit Andreas} \label{Dicit Andreas (Communio)} \grecommentary[5pt]{Io 1:41, 42} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicit_andreas--dominican--id_6487}  \vspace{5pt} \par{Andrew said to his brother Simon: ``We have found the Messiah," which means Christ; and he led him to Jesus.} \newpage
 \subsubsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Dicit Dominus} \label{Dicit Dominus (Communio)} \grecommentary[5pt]{Io 2:7, 8, 9, 10-11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicit_dominus--dominican--id_5103}  \vspace{5pt} \par{The Lord said, ``Fill the jars with water and take them to the chief steward." When the chief steward had tasted the water made wine, he said to the bridegroom, ``You have kept the good wine until now." This first miracle Jesus worked in the presence of His disciples.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Dicite: Pusillanimes} \label{Dicite: Pusillanimes (Communio)} \grecommentary[10pt]{Cf. Is 35:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dicite_pusillanimes--dominican--id_5719}  \vspace{5pt} \par{Say to the faint-hearted: ``Take courage and fear not; behold, our God will come and save us."} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Dico autem vobis} \label{Dico autem vobis (Communio)} \grecommentary[0pt]{Lc 12:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dico_autem_vobis--dominican--id_6548}  \vspace{5pt} \par{But I say to you, My friends, do not be afraid of those who persecute you.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Dico vobis, gaudium} \label{Dico vobis, gaudium (Communio)} \grecommentary[0pt]{Lc 15:10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dico_vobis--dominican--id_7145}  \vspace{5pt} \par{I say to you, there is joy before the angels of God over one sinner who repents.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Diffusa est} \label{Diffusa est (Communio)} \grecommentary[0pt]{Ps 44:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--diffusa_est--dominican--id_6238}  \vspace{5pt} \par{Grace is poured abroad in your lips; therefore has God blessed you forever. T.P. Alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Dilexisti} \label{Dilexisti (Communio)} \grecommentary[0pt]{Ps 44:8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dilexisti--vatican-op}  \vspace{5pt} \par{You have loved justice, and hated iniquity; therefore God has annointed you, your God. \emph{T.P.} Alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Domine Deus meus} \label{Domine Deus meus (Communio)} \grecommentary[0pt]{Ps 7:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_deus_meus--dominican--id_6239}  \vspace{5pt} \par{O Lord my God, in You have I put my trust; save me from all them who persecute me, and deliver me.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Domine Dominus noster} \label{Domine Dominus noster (Communio)} \grecommentary[4pt]{Ps 8:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_dominus_noster--dominican--id_4994}  \vspace{5pt} \par{O Lord, our Lord, how wonderful is Your name in all the earth.} 
 \subsubsection{Communio} Dom. annis B et C et in feriis: \greannotation{VIII} \index[Communio]{Domine, memorabor} \label{Domine, memorabor (Communio)} \grecommentary[0pt]{Ps 70:16, 17, 18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_memorabor--dominican--id_6241}  \vspace{5pt} \par{O Lord, I will be mindful of Your justice alone; You have taught me, O God, from my youth, and unto old age and grey hairs; O God, forsake me not.} \newpage
 \subsubsection{Communio} Dom. anno A: \greannotation{VII} \index[Communio]{Domine quinque talenta} \label{Domine quinque talenta (Communio)} \grecommentary[3pt]{Mt 25:20, 21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_quinque_talenta--dominican--id_5425}  \vspace{5pt} \par{Lord, you did hand over five talents to me; behold, I have gained five others in addition. Well done, faithful servant, because you have been faithful over a few things, I will set you over many things; enter into the joy of your Master.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Domine quinque talenta} \label{Domine quinque talenta (Communio)} \grecommentary[3pt]{Mt 25:20, 21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_quinque_talenta--dominican--id_5425}  \vspace{5pt} \par{Lord, you did hand over five talents to me; behold, I have gained five others in addition. Well done, faithful servant, because you have been faithful over a few things, I will set you over many things; enter into the joy of your Master.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Domine quinque talenta} \label{Domine quinque talenta (Communio)} \grecommentary[3pt]{Mt 25:20, 21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_quinque_talenta--dominican--id_5425}  \vspace{5pt} \par{Lord, you did hand over five talents to me; behold, I have gained five others in addition. Well done, faithful servant, because you have been faithful over a few things, I will set you over many things; enter into the joy of your Master.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Domine quis habitabit} \label{Domine quis habitabit (Communio)} \grecommentary[0pt]{Ps 14:1, 2a} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domine_quis_habitabit--dominican--id_5994}  \vspace{5pt} \par{The right hand of the Lord has wrought strength, the right hand of the Lord has exalted me. I shall not die, but live, and shall declare the works of the Lord.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Dominus dabit} \label{Dominus dabit (Communio)} \grecommentary[5pt]{Ps 84:13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_dabit--dominican--id_6204}  \vspace{5pt} \par{The Lord will bestow His goodness, and our earth shall yield its fruit.} \newpage
 \subsubsection{Communio} Dom. annis A et C: \greannotation{II} \index[Communio]{Dominus firmamentum} \label{Dominus firmamentum (Communio)} \grecommentary[0pt]{Ps 17:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_firmamentum--dominican--id_6031}  \vspace{5pt} \par{The Lord is my firmament, and my refuge, and my deliverer; my God is my helper.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Dominus Iesus postquam} \label{Dominus Iesus postquam (Communio)} \grecommentary[0pt]{Io 13:12, 13, 15} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_iesus--dominican--id_7200}  \vspace{5pt} \par{The Lord Jesus, after He had supped with His disciples, washed their feet, and said to them, ``Do you know what I, your Lord and Master, have done to you? I have given you an example, that so you also should do."} \newpage
 \subsubsection{Communio} Dom. annis B et C et in feriis: \greannotation{II} \index[Communio]{Dominus regit me} \label{Dominus regit me (Communio)} \grecommentary[0pt]{Ps 22:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_regit_me--dominican--id_5335}  \vspace{5pt} \par{The Lord rules me, and nothing shall I want; in a place of pasture He has placed me; near refreshing waters He has led me.} 
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Dominus virtutum} \label{Dominus virtutum (Communio)} \grecommentary[0pt]{Ps 23:10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_virtutum--dominican--id_6229}  \vspace{5pt} \par{Tum to me, O Lord, and deliver my soul; O save me for Your mercy's sake.} \newpage
 \subsubsection{Communio} Feria 3: \greannotation{VIII} \index[Communio]{Dum venerit Paraclitus} \label{Dum venerit Paraclitus (Communio)} \grecommentary[0pt]{Io 16:8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dum_venerit_paraclitus--vatican-op}  \vspace{5pt} \par{When the Paraclete shall come, the Spirit of Truth, he will accuse the world of sin, and of justice, and of judgment, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Ecce Dominus veniet} \label{Ecce Dominus veniet (Communio)} \grecommentary[0pt]{Cf. Zach 14:5, 7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ecce_dominus_veniet--dominican--id_6607}  \vspace{5pt} \par{Behold the Lord shall come, and all His saints with Him; and in that day there shall be a great light.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Ecce sic} \label{Ecce sic (Communio)} \grecommentary[5pt]{Ps 127:4, 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ecce_sic_benedicetur--dominican--id_5537}  \vspace{5pt} \par{Behold, thus shall every man be blessed who fears the Lord; and may you see your children's children; peace upon Israel. \emph{T.P.} Alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Ecce virgo} \label{Ecce virgo (Communio)} \grecommentary[3pt]{Is 7:14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ecce_virgo--dominican--id_6887}  \vspace{5pt} \par{Behold, a virgin shall conceive and bring forth a son, and His name shall be called Emmanuel.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Ego clamavi} \label{Ego clamavi (Communio)} \grecommentary[3pt]{Ps 16:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_clamavi--dominican}  \vspace{5pt} \par{I have cried to You for You, O God, have heard me; O incline Your ear to me, and hear my words.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Ego sum pastor} \label{Ego sum pastor (Communio)} \grecommentary[5pt]{Io 10:14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_sum_pastor--dominican--id_6143}  \vspace{5pt} \par{I am the Good Shepherd, alleluia, and I know My sheep, and Mine know Me, alleluia, alleluia.} \newpage
 \subsubsection{Communio} Dom. annis B et C: \greannotation{VIII} \index[Communio]{Ego sum vitis vera} \label{Ego sum vitis vera (Communio)} \grecommentary[5pt]{Io 15:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_sum_vitis--dominican--id_7015}  \vspace{5pt} \par{I am the true vine and you are the branches; whoever remains in me, and I in him, bears fruit in plenty, alleluia.} \newpage
 \subsubsection{Communio} Dom. anno B: \greannotation{I} \index[Communio]{Ego vos elegi} \label{Ego vos elegi (Communio)} \grecommentary[0pt]{Io 15:16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_vos_elegi_alleluia--dominican--id_5178}  \vspace{5pt} \par{I have chosen you out of the world that you may go and bring forth fruit; and that your fruit may remain, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Ego vos elegi} \label{Ego vos elegi (Communio)} \grecommentary[0pt]{Io 15:16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_vos_elegi--dominican--id_4728}  \vspace{5pt} \par{I have chosen you out of the world, that you should go and bear fruit, and that your fruit should remain.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Erubescant et conturbentur} \label{Erubescant et conturbentur (Communio)} \grecommentary[0pt]{Ps 6:11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--erubescant_et_conturbentur--dominican--id_6145}  \vspace{5pt} \par{Let all my enemies be put to shame, and be troubled; let them be turned back and put to shame very speedily.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Erubescant et revereantur} \label{Erubescant et revereantur (Communio)} \grecommentary[0pt]{Ps 34:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--erubescant_et_revereantur--dominican--id_6809}  \vspace{5pt} \par{} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Et si coram hominibus} \label{Et si coram hominibus (Communio)} \grecommentary[0pt]{Sap 3:4, 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--et_si_coram--dominican--id_4806}  \vspace{5pt} \par{Let them blush and be ashamed together, who rejoice at my evils; let them be clothed with confusion and shame, who speak malicious things against me.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Exiit sermo} \label{Exiit sermo (Communio)} \grecommentary[0pt]{Io 21:23} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--exiit_sermo--dominican--id_5478}  \vspace{5pt} \par{Let them blush and be ashamed together, who rejoice at my evils; let them be clothed with confusion and shame, who speak malicious things against me.} \newpage

 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Exsulta filia Sion} \label{Exsulta filia Sion (Communio)} \grecommentary[0pt]{Zach 9:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--exsulta_filia--dominican--id_6171}  \vspace{5pt} \par{Rejoice greatly, O daughter of Zion, shout for joy, O daughter of Jerusalem; behold your King comes, the holy one, and the Savior of the world.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Exsultavit ut gigas} \label{Exsultavit ut gigas (Communio)} \grecommentary[0pt]{Ps 18:6, 7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--exsultavit_ut_gigas--dominican--id_5080}  \vspace{5pt} \par{He has rejoiced as a giant to run the way; His going out is from the highest heaven, and His circuit even to the end thereof.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Factus est repente} \label{Factus est repente (Communio)} \grecommentary[0pt]{Act 2:2, 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--factus_est_repente--dominican--id_7482}  \vspace{5pt} \par{Suddenly there came a sound from heaven, as of a violent wind blowing, where they were sitting, alleluia! And they were all filled with the Holy Spirit, speaking the wonderful works of God, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Feci iudicium} \label{Feci iudicium (Communio)} \grecommentary[0pt]{Ps 118:121, 122, 128} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--feci_iudicium}  \vspace{5pt} \par{I have done judgment, and justice, O Lord, let not the proud calumniate me; I was directed to all Your commandments; I have hated all wicked ways.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Fidelis servus et prudens} \label{Fidelis servus et prudens (Communio)} \grecommentary[0pt]{Lc 12:42} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--fidelis_servus_alleluia--dominican--id_6516}  \vspace{5pt} \par{A faithful and prudent servant whom the master will set over his household to give them their measure of wheat in due season. \emph{T.P.} Alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Fili, quid fecisti} \label{Fili, quid fecisti (Communio)} \grecommentary[0pt]{Lc 2:48–49} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--fili_quid_fecisti}  \vspace{5pt} \par{``My son, why have you treated us so? Your father and I have been anxiously looking for you." ``How is it that you were seeking me? Did you not know that I must be about my Father's business?"} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Florete flores} \label{Florete flores (Communio)} \grecommentary[0pt]{Sir 39:19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--florete_flores}  \vspace{5pt} \par{Send forth flowers, as the lily, and yield a smell, and bring forth leaves in grace; and praise with canticles, and bless the Lord in His works.} \newpage
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Frumentum Christi sum} \label{Frumentum Christi sum (Communio)} \grecommentary[0pt]{Ecclesia [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--frumentum--vatican-op}  \vspace{5pt} \par{I am the grain of Christ; may I be ground by the teeth of beasts, that the I may be found to be pure bread.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Gaudete iusti} \label{Gaudete iusti (Communio)} \grecommentary[0pt]{Ps 32:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--gaudete_iusti__alleluia--dominican}  \vspace{5pt} \par{Rejoice in the Lord, you just, alleluia. Praise befits the upright, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Gaudete iusti} \label{Gaudete iusti (Communio)} \grecommentary[0pt]{Ps 32:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--gaudete_iusti__alleluia--dominican}  \vspace{5pt} \par{Rejoice in the Lord, you just, alleluia. Praise befits the upright, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Gloriosa} \label{Gloriosa (Communio)} \grecommentary[0pt]{Ps 86:3; Lc 1:49} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--gloriosa--dominican}  \vspace{5pt} \par{Glorious things are told of you, O Mary, for He who is mighty has done great things to you.} \newpage
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Gustate et videte} \label{Gustate et videte (Communio)} \grecommentary[0pt]{Ps 33:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--gustate--dominican--id_5637}  \vspace{5pt} \par{Taste and see that the Lord is sweet; blessed is the man who hopes in Him.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Hoc corpus} \label{Hoc corpus (Communio)} \grecommentary[3pt]{I Cor 11:24, 25} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--hoc_corpus--dominican--id_5947}  \vspace{5pt} \par{``This is my body which is given up for you; this is the chalice of the new covenant in my blood," says the Lord. ``Do this, as often as your receive it, in memory of me."} \newpage
 \subsubsection{Communio} Anno C: \greannotation{VIII} \index[Communio]{Hoc corpus} \label{Hoc corpus (Communio)} \grecommentary[3pt]{I Cor 11:24, 25} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--hoc_corpus--dominican--id_5947}  \vspace{5pt} \par{``This is my body which is given up for you; this is the chalice of the new covenant in my blood," says the Lord. ``Do this, as often as your receive it, in memory of me."} \newpage
 \subsubsection{Communio} Dom. anno B: \greannotation{VI} \index[Communio]{Honora Dominum} \label{Honora Dominum (Communio)} \grecommentary[0pt]{Prov 3:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--honora_dominum--dominican--id_5144}  \vspace{5pt} \par{Honor the Lord with your substance, and with the first of all your fruits; and your barns shall be filled with abundance, and your presses shall run over with wine.} \newpage
 \subsubsection{Communio} Anno B: \greannotation{IV} \index[Communio]{Ierusalem quæ ædificatur} \label{Ierusalem quæ ædificatur (Communio)} \grecommentary[0pt]{Ps 121:3, 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ierusalem_quae--dominican--id_5394}  \vspace{5pt} \par{Jerusalem, which is built as a city, which is compact together; for there did the tribes go up, the tribes of the Lord, to praise Your name, O Lord.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Ierusalem quæ ædificatur} \label{Ierusalem quæ ædificatur (Communio)} \grecommentary[0pt]{Ps 121:3, 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ierusalem_quae--dominican--id_5394}  \vspace{5pt} \par{Jerusalem, which is built as a city, which is compact together; for there did the tribes go up, the tribes of the Lord, to praise Your name, O Lord.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Ierusalem surge} \label{Ierusalem surge (Communio)} \grecommentary[0pt]{Bar 5:5; 4:36} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ierusalem_surge--dominican--id_6773}  \vspace{5pt} \par{Arise, O Jerusalem, and stand on high; and behold the joy that comes to you from your God.} \newpage
 \subsubsection{Communio} Dom. annis B et C: \greannotation{I} \index[Communio]{Illumina faciem tuam} \label{Illumina faciem tuam (Communio)} \grecommentary[0pt]{Ps 30:17, 18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--illumina_faciem--dominican--id_4792}  \vspace{5pt} \par{Let Your face shine upon Your servant, and save me in Your mercy; let me not be confounded, O Lord, for I have called upon You.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{In salutari tuo} \label{In salutari tuo (Communio)} \grecommentary[0pt]{Ps 118:81, 84, 86} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--in_salutari_tuo--dominican--id_6778}  \vspace{5pt} \par{My soul is in Your salvation, and in Your word have I hoped. When will You execute judgment on those who persecute me? The wicked have persecuted me; help me, O Lord my God.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{In splendoribus} \label{In splendoribus (Communio)} \grecommentary[0pt]{Ps 109:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--in_splendoribus--dominican--id_7236}  \vspace{5pt} \par{In the brightness of the saints, from the womb before the day-star I begot You.} \vspace{10pt}
 \subsubsection{Communio} Dom. annis B et C: \greannotation{IV} \index[Communio]{Inclina aurem tuam} \label{Inclina aurem tuam (Communio)} \grecommentary[0pt]{Ps 30:3ab} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--inclina_aurem_tuam--dominican--id_6542}  \vspace{5pt} \par{Bow down Your ear; make haste to deliver me.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Intellege clamorem} \label{Intellege clamorem (Communio)} \grecommentary[0pt]{Ps 5:2, 3, 4a} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--intellige_clamorem--dominican--id_6106}  \vspace{5pt} \par{Understand my cry; hearken to the voice of my prayer, my king, and my God, for, to You will I pray, O Lord.} \newpage
 \subsubsection{Communio} Dom. annis A et C: \greannotation{VIII} \index[Communio]{Introibo} \label{Introibo (Communio)} \grecommentary[5pt]{Ps 42:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--introibo_ad_altare--dominican--id_4851}  \vspace{5pt} \par{I will go to the altar of God; to God who gives joy to my youth.} \newpage
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Iustorum animæ} \label{Iustorum animæ (Communio)} \grecommentary[0pt]{Sap 3:1, 2, 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--iustorum_animae--dominican--id_6276}  \vspace{5pt} \par{The souls of the just are in the hand of God, and the torment of malice shall not touch them; in the sight of the unwise they seemed to die; but they are in peace, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Iustus Dominus} \label{Iustus Dominus (Communio)} \grecommentary[0pt]{Ps 10:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--iustus_dominus--dominican--id_5956}  \vspace{5pt} \par{The Lord is just, and has loved justice; His countenance has beheld righteousness.} \newpage
 \subsubsection{Communio} Dom. anno A: \greannotation{II} \index[Communio]{Lætabimur} \label{Lætabimur (Communio)} \grecommentary[5pt]{Ps 19:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--laetabimur--dominican--id_6160}  \vspace{5pt} \par{We will rejoice in Your salvation, and in the name of the Lord our God we shall be exalted.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Lætabimur} \label{Lætabimur (Communio)} \grecommentary[3pt]{Ps 19:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--laetabimur--dominican--id_6160}  \vspace{5pt} \par{We will rejoice in Your salvation, and in the name of the Lord our God we shall be exalted.} 
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Lætabitur iustus} \label{Lætabitur iustus (Communio)} \grecommentary[0pt]{Ps 63:11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--laetabitur_iustus--dominican--id_6576}  \vspace{5pt} \par{The just man shall rejoice in the Lord, and shall hope in Him; and all the upright in heart shall be praised, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Lavabo inter innocentes} \label{Lavabo inter innocentes (Communio)} \grecommentary[0pt]{Ps 25:6, 7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--lavabo--dominican--id_7091}  \vspace{5pt} \par{I will wash my hands among the innocent, and will compass Your altar, O Lord, that I may bear the voice of Your praise and tell of all Your wondrous works.} \newpage
 \subsubsection{Communio} Anno A (Quando legitur Evangelium de cæco nato): \greannotation{VI} \index[Communio]{Lutum fecit} \label{Lutum fecit (Communio)} \grecommentary[5pt]{Cf. Io 9:6, 11, 38} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--lutum_fecit--dominican--id_6341}  \vspace{5pt} \par{The Lord made clay of spittle, and anointed my eyes, and I went, and washed, and I saw; and I believed in God.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Lux æterna} \label{Lux æterna (Communio)} \grecommentary[5pt]{IV Esdr 2:35; \Vbar. Ps 120:1-8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--lux_aeterna--dominican--id_6519}  \vspace{5pt} \par{May eternal light shine upon them, O Lord, with Your saints forever, because You are merciful. \par \Vbar.\textsuperscript{1} I have lifted up my eyes to the mountains, from whence help shall come to me. \par\Vbar.\textsuperscript{2} My help is from the Lord, who made heaven and earth. \par\Vbar.\textsuperscript{3} May he not suffer your foot to be moved: neither let him slumber that keepeth you. \par\Vbar.\textsuperscript{4} Behold he shall neither slumber nor sleep, that keepeth Israel. \par\Vbar.\textsuperscript{5} The Lord is your keeper, the Lord is thy protection upon thy right hand. \par\Vbar.\textsuperscript{6} The sun shall not burn you by day: nor the moon by night. \par\Vbar.\textsuperscript{7} The Lord keepeth you from all evil: may the Lord keep your soul. \par\Vbar.\textsuperscript{8} May the Lord keep your coming in and thy going out; from henceforth now and for ever.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Magna est gloria eius} \label{Magna est gloria eius (Communio)} \grecommentary[0pt]{Ps 20:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--magna_est--dominican--id_6386}  \vspace{5pt} \par{His glory is great in Your salvation; glory and great beauty shall You lay upon him, O Lord.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Manducaverunt} \label{Manducaverunt (Communio)} \grecommentary[0pt]{Ps 77:29, 30} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--manducaverunt--dominican--id_5897}  \vspace{5pt} \par{They ate and were filled exceedingly, and the Lord gave them their desire; they were not defrauded of that which they craved.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Memento} \label{Memento (Communio)} \grecommentary[0pt]{Ps 118:49, 50} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--memento_verbi_tui--dominican--id_6042}  \vspace{5pt} \par{Be mindful of Your word to Your servant, O Lord, in which You have given me hope; this has comforted me in my humiliation.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Mense septimo} \label{Mense septimo (Communio)} \grecommentary[0pt]{Levit 23:41, 43} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--mense_septimo--dominican--id_6792}  \vspace{5pt} \par{In the seventh month shall you celebrate this feast, as I made the children of Israel to dwell in tabernacles, when I brought them out of the land of Egypt. I am the Lord your God.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Mirabantur omnes} \label{Mirabantur omnes (Communio)} \grecommentary[3pt]{Lc 4:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--mirabantur_omnes--dominican--id_7227}  \vspace{5pt} \par{All marveled at these things that came from the mouth of God.} 
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Mitte manum tuam} \label{Mitte manum tuam (Communio)} \grecommentary[0pt]{Io 20:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--mitte_manum_alleluia--dominican--id_4846}  \vspace{5pt} \par{Put in your hand, and know the place of the nails, alleluia, and be not unbelieving, but believing, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Mitte manum ... alleluia} \label{Mitte manum ... alleluia (Communio)} \grecommentary[0pt]{Io 20:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--mitte_manum_alleluia--dominican--id_4846}  \vspace{5pt} \par{Put in your hand, and know the place of the nails, alleluia, and be not unbelieving, but believing, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Modicum et non} \label{Modicum et non (Communio)} \grecommentary[0pt]{Io 16:16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--modicum--dominican--id_5924}  \vspace{5pt} \par{A little while, and you shall see Me no longer, alleluia! and again a little while, and you shall see Me, because I go to the Father, alleluia, alleluia.} \newpage
 \subsubsection{Communio} Dom. anno B: \greannotation{II} \index[Communio]{Multitudo languentium} \label{Multitudo languentium (Communio)} \grecommentary[3pt]{Lc 6:17, 18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--multitudo_languentium--dominican}  \vspace{5pt} \par{A multitude of the sick, and those who were troubled with unclean spirits, came to him: for power went forth from Him and healed all.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Multitudo languentium} \label{Multitudo languentium (Communio)} \grecommentary[0pt]{Lc 6:17, 18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--multitudo_languentium--dominican}  \vspace{5pt} \par{A multitude of the sick, and those who were troubled with unclean spirits, came to him: for power went forth from Him and healed all.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Narrabo omnia} \label{Narrabo omnia (Communio)} \grecommentary[0pt]{Ps 9:2, 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--narrabo_omnia--dominican--id_6592}  \vspace{5pt} \par{I will declare all Your wonders; I will be glad and rejoice in You; I will sing praise to Your name, O Most High.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Ne tradideris me} \label{Ne tradideris me (Communio)} \grecommentary[0pt]{Ps 26:12} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ne_tradideris--dominican--id_4833}  \vspace{5pt} \par{Deliver me not, O Lord, to the will of them who trouble me, for unjust witnesses have risen up against me, and iniquity has lied to itself.} \newpage
 \subsubsection{Communio} Anno C (Quando legitur Evangelium de muliere adultera): \greannotation{VIII} \index[Communio]{Nemo te condemnavit} \label{Nemo te condemnavit (Communio)} \grecommentary[3pt]{Io 8:10, 11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--nemo_te_condemnavit--dominican--id_7175}  \vspace{5pt} \par{``Has no one condemned you, woman?" ``No one, Lord." ``Neither will I condemn you; now sin no more."} \newpage
 \subsubsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Non vos relinquam} \label{Non vos relinquam (Communio)} \grecommentary[0pt]{Io 14:18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--non_vos_relinquam--dominican--id_6454}  \vspace{5pt} \par{I will not leave you orphans; I will come to you again, alleluia, and your heart shall rejoice, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Notas mihi} \label{Notas mihi (Communio)} \grecommentary[0pt]{Ps 15:11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--notas_mihi--dominican--id_6934}  \vspace{5pt} \par{You have made known to me the ways of life; You shall fill me with joy with Your countenance, O Lord.} 
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Notas mihi} \label{Notas mihi (Communio)} \grecommentary[0pt]{Ps 15:11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--notas_mihi--dominican--id_6934}  \vspace{5pt} \par{You have made known to me the ways of life; You shall fill me with joy with Your countenance, O Lord.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Omnes qui in Christo} \label{Omnes qui in Christo (Communio)} \grecommentary[0pt]{Gal 3:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--omnes_qui_in_christo--dominican--id_5705}  \vspace{5pt} \par{All you who have been baptized in Christ have put on Christ, alleluia.} \newpage
 \subsubsection{Communio} Anno C (Quando legitur Evangelium de filio prodigo): \greannotation{VIII} \index[Communio]{Oportet te} \label{Oportet te (Communio)} \grecommentary[3pt]{Lc 15:32} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--oportet_te_fili--dominican--id_6842}  \vspace{5pt} \par{You ought to rejoice, my son, because Your brother was dead, and has come to life; he was lost, and is found.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Oportet te} \label{Oportet te (Communio)} \grecommentary[0pt]{Lc 15:32} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--oportet_te_fili--dominican--id_6842}  \vspace{5pt} \par{You ought to rejoice, my son, because Your brother was dead, and has come to life; he was lost, and is found.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Optimam partem} \label{Optimam partem (Communio)} \grecommentary[0pt]{Lc 10:42 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--optimam_partem--vatican-op}  \vspace{5pt} \par{Mary has chosen for herself the best portion, which shall never be taken away from her.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Pacem meam ... alleluia} \label{Pacem meam ... alleluia (Communio)} \grecommentary[0pt]{Io 14:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pacem_meam_alleluia--dominican--id_6488}  \vspace{5pt} \par{Peace I leave you, alleluia: My peace I give unto you: alleluia, alleluia.} \newpage
 \subsubsection{Communio} Dom. annis B et C: \greannotation{V} \index[Communio]{Panem de cælo} \label{Panem de cælo (Communio)} \grecommentary[0pt]{Sap 16:20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--panem_de_caelo--dominican--id_6151}  \vspace{5pt} \par{You have given us, O Lord, bread from heaven, having in it all that is delicious, and the sweetness of every taste.} \newpage
 \subsubsection{Communio} Dom. anno A et B: \greannotation{I} \index[Communio]{Panis quem ego dedero} \label{Panis quem ego dedero (Communio)} \grecommentary[0pt]{Io 6:52} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--panis_quem_ego--dominican--id_5825}  \vspace{5pt} \par{The bread that I will give, is My flesh for the life of the world.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Pascha nostrum} \label{Pascha nostrum (Communio)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pascha_nostrum--dominican--id_6187}  \vspace{5pt} \par{Christ our Passover is sacrificed, alleluia; therefore, let us feast with the unleavened bread of sincerity and truth, alleluia, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Pascha nostrum} \label{Pascha nostrum (Communio)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pascha_nostrum--dominican--id_6187}  \vspace{5pt} \par{Christ our Passover is sacrificed, alleluia; therefore, let us feast with the unleavened bread of sincerity and truth, alleluia, alleluia, alleluia.} \newpage
 \subsubsection{Communio} Annis B et C (Quando legitur aliud Evangelium): \greannotation{I} \index[Communio]{Passer invenit} \label{Passer invenit (Communio)} \grecommentary[0pt]{Ps 83:4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--passer_invenit--dominican--id_6674}  \vspace{5pt} \par{The sparrow has found herself a house, and the turtledove a nest where she may lay her young ones: Your altars, O Lord of Hosts, my King, and my God. Blessed are they who dwell in Your house; for ever and ever shall they sing your praise.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Passer invenit} \label{Passer invenit (Communio)} \grecommentary[0pt]{Ps 83:4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--passer_invenit--dominican--id_6674}  \vspace{5pt} \par{The sparrow has found herself a house, and the turtledove a nest where she may lay her young ones: Your altars, O Lord of Hosts, my King, and my God. Blessed are they who dwell in Your house; for ever and ever shall they sing your praise.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Pater cum essem} \label{Pater cum essem (Communio)} \grecommentary[0pt]{Io 17:12, 13, 15} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pater_cum_essem--dominican--id_4810}  \vspace{5pt} \par{Father, while I was with them, I kept them whom You have given Me, alleluia. But now I come to You; I do not pray that You take them out of the world, but that You keep them from evil, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Pater si non potest} \label{Pater si non potest (Communio)} \grecommentary[0pt]{Mt 26:42} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pater_si_non_potest--dominican--id_4841}  \vspace{5pt} \par{Father, if this cup cannot pass away unless I drink it, Your will be done.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Per lignum} \label{Per lignum (Communio)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--per_lignum--dominican--id_4990--good-friday}  \vspace{5pt} \par{By the tree we became slaves, and by the holy cross we have been set free; the fruit of the tree enslaved us, the Son of God redeemed us, alleluia.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Per signum Crucis} \label{Per signum Crucis (Communio)} \grecommentary[3pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--per_signum_crucis--dominican}  \vspace{5pt} \par{By the sign of the cross deliver us from our enemies, O You who are our God.} \newpage
 \subsubsection{Communio} Dom. anno C: \greannotation{I} \index[Communio]{Petite et accipietis} \label{Petite et accipietis (Communio)} \grecommentary[0pt]{Cf. Lc 11:9, 10; Mt 7:7, 8 et 10:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--petite--dominican--id_5618}  \vspace{5pt} \par{Ask, and you shall receive; seek, and you shall find; knock, and it shall be opened to you. For everyone who asks, receives; and he who seeks, finds; and to him who knocks, it shall be opened, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Populus acquisitionis} \label{Populus acquisitionis (Communio)} \grecommentary[0pt]{1 Petr 2:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--populus_acquisitionis--dominican--id_5283}  \vspace{5pt} \par{O purchased people, show forth the virtues of Him, alleluia! who has called you out of darkness into His marvelous light, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Posuerunt mortalia} \label{Posuerunt mortalia (Communio)} \grecommentary[0pt]{Ps 78:2, 11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--posuerunt--dominican--id_6440}  \vspace{5pt} \par{They have given the dead bodies of Your servants, O Lord, as meat for the fowls of the air: the flesh of Your saints to the beasts of the earth. According to the greatness of Your arm take possession of the children of those who have been punished by death.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Posuisti Domine} \label{Posuisti Domine (Communio)} \grecommentary[0pt]{Ps 20:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--posuisti_domine--dominican--id_6199}  \vspace{5pt} \par{You have set on His head, O Lord, a crown of precious stones, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Potum meum} \label{Potum meum (Communio)} \grecommentary[0pt]{Ps 101:10, 13, 14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--potum_meum--dominican--id_5336}  \vspace{5pt} \par{I mingled my drink with tears, because having lifted me up You have cast me down, and I withered like grass; but You, O Lord, continue forever. You shall rise up and have mercy on Zion, because the time to have mercy on her is come.} \newpage
 \subsubsection{Communio} Dom. anno A: \greannotation{VIII} \index[Communio]{Primum quærite} \label{Primum quærite (Communio)} \grecommentary[3pt]{Mt 6:33} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--primum_quaerite--dominican--id_5473}  \vspace{5pt} \par{Seek first the kingdom of God, and all things shall be added unto you, says the Lord.} \newpage
 \subsubsection{Communio} Dom. anno C et in feriis: \greannotation{VIII} \index[Communio]{Primum quærite} \label{Primum quærite (Communio)} \grecommentary[0pt]{Mt 6:33} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--primum_quaerite--dominican--id_5473}  \vspace{5pt} \par{Seek first the kingdom of God, and all things shall be added unto you, says the Lord.} 
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Principes} \label{Principes (Communio)} \grecommentary[0pt]{Ps 118:161, 162} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--principes--dominican--id_5442}  \vspace{5pt} \par{Princes have persecuted me without cause, and my heart has been in awe of Your words. \emph{T.P.} Alleluia.} \newpage
 \subsubsection{Communio} Anno C: \greannotation{I} \index[Communio]{Psallite Domino} \label{Psallite Domino (Communio)} \grecommentary[10pt]{Ps 67:33, 34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--psallite_domino--dominican--id_5669}  \vspace{5pt} \par{Sing to the Lord, who mounts above the heaven of heavens to the East, alleluia.} \newpage
 \subsubsection{Communio} Anno A (Quando legitur Evangelium de Samaritana): \greannotation{VII} \index[Communio]{Qui biberit aquam} \label{Qui biberit aquam (Communio)} \grecommentary[0pt]{Io 4:13, 14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_biberit--dominican--id_4868}  \vspace{5pt} \par{``Whosoever drinks the water that I shall offer," said the Lord (to the Samaritan woman), ``shall have within him a spring of water welling up unto eternal life."} 
 \subsubsection{Communio} Annis A et B: \greannotation{VI} \index[Communio]{Qui manducat} \label{Qui manducat (Communio)} \grecommentary[3pt]{Io 6:57} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_manducat--dominican--id_6212}  \vspace{5pt} \par{He who eats My flesh, and drinks My blood, abides in Me, and I in him, says the Lord.} \newpage
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Qui meditabitur} \label{Qui meditabitur (Communio)} \grecommentary[0pt]{Ps 1:2–3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_meditabitur--dominican--id_6589}  \vspace{5pt} \par{He who shall meditate upon the law of the Lord, day and night, shall bring forth his fruit in due season.} \newpage
 \subsubsection{Communio} Anno B (Quando legitur aliud Evangelium): \greannotation{V} \index[Communio]{Qui mihi ministrat} \label{Qui mihi ministrat (Communio)} \grecommentary[5pt]{Io 12:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_mihi_ministrat--dominican--id_6620}  \vspace{5pt} \par{If anyone serves Me, let him follow Me: and where I am, there also shall my servant be.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Qui mihi ministrat} \label{Qui mihi ministrat (Communio)} \grecommentary[5pt]{Io 12:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_mihi_ministrat--dominican--id_6620}  \vspace{5pt} \par{If anyone serves Me, let him follow Me: and where I am, there also shall my servant be.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Qui vult venire post me} \label{Qui vult venire post me (Communio)} \grecommentary[0pt]{Mt 16:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_vult_venire--dominican--id_6924}  \vspace{5pt} \par{He who wishes to come after Me, let him deny himself, and take up his cross and follow Me.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Quicumque fecerit} \label{Quicumque fecerit (Communio)} \grecommentary[0pt]{Mt 12:50} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--quicumque_fecerit}  \vspace{5pt} \par{Whoever does the will of My Father in heaven, he is My brother and sister and mother, says the Lord.} \newpage
 \subsubsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Quinque prudentes virgines} \label{Quinque prudentes virgines (Communio)} \grecommentary[0pt]{Mt 25:4, 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--quinque_prudentes--dominican--id_6027}  \vspace{5pt} \par{The five wise virgins took oil in their vessels with the lamps; at midnight, however, a cry was made: ``Behold, the bridegroom comes; go forth to meet Christ the Lord."} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Quinque prudentes virgines} \label{Quinque prudentes virgines (Communio)} \grecommentary[0pt]{Mt 25:4, 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--quinque_prudentes--dominican--id_6027}  \vspace{5pt} \par{The five wise virgins took oil in their vessels with the lamps; at midnight, however, a cry was made: ``Behold, the bridegroom comes; go forth to meet Christ the Lord."} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Quis dabit} \label{Quis dabit (Communio)} \grecommentary[0pt]{Ps 13:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--quis_dabit--dominican--id_6077}  \vspace{5pt} \par{Who shall bring out of Zion the salvation of Israel? When the Lord shall have turned away the captivity of his people, Jacob shall rejoice and Israel shall be glad.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Quod dico vobis} \label{Quod dico vobis (Communio)} \grecommentary[0pt]{Mt 10:27 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--quod_dico_vobis--vatican-op}  \vspace{5pt} \par{``That which I tell you in the dark, utter in the light,” says the Lord; ``and that which you hear whispered into your ear, proclaim upon the housetops.”} \newpage
 \subsubsection{Communio} In ritu Ordinis Prædicatorum: \greannotation{VII} \index[Communio]{Quotiescumque} \label{Quotiescumque (Communio)} \grecommentary[3pt]{1 Cor 11:26-27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--quotiescumque--dominican--id_4700}  \vspace{5pt} \par{As often as you shall eat this bread, and drink the cup, you proclaim the death of the Lord, until he comes. Therefore, whoever eats this bread or drinks the cup of the Lord unworthily, will be guilty of the body and blood of the Lord, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Redime me Deus} \label{Redime me Deus (Communio)} \grecommentary[0pt]{Ps 24:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--redime_me--dominican--id_6994}  \vspace{5pt} \par{Redeem me, O God of Israel, from all my tribulations.} 
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Responsum accepit} \label{Responsum accepit (Communio)} \grecommentary[0pt]{Lc 2:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--responsum--dominican--id_6009}  \vspace{5pt} \par{Simeon received an answer from the Holy Spirit, that he should not see death, until be had seen the Christ of the Lord.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Revelabitur} \label{Revelabitur (Communio)} \grecommentary[0pt]{Cf. Is 40:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--revelabitur--dominican--id_7068}  \vspace{5pt} \par{The glory of the Lord shall be revealed, and all flesh shall see the salvation of our God.} 
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Salvator mundi} \label{Salvator mundi (Communio)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--salvator_mundi--dominican}  \vspace{5pt} \par{Savior of the world, save us, you have redeemed us by your Cross and Blood; help us, we beseech you, our God.} 
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Scapulis suis} \label{Scapulis suis (Communio)} \grecommentary[0pt]{Ps 90:4–5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--scapulis_suis--dominican--id_6971}  \vspace{5pt} \par{He will overshadow you with His shoulders, and under His wings you shall trust; His truth shall compass you with a shield.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Sedebit} \label{Sedebit (Communio)} \grecommentary[0pt]{Ps 28:10b, 11b} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--sedebit_dominus--dominican--id_7401}  \vspace{5pt} \par{The Lord shall sit as a King forever; the Lord will bless His people with peace.} 
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Semel iuravi} \label{Semel iuravi (Communio)} \grecommentary[0pt]{Ps 88:36, 37, 38} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--semel_iuravi--dominican--id_5851}  \vspace{5pt} \par{Once have I sworn by My holiness; His seed shall endure forever; and His throne as the sun before me, and as the moon perfect forever, and a faithful witness in heaven. \emph{T.P.} Alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Servite Domino} \label{Servite Domino (Communio)} \grecommentary[0pt]{Ps 2:11–12} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--servite_domino--dominican--id_5572}  \vspace{5pt} \par{Serve the Lord with fear and rejoice before Him with trembling; embrace discipline, lest you perish from the just way.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Si consurrexistis} \label{Si consurrexistis (Communio)} \grecommentary[0pt]{Col 3:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--si_consurrexistis--dominican--id_5184}  \vspace{5pt} \par{If you have risen with Christ, seek the things that are above, where Christ is sitting at the right hand of God, alleluia. Mind the things that are above, alleluia.} \newpage
 \subsubsection{Communio} Anno B: Psallite Domino, \emph{ut infra, vel:} \greannotation{VII} \index[Communio]{Signa} \label{Signa (Communio)} \grecommentary[10pt]{Mk 16:17, 18 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--signa_eos--vatican-op}  \vspace{5pt} \par{These signs will accompany those who believe: they will cast out demons; they will lay their hands upon the sick, and these will recover, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Signa eos} \label{Signa eos (Communio)} \grecommentary[0pt]{Mc 16:17, 18 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--signa_eos--vatican-op}  \vspace{5pt} \par{These signs will accompany those who believe: they will cast out demons; they will lay their hands upon the sick, and these will recover, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Simile est} \label{Simile est (Communio)} \grecommentary[0pt]{Mt 13:45, 46} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--simile_est--dominican--id_6271}  \vspace{5pt} \par{The kingdom of heaven is like a merchant in search of fine pearls; who, when he had found one pearl of great price, gave all that he had, and bought it. \emph{T.P.} Alleluia.} \newpage
 \subsubsection{Communio} Dom. anno C: \greannotation{VI} \index[Communio]{Simon Ioannis} \label{Simon Ioannis (Communio)} \grecommentary[3pt]{Io 21:15, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--simon_ioannis--dominican--id_5102}  \vspace{5pt} \par{``Simon, son of John, do you love Me more than these do?" ``Lord, You know all things; You know, Lord, that I love You."} \newpage

 \subsubsection{Communio} Feria 2: \greannotation{VIII} \index[Communio]{Spiritus qui a Patre} \label{Spiritus qui a Patre (Communio)} \grecommentary[0pt]{Io 15:26; 16:14; 17:1, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--spiritus_qui_a_patre--dominican--id_6662}  \vspace{5pt} \par{The Spirit who proceeds from the Father, alleluia. He shall glorify me, alleluia, alleluia.} \newpage
 \subsubsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Spiritus Sanctus docebit vos} \label{Spiritus Sanctus docebit vos (Communio)} \grecommentary[5pt]{Io 14:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--spiritus_sanctus--dominican--id_4850}  \vspace{5pt} \par{The Holy Spirit shall teach you, alleluia, whatsoever I have said to you, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Spiritus ubi vult} \label{Spiritus ubi vult (Communio)} \grecommentary[0pt]{Io 3:8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--spiritus_ubi_vult--dominican--id_6930}  \vspace{5pt} \par{The Spirit breathes where He will, and you hear His voice, alleluia! but you know not whence He comes nor whither He goes, alleluia, alleluia, alleluia!} \newpage

 \subsubsection{Communio} Dom. anno A: \greannotation{VI} \index[Communio]{Surrexit Dominus} \label{Surrexit Dominus (Communio)} \grecommentary[3pt]{Lc 24:34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--surrexit_dominus--dominican--id_7481}  \vspace{5pt} \par{The Lord has risen, and has appeared to Peter, alleluia.} \newpage
 \subsubsection{Communio} Dom. anno A: \greannotation{IV} \index[Communio]{Tanto tempore} \label{Tanto tempore (Communio)} \grecommentary[0pt]{Io 14:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tanto_tempore--dominican--id_6774}  \vspace{5pt} \par{Have I been so long a time with you, and have you not known Me? Philip, he who sees Me, sees the Father also, alleluia. Do you not believe that I am in the Father, and the Father in Me? Alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Tanto tempore} \label{Tanto tempore (Communio)} \grecommentary[0pt]{Io 14:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tanto_tempore--dominican--id_6774}  \vspace{5pt} \par{Have I been so long a time with you, and have you not known Me? Philip, he who sees Me, sees the Father also, alleluia. Do you not believe that I am in the Father, and the Father in Me? Alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Tolle puerum} \label{Tolle puerum (Communio)} \grecommentary[0pt]{Mt 2:20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tolle_puerum--dominican--id_6020}  \vspace{5pt} \par{Take the child and His mother and go into the land of Israel, for they are dead who sought the life of the child.} \newpage
 \subsubsection{Communio} Dom. anno A et in feriis: \greannotation{IV} \index[Communio]{Tollite hostias} \label{Tollite hostias (Communio)} \grecommentary[0pt]{Ps 95:8, 9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tollite_hostias--dominican--id_7153}  \vspace{5pt} \par{Bring up sacrifices, and come into His courts; adore the Lord in His holy court.} \newpage
 \subsubsection{Communio}  \greannotation{III} \index[Communio]{Tu Domine servabis} \label{Tu Domine servabis (Communio)} \grecommentary[0pt]{Ps 11:8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tu_domine_servabis--dominican--id_5604}  \vspace{5pt} \par{You, O Lord, will preserve us and keep us from this generation forever.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Tu es Petrus} \label{Tu es Petrus (Communio)} \grecommentary[0pt]{Mt 16:18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tu_es_petrus--dominican--id_5396}  \vspace{5pt} \par{You are Peter, and upon this rock I will build My Church.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Tu mandasti} \label{Tu mandasti (Communio)} \grecommentary[0pt]{Ps 118:4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tu_mandasti--dominican--id_4828}  \vspace{5pt} \par{You have commanded Your commandments to be kept most diligently. O that my ways may be directed to keep Your justifications!} \newpage
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Tu, puer} \label{Tu, puer (Communio)} \grecommentary[0pt]{Lc 1:76} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tu_puer--dominican--id_5886}  \vspace{5pt} \par{You, child, shall be called the prophet of the Most High, for you shall go before the face of the Lord, to prepare His ways.} \newpage
 \subsubsection{Communio}  \greannotation{V} \index[Communio]{Ultimo} \label{Ultimo (Communio)} \grecommentary[0pt]{Io 7:37-39} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ultimo_festivitatis--dominican--id_5123}  \vspace{5pt} \par{On the last day of the feast, Jesus said, ``He who believes in Me, out of his stomach shall flow rivers of living water;” but this He said of the Spirit whom they should receive who believed in Him, alleluia, alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Unam petii} \label{Unam petii (Communio)} \grecommentary[0pt]{Ps 26:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--unam_petii--dominican--id_6081}  \vspace{5pt} \par{One thing I have asked of the Lord, this will I seek after: that I may dwell in the house of the Lord all the days of my life.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Unus militum} \label{Unus militum (Communio)} \grecommentary[0pt]{Io 19:34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--unus_militum--dominican--id_5392}  \vspace{5pt} \par{One of the soldiers opened His side with a lance, and immediately there came out blood and water.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Veni, Domine} \label{Veni, Domine (Communio)} \grecommentary[0pt]{Cf. Hab 2:3 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--veni_domine--solesmes_1974-op}  \vspace{5pt} \par{Come, O Lord, and do not delay; forgive the crimes of your people.} \newpage
 \subsubsection{Communio} \emph{Ad libitum:} Dom. annis A et B: \greannotation{VIII} \index[Communio]{Venite post me} \label{Venite post me (Communio)} \grecommentary[5pt]{Mt 4:19-20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--venite_post_me--dominican--id_7007}  \vspace{5pt} \par{Come, follow Me, I will make you fishers of men: at that, they left the nets and boat and followed the Lord.} \newpage
 \subsubsection{Communio} Anno A (Quando legitur Evangelium de Lazaro): \greannotation{I} \index[Communio]{Videns Dominus flentes} \label{Videns Dominus flentes (Communio)} \grecommentary[3pt]{Io 11:33, 35, 43, 44, 39} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--videns_dominus--dominican--id_7057}  \vspace{5pt} \par{When the Lord saw the sisters of Lazarus in tears near the tomb, He wept in the presence of the Jews, and cried out: ``Lazarus, come forth!" And he came forth, with bound feet and hands, he who had been dead four days.} \newpage
 \subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Video cælos apertos} \label{Video cælos apertos (Communio)} \grecommentary[0pt]{Act 7:56, 59, 60} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--video_caelos--dominican--id_7087}  \vspace{5pt} \par{I see the heavens opened, and Jesus standing on the right hand of the power of God: Lord Jesus, receive my spirit, and do not lay this sin against them.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Viderunt omnes} \label{Viderunt omnes (Communio)} \grecommentary[5pt]{Ps 97:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--viderunt_omnes--dominican--id_5158}  \vspace{5pt} \par{All the ends of the earth have seen the salvation of our God.} \newpage
 \subsubsection{Communio}  \greannotation{IV} \index[Communio]{Vidimus stellam} \label{Vidimus stellam (Communio)} \grecommentary[0pt]{Cf. Mt 2:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vidimus_stellam--dominican--id_5896}  \vspace{5pt} \par{We have seen His star in the east, and have come with gifts to adore Him.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Vincenti dabo} \label{Vincenti dabo (Communio)} \grecommentary[8pt]{Apoc 2:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vincenti_dabo--dominican--id_6089}  \vspace{5pt} \par{To Vincent I will give to eat of the tree of life, which is in the paradise of my God. \emph{T.P.} Alleluia.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Visionem quam vidistis} \label{Visionem quam vidistis (Communio)} \grecommentary[0pt]{Mt 17:9 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--visionem--vatican}  \vspace{5pt} \par{Of the vision you have seen, tell no one until the Son of Man has risen from the dead.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Visionem} \label{Visionem (Communio)} \grecommentary[0pt]{Mt 17:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--visionem--vatican}  \vspace{5pt} \par{Of the vision you have seen, tell no one until the Son of Man has risen from the dead.} \newpage
 \subsubsection{Communio}  \greannotation{VI} \index[Communio]{Voce mea} \label{Voce mea (Communio)} \grecommentary[0pt]{Ps 3:5, 7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--voce_mea--dominican--id_6687}  \vspace{5pt} \par{I have cried to the Lord with my voice, and He has heard me from His holy mountain. I will not fear thousands of the people surrounding me.} \newpage
 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Vos qui secuti ... tribus Israel} \label{Vos qui secuti ... tribus Israel (Communio)} \grecommentary[0pt]{Mt 19:28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vos_qui_secuti--dominican--id_5171}  \vspace{5pt} \par{You who have followed Me shall sit on seats judging the twelve tribes of Israel.} 
 \subsubsection{Communio}  \greannotation{II} \index[Communio]{Vovete} \label{Vovete (Communio)} \grecommentary[0pt]{Ps 75:12, 13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vovete--dominican--id_4748}  \vspace{5pt} \par{Vow and pay to the Lord your God, all you who round about Him bring presents; to Him who is terrible, even to Him who takes away the spirit of princes; to the terrible with all the kings of the earth.} \newpage
 \subsubsection{Communio}  \greannotation{VII} \index[Communio]{Vox in Rama audita est} \label{Vox in Rama audita est (Communio)} \grecommentary[3pt]{Mt 2:18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vox_in_rama--dominican--id_4760}  \vspace{5pt} \par{A voice was heard in Rama, weeping and loud lamentation: Rachel weeping for her children; she would not be comforted, because they are no more.} \newpage