\input{000_header}


\chapter[3\textsuperscript{rd} Sunday in Ordinary Time]{Graduale Novum\\Ordinis Prædicatorum}
\section{3\textsuperscript{rd} Sunday in Ordinary Time}

\input{001_edited}

\newpage


%%Combination

\subsubsection{Officium} Dom. annis A et B: \greannotation{I} \index[Officium]{Dominus secus mare} \label{Dominus secus mare (Officium)} \grecommentary[7pt]{Mt 4:18, 19; \Vbar. 20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--dominus_secus_mare--dominican--id_4298}  \vspace{5pt} \par{The Lord, walking by the sea of Galilee, saw two brothers, Peter and Andrew, and He called out to them: ``Come after Me; I will make you fishers of men.'' \Vbar. At that, leaving their nets and their boat, they followed Him.} \newpage
\subsubsection{Officium} Dom. anno C et in feriis: \greannotation{VII} \index[Officium]{Adorate Deum} \label{Adorate Deum (Officium)} \grecommentary[5pt]{Ps 96:7-8; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--adorate_deum--dominican--id_5980}  \vspace{5pt} \par{Adore God, all you His angels. Zion heard, and was glad; and the daughters of Judah rejoiced. \Vbar. The Lord has reigned; let the earth rejoice; let the multitude of the islands be glad.} \newpage
\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Timebunt gentes} \label{Timebunt gentes (Responsorium)} \grecommentary[5pt]{Ps 101:16; \Vbar. 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--timebunt_gentes--dominican--id_4967}  \vspace{5pt} \par{The nations shall fear Your name, O Lord, and all the kings of the earth Your glory. \Vbar. For the Lord has built up Zion, and He shall be seen in His majesty.} \newpage




\subsubsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Dominus regnavit exsultet} \label{Dominus regnavit exsultet (Alleluia)} \grecommentary[0pt]{Ps 96:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--dominus_regnavit_exsultet--dominican--id_6766}  \vspace{5pt} \par{The Lord has reigned, let the earth rejoice; let the multitude of the islands be glad.} \newpage



\subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{Dextera Domini} \label{Dextera Domini (Offertorium)} \grecommentary[5pt]{Ps 117:16, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--dextera_domini--dominican--id_4758}  \vspace{5pt} \par{The right hand of the Lord has wrought strength; the right hand of the Lord has exalted me. I shall not die, but live, and shall declare the works of the Lord.} \newpage
\subsubsection{Communio}  \greannotation{VII} \index[Communio]{Mirabantur omnes} \label{Mirabantur omnes (Communio)} \grecommentary[3pt]{Lc 4:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--mirabantur_omnes--dominican--id_7227}  \vspace{5pt} \par{All marveled at these things that came from the mouth of God.} \newpage
\subsubsection{Communio} \emph{Ad libitum:} Dom. annis A et B: \greannotation{VIII} \index[Communio]{Venite post me} \label{Venite post me (Communio)} \grecommentary[5pt]{Mt 4:19-20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--venite_post_me--dominican--id_7007}  \vspace{5pt} \par{Come after Me; I will make you fishers of men; at that, leaving their nets and their boat, they followed the Lord.} \newpage
\subsubsection{Communio} \emph{Ad libitum:} Dom. anno C: \greannotation{VIII} \index[Communio]{Comedite pinguia} \label{Comedite pinguia (Communio)} \grecommentary[5pt]{2 Esdr 8:10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--comedite_pinguia--dominican--id_6323}  \vspace{5pt} \par{Eat rich meats, and drink sweet wine, and send portions to those who have not prepared for themselves; this is a holy day of the Lord; do not be saddened, for the joy of the Lord is our strength.} \newpage

\end{document}
