\input{000_header}

\chapter[4\textsuperscript{th} Sunday in Ordinary Time]{Graduale Novum\\Ordinis Prædicatorum}
\section{4\textsuperscript{th} Sunday in Ordinary Time}

\input{001_edited}

\newpage


%%Combination
\subsubsection{Officium}  \greannotation{II} \index[Officium]{Lætetur cor} \label{Lætetur cor (Officium)} \grecommentary[0pt]{Ps 104:3, 4; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--laetetur_cor--dominican--id_6129}  \vspace{5pt} \par{Let the hearts of those who seek the Lord rejoice. Seek the Lord, and be strengthened; seek His face always. \Vbar. Give praise to the Lord, and call upon His name; declare His works among the nations.} \newpage
\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Quis sicut Dominus} \label{Quis sicut Dominus (Responsorium)} \grecommentary[0pt]{Ps 112:5, 6; \Vbar. 7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--quis_sicut_dominus--dominican--id_5616}  \vspace{5pt} \par{Who is like the Lord our God, who dwells on high, looking down on the lowly in heaven and on earth? \Vbar. Raising up the needy from the earth, and lifting up the poor out of the dunghill.} \newpage

\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Adorabo ad templum} \label{Adorabo ad templum (Alleluia)} \grecommentary[0pt]{Ps 137:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--adorabo--dominican--id_5217}  \vspace{5pt} \par{I will worship toward Your holy temple, and I will praise Your name.} \newpage
\subsubsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Bonum est confiteri} \label{Bonum est confiteri (Offertorium)} \grecommentary[0pt]{Ps 91:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--bonum_est_confiteri--dominican--id_7242}  \vspace{5pt} \par{It is good to give praise to the Lord, and to sing to Your name, O Most High.} \newpage
\subsubsection{Communio} Dom. anno A: \greannotation{I} \index[Communio]{Beati mundo corde} \label{Beati mundo corde (Communio)} \grecommentary[0pt]{Mt 5:8, 9, 10 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beati_mundo_corde--vatican}  \vspace{5pt} \par{Blessed are the pure in heart, for they shall see God; blessed are the peacemakers, for they shall be called sons of God; blessed are those who are persecuted for the sake of justice, for theirs is the kingdom of heaven.} \newpage
\subsubsection{Communio} Dom. annis B et C et in feriis: \greannotation{I} \index[Communio]{Illumina faciem tuam} \label{Illumina faciem tuam (Communio)} \grecommentary[0pt]{Ps 30:17, 18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--illumina_faciem--dominican--id_4792}  \vspace{5pt} \par{Let Your face shine upon Your servant, and save me in Your mercy; O Lord, let me not be confounded, for I have called upon You.} \newpage

\end{document}
