\input{000_header}

\chapter[6\textsuperscript{th} Sunday in Ordinary Time]{Graduale O.P.}
\section{6\textsuperscript{th} Sunday in Ordinary Time}

\input{001_edited}

\newpage

%%Combination
\subsubsection{Officium}  \greannotation{VI} \index[Officium]{Esto mihi} \label{Esto mihi (Officium)} \grecommentary[0pt]{Ps 30:3, 4; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--esto_mihi--dominican--id_4916}  \vspace{5pt} \par{Be to me a God of protection and a place of refuge, to save me; for You are my strength and my refuge; and for Your name’s sake You will lead me and nourish me. \Vbar. In You, O Lord, have I hoped; let me never be confounded; in Your justice deliver me and rescue me.} \newpage
\subsubsection{Responsorium}  \greannotation{III} \index[Responsorium]{Tu es Deus} \label{Tu es Deus (Responsorium)} \grecommentary[5pt]{Ps 76:15; \Vbar. 16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--tu_es_deus--dominican--id_4883}  \vspace{5pt} \par{You are God, who alone does wonders.  You have made Your power known among the nations. \Vbar. With Your arm you have delivered your people, the children of Israel and of Joseph.} \newpage
\subsubsection{Alleluia}  \greannotation{I} \index[Alleluia]{Cantate Domino (d-a)} \label{Cantate Domino (d-a) (Alleluia)} \grecommentary[3pt]{Ps 97:1 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--cantate_domino_altera_melodia--solesmes}  \vspace{5pt} \par{Sing to the Lord a new song; for the Lord has done wondrous things.} \newpage


\subsubsection{Offertorium}  \greannotation{III} \index[Offertorium]{Benedictus es... in labiis} \label{Benedictus es... in labiis (Offertorium)} \grecommentary[0pt]{Ps 118:12, 13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--benedictus_es_in_labiis--dominican--id_6310}  \vspace{5pt} \par{Blessed are You, O Lord; teach me Your justifications. With my lips I have pronounced all the judgments of Your mouth.} \newpage

\subsubsection{Communio}  \greannotation{I} \index[Communio]{Manducaverunt} \label{Manducaverunt (Communio)} \grecommentary[3pt]{Ps 77:29, 30} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--manducaverunt--dominican--id_5897}  \vspace{5pt} \par{They ate and were filled exceedingly, and the Lord gave them their desire; they were not defrauded of that which they craved.} \newpage

\end{document}
