\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}



%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[9\textsuperscript{th} Sunday in Ordinary Time]{Graduale O.P.}
\section{9\textsuperscript{th} Sunday in Ordinary Time}

\newpage


%%Combination
 \subsection{Officium}  \greannotation{VI} \index[Officium]{Respice in me} \label{Respice in me (Officium)} \grecommentary[0pt]{Ps 24:16, 18; \Vbar. 1-2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--respice_in_me--dominican--id_5226}  \vspace{5pt} \par{Look upon me, and have mercy on me, O Lord, for I am alone and poor; see my abjection and my labor: and forgive me all my sins, O my God. \Vbar. To You, O Lord, have I lifted up my soul; in You, O my God, I put my trust, let me not be ashamed.} \newpage
 \subsection{Responsorium}  \greannotation{V} \index[Responsorium]{Esto mihi in Deum protectorem} \label{Esto mihi in Deum protectorem (Responsorium)} \grecommentary[0pt]{Ps 70:3; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--esto_mihi--dominican--id_5683}  \vspace{5pt} \par{Be to me a God of protection, and a place of refuge, to save me. \Vbar. In You, O God, have I hoped; O Lord, let me never be confounded.} \newpage
 \subsection{Responsorium}  \greannotation{VII} \index[Responsorium]{Iacta} \label{Iacta (Responsorium)} \grecommentary[7pt]{Ps 54:23; \Vbar. 17a, 18b, 19a} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--iacta_cogitatum--dominican--id_6299}  \vspace{5pt} \par{Cast your care upon the Lord, and He will sustain you. \Vbar. While I cried to the Lord, He heard my voice from those who draw near to me.} \newpage




 \subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Deus iudex iustus} \label{Deus iudex iustus (Alleluia)} \grecommentary[10pt]{Ps 7:12} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--deus_iudex--dominican--id_4749}  \vspace{5pt} \par{God is a just judge, strong and patient; is He angry every day?} \newpage
 \subsection{Offertorium}  \greannotation{III} \index[Offertorium]{Sperent in te} \label{Sperent in te (Offertorium)} \grecommentary[5pt]{Ps 9:11, 12, 13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--sperent_in_te--dominican--id_6410}  \vspace{5pt} \par{Let them trust in You who know Your name, O Lord; for You have not forsaken them who seek You. Sing to the Lord who dwells in Zion, for He has not forgotten the cry of the poor.} \newpage



 \subsection{Communio}  \greannotation{VIII} \index[Communio]{Ego clamavi} \label{Ego clamavi (Communio)} \grecommentary[3pt]{Ps 16:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_clamavi--dominican}  \vspace{5pt} \par{I have cried to You for You, O God, have heard me; O incline Your ear to me, and hear my words.} \newpage
 \subsection{Communio} \emph{Vel:} \greannotation{I} \index[Communio]{Amen dico vobis, quidquid} \label{Amen dico vobis, quidquid (Communio)} \grecommentary[3pt]{Mc 11:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quidquid--dominican--id_5918}  \vspace{5pt} \par{Amen I say to you, all things whatever you ask for in prayer, believe that you shall receive, and it shall be done to you.} \newpage

\end{document}
