\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage[normalem]{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[16\textsuperscript{th} Sunday in Ordinary Time]{Graduale Novum\\Ordinis Prædicatorum}
\section{16\textsuperscript{th} Sunday in Ordinary Time}

\input{001_edited}

\newpage


%%Combination
\subsubsection{Officium}  \greannotation{V} \index[Officium]{Ecce Deus adiuvat me} \label{Ecce Deus adiuvat me (Officium)} \grecommentary[0pt]{Ps 53:6, 7 et 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--ecce_deus--dominican--id_6270}  \vspace{5pt} \par{Behold, God is my helper, and the Lord is the protector of my soul; turn back the evils upon my enemies, and in Your truth destroy them, O Lord my protector. \Vbar. O God, in Your name save me, and in Your strength deliver me.} \newpage
\subsubsection{Responsorium} Dom. annis A et C et in feriis: \greannotation{V} \index[Responsorium]{Domine Dominus noster} \label{Domine Dominus noster (Responsorium)} \grecommentary[0pt]{Ps 8:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--domine_dominus_noster--dominican--id_6622}  \vspace{5pt} \par{O Lord, our Lord, how admirable is Your name in the whole earth. \Vbar. For Your magnificence is elevated above the heavens.} \newpage
\subsubsection{Responsorium} Dom. anno B: \greannotation{I} \index[Responsorium]{Si ambulem} \label{Si ambulem (Responsorium)} \grecommentary[0pt]{Ps 22:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--si_ambulem--dominican--id_6258}  \vspace{5pt} \par{If I should walk in the midst of the shadow of death, I will fear no evil, for You are with me, O Lord. \Vbar. Your rod and Your staff have consoled me.} \newpage

\subsubsection{Alleluia}  \greannotation{II} \index[Alleluia]{Eripe me} \label{Eripe me (Alleluia)} \grecommentary[0pt]{Ps 58:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--eripe_me--dominican--id_5523}  \vspace{5pt} \par{Deliver me from my enemies, O my God: and defend me from those who rise up against me.} \newpage

\subsubsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Iustitiæ Domini} \label{Iustitiæ Domini (Offertorium)} \grecommentary[0pt]{Ps 18:9, 11, 12} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--iustitiae_domini--dominican--id_6109}  \vspace{5pt} \par{The precepts of the Lord are right, rejoicing hearts, and His judgments are sweeter than honey and the honeycomb, for Your servant will keep them.} \newpage
\subsubsection{Communio} Dom. annis A et B et in feriis: \greannotation{IV} \index[Communio]{Acceptabis sacrificium} \label{Acceptabis sacrificium (Communio)} \grecommentary[0pt]{Ps 50:21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--acceptabilis--dominican--id_7167}  \vspace{5pt} \par{You will accept the sacrifice of justice, oblations and burnt offerings, upon Your altar, O Lord.} \newpage
\subsubsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Optimam partem} \label{Optimam partem (Communio)} \grecommentary[3pt]{Lc 10:42 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--optimam_partem--vatican-op}  \vspace{5pt} \par{Mary has chosen for herself the best portion, which shall never be taken away from her.} \newpage

\end{document}
