\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[17\textsuperscript{th} Sunday in Ordinary Time]{Graduale Novum\\Ordinis Prædicatorum}
\section{17\textsuperscript{th} Sunday in Ordinary Time}

\input{001_edited}

\newpage


%%Combination
\subsubsection{Officium}  \greannotation{V} \index[Officium]{Deus in loco sancto suo} \label{Deus in loco sancto suo (Officium)} \grecommentary[0pt]{Ps 67:6, 7, 36; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--deus_in_loco--dominican--id_5659}  \vspace{5pt} \par{God is in His holy dwelling place; God, who makes men dwell unanimously in the house, shall Himself give power and strength to His people. \Vbar. Let God arise, and let His enemies be scattered; and let those who hate Him flee from before His face.} \newpage

\subsubsection{Responsorium} Dom. annis A et C et in feriis: \greannotation{V} \index[Responsorium]{In Deo speravit} \label{In Deo speravit (Responsorium)} \grecommentary[0pt]{Ps 27:7; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--in_deo_speravit--dominican--id_5863}  \vspace{5pt} \par{In God has my heart confided, and I have been helped; and my flesh has flourished again; and with my will I will give praise to Him. \Vbar. To You, O Lord, have I cried; O my God, be not silent; depart not from me.} \newpage
\subsubsection{Responsorium} Dom. anno B: \greannotation{VII} \index[Responsorium]{Oculi omnium} \label{Oculi omnium (Responsorium)} \grecommentary[0pt]{Ps 144:15; \Vbar. 16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--oculi_omnium--dominican--id_5738}  \vspace{5pt} \par{The eyes of all hope in You, O Lord; and You give them meat in due season. \Vbar. You open Your hand, and fill every living creature with Your blessing.} \newpage
\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Exultate Deo} \label{Exultate Deo (Alleluia)} \grecommentary[0pt]{Ps 80:2, 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--exultate_deo--dominican--id_7005}  \vspace{5pt} \par{Rejoice to God, our helper; sing aloud to the God of Jacob; begin a pleasing psalm with the lute.} \newpage
\subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{Exaltabo te Domine} \label{Exaltabo te Domine (Offertorium)} \grecommentary[0pt]{Ps 29:2, 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--exaltabo_te--dominican--id_7207}  \vspace{5pt} \par{I will extol You, O Lord, for You have upheld me and have not made my enemies rejoice over me; O Lord, I have cried to You, and You have healed me.} \newpage
\subsubsection{Communio} Dom. anno A et feria 4: \greannotation{VIII} \index[Communio]{Simile est} \label{Simile est (Communio)} \grecommentary[3pt]{Mt 13:45, 46} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--simile_est--dominican--id_6271--no-alleluia}  \vspace{5pt} \par{The kingdom of heaven is like a merchant in search of fine pearls; who, when he had found one pearl of great price, gave all that he had, and bought it.} \newpage
\subsubsection{Communio} Dom. anno B et in feriis: \greannotation{VI} \index[Communio]{Honora Dominum} \label{Honora Dominum (Communio)} \grecommentary[0pt]{Prov 3:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--honora_dominum--dominican--id_5144}  \vspace{5pt} \par{Honor the Lord with your substance, and with the first of all your fruits; and your barns shall be filled with abundance, and your presses shall run over with wine.} \newpage
\subsubsection{Communio} Dom. anno C: \greannotation{I} \index[Communio]{Petite et accipietis} \label{Petite et accipietis (Communio)} \grecommentary[3pt]{Cf. Lc 11:9, 10; Mt 7:7, 8 et 10:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--petite--dominican--id_5618}  \vspace{5pt} \par{Ask, and you shall receive; seek, and you shall find; knock, and it shall be opened to you. For everyone who asks, receives; and he who seeks, finds; and to him who knocks, it shall be opened, alleluia.} \newpage

\end{document}
