\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage[normalem]{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[19\textsuperscript{th} Sunday in Ordinary Time]{Graduale Novum\\Ordinis Prædicatorum}
\section{19\textsuperscript{th} Sunday in Ordinary Time}

\input{001_edited}

\newpage


%%Combination

\subsubsection{Officium}  \greannotation{VII} \index[Officium]{Respice Domine} \label{Respice Domine (Officium)} \grecommentary[0pt]{Ps 73:20, 19, 22, 23; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--respice_domine--dominican--id_5000}  \vspace{5pt} \par{Consider, O Lord, Your covenant, and forsake not forever the souls of Your poor. Arise, O Lord, and judge Your cause, and forget not the voices of those who seek You. \Vbar. Why, O God, have You cast us off forever? Why is Your wrath kindled against the sheep of Your pasture?} \newpage
\subsubsection{Responsorium} Dom. anno A: \greannotation{VIII} \index[Responsorium]{Ostende nobis} \label{Ostende nobis (Responsorium)} \grecommentary[0pt]{Ps 84:8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--ostende_nobis--dominican--id_5522}  \vspace{5pt} \par{Show us, O Lord, Your mercy, and grant us Your salvation. \Vbar. You have blessed Your land, O Lord; You have averted the captivity of Jacob.} \newpage
\subsubsection{Responsorium} Dom. anno B et in feriis: \greannotation{V} \index[Responsorium]{Respice, Domine} \label{Respice, Domine (Responsorium)} \grecommentary[0pt]{Ps 73:20, 19; \Vbar. 22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--respice_domine--dominican--id_5270}  \vspace{5pt} \par{Consider, O Lord, Your covenant, and forsake not forever the souls of Your poor. \Vbar. Arise, O Lord, and judge Your cause: remember the reproach of Your servants.} \newpage
\subsubsection{Responsorium} Dom. anno C: \greannotation{I} \index[Responsorium]{Beata gens} \label{Beata gens (Responsorium)} \grecommentary[3pt]{Ps 32:12; \Vbar. 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--beata_gens--dominican--id_7138}  \vspace{5pt} \par{Blessed is the nation whose God is the Lord; the people whom the Lord has chosen for His inheritance. \Vbar. By the word of the Lord the heavens were established, and all the power of them by the spirit of His mouth.} \newpage
\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Domine refugium} \label{Domine refugium (Alleluia)} \grecommentary[0pt]{Ps 89:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--domine_refugium--dominican--id_5977}  \vspace{5pt} \par{Lord, You have been our refuge, from generation to generation.} \newpage
\subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{In te speravi} \label{In te speravi (Offertorium)} \grecommentary[4pt]{Ps 30:15, 16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--in_te_speravi--dominican--id_6005}  \vspace{5pt} \par{In You have I hoped, O Lord. I said, ``You are my God, my times are in Your hands."} \newpage
\subsubsection{Communio} Dom. anno A et B et in feriis: \greannotation{I} \index[Communio]{Panis quem ego dedero} \label{Panis quem ego dedero (Communio)} \grecommentary[0pt]{Io 6:52} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--panis_quem_ego--dominican--id_5825}  \vspace{5pt} \par{The bread that I will give is My flesh for the life of the world.} \newpage
\subsubsection{Communio} Dom. anno C: \greannotation{III} \index[Communio]{Beatus servus} \label{Beatus servus (Communio)} \grecommentary[3pt]{Mt 24:46, 47} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--beatus_servus--dominican--id_5854--no_alleluia}  \vspace{5pt} \par{Blessed is that servant whom his master, when he comes, shall find watching. Amen, I say to you, over all his goods he will set him.} \newpage

\end{document}
