\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[20\textsuperscript{th} Sunday in Ordinary Time]{Graduale Novum\\Ordinis Prædicatorum}
\section{20\textsuperscript{th} Sunday in Ordinary Time}

\input{001_edited}

\newpage


%%Combination
\subsubsection{Officium}  \greannotation{IV} \index[Officium]{Protector noster} \label{Protector noster (Officium)} \grecommentary[1pt]{Ps 83:10, 11; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--protector_noster--dominican--id_6928}  \vspace{5pt} \par{Behold, O God our protector, and look on the face of Your Christ, for better is one day in Your courts than thousands elsewhere. \Vbar. How lovely are Your tabernacles, O Lord of hosts.} \newpage

\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Bonum est confidere} \label{Bonum est confidere (Responsorium)} \grecommentary[0pt]{Ps 117:8; \Vbar. 9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--bonum_est_confidere--dominican--id_7119}  \vspace{5pt} \par{It is good to confide in the Lord, rather than to have confidence in man. \Vbar. It is good to trust in the Lord, rather than to trust in princes.} \newpage
\subsubsection{Alleluia} Dom. anno A et C et in feriis: \greannotation{VII} \index[Alleluia]{Venite exsultemus} \label{Venite exsultemus (Alleluia)} \grecommentary[0pt]{Ps 94:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--venite_exsultemus--dominican--id_5068}  \vspace{5pt} \par{Come, let us rejoice in the Lord; let us sing joyfully to God our Savior.} \newpage
\subsubsection{Alleluia} Dom. anno B: \greannotation{VII} \index[Alleluia]{Caro mea} \label{Caro mea (Alleluia)} \grecommentary[0pt]{Io 6:56, 57} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--caro_mea--dominican--id_4939}  \vspace{5pt} \par{My flesh is food indeed, and My blood is drink indeed. He who eats My flesh and drinks My blood, abides in Me, and I in him.} \newpage
\subsubsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Immittit angelus} \label{Immittit angelus (Offertorium)} \grecommentary[0pt]{Ps 33:8, 9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--immittit_angelus--dominican--id_6481}  \vspace{5pt} \par{The angel of the Lord encamps around about those who fear Him, and shall deliver them. O taste and see that the Lord is sweet.} \newpage
\subsubsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Domus mea} \label{Domus mea (Communio)} \grecommentary[0pt]{Mt 21:13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domus_mea--dominican--id_7050--no_alleluia}  \vspace{5pt} \par{``My house shall be called a house of prayer," says the Lord. ``In it, all who ask, receive; and he who seeks, finds; and to him who knocks, it shall be opened." \emph{T.P.} Alleluia, alleluia.} \newpage
\subsubsection{Communio} Dom. anno B: \greannotation{VI} \index[Communio]{Qui manducat} \label{Qui manducat (Communio)} \grecommentary[3pt]{Io 6:57} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_manducat--dominican--id_6212--no-alleluia}  \vspace{5pt} \par{He who eats My flesh, and drinks My blood, abides in Me, and I in him, says the Lord.} \newpage
\subsubsection{Communio} Dom. anno C et in feriis: \greannotation{VIII} \index[Communio]{Primum quærite} \label{Primum quærite (Communio)} \grecommentary[3pt]{Mt 6:33} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--primum_quaerite--dominican--id_5473}  \vspace{5pt} \par{Seek first the kingdom of God, and all things shall be added unto you, says the Lord.} \newpage

\end{document}
