\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[23\textsuperscript{th} Sunday in Ordinary Time]{Graduale O.P.}
\section{23\textsuperscript{th} Sunday in Ordinary Time}

\input{001_edited}

\newpage


%%Combination
\subsubsection{Officium}  \greannotation{I} \index[Officium]{Iustus es Domine} \label{Iustus es Domine (Officium)} \grecommentary[4pt]{Ps 118:137, 124; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--iustus_es_domine--dominican--id_4284}  \vspace{5pt} \par{You are just, O Lord, and Your judgment is right; deal with Your servant according to Your mercy. \Vbar. Blessed are the undefiled in the way, who walk in the law of the Lord.} \newpage
\subsubsection{Responsorium} Dom. annis A et B et in feriis: \greannotation{I} \index[Responsorium]{Beata gens} \label{Beata gens (Responsorium)} \grecommentary[3pt]{Ps 32:12; \Vbar. 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--beata_gens--dominican--id_7138}  \vspace{5pt} \par{Blessed is the nation whose God is the Lord; the people whom the Lord has chosen for His inheritance. \Vbar. By the word of the Lord the heavens were established, and all the power of them by the spirit of His mouth.} \newpage
\subsubsection{Responsorium} Dom. anno C: \greannotation{II} \index[Responsorium]{Domine refugium} \label{Domine refugium (Responsorium)} \grecommentary[0pt]{Ps 89:1; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--domine_refugium--dominican--id_6881}  \vspace{5pt} \par{Lord, You have been our refuge from generation to generation. \Vbar. Before the mountains were made, or the earth and the world was formed, from eternity and to eternity You are God.} \newpage

\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Domine exaudi} \label{Domine exaudi (Alleluia)} \grecommentary[0pt]{Ps 101:2 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--domine_exaudi--solesmes-op}  \vspace{5pt} \par{O Lord, hear my prayer, and let my cry come to You.} \newpage

\subsubsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Oravi deum} \label{Oravi deum (Offertorium)} \grecommentary[0pt]{Dan 9:4, 2, 17, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--oravi_deum--dominican--id_6545}  \vspace{5pt} \par{I, Daniel, prayed to my God, saying, ``Hear, O Lord, the prayers of Your servant; let Your face shine upon Your sanctuary, and favorably look down upon this people, upon whom Your name is invoked, O God."} \newpage
\subsubsection{Communio}  \greannotation{II} \index[Communio]{Make and fulfill vows to the Lord your God; all you who are in His circle, bring gifts; to Him who is feared, to Him who takes away the spirit of princes; to Him who is feared by all the kings of the earth.} \label{Make and fulfill vows to the Lord your God; all you who are in His circle, bring gifts; to Him who is feared, to Him who takes away the spirit of princes; to Him who is feared by all the kings of the earth. (Communio)} \grecommentary[0pt]{Ps 75:12, 13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--vovete--dominican--id_4748}  \vspace{5pt} \par{Make a vow and pray to the Lord your God, all you who round about him bring presents: to the venerable one and to Him who takes away the spirit of princes, to the venerable one before all the kings of the earth.} \newpage

\end{document}
