\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsection}{0pt}{10pt}{*0}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\large\sc\center}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\normalsize\it}{\thesubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}



%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[26\textsuperscript{th} Sunday in Ordinary Time]{Graduale O.P.}
\section{26\textsuperscript{th} Sunday in Ordinary Time}

\newpage


%%Combination
 
 \subsection{Officium} Dom. anno A: \greannotation{III} \index[Officium]{In nomine Domini} \label{In nomine Domini (Officium)} \grecommentary[8pt]{Phil 2:10, 8, 11; \Vbar. Ps 101:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--in_nomine_domini--dominican}  \vspace{5pt} \par{At the name of the Lord every knee should bend, of those in heaven, on earth and under the earth, for the Lord became obedient unto death, even to death on a Cross. Therefore our Lord Jesus Christ is in the glory of God the Father. \Vbar. O Lord, hear my prayer, and let my cry come to You.} \newpage
 \subsection{Officium} Dom. annis B et C et in feriis: \greannotation{III} \index[Officium]{Omnia quæ fecisti} \label{Omnia quæ fecisti (Officium)} \grecommentary[9pt]{Dan 3:31, 29, 20, 43, 42; \Vbar. Ps 118:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.3cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--omnia_quae_fecisti--dominican--id_6970}  \vspace{5pt} \par{All that You have done to us, O Lord, You have done in true judgment; because we have sinned against You, and we have not obeyed Your commandments; but give glory to Your name, and deal with us according to the multitude of Your mercy. \Vbar. Blessed are the undefiled in the way, who walk in the law of the Lord.} \newpage
 \subsection{Responsorium} Dom. anno A: \greannotation{V} \index[Responsorium]{Christus factus est} \label{Christus factus est (Responsorium)} \grecommentary[8pt]{Phil 2:8; \Vbar. 9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--christus_factus_est--dominican--id_6737}  \vspace{5pt} \par{Christ became obedient for us unto death, even to death on a cross. \Vbar. Therefore, God also has exalted Him and has given Him the name that is above every name.} \newpage
 \subsection{Responsorium} Dom. annis B et C et in feriis: \greannotation{VII} \index[Responsorium]{Oculi omnium} \label{Oculi omnium (Responsorium)} \grecommentary[0pt]{Ps 144:15; \Vbar. 16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--oculi_omnium--dominican--id_5738}  \vspace{5pt} \par{The eyes of all hope in You, O Lord; and You give them meat in due season. \Vbar. You open Your hand, and fill every living creature with Your blessing.} \newpage

 \subsection{Alleluia}  \greannotation{III} \index[Alleluia]{Paratum cor meum} \label{Paratum cor meum (Alleluia)} \grecommentary[0pt]{Ps 107:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--paratum_cor_meum--dominican--id_6033}  \vspace{5pt} \par{My heart is ready, O God, my heart is ready; I will sing, and will give praise, with my glory.} \newpage

 \subsection{Offertorium}  \greannotation{I} \index[Offertorium]{Super flumina} \label{Super flumina (Offertorium)} \grecommentary[3pt]{Ps 136:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--super_flumina--dominican--id_5353}  \vspace{5pt} \par{Upon the rivers of Babylon, there we sat and wept, when we remembered You, O Zion.} \newpage
 \subsection{Communio}  \greannotation{IV} \index[Communio]{Memento} \label{Memento (Communio)} \grecommentary[0pt]{Ps 118:49, 50} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--memento_verbi_tui--dominican--id_6042}  \vspace{5pt} \par{Be mindful of Your word to Your servant, O Lord, in which You have given me hope; this has comforted me in my humiliation.} \newpage
 
 
 
 
\end{document}
