\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[32\textsuperscript{nd} Sunday in Ordinary Time]{Graduale Novum\\Ordinis Prædicatorum}
\section{32\textsuperscript{nd} Sunday in Ordinary Time}

\input{001_edited}


\newpage

%%Combination
 \subsubsection{Officium}  \greannotation{III} \index[Officium]{Intret oratio mea} \label{Intret oratio mea (Officium)} \grecommentary[0pt]{Ps 87:3; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--intret_oratio--dominican--id_5682}  \vspace{5pt} \par{Let my prayer enter into Your presence; incline Your ear to my supplication, O Lord. \Vbar. O Lord, the God of my salvation, I have cried in the day, and in the night before You.} \newpage
 \subsubsection{Responsorium}  \greannotation{VII} \index[Responsorium]{Dirigatur} \label{Dirigatur (Responsorium)} \grecommentary[3pt]{Ps 140:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--dirigatur_oratio_mea--dominican--id_5920}  \vspace{5pt} \par{Let my prayer ascend like incense in Your presence, O Lord. \Vbar. May the lifting up of my hands be an evening sacrifice.} \newpage



 \subsubsection{Alleluia} Dom. anno A: \greannotation{VII} \index[Alleluia]{Quinque prudentes virgines} \label{Quinque prudentes virgines (Alleluia)} \grecommentary[0pt]{Mt 25:4, 6 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--quinque_prudentes--vatican-op}  \vspace{5pt} \par{The five wise virgins took oil in their vessels with the lamps; at midnight, however, a cry was made: ``Behold, the bridegroom comes; go forth to meet Christ the Lord."} \newpage
 \subsubsection{Alleluia} Dom. annis B et C et in feriis: \greannotation{I} \index[Alleluia]{Qui posuit fines} \label{Qui posuit fines (Alleluia)} \grecommentary[0pt]{Ps 147:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--qui_posuit_fines--dominican--id_6791}  \vspace{5pt} \par{Who has made peace in your borders; and filled you with the fat of corn.} \newpage


 \subsubsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Gressus meos} \label{Gressus meos (Offertorium)} \grecommentary[3pt]{Ps 118:133} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--gressus_meos--dominican--id_5995}  \vspace{5pt} \par{Direct my steps, O Lord, according to Your word: that no iniquity may have dominion, O Lord.} \newpage
 \subsubsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Quinque prudentes virgines} \label{Quinque prudentes virgines (Communio)} \grecommentary[0pt]{Mt 25:4, 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--quinque_prudentes--dominican--id_6027}  \vspace{5pt} \par{The five wise virgins took oil in their vessels with the lamps; at midnight, however, a cry was made: ``Behold, the bridegroom comes; go forth to meet Christ the Lord."} \newpage
 \subsubsection{Communio} Dom. annis B et C et in feriis: \greannotation{II} \index[Communio]{Dominus regit me} \label{Dominus regit me (Communio)} \grecommentary[0pt]{Ps 22:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--dominus_regit_me--dominican--id_5335}  \vspace{5pt} \par{The Lord rules me, and nothing shall I want; in a place of pasture He has placed me; near refreshing waters He has led me.} 

\end{document}
