\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Common of the Dedication of a Church]{Graduale O.P.}
\section{Common of the Dedication of a Church}


\input{001_edited}

\newpage


%%Combination
\subsubsection{Officium} In ipsa ecclesia dedicata: \greannotation{II} \index[Officium]{Terribilis est} \label{Terribilis est (Officium)} \grecommentary[5pt]{Gen. 28:17, 22; \Vbar. Ps 83:2-3} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--terribilis_est--dominican--id_6221} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{Awesome is this place; it is the house of God, and the gate of heaven, and it shall be called the court of God. \textit{T.P.} Alleluia. \Vbar. How lovely are Your tabernacles, O Lord of hosts. My soul longs and faints for the courts of the Lord.} \newpage
\subsubsection{Officium} In aliis ecclesiis: \greannotation{I} \index[Officium]{Dicit Dominus sermones (V. Quam dilecta)} \label{Dicit Dominus sermones (V. Quam dilecta) (Officium)} \grecommentary[0pt]{Is 59:21, 56:7; \Vbar. Ps 101:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--dicit_dominus_sermones--dominican--id_4299}  \vspace{5pt} \par{Thus says the Lord: ``My words, which I put in your mouth, will not depart from your mouth. Your name and your gifts will be accepted on my altar."} \newpage
\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Locus iste} \label{Locus iste (Responsorium)} \grecommentary[3pt]{Cf. 4 Esd. 8:21, 24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--locus_iste--dominican--id_6283}  \vspace{5pt} \par{This place has been made by God, an inestimable sacrament, it is without reproof. \Vbar. O God, before whom stands the choir of angels, hear the supplications of your servants.} \newpage
\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Adorabo ad templum} \label{Adorabo ad templum (Alleluia)} \grecommentary[0pt]{Ps 137:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--adorabo--dominican--id_5217}  \vspace{5pt} \par{I will worship toward Your holy temple, and I will praise Your name.} \newpage
\subsubsection{Tractus}  \greannotation{II} \index[Tractus]{Domus mea} \label{Domus mea (Tractus)} \grecommentary[0pt]{Cf. Is 56:7; Mt 7:8, 24-25} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.45cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--domus_mea--dominican--id_6154}  \vspace{5pt} \par{My house shall be called a house of prayer, says the Lord. \Vbar. In it, all who ask, receive; and he who seeks, finds; and to him who knocks, it shall be opened. \Vbar. This is the house of the Lord strongly built; it is well founded upon a firm rock.} \newpage
\subsubsection{Offertorium}  \greannotation{VI} \index[Offertorium]{Domine Deus} \label{Domine Deus (Offertorium)} \grecommentary[5pt]{1 Chr 29:17, 18} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--domine_deus_in_simplicitate--dominican--id_5927}  \vspace{5pt} \par{O Lord God, in the simplicity of my heart, I have joyfully offered all these things; and your people, who are present, I have seen with great joy. O God of Israel, keep this will. \textit{T.P.} Alleluia.} \newpage
\subsubsection{Communio}  \greannotation{V} \index[Communio]{Domus mea} \label{Domus mea (Communio)} \grecommentary[0pt]{Mt 21:13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--domus_mea--dominican--id_7050}  \vspace{5pt} \par{``My house shall be called a house of prayer," says the Lord. ``In it, all who ask, receive; and he who seeks, finds; and to him who knocks, it shall be opened." \textit{T.P.} Alleluia, alleluia.} \newpage

\end{document}
