\input{000_header}

\chapter[Memorial of the Blessed Virgin Mary on Saturday]{Graduale Novum\\Ordinis Prædicatorum}
\section{Memorial of the\\Blessed Virgin Mary on Saturday}
\begin{center}
\textit{From the Feast of the Presentation of the Lord until Advent}
\end{center}

\input{001_edited}

\newpage


%%Combination
 \subsubsection{Officium}  \greannotation{II} \index[Officium]{Salve sancta Parens} \label{Salve sancta Parens (Officium)} \grecommentary[4pt]{Sedulius, \textit{Carmen Paschale}; \Vbar. Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--salve_sancta_parens--dominican--id_6966--alleluia}  \vspace{5pt} \par{Hail, Holy mother, the Child-Bearer who gave birth to the King who rules heaven and earth forever. \textit{T.P.} Alleluia. \Vbar. After childbirth, O Virgin, you remained inviolate; Mother of God, intercede for us.} \newpage


 \subsubsection{Offertorium}  \greannotation{I} \index[Offertorium]{Recordare virgo} \label{Recordare virgo (Offertorium)} \grecommentary[0pt]{Cf. Ier 18:20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--recordare_virgo--dominican--id_5119}  \vspace{5pt} \par{Remember, Virgin Mother, when you stand in the sight of God, that you should speak good things for us, and that you should turn away his indignation from us. \textit{T.P.} Alleluia.} \newpage

 \subsubsection{Communio}  \greannotation{I} \index[Communio]{Ave regina} \label{Ave regina (Communio)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ave_regina_caelorum--dominican--id_5936}  \vspace{5pt} \par{Hail Queen of Heaven, Mother of the King of Angels. O Mary, flower of virgins, like the rose or the lily, pour forth prayers to your Son for the salvation of the faithful. \textit{T.P.} Alleluia, alleluia.} \newpage
\end{document}
