\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Masses for the Dead]{Graduale O.P.}
\subsection{Masses for the Dead}
\section{For the Funeral}

\input{001_edited}

\newpage

%%Combination



\subsubsection{Officium}  \greannotation{VI} \index[Officium]{Requiem} \label{Requiem (Officium)} \grecommentary[5pt]{IV Esdr 2:34, 35; \Vbar. Ps 64:2, 3, 4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--requiem--dominican--id_6527}  \vspace{5pt} \par{Eternal rest give to them, O Lord; and let perpetual light shine upon them. \par\Vbar.\textsuperscript{2} A hymn, O God, becomes You in Zion, and a vow shall be paid to You in Jerusalem; \textsuperscript{4} hear my prayer; all flesh shall come to You. \par\Vbar.\textsuperscript{4} The words of the wicked have prevailed over us: and you will pardon our transgressions.  \par\Vbar.\textsuperscript{5} Blessed is he whom you have chosen and taken to yourself: he shall dwell in your courts. \par\Vbar.\textsuperscript{5b} We shall be filled with the good things of your house; holy is your temple, wonderful in justice.} \newpage
\subsubsection{Kyrie}  \greannotation{VIII} \index[Kyrie]{Kyrie (Requiem)} \label{Kyrie (Requiem) (Kyrie)} \grecommentary[]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/ky--kyrie_(requiem)--dominican}  \vspace{5pt} \par{Lord, have mercy. Christ, have mercy. Lord, have mercy.} \newpage
\subsubsection{Responsorium} For multiple deceased persons: \greannotation{II} \index[Responsorium]{Requiem V. Animae} \label{Requiem V. Animae (Responsorium)} \grecommentary[5pt]{IV Esdr 2:34, 35; \Vbar. Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--requiem--dominican--id_6001}  \vspace{5pt} \par{Eternal rest give to them, O Lord; and let perpetual light shine upon them. \Vbar. Their souls shall dwell amid good things, and their seed shall inherit the earth.} \newpage
\subsubsection{Responsorium} For a deceased pope, bishop, or priest: \greannotation{II} \index[Responsorium]{Requiem V. In memoria} \label{Requiem V. In memoria (Responsorium)} \grecommentary[5pt]{IV Esdr 2:34, 35; \Vbar. Ps 111:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--requiem--dominican--id_6001--in_memoria}  \vspace{5pt} \par{Eternal rest give to them, O Lord; and let perpetual light shine upon them. \Vbar. The just shall be in everlasting remembrance; he shall not fear the evil hearing.} \newpage
\subsubsection{Tractus}  \greannotation{VIII} \index[Tractus]{Absolve Domine} \label{Absolve Domine (Tractus)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--absolve--dominican--id_6367}  \vspace{5pt} \par{Absolve, O Lord, the souls of all the faithful departed from every bond of sin. \Vbar. And by the help of Your grace may they be enabled to escape the judgment of punishment, and enjoy the happiness of eternal light.} \newpage
\subsubsection{Responsorium} For a deceased person when the body is present, and whenever the Mass is celebrated for an individual non-cleric: \greannotation{I} \index[Responsorium]{Si ambulem} \label{Si ambulem (Responsorium)} \grecommentary[0pt]{Ps 22:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--si_ambulem--dominican--id_6258}  \vspace{5pt} \par{If I should walk in the midst of the shadow of death, I will fear no evils, for You are with me, O Lord. \Vbar. Your rod and Your staff have comforted me.} \newpage
\subsubsection{Tractus}  \greannotation{VIII} \index[Tractus]{Sicut cervus} \label{Sicut cervus (Tractus)} \grecommentary[0pt]{Ps 41:2, 3, 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--sicut_cervus--dominican--id_7107}  \vspace{5pt} \par{As the deer longs for fountains of water, so my soul longs for You, O God. \par \Vbar. My soul has thirsted after the strong living God; when shall I come and appear before the face of my God? \par \Vbar. My tears have been my bread day and night, while it is said to me daily: "Where is your God?"} \newpage
\subsubsection{Sequentia}  \greannotation{II} \index[Sequentia]{Dies irae} \label{Dies irae (Sequentia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/se--dies_irae--dominican--id_6704}  \vspace{5pt} \par{The day of wrath, that day will dissolve all in ashes as foretold by David with the Sibyl. \par \vbar. How much tremor there will be when the Judge will come, investigating all strictly. \par \vbar. The trumpet, scattering a wondrous sound through the sepulchers of the region, will summon all before the throne. \par \vbar. Death with nature shall marvel when the creature arises to respond to the Judge. \par \vbar. The book of record shall be brought forth, in which all is contained, from which the world shall be judged. \par \vbar. When therefore the Judge will sit, whatever hides shall appear: nothing shall remain unpunished. \par \vbar. What am I, miserable, then to say? Which patron to ask? Whenever the just may hardly be secure. \par \vbar. King of tremendous majesty, who freely saves those who are to be saved, save me, font of mercy. \par \vbar. Remember, merciful Jesus, that I am the cause of you way: lest you lose me in that day. \par \vbar. Seeking me, you sat tired: you redeemed me, having suffered the cross: let not so much hardship be lost. \par \vbar. Just Judge of retribution, give the gift of remission before the day of reckoning. \par \vbar. I sigh, like the guilty: my face reddens in guilt: spare your supplicant, O God. \par \vbar. You who absolved Mary, and heard the robber, give hope to me also. \par \vbar. My prayers are unworthy: but you, good Lord, have mercy, lest I am burned up by the eternal fire. \par \vbar. Among your sheep grant me a place, and take me out from among the goats, setting me on the right hand. \par \vbar. When the wicked are confounded, sentenced to acrid flames: call me among the blessed. \par \vbar. I meekly and humbly pray, my heart is as crushed as the cinders: perform the healing of my end. \par \vbar. Tearful will be that day, on which from the ashes arises the guilty man who is to be judged. \par \vbar. Spare him therefore, O God. Merciful Lord Jesus, grant them rest. Amen. } \newpage
\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{De profundis} \label{De profundis (Alleluia)} \grecommentary[0pt]{Ps 129:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--de_profundis--dominican--id_6472}  \vspace{5pt} \par{Out of the depths I have cried out to You, O Lord; Lord, hear my prayer.} \newpage
\subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{Domine Iesu Christe} \label{Domine Iesu Christe (Offertorium)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--domine_iesu_christe--dominican--id_6575}  \vspace{5pt} \par{O Lord Jesus Christ, king of glory, deliver the souls of all the faithful departed from the pains of hell and from the deep pit; deliver them from the mouth of the lion, that hell may not swallow them up, and they may not fall into darkness; but may the holy standard bearer Michael introduce them to the holy light, \GreStar{} which You promised of old to Abraham and to his seed. \Vbar. We offer to You, O Lord, sacrifice of praise and prayers; receive them in behalf of those souls whom we commemorate this day; grant them, O Lord, to pass from death to that life, \GreStar{} which You promised of old to Abraham and to his seed.} \newpage
\subsubsection{Sanctus}  \greannotation{} \index[Sanctus]{Sanctus (Requiem)} \label{Sanctus (Requiem) (Sanctus)} \grecommentary[]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/ky--sanctus_requiem}  \vspace{5pt} \par{} \newpage
\subsubsection{Agnus Dei}  \greannotation{} \index[Agnus Dei]{Agnus Dei (Requiem)} \label{Agnus Dei (Requiem) (Agnus Dei)} \grecommentary[]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/ky--agnus_requiem}  \vspace{5pt} \par{Lamb of God, who takes away the sins of the world, grant unto them rest. Lamb of God, who takes away the sins of the world, grant unto them rest Lamb of God, who takes away the sins of the world, grant unto them rest eternal. } \newpage
\subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Lux æterna} \label{Lux æterna (Communio)} \grecommentary[5pt]{IV Esdr 2:35; \Vbar. Ps 120:1-8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--lux_aeterna--dominican--id_6519}  \vspace{5pt} \par{May eternal light shine upon them, O Lord, with Your saints forever, because You are merciful. \par \Vbar.\textsuperscript{1} I have lifted up my eyes to the mountains, from whence help shall come to me. \par\Vbar.\textsuperscript{2} My help is from the Lord, who made heaven and earth. \par\Vbar.\textsuperscript{3} May he not suffer your foot to be moved: neither let him slumber that keepeth you. \par\Vbar.\textsuperscript{4} Behold he shall neither slumber nor sleep, that keepeth Israel. \par\Vbar.\textsuperscript{5} The Lord is your keeper, the Lord is thy protection upon thy right hand. \par\Vbar.\textsuperscript{6} The sun shall not burn you by day: nor the moon by night. \par\Vbar.\textsuperscript{7} The Lord keepeth you from all evil: may the Lord keep your soul. \par\Vbar.\textsuperscript{8} May the Lord keep your coming in and thy going out; from henceforth now and forever.} \newpage
\subsubsection{Antiphona}  \greannotation{III} \index[Antiphona]{Clementissime} \label{Clementissime (Antiphona)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.75cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--clementissime}  \vspace{5pt} \par{Most merciful Lord, who on account of our misery bore the humiliation of death at the hands of the ungodly: deliver his soul from the chasm of Hell and set him free from the chains of death, O merciful one; and wipe away all his sins in perpetual oblivion; and may angels draw him to your light and bring him to the door of Paradise, that while the body is handed over to dust, they may lead him to eternity. O Lord, have mercy on a sinner.} \newpage
\subsubsection{Responsorium}  \greannotation{II} \index[Responsorium]{Libera me Domine} \label{Libera me Domine (Responsorium)} \grecommentary[5pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.75cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/re--libera_me_domine--dominican--omitting--verses}  \vspace{5pt} \par{Deliver me, O Lord, from death eternal in that awful day. When the heavens and the earth shall be moved: When you shall come to judge the world through fire. \Vbar. That day, that day of wrath, of sore distress and of misery, that great and exceeding bitter day. \Vbar. Dread has laid hold on me, and I fear exceedingly because of the judgment and of the wrath to come. \Vbar. O God, creator of all things  who has formed me from the mire of the earth and has wonderfully redeemed me by your own blood, and although my body may yet decay, you shall make it rise from the tomb on judgement day. Hear, O hear, O hear me, that my soul would you gather to the bosom of Abraham your patriarch.} \newpage

\end{document}
