\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}



%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[29 April]{Graduale O.P.}
\subsection{29 April}
\section{St. Catherine of Siena}
\subsection{Solemnity}



\newpage

%%Combination
\subsection{Officium}  \greannotation{VII} \index[Officium]{Mihi adhærere} \label{Mihi adhærere (Officium)} \grecommentary[3pt]{Ps 72:28, 26; \Vbar. 1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--mihi_adhaere_deo--dominican--id_7243}  \vspace{5pt} \par{It is good for me to hold fast to my God, to put my hope in the Lord God; my flesh and my heart have failed; You are the God of my heart, and the God that is my portion forever. \emph{T.P.} Alleluia, alleluia. \Vbar. How good is God to Israel, to those who are upright of heart.} \newpage
\subsection{Responsorium} Extra tempus Paschale: \greannotation{VII} \index[Responsorium]{Quasi stella} \label{Quasi stella (Responsorium)} \grecommentary[3pt]{Sir 50:6-7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/gr--quasi_stella_quasi_sol--dominican--id_7230}  \vspace{5pt} \par{As the morning star in the midst of a cloud, and as the sun when it shines, so did Catherine shine in the temple of God. \Vbar. In her days the wells of water flowed out, and they were filled as the sea above measure.} \newpage
\subsection{Tractus} Infra Septuagesimam: \greannotation{II} \index[Tractus]{Defecit caro mea} \label{Defecit caro mea (Tractus)} \grecommentary[0pt]{Ps 72:26; \Vbar. Ct 5:6; \Vbar. Ct 5:4; \Vbar. Ct 2:5; \Vbar. Ct 2:6} \gresetinitiallines{1}  \gregorioscore{graduale-chants/tr--defecit_caro_mea--dominican--id_6801}  \vspace{5pt} \par{My flesh grows weak, as does my heart; the God of my heart, God is my portion forever. \par \Vbar. My soul is made like liquid, for my beloved has spoken. \par \Vbar. He brought me into his wine cellar, he ordered love within me. \par \Vbar. Support me with flowers, for evil has pressed around me, because I languish for love. \par \Vbar. With his left hand under my head, with his right hand he will embrace me.} \newpage
\subsection{Alleluia} Tempore Paschali et post Trinitatem: \greannotation{I} \index[Alleluia]{Sideribus} \label{Sideribus (Alleluia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1}  \gregorioscore{graduale-chants/al--sideribus_cunctis--dominican--id_5405}  \vspace{5pt} \par{Brighter than all the stars shines Catherine, and she is forever the glory of virgins.} \newpage
\subsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Veritatem dico} \label{Veritatem dico (Offertorium)} \grecommentary[5pt]{Rom 9:1-3} \gresetinitiallines{1}  \gregorioscore{graduale-chants/of--veritatem--dominican--id_5660}  \vspace{5pt} \par{I speak the truth in Christ, I do not lie; that I have great sadness, and continuous sorrow in my heart. For I could wish to be anathema myself from Christ for the sake of my brethren. \emph{T.P.} Alleluia.} \newpage
\subsection{Communio}  \greannotation{V} \index[Communio]{Benedicta} \label{Benedicta (Communio)} \grecommentary[0pt]{Jud 13:23, 25} \gresetinitiallines{1}  \gregorioscore{graduale-chants/co--benedicta--dominican--id_4820}  \vspace{5pt} \par{Blessed are you, O daughter, by the Lord the most high God above all women upon the earth; because He has so magnified your name that your praise shall not depart out of the mouth of men. \emph{T.P.} Alleluia.} \newpage

\end{document}
