\input{000_header}

\chapter[February 2]{Graduale Novum\\Ordinis Prædicatorum}
\subsection{February 2}
\section{The Presentation of the Lord}
\subsection{Feast}

\input{001_edited}

\newpage

%%Combination
\subsection{Ad benedictionem candelarum}
 \textit{Dum accenduntur candelæ, cantatur antiphona:}
\subsubsection{Antiphona}  \greannotation{III} \index[Antiphona]{Ecce Dominus noster} \label{Ecce Dominus noster (Antiphona)} \grecommentary[4pt]{Is 35:4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--ecce_dominus_noster--dominican--id_6431-graduale}  \vspace{5pt} \par{Behold, our Lord will come with power, to enlighten the eyes of His servants, alleluia.} \newpage




\subsection{Ad processionum}
\vspace{-5pt} \subsubsection{Antiphona} \vspace{-5pt} \greannotation{VIII} \index[Antiphona]{Lumen ad revelationem gentium} \label{Lumen ad revelationem gentium (Antiphona)} \grecommentary[2pt]{Lc 2:32; \Vbar. 29-32} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.45cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/an--lumen_ad_revelationem} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{3pt} \par{A light for the revelation of the nations, and the glory of Your people Israel. \Vbar. Now you dismiss your servant, O Lord, according to your word in peace. \Vbar. For my eyes have seen your salvation. \Vbar. Which you have prepared before the face of all people.}



\subsubsection{Sequentia}  \greannotation{VI} \index[Sequentia]{Laetabundus} \label{Laetabundus (Sequentia)} \grecommentary[7pt]{Ecclesia [Proprium O.P. 1985]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/se--laetabundus_1985_version--dominican--id_4215}  \vspace{5pt} \par{\newpage Let the chorus of the faithful joyfully rejoice, alleluia. \par 2. The King of kings was brought forth from the womb of the undefiled: O wondrous thing. \par 3. The Angel of counsel is born of the Virgin: the sun from the star. \par 4. The sun knows no setting, the star ever shining, ever bright. \par 5. As the star brings forth its ray, so the Virgin brings forth her son, equal in form. \par 6. Neither the star by its ray, nor the mother by her son, is corrupted. \par 7. The tall cedar of Lebanon is fashioned into the hyssop, in our valley. \par 8. The Word, the being of the Most High, has deigned to become incarnate, taking on flesh. \par 9. Isaiah foretold it, the Synagogue remembers it, yet she never ceases to be bound. \par 10. If her own prophets she will not heed, let her believe those of the nations: in the verses of the Sibyl these things were predicted. \par 11. Unhappy man, make haste; believe even these things of old: why be condemned, you chosen ones? \par 12. Contemplate the newborn one whom the scriptures reveal, whom the child-bearing woman has begotten. Alleluia.} \newpage



\end{document}
