\input{000_header}

\chapter[December 8]{Graduale Novum\\Ordinis Prædicatorum}
\subsection{December 8}
\section{The Immaculate Conception \\ of the Blessed Virgin Mary}
\subsection{Solemnity}

\input{001_edited}

\newpage

%%Combination
\subsubsection{Officium}  \greannotation{V} \index[Officium]{Gaudens gaudebo} \label{Gaudens gaudebo (Officium)} \grecommentary[3pt]{Is 61:10; \Vbar. Ps 29:2} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--gaudens_gaudebo--dominican} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{Rejoicing I will rejoice in the Lord, an my soul will exult in my God; for he has clothed me with the robes of salvation, and wrapped me in a mantle of justice, like a bride adorned with her jewels. \Vbar. I will extol You, O Lord, for you have lifted me up, and have not let my enemies rejoice over me.} \newpage
\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Benedicta es tu} \label{Benedicta es tu (Responsorium)} \grecommentary[0pt]{Iudith 13:23; \Vbar. 15:10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--benedicta_es--dominican}  \vspace{5pt} \par{Blessed are you, O virgin Mary, by the Lord, the most high God, above all women upon the earth. \Vbar. You are the glory of Jerusalem; you are the joy of Israel, you are the great honor of our people.} \newpage
\subsubsection{Alleluia}  \greannotation{I} \index[Alleluia]{Tota pulchra es} \label{Tota pulchra es (Alleluia)} \grecommentary[0pt]{Cant 4:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--tota_pulchra_es--dominican}  \vspace{5pt} \par{You are all fair, O Mary, and the stain of original sin is not in you.} \newpage
\subsubsection{Offertorium}  \greannotation{I} \index[Offertorium]{Ave Maria [In Conceptione Immaculata B.M.V.]} \label{Ave Maria [In Conceptione Immaculata B.M.V.] (Offertorium)} \grecommentary[3pt]{Lc 1:28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--ave_maria--dominican}  \vspace{5pt} \par{Hail Mary, full of grace, the Lord is with you. Blessed are you among women, alleluia.} \newpage
\subsubsection{Communio}  \greannotation{III} \index[Communio]{Gloriosa} \label{Gloriosa (Communio)} \grecommentary[3pt]{Ps 86:3; Lc 1:49} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--gloriosa--dominican}  \vspace{5pt} \par{Glorious things are said of you, O Mary, for he who is mighty has done great things for you.} \newpage

\end{document}
