\input{000_header}


\chapter[August 8]{Graduale Novum\\Ordinis Prædicatorum}
\subsection{August 8}
\section{Our Holy Father Dominic}
\subsection{Solemnity}

\input{001_edited}

\newpage

%%Combination

 \subsubsection{Officium}  \greannotation{VI} \index[Officium]{In medio Ecclesiæ} \label{In medio Ecclesiæ (Officium)} \grecommentary[3pt]{Sir 15:5; \Vbar. 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--in_medio--dominican--no_alleluia}  \vspace{5pt} \par{In the midst of the Church he opened his mouth, and the Lord filled him with the spirit of wisdom and understanding; he clothed him with a robe of glory. \Vbar. A treasure of joy and gladness he heaped upon him.} \newpage

  \subsubsection{Sequentia}  \greannotation{VI} \index[Sequentia]{In caelesti hierarchia} \label{In caelesti hierarchia (Sequentia)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/se--in_caelesti_hierarchia--dominican--id_5838}  \vspace{5pt} \par{1. In the heavenly hierarchy, let there sound a new harmony, produced by a new canticle. \par 2. Let the melody of our choir on this earth be in harmony with it, rejoicing together with Dominic. \par 3. From the waste of Egypt the creator of the world called the man of his will. \par 4. In the basket of poverty he crosses the river of vanity for the salvation of souls. \par 5. Under the figure of a dog the preacher of the world is shown beforehand to his mother. \par 6. Bearing in his mouth a torch, he exhorts the people to the rule of love. \par 7. He is a new lawgiver, he is the imitator of Elias and a detester of crimes. \par 8. He scatters the foxes of Samson, and with the trumpet of Gideon he puts to flight the hosts of the enemy. \par 9. While still living in the body, he restores alive to a mother her son recalled from the dead. \par 10. A storm bows to his sign of the Cross. The company of the brethren eats bread sent as a gift of God. \par 11. The blessed man, in whom all the Church now takes joy, is exalted. \par 12. He fills the world with his seed, and at last is stationed with the army of heaven. \par 13. The grain of wheat lies hidden, the star lurks concealed; but the maker of all things \par 14. Commands the bones of Joseph to germinate and the star to radiate for the salvation of the nations. \par 15. O how the fragrance of his tomb, surpassing every aroma, proves the bloom of his flesh! \par 16. The sick come with haste and are cured, the blind and the lame are restored by the frequency of his miracles. \par 17. Therefore let us sound forth with full voice our praises to the wondrous Dominic. \par 18. O people of need, as you follow in his footsteps, call on him to intercede. \par 19. But you, O father loving and good, shepherd of your flock and patron, forever by your constant prayer \par 20. Commend throughout the ages the needs of your forsaken flock in the presence of the great king. Amen. Alleluia.} \newpage

\end{document}
