\input{000_header}

\chapter[February 2]{Graduale Novum\\Ordinis Prædicatorum}
\subsection{February 2}
\section{The Presentation of the Lord}
\subsection{Feast}

\input{001_edited}

\newpage

%%Combination
\subsection{Ad benedictionem candelarum}
 \textit{Dum accenduntur candelæ, cantatur antiphona:}
\subsubsection{Antiphona}  \greannotation{III} \index[Antiphona]{Ecce Dominus noster} \label{Ecce Dominus noster (Antiphona)} \grecommentary[4pt]{Is 35:4, 5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--ecce_dominus_noster--dominican--id_6431-graduale}  \vspace{5pt} \par{Behold, our Lord will come with power, to enlighten the eyes of His servants, alleluia.} \newpage




\subsection{Ad processionum}
\vspace{-5pt} \subsubsection{Antiphona} \vspace{-5pt} \greannotation{VIII} \index[Antiphona]{Lumen ad revelationem gentium} \label{Lumen ad revelationem gentium (Antiphona)} \grecommentary[2pt]{Lc 2:32; \Vbar. 29-32} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.45cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/an--lumen_ad_revelationem} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{3pt} \par{A light for the revelation of the nations, and the glory of Your people Israel. \Vbar. Now you dismiss your servant, O Lord, according to your word in peace. \Vbar. For my eyes have seen your salvation. \Vbar. Which you have prepared before the face of all people.} \newpage
\subsubsection{Antiphona}  \greannotation{I} \index[Antiphona]{Ave gratia plena} \label{Ave gratia plena (Antiphona)} \grecommentary[7pt]{Cf. Lc 1:28; Mal 4:2; Lc 1:79, 2:28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--ave_gratia_plena--dominican}  \vspace{5pt} \par{Hail, full of grace, Virgin Mother of God, for from you has been born the sun of justice, illuminating those who are in darkness. Rejoice, you elderly just man, receiving in your arms the Liberator of our souls, who gives to us even resurrection.} \newpage
\subsubsection{Antiphona}  \greannotation{V} \index[Antiphona]{Adorna thalamum} \label{Adorna thalamum (Antiphona)} \grecommentary[1pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--adorna_thalamum--dominican}  \vspace{5pt} \par{Adorn your bridal chamber, Sion, and receive Christ the King; embrace Mary, who is the gate of heaven, for she herself bears the King of glory. With a new light the Virgin stands, leading by the hand the Son who was begotten before the day-star, whom Simeon, receiving him in his arms, proclaims to the peoples to be the Lord of life and death, and the Salvation of the world.} \newpage
 \textit{Appropinquante processione ad ecclesiam, cantatur:}
\subsubsection{Antiphona}  \greannotation{II} \index[Antiphona]{Responsum} \label{Responsum (Antiphona)} \grecommentary[0pt]{Cf. Lc 2:26-29} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--responsum--dominican}  \vspace{5pt} \par{Simeon received a revelation from the Holy Spirit that he would not see death until he had seen the Christ of the Lord; and when they brought the child into the temple, he took Him in his arms, and blessed God, and said: ``Now, O Lord, you dismiss your servant in peace."} \newpage
\subsubsection{Antiphona}  \greannotation{I} \index[Antiphona]{Hodie beata Maria} \label{Hodie beata Maria (Antiphona)} \grecommentary[5pt]{Cf. Lc 2:25, 28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--hodie_beata_virgo_nunc_dimitis}  \vspace{5pt} \par{Today the Blessed Virgin Mary presented the child Jesus in the temple; and Simeon, filled with the Holy Spirit, took Him in his arms, and blessed God, and said: ``Now, O Lord, you dismiss your servant in peace."} \newpage
\subsection{Ad Misssam}
 \textit{Ingrediente processione in ecclesiam, cantatur:}
\subsubsection{Officium}  \greannotation{I} \index[Officium]{Suscepimus} \label{Suscepimus (Officium)} \grecommentary[4pt]{Ps 47:10, 11; \Vbar. 2} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--suscepimus--dominican--id_5439--two-line} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{We have received Your mercy, O God, in the midst of Your temple; according to Your name, O God, so also is Your praise unto the ends of the earth. Your right hand is full of justice. \Vbar. Great is the Lord, and greatly to be praised, in the city of our God, on His holy mountain.} \newpage

\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Suscepimus} \label{Suscepimus (Responsorium)} \grecommentary[1pt]{Ps 47:10, 11; \Vbar. 9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--suscepimus_deus--dominican--id_6094}  \vspace{5pt} \par{We have received Your mercy, O God, in the midst of Your temple; according to Your name, O God, so also is Your praise unto the ends of the earth. Your right hand is full of justice. \Vbar. Great is the Lord, and greatly to be praised, in the city of our God, in His holy mountain.} \newpage
\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Adorabo ad templum} \label{Adorabo ad templum (Alleluia)} \grecommentary[3pt]{Ps 137:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--adorabo--dominican--id_5217}  \vspace{5pt} \par{I will worship toward Your holy temple, and I will praise Your name.} \newpage
\subsubsection{Sequentia}  \greannotation{VI} \index[Sequentia]{Laetabundus} \label{Laetabundus (Sequentia)} \grecommentary[7pt]{Ecclesia [Proprium O.P. 1985]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/se--laetabundus_1985_version--dominican--id_4215}  \vspace{5pt} \par{\newpage Let the chorus of the faithful joyfully rejoice, alleluia. \par 2. The King of kings was brought forth from the womb of the undefiled: O wondrous thing. \par 3. The Angel of counsel is born of the Virgin: the sun from the star. \par 4. The sun knows no setting, the star ever shining, ever bright. \par 5. As the star brings forth its ray, so the Virgin brings forth her son, equal in form. \par 6. Neither the star by its ray, nor the mother by her son, is corrupted. \par 7. The tall cedar of Lebanon is fashioned into the hyssop, in our valley. \par 8. The Word, the being of the Most High, has deigned to become incarnate, taking on flesh. \par 9. Isaiah foretold it, the Synagogue remembers it, yet she never ceases to be bound. \par 10. If her own prophets she will not heed, let her believe those of the nations: in the verses of the Sibyl these things were predicted. \par 11. Unhappy man, make haste; believe even these things of old: why be condemned, you chosen ones? \par 12. Contemplate the newborn one whom the scriptures reveal, whom the child-bearing woman has begotten. Alleluia.} \newpage
\subsubsection{Offertorium}  \greannotation{I} \index[Offertorium]{Felix namque} \label{Felix namque (Offertorium)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--felix_namque--dominican}  \vspace{5pt} \par{For you are happy, O holy Virgin Mary, and most worthy of all praise, because from you arose the sun of justice, Christ our God.} \newpage
\subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Responsum accepit} \label{Responsum accepit (Communio)} \grecommentary[0pt]{Lc 2:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--responsum--dominican--id_6009}  \vspace{5pt} \par{Simeon received a revelation from the Holy Spirit that he would not see death until he had seen the Christ of the Lord.} \newpage


\end{document}
