\input{000_header}

\chapter[Our Lord Jesus Christ, King of the Universe]{Graduale Novum\\Ordinis Prædicatorum}
\subsection{Last Sunday in Ordinary Time}
\section[Our Lord Jesus Christ, King of the Universe]{Our Lord Jesus Christ,\\King of the Universe}
\subsection{Solemnity}

\input{001_edited}

\newpage

%%Combination

\subsubsection{Officium}  \greannotation{III} \index[Officium]{Dignus est Agnus} \label{Dignus est Agnus (Officium)} \grecommentary[7pt]{Apoc 5:12 et 1:6; \Vbar. Ps 71:1} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--dignus_est_agnus--dominican--id_7395} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{Worthy is the Lamb who was slain to receive power and divinity, and wisdom and strength and honor. To him be glory and power forever and ever. \Vbar. O God, with your judgment endow the king, and with your justice, the king's son.} \newpage
\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Dominabitur} \label{Dominabitur (Responsorium)} \grecommentary[3pt]{Ps 71:8; \Vbar. 11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--dominabitur--dominican--id_7398}  \vspace{5pt} \par{He shall rule from sea to sea, and from the river to the ends of the earth. \Vbar. And all kings of the earth shall adore him; all nations shall serve him.} \newpage
\subsubsection{Alleluia}  \greannotation{I} \index[Alleluia]{Potestas eius} \label{Potestas eius (Alleluia)} \grecommentary[0pt]{Dan 7:14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--potestas_ejus--dominican--id_7399}  \vspace{5pt} \par{His power is an everlasting power that shall not be taken away, and his kingdom shall not be destroyed.} \newpage
\subsubsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Postula a me} \label{Postula a me (Offertorium)} \grecommentary[0pt]{Ps 2:8} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--postula_a_me--dominican--id_7400}  \vspace{5pt} \par{Ask of me, and I will give you the nations as your inheritance, and the ends of the earth as your possession.} \newpage
\subsubsection{Communio} Anno A: \greannotation{I} \index[Communio]{Amen dico vobis, quod uni} \label{Amen dico vobis, quod uni (Communio)} \grecommentary[3pt]{Mt 25:40, 34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--amen_dico_vobis_quod_uni--op}  \vspace{5pt} \par{Amen, I say to you, that what you did to the least of mine, you did to me; come, blessed of my Father, inherit the kingdom that has been prepared for you from the beginning of the world.} \newpage
\subsubsection{Communio} Annis B et C: \greannotation{VI} \index[Communio]{Sedebit} \label{Sedebit (Communio)} \grecommentary[0pt]{Ps 28:10b, 11b} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--sedebit_dominus--dominican--id_7401}  \vspace{5pt} \par{The Lord shall sit as King forever; the Lord will bless his people with peace.} \newpage

\end{document}
