\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage[normalem]{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Third Sunday of Easter]{Graduale O.P.}
\section{Third Sunday of Easter}


\input{001_edited}

\newpage

\subsubsection{Officium}  \greannotation{VIII} \index[Officium]{Iubilate Deo omnis terra alleluia} \label{Iubilate Deo omnis terra alleluia (Officium)} \grecommentary[5pt]{Ps 65:1-2; \Vbar. 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--iubilate_deo--dominican--id_6146}  \vspace{5pt} \par{Sing joyfully to God, all the earth, alleluia. Sing a psalm to His name, alleluia. Give glory to His praise, alleluia, alleluia, alleluia. \Vbar. Say to God: How awesome are Your works, O Lord; in the greatness of Your power.} \newpage

\subsubsection{Alleluia I}  \greannotation{III} \index[Alleluia I]{Cognoverunt discipuli} \label{Cognoverunt discipuli (Alleluia I)} \grecommentary[5pt]{Lc 24:35 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--cognoverunt--vatican-op}  \vspace{5pt} \par{The disciples recognized the Lord Jesus in the breaking of the bread.} \newpage
\subsubsection{Alleluia II}  \greannotation{VIII} \index[Alleluia II]{Oportebat pati} \label{Oportebat pati (Alleluia II)} \grecommentary[0pt]{Lc 24:46} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--oportebat_pati--dominican--id_6843}  \vspace{5pt} \par{It was fitting for Christ to suffer, and rise from the dead, and so enter into the glory of God.} \newpage

 


\subsubsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Lauda anima mea} \label{Lauda anima mea (Offertorium)} \grecommentary[0pt]{Ps 145:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--lauda_anima_mea--dominican--id_6999}  \vspace{5pt} \par{Praise the Lord, O my soul; I will praise the Lord throughout my life; I will sing praises to my God as long as I have being, alleluia.} \newpage
\subsubsection{Communio} Dom. anno A: \greannotation{VI} \index[Communio]{Surrexit Dominus} \label{Surrexit Dominus (Communio)} \grecommentary[3pt]{Lc 24:34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--surrexit_dominus--dominican--id_7481}  \vspace{5pt} \par{The Lord has risen, and has appeared to Peter, alleluia.} \newpage
\subsubsection{Communio} Dom. anno B: \greannotation{I} \index[Communio]{Cantate Domino} \label{Cantate Domino (Communio)} \grecommentary[5pt]{Ps 95:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--cantate_domino--dominican--id_5304}  \vspace{5pt} \par{Sing to the Lord, alleluia. Sing to the Lord, and bless His name. Announce His salvation from day to day, alleluia, alleluia.} \newpage
\subsubsection{Communio} Dom. anno C: \greannotation{VI} \index[Communio]{Simon Ioannis} \label{Simon Ioannis (Communio)} \grecommentary[3pt]{Io 21:15, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--simon_ioannis--dominican--id_5102--alleluia}  \vspace{5pt} \par{``Simon, son of John, do you love Me more than these?" ``Lord, You know all things; You know, Lord, that I love You." Alleluia.} \newpage

\end{document}
