\input{000_header}

\chapter[1\textsuperscript{st} Sunday of Lent]{Graduale Novum\\Ordinis Prædicatorum}
\section{1\textsuperscript{st} Sunday of Lent}

\input{001_edited}

\newpage

%%Combination

\subsubsection{Officium}  \greannotation{VIII} \index[Officium]{Invocabit me} \label{Invocabit me (Officium)} \grecommentary[0pt]{Ps 90:15–16; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--invocavit_me--dominican--id_5614}  \vspace{5pt} \par{He called upon Me, and I will hear him; I will deliver him, and I will glorify him; I will fill him with length of days. \Vbar. He who dwells in the shelter of the Most High shall abide under the protection of the God of heaven.} \newpage
\subsubsection{Responsorium}  \greannotation{III} \index[Responsorium]{Angelis suis} \label{Angelis suis (Responsorium)} \grecommentary[5pt]{Ps 90:11; \Vbar. 12} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--angelis_suis--dominican--id_5301}  \vspace{5pt} \par{He has given His angels charge over you, to keep you in all your ways. \Vbar. In their hands they shall bear you up, lest you dash you foot against a stone.} \newpage
\subsubsection{Tractus}  \greannotation{II} \index[Tractus]{Qui habitat} \label{Qui habitat (Tractus)} \grecommentary[0pt]{Ps 90:1–7, 11–16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--qui_habitat--dominican--id_5592}  \vspace{5pt} \par{He who dwells in the shelter of the Most High, shall abide under the protection of the God of heaven. \par \Vbar. He shall say to the Lord: You are my protector, and my refuge: my God, in Him will I trust. \par \Vbar. For He will deliver me from the snare of the hunters and from the sharp word. \par \Vbar. He will overshadow you with His shoulders, and under His wings you shall trust. \par \Vbar. His truth shall compass you with a shield; you shall not be afraid of the terror of the night. \par \Vbar. Of the arrow that flies in the day; of the business that walks in the dark; of ruin, or of the noonday devil. \par \Vbar. A thousand shall fall at your side, and ten thousand at your right hand; but it shall not come near to you. \par \Vbar. For He has given His angels charge over you, to keep you in all your ways. \par \Vbar. In their hands they  shall bear you up lest you dash your foot against a stone. \par \Vbar. You shall walk upon the asp and the basilisk, and you shall trample underfoot the lion and the dragon. \par \Vbar. Because he has hoped in Me, I will deliver him; I will protect him, because he has known My name. \par \Vbar. He shall call upon Me, and I will hear him; I am with him in tribulation. \par \Vbar. I will deliver him, and I will glorify him; I will fill him with length of days, and I will show him My salvation.} \newpage
\subsubsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Scapulis suis} \label{Scapulis suis (Offertorium)} \grecommentary[0pt]{Ps 90:4–5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--scapulis_suis--dominican--id_5204}  \vspace{5pt} \par{The Lord will overshadow you with His shoulders, and under His wings you shall trust; His truth shall compass you with a shield.} \newpage
\subsubsection{Communio}  \greannotation{III} \index[Communio]{Scapulis suis} \label{Scapulis suis (Communio)} \grecommentary[3pt]{Ps 90:4–5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--scapulis_suis--dominican--id_6971}  \vspace{5pt} \par{He will overshadow you with His shoulders, and under His wings you shall trust; His truth shall compass you with a shield.} \newpage

\end{document}
