\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Easter Sunday of the Resurrection of the Lord]{Graduale O.P.}
\section{Easter Sunday of the Resurrection of the Lord}
\subsection{At the Mass during the Day}

\input{001_edited}

\newpage


\subsubsection{Officium}  \greannotation{IV} \index[Officium]{Resurrexi} \label{Resurrexi (Officium)} \grecommentary[5pt]{Ps 138:18, 5, 6; \Vbar. 1-2} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable}  \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--resurrexi--dominican--id_6541} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{I have risen, and I am with you still, alleluia. You have laid your hand upon me, alleluia; Your knowledge is become wonderful, alleluia, alleluia. \Vbar. Lord, You have proved me, and known me; You have known my resting and my rising.} \newpage
\subsubsection{Responsorium}  \greannotation{II} \index[Responsorium]{Hæc dies V. Confitemini} \label{Hæc dies V. Confitemini (Responsorium)} \grecommentary[3pt]{Ps 117:24; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--haec_dies_v_confitemini--dominican--id_6471}  \vspace{5pt} \par{This is the day which the Lord has made; let us be glad and rejoice in it. \Vbar. Give praise to the Lord, for He is good, for His mercy endures forever.} \newpage
\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Pascha nostrum} \label{Pascha nostrum (Alleluia)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--pascha_nostrum--dominican--id_7076-c3}  \vspace{5pt} \par{Christ our Passover is sacrificed.} \newpage
\subsubsection{Sequentia}  \greannotation{I} \index[Sequentia]{Victimæ paschali laudes} \label{Victimæ paschali laudes (Sequentia)} \grecommentary[5pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.35cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/se--victimae_paschali_laudes--dominican}  \vspace{5pt} \par{To the Paschal Victim let Christians offer their praises. The Lamb has redeemed the sheep; the sinless One has reconciled the sinners to His Father. \par \Vbar. Death and life contend in a wondrous conflict. The Prince of life died, yet living, reigns. \par \Vbar. Tell us, Mary, what did you see on the way? \par \Vbar. I saw the sepulcher of the living Christ and the glory of the Risen Savior; the angelic witnesses, the linen cloth and the clothing. \par \Vbar. Christ my hope has risen; He goes before you into Galilee. \par \Vbar. We know that Christ is truly risen from the dead. O victorious King, have mercy on us. Amen. Alleluia.} \newpage
\subsubsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam (Haec est dies)} \label{Vidi aquam (Haec est dies) (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9; \Vbar. Ps 117:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348--haec_est_dies}  \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia; and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \Vbar. This is the day the Lord has made; let us exult and rejoice in it.} \newpage
\subsubsection{Offertorium}  \greannotation{IV} \index[Offertorium]{Terra tremuit} \label{Terra tremuit (Offertorium)} \grecommentary[0pt]{Ps 75:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--terra_tremuit--dominican--id_5651}  \vspace{5pt} \par{The earth trembled and was still, when God arose in judgment, alleluia.} \newpage
\subsubsection{Communio}  \greannotation{VI} \index[Communio]{Pascha nostrum} \label{Pascha nostrum (Communio)} \grecommentary[0pt]{1 Cor 5:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pascha_nostrum--dominican--id_6187}  \vspace{5pt} \par{Christ our Passover is sacrificed, alleluia; therefore, let us feast with the unleavened bread of sincerity and truth, alleluia, alleluia, alleluia.} \newpage


\end{document}
