\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[2\textsuperscript{nd} Sunday of Lent]{Graduale O.P.}
\section{2\textsuperscript{nd} Sunday of Lent}

\input{001_edited}

\newpage


%%Combination

\subsubsection{Officium}  \greannotation{III} \index[Officium]{Tibi dixit cor meum} \label{Tibi dixit cor meum (Officium)} \grecommentary[7pt]{Ps 26:8, 9; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--tibi_dixit--dominican--id_5182}  \vspace{5pt} \par{My heart has said to You: I have sought Your face; Your face, O Lord, will I seek: turn not away Your face from me. \Vbar. The Lord is my light and my salvation; whom shall I fear?} \newpage
\subsubsection{Officium} \textit{Vel:} \greannotation{IV} \index[Officium]{Reminiscere} \label{Reminiscere (Officium)} \grecommentary[4pt]{Ps 24:6, 3, 22; \Vbar. 1-2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--reminiscere--dominican--id_5181}  \vspace{5pt} \par{Remember Your compassion, O Lord, and Your mercies, for they are from of old; lest at any time our enemies rule over us. Deliver us, O God of Israel, from all our tribulations. \Vbar. To you, O Lord, have I lifted up my soul; my God, in You have I put my trust, let me not be ashamed.} \newpage
\subsubsection{Responsorium}  \greannotation{I} \index[Responsorium]{Sciant gentes} \label{Sciant gentes (Responsorium)} \grecommentary[0pt]{Ps 82:19; \Vbar. 14} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--sciant_gentes--dominican--id_6179}  \vspace{5pt} \par{Let the nations know that God is Your name; You alone are the Most High over all the earth. \Vbar. O my God, make them like a wheel and as stubble before the face of the wind.} \newpage
\subsubsection{Tractus}  \greannotation{VIII} \index[Tractus]{Commovisti} \label{Commovisti (Tractus)} \grecommentary[0pt]{Ps 59:4, 6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--commovisti--dominican--id_5242}  \vspace{5pt} \par{You have moved the earth, O Lord, and have troubled it. \Vbar. Heal the breaches thereof, for it has been moved. \Vbar. That they may flee from before the bow; that Your elect may be delivered.} \newpage
\subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{Meditabor in mandatis} \label{Meditabor in mandatis (Offertorium)} \grecommentary[5pt]{Ps 118:47, 48} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--meditabor--dominican--id_6142}  \vspace{5pt} \par{I will meditate on Your commandments, which I have loved exceedingly, and I will lift up my hands to Your commandments, which I have loved.} \newpage
\subsubsection{Communio}  \greannotation{I} \index[Communio]{Visionem quam vidistis} \label{Visionem quam vidistis (Communio)} \grecommentary[0pt]{Mt 17:9 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--visionem--vatican}  \vspace{5pt} \par{Of the vision you have seen, tell no one until the Son of Man has risen from the dead.} \newpage

\end{document}
