\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage[normalem]{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Fifth Sunday of Easter]{Graduale O.P.}
\section{Fifth Sunday of Easter}

\input{001_edited}

\newpage

\subsubsection{Officium}  \greannotation{VI} \index[Officium]{Cantate Domino} \label{Cantate Domino (Officium)} \grecommentary[0pt]{Ps 97:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--cantate_domino--dominican--id_6037}  \vspace{5pt} \par{Sing to the Lord a new song, alleluia; for the Lord has done wondrous things, alleluia. In the sight of the nations He has revealed His justice, alleluia, alleluia. \Vbar. His right hand has wrought for Him salvation; and His arm is holy.} \newpage

\subsubsection{Alleluia I}  \greannotation{I} \index[Alleluia I]{Dextera Dei} \label{Dextera Dei (Alleluia I)} \grecommentary[3pt]{Ps 117:16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--dextera_dei--dominican--id_6041}  \vspace{5pt} \par{The right hand of God has wrought strength; the right hand of the Lord has exalted me.} \newpage
\subsubsection{Alleluia II}  \greannotation{I} \index[Alleluia II]{Christus resurgens} \label{Christus resurgens (Alleluia II)} \grecommentary[0pt]{Rom 6:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--christus_resurgens--dominican--id_6484}  \vspace{5pt} \par{Christ, rising again from the dead, now dies no more; death shall no longer have dominion over Him.} \newpage



 


\subsubsection{Offertorium}  \greannotation{I} \index[Offertorium]{Iubilate Deo universa} \label{Iubilate Deo universa (Offertorium)} \grecommentary[5pt]{Ps 65:1, 2, 16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--iubilate_deo_universa--dominican--id_4862}  \vspace{5pt} \par{Sing joyfully to God, all the earth; sing a psalm to His name; come and hear, and I will tell you, all you who fear God, what things the Lord has done for my soul, alleluia.} \newpage
\subsubsection{Communio} Dom. anno A: \greannotation{IV} \index[Communio]{Tanto tempore} \label{Tanto tempore (Communio)} \grecommentary[0pt]{Io 14:9, 10} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--tanto_tempore--dominican--id_6774}  \vspace{5pt} \par{Have I been so long a time with you, and have you not known Me? Philip, he who sees Me, sees the Father also, alleluia. Do you not believe that I am in the Father, and the Father in Me? Alleluia, alleluia.} \newpage
\subsubsection{Communio} Dom. annis B et C: \greannotation{VIII} \index[Communio]{Ego sum vitis vera} \label{Ego sum vitis vera (Communio)} \grecommentary[5pt]{Io 15:5} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_sum_vitis--dominican--id_7015}  \vspace{5pt} \par{I am the true vine and you are the branches; whoever remains in me, and I in him, bears fruit in plenty, alleluia.} \newpage


\subsubsection{Communio}  \greannotation{VIII} \index[Communio]{Pacem meam ... alleluia} \label{Pacem meam ... alleluia (Communio)} \grecommentary[0pt]{Io 14:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--pacem_meam_alleluia--dominican--id_6488}  \vspace{5pt} \par{Peace I leave you, alleluia: My peace I give unto you: alleluia, alleluia.} \newpage
\end{document}
