 \documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Ash Wednesday]{Graduale O.P.}
\section{Ash Wednesday}

\input{001_edited}

\newpage

%%Combination

\subsection{Ad ritus initiales et liturgiam verbi}
\subsubsection{Officium}  \greannotation{I} \index[Officium]{Misereris omnium} \label{Misereris omnium (Officium)} \grecommentary[2pt]{Sap 11:24–25, 27; \Vbar. Ps 56:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--misereris_omnium--dominican--id_4279}  \vspace{5pt} \par{You are merciful to all, O Lord, and despise nothing that You have made, overlooking the sins of men for the sake of repentance and sparing them, for You are the Lord our God. \Vbar. Have mercy on me, O God, have mercy on me, for my soul confides in You.} \newpage
\subsubsection{Responsorium}  \greannotation{I} \index[Responsorium]{Miserere mei} \label{Miserere mei (Responsorium)} \grecommentary[0pt]{Ps 56:2; \Vbar. 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--miserere_mei_deus--dominican--id_5398}  \vspace{5pt} \par{Have mercy on me, O God, have mercy on me, for my soul confides in You. \Vbar. He has sent forth from heaven and delivered me; He has made them a reproach who trod upon me.} \newpage
\subsubsection{Tractus}  \greannotation{II} \index[Tractus]{Domine non secundum} \label{Domine non secundum (Tractus)} \grecommentary[0pt]{Ps 102:10; Ps 78:8–9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--domine_non_secundum--dominican--id_6453}  \vspace{5pt} \par{O Lord, you have not dealt with us according to our sins, nor repaid us according to our iniquities. \Vbar. O Lord, do not remember our iniquities of old; let Your mercies speedily come before us, for we have become very poor. \Vbar. Help us, O God our Savior, and for the glory of Your name, O Lord, deliver us, and forgive us our sins for Your name's sake.} \newpage
\subsection{Ad benedictionem\\et impositionem cinerum}
 \emph{Dum celebrans principalis imponit cineres, cantantur:}
\subsubsection{Antiphona}  \greannotation{I} \index[Antiphona]{Immutemur habitu} \label{Immutemur habitu (Antiphona)} \grecommentary[0pt]{Cf. Ioel 2:13} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--immutemur_habitu--dominican--id_5601}  \vspace{5pt} \par{Let us change our garments for ashes and sackcloth; let us fast and lament before the Lord; for plenteous in mercy to forgive our sins is our God.} \newpage
\subsubsection{Antiphona}  \greannotation{II} \index[Antiphona]{Iuxta vestibulum} \label{Iuxta vestibulum (Antiphona)} \grecommentary[4pt]{Ioel 2:7; Est 13:17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--iuxta_vestibulum--dominican}  \vspace{5pt} \par{Between the porch and the altar the priests and the Levites, the ministers of the Lord, shall weep and shall say: ``Spare, O Lord, spare Your people, and destroy not the mouths of those who cry to You, O Lord."} \newpage
\subsubsection{Responsorium}  \greannotation{II} \index[Responsorium]{Emendemus in melius} \label{Emendemus in melius (Responsorium)} \grecommentary[0pt]{Cf. Bar 3:2; \Vbar. Ps 106:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/re--emendemus_in_melius--dominican--id_5915}  \vspace{5pt} \par{Let us make amends for the sins which through ignorance we have committed, lest suddenly overtaken by the day of death, we seek time for repentance, and are unable to find it. \GreStar{} Hearken, O Lord, and have mercy, for we have sinned against You. \Vbar. We have sinned like our fathers; we have committed injustice and have done wrong. \GreStar{} Hearken, O Lord.} \newpage
\subsubsection{Antiphona} \emph{Vel, simpliciore forma:} \greannotation{VII} \index[Antiphona]{Exaudi nos Domine} \label{Exaudi nos Domine (Antiphona)} \grecommentary[7pt]{Ps 68:17; \Vbar. 1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--exaudi_nos--dominican--id_4802}  \vspace{5pt} \par{Hear us, O Lord, for Your mercy is kind; according to the multitude of Your mercies look upon us, O Lord. \Vbar. Save me, O God, for the waters have come in even unto my soul.} \newpage
\subsection{Ad liturgiam Eucharisticam}
\subsubsection{Offertorium}  \greannotation{III} \index[Offertorium]{Exaltabo te} \label{Exaltabo te (Offertorium)} \grecommentary[0pt]{Ps 29:2, 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--exaltabo_te--dominican--id_7207}  \vspace{5pt} \par{I will extol You, O Lord, for You have upheld me and have not made my enemies rejoice over me; O Lord, I have cried to You, and You have healed me.} \newpage
\subsubsection{Communio}  \greannotation{III} \index[Communio]{Qui meditabitur} \label{Qui meditabitur (Communio)} \grecommentary[0pt]{Ps 1:2–3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--qui_meditabitur--dominican--id_6589}  \vspace{5pt} \par{He who shall meditate upon the law of the Lord day and night shall bring forth his fruit in due season.} \newpage

\end{document}
