\input{000_header}

\chapter[Sixth Sunday of Easter]{Graduale Novum\\Ordinis Prædicatorum}
\section{Sixth Sunday of Easter}

\input{001_edited}

\newpage

\subsubsection{Officium}  \greannotation{III} \index[Officium]{Vocem iucunditatis} \label{Vocem iucunditatis (Officium)} \grecommentary[7pt]{Cf. Is 48:20; \Vbar. Ps 65: 1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.45cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--vocem_iucunditatis--dominican--id_6200}  \vspace{5pt} \par{Declare the voice of joy, and let it be heard, alleluia; declare it even to the ends of the earth: the Lord has delivered His people, alleluia, alleluia. \Vbar. Sing joyfully to God, all the earth, sing a psalm to His name; give glory to His praise.} \newpage
\subsubsection{Alleluia I} Dom. anno A: \greannotation{I} \index[Alleluia I]{Surrexit Christus et illuxit} \label{Surrexit Christus et illuxit (Alleluia I)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--surrexit_christus_et_illuxit--dominican--id_6350}  \vspace{5pt} \par{Christ is risen, and has shone upon His people whom He redeemed with His blood.} \newpage
\subsubsection{Alleluia II} Dom. anno A: \greannotation{I} \index[Alleluia II]{Non vos relinquam} \label{Non vos relinquam (Alleluia II)} \grecommentary[0pt]{Cf. Io 14:18; 14:28; 16:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--non_vos_relinquam--dominican--id_6071}  \vspace{5pt} \par{I will not leave you orphans; I go away, and I come to you, and your heart shall rejoice.} \newpage
\subsubsection{Alleluia I} Dom. anno B: \greannotation{VII} \index[Alleluia I]{Exivi a Patre} \label{Exivi a Patre (Alleluia I)} \grecommentary[0pt]{Io 16:28} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--exivi_a_patre--dominican--id_6244}  \vspace{5pt} \par{I came forth from the Father, and have come into the world; again I leave the world, and I go to the Father.} \newpage
\subsubsection{Alleluia II} Dom. anno B: \greannotation{I} \index[Alleluia II]{Ego vos elegi} \label{Ego vos elegi (Alleluia II)} \grecommentary[0pt]{Io 15:16 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--ego_vos_elegi--vatican-op}  \vspace{5pt} \par{I have chosen you from the world, so that you might go, and bear fruit, and that your fruit should last.} \newpage
\subsubsection{Alleluia} Dom. anno C (I): Surrexit Christus \textit{vel} Exivi a Patre, \textit{ut supra.} \par \vspace{5pt} Dom. anno C (II): \greannotation{VIII} \index[Alleluia]{Spritus Sanctus docebit vos} \label{Spritus Sanctus docebit vos (Alleluia)} \grecommentary[0pt]{Io 14:26 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--spiritus_sanctus_docebit--vatican-op}  \vspace{5pt} \par{The Holy Spirit will teach you whatsoever I have said to you.} \newpage

\subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{Benedicite gentes} \label{Benedicite gentes (Offertorium)} \grecommentary[0pt]{Ps 65:8, 9, 20} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--benedicite_gentes--dominican--id_6100}  \vspace{5pt} \par{O bless the Lord our God, you nations, and make the voice of His praise to be heard who has set my soul to live, and has not suffered my feet to be moved. Blessed be the Lord, who has not turned away my prayer and His mercy from me, alleluia.} \newpage
\subsubsection{Communio} Dom. anno A: \greannotation{V} \index[Communio]{Non vos relinquam} \label{Non vos relinquam (Communio)} \grecommentary[0pt]{Cf. Io 14:18; 16:22} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--non_vos_relinquam--dominican--id_6454}  \vspace{5pt} \par{I will not leave you orphans; I will come to you again, alleluia, and your heart shall rejoice, alleluia, alleluia.} \newpage
\subsubsection{Communio} Dom. anno B: \greannotation{I} \index[Communio]{Ego vos elegi} \label{Ego vos elegi (Communio)} \grecommentary[0pt]{Io 15:16} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ego_vos_elegi_alleluia--dominican--id_5178}  \vspace{5pt} \par{I have chosen you from the world, so that you might go, and bear fruit, and that your fruit should last.} \newpage
\subsubsection{Communio} Dom. anno C: \greannotation{VIII} \index[Communio]{Spiritus Sanctus docebit vos} \label{Spiritus Sanctus docebit vos (Communio)} \grecommentary[5pt]{Io 14:26} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--spiritus_sanctus--dominican--id_4850}  \vspace{5pt} \par{The Holy Spirit shall teach you, alleluia, whatsoever I have said to you, alleluia, alleluia.} \newpage


\end{document}
