\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}

\chapter[Solemnity of Mary, the Holy Mother of God]{Graduale O.P.}
\subsection{January 1}
\subsection{The Octave Day of the Nativity of the Lord}
\section{Solemnity of Mary, \\ the Holy Mother of God}

\input{001_edited}

\newpage

%%Combination
\subsubsection{Officium}  \greannotation{II} \index[Officium]{Salve sancta Parens} \label{Salve sancta Parens (Officium)} \grecommentary[4pt]{Sedulius, \textit{Carmen Paschale}; \Vbar. Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--salve_sancta_parens--dominican--id_6966}  \vspace{5pt} \par{Hail holy mother, the Child-Bearer who has brought forth the King, who rules heaven and earth for ever and ever. \Vbar. After childbirth, O Virgin, you remained inviolate; O Mother of God, intercede for us.} \newpage
\subsubsection{Officium} \textit{Vel:} \greannotation{VIII} \index[Officium]{Lux fulgebit} \label{Lux fulgebit (Officium)} \grecommentary[7pt]{Cf. Is 9:2, 6; Lc 1:33; Ps 92:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--lux_fulgebit--dominican--id_6395}  \vspace{5pt} \par{A light shall shine upon us today, for our Lord is born to us; and He shall be called Wonderful, God, the Prince of peace, the Father of the world to come: of whose reign there shall be no end. \Vbar. The Lord has reigned, He is clothed with beauty; the Lord is clothed with strength, and has girded Himself with power.} \newpage
\subsubsection{Responsorium}  \greannotation{V} \index[Responsorium]{Diffusa est} \label{Diffusa est (Responsorium)} \grecommentary[3pt]{Ps 44:3; \Vbar. 5 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--diffusa_est--vatican}  \vspace{5pt} \par{Grace is poured out upon your lips; therefore has God blessed you for ever. \Vbar. Grace is poured out upon your lips; therefore has God blessed you for ever. \Vbar. For the cause of truth and goodness and righteousness, your right hand shall lead you wonderfully.} \newpage
\subsubsection{Alleluia}  \greannotation{VII} \index[Alleluia]{Multifarie} \label{Multifarie (Alleluia)} \grecommentary[4pt]{Hebr 1:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--multifarie--dominican--id_4775}  \vspace{5pt} \par{In many ways in the past, God spoke to the fathers through the prophets; last of all in these days, he has spoken to us through his Son.} \newpage
\subsubsection{Offertorium}  \greannotation{I} \index[Offertorium]{Felix namque} \label{Felix namque (Offertorium)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--felix_namque--dominican}  \vspace{5pt} \par{For you are happy, O holy Virgin Mary, and most worthy of all praise, because from you arose the sun of justice, Christ our God.} \newpage
\subsubsection{Communio}  \greannotation{IV} \index[Communio]{Exsulta filia Sion} \label{Exsulta filia Sion (Communio)} \grecommentary[0pt]{Zach 9:9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--exsulta_filia--dominican--id_6171}  \vspace{5pt} \par{Rejoice greatly, O daughter of Zion, shout for joy, O daughter of Jerusalem; behold your King comes, the holy one and Savior of the world.} \newpage

\end{document}
