\input{000_header}


\chapter[The Easter Vigil in the Holy Night]{Graduale Novum\\Ordinis Prædicatorum}
\section{The Easter Vigil in the Holy Night}
\subsubsection{Dominican House of Studies}

\input{001_edited}

\newpage

\subsubsection{Canticum}  \greannotation{VIII} \index[Canticum]{Cantemus Domino} \label{Cantemus Domino (Canticum)} \grecommentary[3pt]{Ex 15:1, 2; Idt 16:3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--cantemus_domino--dominican--id_5971}  \vspace{5pt} \par{Let us sing to the Lord, for he is gloriously triumphant; horse and rider he has cast into the sea; he has become my strength and refuge unto salvation. \Vbar. This is my God and I will praise him, the God of my father, I will extoll him. \Vbar. The Lord crushes wars; Lord is his name.} \newpage



\subsubsection{Canticum}  \greannotation{VIII} \index[Canticum]{Vinea facta} \label{Vinea facta (Canticum)} \grecommentary[0pt]{Is 5:1, 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--vinea_facta_est--dominican--id_6418}  \vspace{5pt} \par{The beloved had a vineyard on a hill in a fruitful place. \Vbar. And he enclosed it with a wall, and dug around it, and planted the vine of Sorec, and built a tower in its midst. \Vbar. And he dug a winepress therein, for the vineyard of the Lord of Hosts is the house of Israel.} \newpage



\subsubsection{Canticum}  \greannotation{VIII} \index[Canticum]{Sicut cervus} \label{Sicut cervus (Canticum)} \grecommentary[3pt]{Ps 41:2, 3, 4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/tr--sicut_cervus--dominican--id_7107}  \vspace{5pt} \par{As the deer longs for flowing streams, so my soul longs for you, O God. \Vbar. My soul has thirsted for the living God. When shall I come and appear before the face of my God? \Vbar. My tears have been my bread day and night, while they say to me every day: ``Where is your God?"} \newpage









\subsubsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam (Haec est dies)} \label{Vidi aquam (Haec est dies) (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9; \Vbar. Ps 117:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348--haec_est_dies}  \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia; and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \Vbar. This is the day the Lord has made; let us exult and rejoice in it.} \newpage

 \subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{Dextera Domini} \label{Dextera Domini (Offertorium)} \grecommentary[5pt]{Ps 117:16, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--dextera_domini--alleluia--dominican--id_4758}  \vspace{5pt} \par{The right hand of the Lord has wrought strength; the right hand of the Lord has exalted me. I shall not die, but live, and shall declare the works of the Lord. Alleluia.} \newpage



\end{document}
