\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage[normalem]{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Vigil of Pentecost]{Graduale O.P.}
\section{Vigil of Pentecost}
\subsection{Solemnity}

\input{001_edited}

\newpage

\subsubsection{Officium}  \greannotation{III} \index[Officium]{Caritas Dei} \label{Caritas Dei (Officium)} \grecommentary[5pt]{Rom 5:5, 10, 11; \Vbar. Ps 87:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--caritas_dei_nostris_alleluia--dominican--id_6242}  \vspace{5pt} \par{The charity of God is poured into our hearts, alleluia, by His Spirit dwelling within us, alleluia, alleluia. \Vbar. O Lord, the God of my salvation, in the day and in the night I have cried out before You.} \newpage
\subsubsection{Alleluia I}  \greannotation{I} \index[Alleluia I]{Loquebantur} \label{Loquebantur (Alleluia I)} \grecommentary[0pt]{Act 2:4} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--loquebantur--dominican--id_5244}  \vspace{5pt} \par{The Apostles spoke in many tongues of the wonders of God, alleluia.} \newpage
\subsubsection{Alleluia II}  \greannotation{I} \index[Alleluia II]{Factus est repente} \label{Factus est repente (Alleluia II)} \grecommentary[0pt]{Act 2:2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--factus_est_repente--dominican--id_5665}  \vspace{5pt} \par{Suddenly there came a sound from heaven, as of the coming of a mighty wind.} \newpage
\subsubsection{Alleluia III}  \greannotation{III} \index[Alleluia III]{Spiritus Domini} \label{Spiritus Domini (Alleluia III)} \grecommentary[0pt]{Sap 1:7} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--spiritus_domini--dominican--id_6667}  \vspace{5pt} \par{The Spirit of the Lord has filled the whole earth; and that which contains all things has knowledge of the voice.} \newpage
\subsubsection{Alleluia IV}  \greannotation{IV} \index[Alleluia IV]{Emitte Spiritum} \label{Emitte Spiritum (Alleluia IV)} \grecommentary[3pt]{Ps 103:30} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--emitte_spiritum--dominican--id_6596}  \vspace{5pt} \par{Send forth Your Spirit, and they shall be created; and You shall renew the face of the earth.} \newpage
\subsubsection{Alleluia V}  \greannotation{I} \index[Alleluia V]{Dum complerentur} \label{Dum complerentur (Alleluia V)} \grecommentary[0pt]{Cf. Act 2:1} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--dum_complerentur--dominican--id_7180}  \vspace{5pt} \par{When the days of Pentecost were completed they were all together.} \newpage
\subsubsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Emitte Spiritum} \label{Emitte Spiritum (Offertorium)} \grecommentary[10pt]{Ps 103:30, 31} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--emitte_spiritum--dominican--id_6932}  \vspace{5pt} \par{Send forth Your Spirit, and they shall be created; and You shall renew the face of the earth. May the glory of the Lord endure forever, alleluia.} \newpage
\subsubsection{Communio}  \greannotation{V} \index[Communio]{Ultimo} \label{Ultimo (Communio)} \grecommentary[0pt]{Io 7:37-39} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--ultimo_festivitatis--dominican--id_5123}  \vspace{5pt} \par{On the last day of the feast, Jesus said, ``He who believes in Me, rivers of living water shall flow from within him.” Now He said this about the Spirit whom they who believed in Him would receive, alleluia, alleluia.} \newpage

\end{document}
