\input{000_header}

\chapter[Holy Thursday]{Graduale Novum\\Ordinis Prædicatorum}
\section{Holy Thursday\\Mass of the Lord's Supper}
\subsubsection{Dominican House of Studies}

\input{001_edited}

\newpage

 \subsubsection{Officium}  \greannotation{IV} \index[Officium]{Nos autem gloriari} \label{Nos autem gloriari (Officium)} \grecommentary[3pt]{Cf. Gal 6:14; \Vbar. Ps 66:2} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--nos_autem--dominican--id_6834} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{We should glory in the Cross of our Lord Jesus Christ, in whom is our salvation, life, and resurrection; through whom we are saved and delivered. \Vbar. May God have mercy on us, and bless us; may he let his face shine upon us, and have mercy on us.} \newpage

\subsubsection{Offertorium}  \greannotation{II} \index[Offertorium]{Dextera Domini} \label{Dextera Domini (Offertorium)} \grecommentary[5pt]{Ps 117:16, 17} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--dextera_domini--dominican--id_4758}  \vspace{5pt} \par{The right hand of the Lord has wrought strength; the right hand of the Lord has exalted me. I shall not die, but live, and shall declare the works of the Lord.} 
\subsubsection{Cantus} \textit{Ad libitum:} \greannotation{VI} \index[Cantus]{Ubi caritas} \label{Ubi caritas (Cantus)} \grecommentary[0pt]{Auctor ignotus in Italia (sæc. IX–X?)} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/misc--ubi_caritas_est_vera--solesmes}  \vspace{5pt} \par{Where love is true, God is there. \par \Vbar. The love of Christ has gathered us into one. Let us rejoice and be glad in him. Let us fear and love the living God, and let us love one another with a sincere heart. \par \Vbar. Therefore when we are together, let us take heed not to be divided in mind. Let there be an end to spiteful strife, an end to quarrels, and in our midst be Christ our God. \par \Vbar. And, in company with the blessed, may we see your face in glory, Christ our God: joy that is boundless and pure for ever and for ever.} \newpage



\end{document}
