\input{000_header}

\chapter[Easter Sunday of the Resurrection of the Lord]{Graduale Novum\\Ordinis Prædicatorum}
\section{Easter Sunday\\of the Resurrection of the Lord}
\subsection{At the Mass during the Day}
\subsubsection{Dominican House of Studies}

\input{001_edited}

\newpage

 \subsubsection{Officium}  \greannotation{IV} \index[Officium]{Resurrexi} \label{Resurrexi (Officium)} \grecommentary[5pt]{Ps 138:18, 5, 6; \Vbar. 1–2} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable}  \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--resurrexi--dominican--id_6541} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{I have risen, and I am with you still, alleluia. You have laid your hand upon me, alleluia. Your knowledge has become wonderful, alleluia, alleluia. \Vbar. Lord, you have searched me and known me; you have known my resting and my rising.} \newpage

  \subsubsection{Antiphona}  \greannotation{VIII} \index[Antiphona]{Vidi aquam (Haec est dies)} \label{Vidi aquam (Haec est dies) (Antiphona)} \grecommentary[0pt]{Ezech 47:1, 9; \Vbar. Ps 117:24} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/an--vidi_aquam--dominican--id_7348--haec_est_dies}  \vspace{5pt} \par{I saw water flowing from the right side of the temple, alleluia; and all to whom that water came were saved, and they shall say: Alleluia, alleluia. \Vbar. This is the day the Lord has made; let us exult and rejoice in it.} \newpage

   \subsubsection{Sequentia}  \greannotation{I} \index[Sequentia]{Victimæ paschali laudes} \label{Victimæ paschali laudes (Sequentia)} \grecommentary[5pt]{Ecclesia} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.35cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/se--victimae_paschali_laudes--dominican}  \vspace{5pt} \par{To the Paschal Victim let Christians offer their praises. The Lamb has redeemed the sheep; the sinless One has reconciled the sinners to His Father. \par \Vbar. Death and life contend in a wondrous conflict. The Prince of life died, yet living, reigns. \par \Vbar. Tell us, Mary, what did you see on the way? \par \Vbar. I saw the sepulcher of the living Christ and the glory of the Risen Savior; the angelic witnesses, the linen cloth and the clothing. \par \Vbar. Christ my hope has risen; He goes before you into Galilee. \par \Vbar. We know that Christ is truly risen from the dead. O victorious King, have mercy on us. Alleluia.} \newpage



\end{document}
