\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-2}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thepart}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}

\chapter[The Baptism of the Lord]{Graduale O.P.}
\subsection{Sunday after the Epiphany of the Lord}
\section{The Baptism of the Lord}
\subsection{Feast}

\vspace{10pt}

\emph{Where the Solemnity of the Epiphany is transferred to Sunday, if this Sunday occurs on January 7 or 8, the feast of the Baptism of the Lord is celebrated on the following Monday.}

\input{001_edited}

\newpage

%%Combination
\subsubsection{Officium}  \greannotation{VIII} \index[Officium]{Dilexisti} \label{Dilexisti (Officium)} \grecommentary[0pt]{Ps 44:8; \Vbar. 2} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/in--dilexisti--dominican--id_5384}  \vspace{5pt} \par{You have loved justice, and hated iniquity; therefore God, your God, has anointed you with the oil of gladness above your fellows. \Vbar. My heart has uttered a good word; I speak my works to the king.} \newpage
\subsubsection{Responsorium}  \greannotation{VII} \index[Responsorium]{Benedictus Dominus} \label{Benedictus Dominus (Responsorium)} \grecommentary[0pt]{Ps 71:18; \Vbar. 3} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--benedictus_dominus_deus--dominican}  \vspace{5pt} \par{Blessed be the Lord, the God of Israel, Who alone does great wonders from all eternity. \Vbar. Let the mountains receive peace for your people, and the hills justice.} \newpage
\subsubsection{Responsorium} \emph{Vel:} \greannotation{VIII} \index[Responsorium]{Dilexisti} \label{Dilexisti (Responsorium)} \grecommentary[10pt]{Ps 44:8a; \Vbar. 8b} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--dilexisti--dominican}  \vspace{5pt} \par{You have loved justice, and hated iniquity. \Vbar. Therefore God, your God, has anointed you with the oil of gladness.} \newpage
\subsubsection{Alleluia}  \greannotation{II} \index[Alleluia]{Inveni David} \label{Inveni David (Alleluia)} \grecommentary[5pt]{Ps 88:21} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--inveni_david--dominican--id_6785}  \vspace{5pt} \par{I have found Davd My servant; with My holy oil I have anointed him.} \newpage
\subsubsection{Offertorium}  \greannotation{VIII} \index[Offertorium]{Benedictus qui venit} \label{Benedictus qui venit (Offertorium)} \grecommentary[10pt]{Ps 117:26–27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--benedictus_qui_venit--dominican--id_6857}  \vspace{5pt} \par{Blessed is He who comes in the name of the Lord; we have blessed You out of the house of the Lord; the Lord is God, and He has shone upon us, alleluia, alleluia.} \newpage
\subsubsection{Communio}  \greannotation{II} \index[Communio]{Omnes qui in Christo} \label{Omnes qui in Christo (Communio)} \grecommentary[2pt]{Gal 3:27} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--omnes_qui_in_christo--dominican--id_5705}  \vspace{5pt} \par{All you who have been baptized in Christ have put on Christ, alleluia.} \newpage

\end{document}
