\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsection}{0pt}{10pt}{*0}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\large\sc\center}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\normalsize\it}{\thesubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}



%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[The Ascension of the Lord]{Graduale O.P.}
\section{The Ascension of the Lord}


\newpage

\subsection{Officium}  \greannotation{VII} \index[Officium]{Viri Galilæi} \label{Viri Galilæi (Officium)} \grecommentary[5pt]{Act 1:11; \Vbar. 10} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.4cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/in--viri_galilaei--dominican--id_6603} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{Men of Galilee, why do you stand looking up to heaven? Alleluia! He shall come in the same way as you have seen Him going up to heaven, alleluia, alleluia, alleluia. \Vbar. And while they were gazing up to heaven as He went, behold, two men stood by them in white garments.} \newpage
\subsection{Alleluia}  \greannotation{IV} \index[Alleluia]{Ascendit Deus} \label{Ascendit Deus (Alleluia)} \grecommentary[0pt]{Ps 46:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--ascendit_deus--dominican--id_5352}  \vspace{5pt} \par{God has ascended with jubilation; and the Lord with the sound of trumpet.} \newpage
\subsection{Alleluia}  \greannotation{VIII} \index[Alleluia]{Dominus in Sina} \label{Dominus in Sina (Alleluia)} \grecommentary[3pt]{Ps 67:18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.3cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/al--dominus_in_sina--dominican--id_6865}  \vspace{5pt} \par{The Lord is in Holy Sinai; ascending on high, He has led captivity captive.} \newpage
\subsection{Offertorium}  \greannotation{I} \index[Offertorium]{Viri Galilæi} \label{Viri Galilæi (Offertorium)} \grecommentary[5pt]{Act 1:11} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.6cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--viri_galilaei--dominican--id_4934}  \vspace{5pt} \par{Men of Galilee, why do you stand looking up to heaven? This Jesus, who is taken up from you into heaven, shall come in the same way as you have seen Him going up to heaven, alleluia.} \newpage
\subsection{Offertorium} \emph{Vel:} \greannotation{I} \index[Offertorium]{Ascendit Deus} \label{Ascendit Deus (Offertorium)} \grecommentary[5pt]{Ps 46:6} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/of--ascendit_deus--dominican--id_6403}  \vspace{5pt} \par{God has ascended with jubilation, the Lord with the sound of trumpet, alleluia.} \newpage
\subsection{Communio} Anno A: \greannotation{I} \index[Communio]{Data est mihi} \label{Data est mihi (Communio)} \grecommentary[5pt]{Mt 28:18, 19} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--data_est_mihi--dominican--id_7085}  \vspace{5pt} \par{All power in heaven and on earth has been given to Me, alleluia. Go, teach all nations, baptizing them in the name of the Father, and of the Son, and of the Holy Spirit, alleluia, alleluia.} \newpage
\subsection{Communio} Anno B: Psallite Domino, \emph{ut infra, vel:} \greannotation{VII} \index[Communio]{Signa} \label{Signa (Communio)} \grecommentary[10pt]{Mk 16:17, 18 [GR]} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--signa_eos--vatican-op}  \vspace{5pt} \par{These signs will accompany those who believe: they will cast out demons, and when they lay their hands upon the sick, these will recover, alleluia.} \newpage
\subsection{Communio} Anno C: \greannotation{I} \index[Communio]{Psallite Domino} \label{Psallite Domino (Communio)} \grecommentary[10pt]{Ps 67:33, 34} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/co--psallite_domino--dominican--id_5669}  \vspace{5pt} \par{Sing to the Lord, who mounts above the heaven of heavens to the East, alleluia.} \newpage

\end{document}
