\input{000_header}

\chapter[Palm Sunday of the Lord's Passion]{Graduale Novum\\Ordinis Prædicatorum}
\section{Palm Sunday of the Lord's Passion}
\subsubsection{Dominican House of Studies}

\input{001_edited}


\newpage

 \subsubsection{Antiphona} \textit{Dum celebrans principalis accedit, cantatur:} \vspace{5pt} \greannotation{VII a} \index[Antiphona]{Hosanna filio David} \label{Hosanna filio David (Antiphona)} \grecommentary[4pt]{Mt 21:9; \Vbar. Ps 117:1, 22, 23, 27, 28} \gresetinitiallines{2} \grechangedim{maxbaroffsettextleft@nobar}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel} \grechangestyle{initial}{\fontsize{120}{120}\selectfont} \gregorioscore{graduale-chants/an--hosanna_filio_david--dominican--id_5587-with-psalm} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \vspace{5pt} \par{Hosanna to the Son of David; blessed is he who comes in the name of the Lord. \par\Vbar.\textsuperscript{1} Give praise to the Lord, for he is good: for his mercy endures for ever. \par\Vbar.\textsuperscript{22} The stone which the builders rejected, the same has become the head of the corner. \par\Vbar.\textsuperscript{23} This is the Lord's doing, and it is wonderful in our eyes.\par\Vbar.\textsuperscript{27} The Lord is God, and he has shone upon us. Appoint a solemn day, with shady boughs, even to the horn of the altar. \par\Vbar.\textsuperscript{28} You are my God, and I will praise you; you are my God, and I will extol you.} \newpage

 \subsubsection{Responsorium} \textit{Ad libitum, post lectionem II:} \greannotation{V} \index[Responsorium]{Christus factus est} \label{Christus factus est (Responsorium)} \grecommentary[5pt]{Phil 2:8; \Vbar. 9} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \gregorioscore{graduale-chants/gr--christus_factus_est--dominican--id_6737}  \vspace{5pt} \par{Christ became obedient for us unto death, even death on a Cross. \Vbar. Therefore God has exalted him and bestowed on the name that is above every name.} \newpage

\end{document}
