\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.3in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Graduale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\part}{0pt}{*0}{*1}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\huge\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\LARGE\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}


\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}



%% Style for translation line
\grechangestyle{translation}{\textnormal\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}



%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Graduale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers (\today)}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom
\grechangedim{maxbaroffsettextleft}{0 cm}{scalable}


\chapter[Parish Study: The Propers of the Mass]{Graduale O.P.}
\section{Parish Study: The Propers of the Mass}



\newpage

%%Combination


\section{First Sunday of Advent} \subsection{Officium}  \greannotation{VIII} \index[Officium]{Ad te levavi} \label{Ad te levavi (Officium)} \grecommentary[7pt]{Ps 24:1–3; \Vbar. 4} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--ad_te_levavi--dominican--id_5367}  \vspace{5pt} \par{To You have I lifted up my soul; my God, in you I put my trust, let me not be ashamed; neither let my enemies laugh at me, for no one who waits for You shall be confounded. \Vbar. Show, O Lord, Your ways to me, and teach me Your paths.}
\section{Third Sunday of Advent} \subsection{Officium}  \greannotation{I} \index[Officium]{Gaudete in Domino} \label{Gaudete in Domino (Officium)} \grecommentary[0pt]{Phil 4:4, 5; \Vbar. 7} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--gaudete_in_domino--dominican--id_4287}  \vspace{5pt} \par{Rejoice in the Lord always; again, I say, rejoice. Let your moderation be known to all men. The Lord is near. Have no anxiety, but in every prayer let your petitions be made known to God. \Vbar. And may the peace of God, which surpasses all understanding, keep your hearts and minds.}
\section{Christmas: Mass of the Night} \subsection{Officium}  \greannotation{II} \index[Officium]{Dominus dixit} \label{Dominus dixit (Officium)} \grecommentary[0pt]{Ps 2:7; \Vbar. 1, 2, 8} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--dominus_dixit--dominican--id_6135-antiphon-only}  \vspace{5pt} \par{The Lord said to me: ``You are my Son, this day have I begotten you.'' \par \Vbar.\textsuperscript{1} Why have the Gentiles raged, and the people devised vain things? \par \Vbar.\textsuperscript{2} The kings of the earth stand by, and the princes come together as one against the Lord, and against his Christ. \par \Vbar.\textsuperscript{8} Ask of me, and I will give you the nations as your inheritance, and the ends of the earth as your possession.}
 \subsection{Versus Officii}  \greannotation{II} \index[Versus Officii]{Dominus dixit (Verses)} \label{Dominus dixit (Verses) (Versus Officii)} \grecommentary[0pt]{Ps 2:7; \Vbar. 1, 2, 8} \gresetinitiallines{0}  \gregorioscore{graduale-chants/in--dominus_dixit--dominican--id_6135-verses-only}  \vspace{5pt} \par{}
\section{Christmas: Mass at Dawn} \subsection{Officium}  \greannotation{VIII} \index[Officium]{Lux fulgebit} \label{Lux fulgebit (Officium)} \grecommentary[7pt]{Cf. Is 9:2, 6; Lc 1:33; Ps 92:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--lux_fulgebit--dominican--id_6395}  \vspace{5pt} \par{A light shall shine upon us this day, for our Lord is born to us; and He shall be called Wonderful, God, the Prince of peace, the Father of the world to come: of whose reign there shall be no end. \Vbar. The Lord has reigned, He is clothed with beauty; the Lord is clothed with strength, and has girded Himself with power.}
\section{Christmas: Mass in the Day} \subsection{Officium}  \greannotation{VII} \index[Officium]{Puer natus est} \label{Puer natus est (Officium)} \grecommentary[3pt]{Is 9:6; Ps 97:1} \gresetinitiallines{1}  \gregorioscore{graduale-chants/in--puer_natus_est--dominican--id_5324}  \vspace{5pt} \par{A child is born to us and a son is given to us, whose government is upon His shoulders; and His name shall be called the angel of great counsel. \Vbar. Sing to the Lord a new canticle, for He has done wonderful things.}
\section{Ash Wednesday} \subsection{Antiphona}  \greannotation{I} \index[Antiphona]{Immutemur habitu} \label{Immutemur habitu (Antiphona)} \grecommentary[0pt]{Cf. Ioel 2:13} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/an--immutemur_habitu--dominican--id_5601} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{Let us change our garments for ashes and sackcloth; let us fast and lament before the Lord; for plenteous in mercy to forgive our sins is our God.} 
\section{Fourth Sunday of Lent} \subsection{Officium}  \greannotation{V} \index[Officium]{Lætare Ierusalem} \label{Lætare Ierusalem (Officium)} \grecommentary[0pt]{Cf. Is 66:10, 11; Ps 121} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/in--laetare_ierusalem--dominican--id_5261} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{Rejoice, O Jerusalem, and come together all you who love her; rejoice with joy, you who have been in sorrow, that you may exult, and be filled from the breasts of your consolation. \Vbar. I rejoiced because they said to me, "We will go into the house of the Lord."}
\section{Easter: Mass of the Day} \subsection{Officium}  \greannotation{IV} \index[Officium]{Resurrexi} \label{Resurrexi (Officium)} \grecommentary[0pt]{Ps 138:18, 5, 6 et 1-2} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/in--resurrexi--dominican--id_6541} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{I arose, and am still with you, alleluia! You have laid your hand upon me, alleluia! Your knowledge is become wonderful, alleluia, alleluia! \Vbar. Lord, You have proved me, and known me; You have known when I sit and when I stand.}
\section{Ascension of the Lord} \subsection{Officium}  \greannotation{VII} \index[Officium]{Viri Galilæi} \label{Viri Galilæi (Officium)} \grecommentary[0pt]{Act 1:11; Ps 46} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/in--viri_galilaei--dominican--id_6603} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{Men of Galilee, why do you stand looking up to heaven? Alleluia! He shall come in the same way as you have seen Him going up to heaven, alleluia, alleluia, alleluia! \Vbar. And while they were gazing up to heaven as He went, behold, two men stood by them in white garments.}
\section{Our Holy Father Dominic} \subsection{Officium}  \greannotation{VI} \index[Officium]{In medio Ecclesiæ} \label{In medio Ecclesiæ (Officium)} \grecommentary[0pt]{Sir 15:5; Ps 91} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.6cm}{scalable} \gregorioscore{graduale-chants/in--in_medio_all_all_all--dominican--id_6482} \grechangedim{spaceabovelines}{0 cm}{scalable} \vspace{5pt} \par{In the midst of the Church the Lord opened his mouth, and filled him with the spirit of wisdom and understanding; He clothed him with a robe of glory. T.P. Alleluia, alleluia, alleluia. \Vbar. He heaped upon him a treasure of joy and gladness.}

\end{document}
