\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


\AtBeginDocument{\grelatexsimpledefbarredsymbol{V}{0.1em}{0.12em}{0.14em}{0.18em}}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{Good Friday}
\section{Office of Readings}
              \par \emph{At the Prior’s signal all stand, face the high altar and silently make the Sign of the Cross.}
 \subsubsection{Invitatory Psalm}   \index[Psalmus]{Invitatory Psalm} \label{Invitatory Psalm (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm094english--good_friday}
 \subsubsection{Hymn}   \index[Hymn]{Hymn} \label{Hymn (Hymn)}         \input{varia/hy--pange_lingua_gloriosa_proelium--english--text--only}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         Earthly kings rise up, in revolt; princes conspire together against the Lord and his Anointed.
 \subsubsection{Psalm 2} \paragraph{The Messiah, king and conqueror}  \index[Psalmus]{Psalm 2} \label{Psalm 2 (Psalmus)} \emph{The rulers of the earth joined forces to overthrow Jesus, your anointed Son (Acts 4:27).}        \par \vspace{5pt} \input{psalms/psalm002english}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         They divided my garments among them; they cast lots for my clothing.
 \subsubsection{Psalm 22:2-23} \paragraph{God hears the suffering of his Holy One}  \index[Psalmus]{Psalm 22:2-23} \label{Psalm 22:2-23 (Psalmus)} \emph{Jesus cried with a loud voice: My God, my God, why have you forsaken me? (Matthew 27:46).}        \par \vspace{5pt} \input{psalms/psalm021.2-23english}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         They sought to take my life by violence.
 \subsubsection{Psalm 38} \paragraph{A sinner in extreme danger prays earnestly to God}  \index[Psalmus]{Psalm 38} \label{Psalm 38 (Psalmus)} \emph{All his friends were standing at a distance (Luke 23:49).}        \par \vspace{5pt} \input{psalms/psalm037english}
                 \par \vspace{5pt} \Vbar. They brought false evidence against me. \par \Rbar. They were breathing out fury. \newpage
 \subsubsection{First Reading}             \input{readings/lectio_prior_Heb.9.11-28--Good_Friday.tex}
 \subsubsection{Second Reading}             \input{readings/lectio_altera--ex_catechesibus_sancti_ioannis_chrysostomi--Good_Friday.tex}    \newpage
\section{Morning Prayer}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         God did not spare his own Son, but gave him up to suffer for our sake. 
 \subsubsection{Psalm 51} \paragraph{O God, have mercy on me}  \index[Psalmus]{Psalm 51} \label{Psalm 51 (Psalmus)} \emph{Your inmost being must be renewed, and you must put on the new man (Ephesians 4:23-24).}        \par \vspace{5pt} \input{psalms/psalm050english}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         Jesus Christ loved us, and poured out his own blood for us to wash away our sins.
 \subsubsection{Canticle: Habakkuk 3:2-4, 13a, 15-19} \paragraph{God comes to judge}  \index[Psalmus]{Canticle: Habakkuk 3:2-4, 13a, 15-19} \label{Canticle: Habakkuk 3:2-4, 13a, 15-19 (Psalmus)} \emph{Lift up your heads for your redemption is at hand (Luke 21:28).}        \par \vspace{5pt} \input{psalms/hab3_2-4.13.15-19english}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         We worship your cross, O Lord, and we praise and glorify your holy resurrection, for the wood of the cross has brought joy to the world.
 \subsubsection{Psalm 147:12-20} \paragraph{The restoration of Jerusalem}  \index[Psalmus]{Psalm 147:12-20} \label{Psalm 147:12-20 (Psalmus)} \emph{Come, I will show you the bride of the Lamb (Revelation 21:9).}        \par \vspace{5pt} \input{psalms/psalm147english}
 \subsubsection{Reading}     \hfill Is 52:13-15        \input{readings/lectio_brevis_Is.52.13-15.tex}
 \subsubsection{Responsory}  \greannotation{VI} \index[Responsory]{For our sake} \label{For our sake (Responsory)} \grecommentary[0pt]{Ph 2:8} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/misc.christus_factus--english}
 \subsubsection{Gospel Canticle}   \index[Antiphon]{Gospel Canticle} \label{Gospel Canticle (Antiphon)}         Over his head they hung their accusation: Jesus of Nazareth, King of the Jews.
 \subsubsection{Canticle of Zechariah (Luke 1:68-79)} \paragraph{The Messiah and his forerunner}  \index[Psalmus]{Canticle of Zechariah (Luke 1:68-79)} \label{Canticle of Zechariah (Luke 1:68-79) (Psalmus)}         \par \vspace{5pt} \input{psalms/lc1_68-79english}    \newpage
 \subsubsection{Preces} \emph{For the \emph{Preces} all stand facing the altar. Two friars (A) stand by the foot of the high altar, and two friars (B) stand in the middle of the choir.} \par \vspace{5pt} \greannotation{IV} \index[Preces]{Good Friday Preces} \label{Good Friday Preces (Preces)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/misc.versus_litanici_in_cantu_feria_vi--dominican--english--simple--rubrics}    \newpage
 \subsubsection{The Lord's Prayer} \emph{When the \emph{Preces} are concluded all remain standing in silence until the Prior begins the Our Father.} \par \vspace{5pt}  \index[Varia]{The Lord's Prayer} \label{The Lord's Prayer (Varia)}         \input{varia/lords-prayer}
 \subsubsection{Concluding Prayer} \emph{When the Our Father is concluded the choir turns and kneels for the concluding collect.} \par \vspace{5pt}  \index[Concluding Prayer]{Good Friday} \label{Good Friday (Concluding Prayer)}         \input{prayers/or-holy-week-6-good-friday-morning-prayer}
              \par \vspace{10pt} \emph{All depart in silence.}

 \end{document}
