\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination

\chapter{Good Friday}
\section{Matins}
              \par \textit{At the Prior’s signal all stand, face the high altar and silently make the Sign of the Cross.}
 \subsubsection{Invitatory}   \index[Psalmus]{Invitatory} \label{Invitatory (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm094english--good_friday-notated}
 \subsubsection{Hymn}  \greannotation{III} \index[Hymn]{Hymn} \label{Hymn (Hymn)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/hy--pange_lingua_gloriosi_proelium--english-icel}   \par \vspace{5pt} Text: \textit{Pange, lingua gloriosi prœlium certaminis}, Venantius Fortunatus, d. ca 600, tr. \textit{Roman Missal}, 2010. \newpage
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         \noindent Earthly kings rise up, in revolt; princes conspire together against the Lord and his Anointed.
 \subsubsection{Psalm 2} \paragraph{The Messiah, king and conqueror}  \index[Psalmus]{Psalm 2} \label{Psalm 2 (Psalmus)} \textit{The rulers of the earth joined forces to overthrow Jesus, your anointed Son (Acts 4:27).}        \par \vspace{5pt} \input{psalms/psalm002english}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         \noindent They divided my garments among them; they cast lots for my clothing.
 \subsubsection{Psalm 22:2-23} \paragraph{God hears the suffering of his Holy One}  \index[Psalmus]{Psalm 22:2-23} \label{Psalm 22:2-23 (Psalmus)} \textit{Jesus cried with a loud voice: My God, my God, why have you forsaken me? (Matthew 27:46).}        \par \vspace{5pt} \input{psalms/psalm021.2-23english}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         \noindent They sought to take my life by violence.
 \subsubsection{Psalm 38} \paragraph{A sinner in extreme danger prays earnestly to God}  \index[Psalmus]{Psalm 38} \label{Psalm 38 (Psalmus)} \textit{All his friends were standing at a distance (Luke 23:49).}        \par \vspace{5pt} \input{psalms/psalm037english}
                 \par \vspace{5pt} \Vbar. They brought false evidence against me. \par \Rbar. They were breathing out fury. \newpage
 \subsubsection{First Reading}             \input{readings/lectio_prior_Heb.9.11-28--Good_Friday.tex}
 \subsubsection{Responsorium prolixum}  \greannotation{II} \index[Responsorium prolixum]{Velum templi} \label{Velum templi (Responsorium prolixum)} \grecommentary[5pt]{Cf. Mt 27:51; Lc 23:42; \Vbar. Lc 23:43} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/rp--velum_templi--dominican} \vspace{5pt} \textit{The veil of the temple was torn and all the earth trembled. The thief cried out from the cross: ``Remember me, Lord, when you come in your kingly power." \Vbar. Truly, I say to you, this day you will be with me in paradise. * ``Remember me, Lord, when you come in your kingly power." }
 \subsubsection{Second Reading}             \input{readings/lectio_altera--ex_catechesibus_sancti_ioannis_chrysostomi--Good_Friday.tex}
 \subsubsection{Responsorium prolixum}  \greannotation{II} \index[Responsorium prolixum]{Barabbas} \label{Barabbas (Responsorium prolixum)} \grecommentary[5pt]{Cf. Io 18:40; Lc 22:48; \Vbar. Cf. Lc 22:47} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/rp--barabbas--dominican} \vspace{5pt} \textit{Barabbas the robber is released and the innocent Christ is slain; for Judas, skilled in the weapons of sin, and knowing how to wage war by means of peace, betrayed the Lord Jesus with a kiss. \Vbar. Behold, a crowd came, and he who was called Judas, who when he had drawn near to Jesus * betrayed the Lord Jesus with a kiss.}   \newpage
\section{Lauds}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         \noindent God did not spare his own Son, but gave him up to suffer for our sake.
 \subsubsection{Psalm 51} \paragraph{O God, have mercy on me}  \index[Psalmus]{Psalm 51} \label{Psalm 51 (Psalmus)} \textit{Your inmost being must be renewed, and you must put on the new man (Ephesians 4:23-24).}        \par \vspace{5pt} \input{psalms/psalm050english}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         \noindent Jesus Christ loved us, and poured out his own blood for us to wash away our sins.
 \subsubsection{Canticle: Habakkuk 3:2-4, 13a, 15-19} \paragraph{God comes to judge}  \index[Psalmus]{Canticle: Habakkuk 3:2-4, 13a, 15-19} \label{Canticle: Habakkuk 3:2-4, 13a, 15-19 (Psalmus)} \textit{Lift up your heads for your redemption is at hand (Luke 21:28).}        \par \vspace{5pt} \input{psalms/hab3_2-4.13.15-19english}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         \noindent We worship your cross, O Lord, and we praise and glorify your holy resurrection, for the wood of the cross has brought joy to the world.
 \subsubsection{Psalm 147:12-20} \paragraph{The restoration of Jerusalem}  \index[Psalmus]{Psalm 147:12-20} \label{Psalm 147:12-20 (Psalmus)} \textit{Come, I will show you the bride of the Lamb (Revelation 21:9).}        \par \vspace{5pt} \input{psalms/psalm147english}
 \subsubsection{Reading}     \hfill Is 52:13-15        \input{readings/lectio_brevis_Is.52.13-15.tex}    \newpage
 \subsubsection{Responsory}  \greannotation{VI} \index[Responsory]{Christus factus est} \label{Christus factus est (Responsory)} \grecommentary[5pt]{Ph 2:8} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/gr--christus_factus_est--dominican--id_6737-respond_only} \vspace{5pt} \textit{Christ became obedient for us unto death, even death on a Cross.}

 \subsubsection{Antiphona ad Benedictus}  \greannotation{I \textsc{d}} \index[Antiphona ad Benedictus]{Posuerunt super caput} \label{Posuerunt super caput (Antiphona ad Benedictus)} \grecommentary[3pt]{Mt 27:37} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--posuerunt--dominican}   \vspace{5pt} \textit{Over his head they hung their accusation: Jesus of Nazareth, King of the Jews.}
 \subsubsection{Canticum Evangelicum} \paragraph{The Messiah and his forerunner} \greannotation{I \textsc{d}} \index[Canticum Evangelicum]{Benedictus} \label{Benedictus (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/Benedictus-solemn1D}
 \subsubsection{Gospel Canticle}   \index[Antiphon]{Gospel Canticle} \label{Gospel Canticle (Antiphon)}         \noindent Over his head they hung their accusation: Jesus of Nazareth, King of the Jews.
 \subsubsection{Canticle of Zechariah (Luke 1:68-79)} \paragraph{The Messiah and his forerunner}  \index[Psalmus]{Canticle of Zechariah (Luke 1:68-79)} \label{Canticle of Zechariah (Luke 1:68-79) (Psalmus)}         \par \vspace{5pt} \input{psalms/lc1_68-79english}    \newpage
 \subsubsection{Preces} \textit{For the \textit{Preces} all stand facing the altar. Two friars stand by the Lady Lectern and two friars stand in the middle of the choir.} \par \vspace{5pt} \greannotation{IV} \index[Preces]{Good Friday Preces} \label{Good Friday Preces (Preces)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/misc.versus_litanici_in_cantu_feria_vi--dominican-dhs}   \vspace{5pt} \textit{Lord have mercy. Lord have mercy. Lord have mercy. Have mercy, Lord. Christ the Lord became obedient unto death. The meek lamb to whom the wolf gave treach'rous kisses, Christ have mercy. Life dies upon the tree; hell and death, mourning are robbed of their prey. Christ have mercy. You who willed to be fettered and have set us free from the bonds of death, Christ have mercy. Have mercy, Lord. Christ the Lord became obedient unto death. Lord have mercy. Lord have mercy. Lord have mercy. Have mercy, Lord. Christ the Lord became obedient unto death. Even death on a cross! } \newpage
 \subsubsection{The Lord's Prayer} \textit{When the \textit{Preces} are concluded all remain standing in silence until the Prior begins the Our Father.} \par \vspace{5pt}  \index[Varia]{The Lord's Prayer} \label{The Lord's Prayer (Varia)}         \input{varia/lords-prayer}
 \subsubsection{Concluding Prayer} \textit{When the Our Father is concluded the choir turns and kneels for the concluding collect.} \par \vspace{5pt}  \index[Concluding Prayer]{Good Friday} \label{Good Friday (Concluding Prayer)}         \input{prayers/or-holy-week-6-good-friday-morning-prayer}
              \par \vspace{10pt} \textit{All depart in silence.}
 
 \end{document}
