\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage[normalem]{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{Holy Thursday}
                 \lettrine[lines=3]{O}{} Sacred Banquet, in which Christ becomes our food, the memory of his passion is celebrated, the soul is filled with grace, and the pledge of future glory is given to us. \par \vspace{5pt} \Vbar. You gave them bread from heaven. \par \Rbar. Containing every blessing. \vspace{5pt} \par Let us pray. \par \lettrine[lines=2]{O}{} God, who in this wonderful sacrament have left us a memorial of your Passion, grant us, we pray, so to revere the sacred mysteries of your Body and Blood that we may always experience in ourselves the fruits of your redemption. Who live and reign forever and ever. \Rbar. Amen. \par \vspace{5pt}
\section{Office of Readings}
    \index[Varia]{O Lord open my lips} \label{O Lord open my lips (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.o_lord_open_my_lips-psj}
 \subsubsection{Invitatory Psalm}   \index[Psalmus]{Invitatory Psalm} \label{Invitatory Psalm (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm094english--holy_thursday}
 \subsubsection{Hymn}   \index[Hymn]{Hymn} \label{Hymn (Hymn)}         \input{varia/hy--pange_lingua_gloriosa_corporis--english--text--only}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         I am worn out with crying, with longing for my God.
 \subsubsection{Psalm 69:2-22, 30-37} \paragraph{I am consumed with zeal for your house}  \index[Psalmus]{Psalm 69:2-22, 30-37} \label{Psalm 69:2-22, 30-37 (Psalmus)} \emph{They offered him a mixture of wine and gall (Matthew 27:34).}        \par \vspace{5pt} \input{psalms/psalm068english_part_1}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         I needed food and they gave me gall; I was parched with thirst and they gave me vinegar.
 \subsubsection{II}   \index[Psalmus]{II} \label{II (Psalmus)}         \input{psalms/psalm068english_part_2}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         Seek the Lord and you will live.
 \subsubsection{III}   \index[Psalmus]{III} \label{III (Psalmus)}         \input{psalms/psalm068english_part_3}
                 \par \vspace{5pt} \Vbar. When I am lifted up from the earth. \par \Rbar. I will draw all people to myself. \newpage
 \subsubsection{First Reading}             \input{readings/lectio_prior_Heb.4.14-5.10--Holy_Thursday.tex}
 \subsubsection{Second Reading}             \input{readings/lectio_altera--ex_homilia_melitonis_sardiani--Holy_Thursday.tex}
\section{Morning Prayer}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         Look, O Lord, and see my suffering. Come quickly to my aid.
 \subsubsection{Psalm 80} \paragraph{Lord, come, take care of your vineyard}  \index[Psalmus]{Psalm 80} \label{Psalm 80 (Psalmus)} \emph{Come, Lord Jesus (Revelation 22:20).}        \par \vspace{5pt} \input{psalms/psalm079english}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         God is my savior; I trust in him and shall not fear.
 \subsubsection{Canticle: Isaiah 12:1-6} \paragraph{Joy of God’s ransomed people}  \index[Psalmus]{Canticle: Isaiah 12:1-6} \label{Canticle: Isaiah 12:1-6 (Psalmus)} \emph{If anyone thirsts, let him come to me and drink (John 7:37).}        \par \vspace{5pt} \input{psalms/is12_1-6english}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         The Lord has fed us with the finest wheat; he has filled us with honey from the rock.
 \subsubsection{Psalm 81} \paragraph{Solemn renewal of the Covenant}  \index[Psalmus]{Psalm 81} \label{Psalm 81 (Psalmus)} \emph{See that no one among you has a faithless heart (Hebrews 3:12).}        \par \vspace{5pt} \input{psalms/psalm080english}
 \subsubsection{Reading}     \hfill Heb 2:9-10        \input{readings/lectio_brevis_Heb.2.9-10.tex}    \newpage
 \subsubsection{Responsory}   \index[Responsory]{Responsory} \label{Responsory (Responsory)}         \input{varia/rb--holy_thursday_morning_prayer}
 \subsubsection{Gospel Canticle}   \index[Antiphon]{Gospel Canticle} \label{Gospel Canticle (Antiphon)}         I have longed to eat this meal with you before I suffer.
 \subsubsection{Canticle of Zechariah (Luke 1:68-79)} \paragraph{The Messiah and his forerunner}  \index[Psalmus]{Canticle of Zechariah (Luke 1:68-79)} \label{Canticle of Zechariah (Luke 1:68-79) (Psalmus)}         \par \vspace{5pt} \input{psalms/lc1_68-79english}
 \subsubsection{Preces}   \index[Preces]{Holy Thursday} \label{Holy Thursday (Preces)}         \input{intercessions/intercessions-holy-week-5-holy-thursday-morning-prayer}
 \subsubsection{The Lord's Prayer}   \index[Varia]{The Lord's Prayer} \label{The Lord's Prayer (Varia)}         \input{varia/lords-prayer}
 \subsubsection{Concluding Prayer}   \index[Concluding Prayer]{Holy Thursday} \label{Holy Thursday (Concluding Prayer)}         \input{prayers/or-holy-week-5-holy-thursday-morning-prayer}
 \subsubsection{Dismissal}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen. \par \Vbar. Go in peace. \par \Rbar. Thanks be to God.

\chapter{Good Friday}
\section{Office of Readings}
 \subsubsection{Invitatory Psalm}   \index[Psalmus]{Invitatory Psalm} \label{Invitatory Psalm (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm094english--good_friday}
 \subsubsection{Hymn}   \index[Hymn]{Hymn} \label{Hymn (Hymn)}         \input{varia/hy--pange_lingua_gloriosa_proelium--english--text--only}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         Earthly kings rise up, in revolt; princes conspire together against the Lord and his Anointed.
 \subsubsection{Psalm 2} \paragraph{The Messiah, king and conqueror}  \index[Psalmus]{Psalm 2} \label{Psalm 2 (Psalmus)} \emph{The rulers of the earth joined forces to overthrow Jesus, your anointed Son (Acts 4:27).}        \par \vspace{5pt} \input{psalms/psalm002english}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         They divided my garments among them; they cast lots for my clothing.
 \subsubsection{Psalm 22:2-23} \paragraph{God hears the suffering of his Holy One}  \index[Psalmus  ]{Psalm 22:2-23} \label{Psalm 22:2-23 (Psalmus)} \emph{Jesus cried with a loud voice: My God, my God, why have you forsaken me? (Matthew 27:46).}        \par \vspace{5pt} \input{psalms/psalm021.2-23english}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         They sought to take my life by violence.
 \subsubsection{Psalm 38} \paragraph{A sinner in extreme danger prays earnestly to God}  \index[Psalmus]{Psalm 38} \label{Psalm 38 (Psalmus)} \emph{All his friends were standing at a distance (Luke 23:49).}        \par \vspace{5pt} \input{psalms/psalm037english}
                 \par \vspace{5pt} \Vbar. They brought false evidence against me. \par \Rbar. They were breathing out fury. \newpage
 \subsubsection{First Reading}             \input{readings/lectio_prior_Heb.9.11-28--Good_Friday.tex}
 \subsubsection{Second Reading}             \input{readings/lectio_altera--ex_catechesibus_sancti_ioannis_chrysostomi--Good_Friday.tex}
\section{Morning Prayer}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         God did not spare his own Son, but gave him up to suffer for our sake.
 \subsubsection{Psalm 51} \paragraph{O God, have mercy on me}  \index[Psalmus]{Psalm 51} \label{Psalm 51 (Psalmus)} \emph{Your inmost being must be renewed, and you must put on the new man (Ephesians 4:23-24).}        \par \vspace{5pt} \input{psalms/psalm050english}


 \end{document}
