\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{Holy Saturday}
\section{Office of Readings}
              \par \emph{At the Prior’s signal all stand, face the high altar and silently make the Sign of the Cross.}
 \subsubsection{Invitatory Psalm}   \index[Psalmus]{Invitatory Psalm} \label{Invitatory Psalm (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm094english--holy_saturday}
 \subsubsection{Hymn}   \index[Hymn]{Hymn} \label{Hymn (Hymn)}         \input{varia/hy--lustris_sex_qui_iam_peractis--english--text--only}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         In peace, I will lie down and sleep.
 \subsubsection{Psalm 4} \paragraph{Thanksgiving}  \index[Psalmus]{Psalm 4} \label{Psalm 4 (Psalmus)} \emph{The resurrection of Christ was God’s supreme and wholly marvelous work (Saint Augustine).}        \par \vspace{5pt} \input{psalms/psalm004english}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         My body shall rest in hope.
 \subsubsection{Psalm 16} \paragraph{God is my portion, my heritage}  \index[Psalmus]{Psalm 16} \label{Psalm 16 (Psalmus)} \emph{The Father raised up Jesus from the dead and broke the bonds of death (Acts 2:24).}        \par \vspace{5pt} \input{psalms/psalm015english}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         Lift high the ancient portals. The King of glory enters.
 \subsubsection{Psalm 24} \paragraph{The Lord’s entry into his temple}  \index[Psalmus]{Psalm 24} \label{Psalm 24 (Psalmus)} \emph{Christ opened heaven for us in the humanity he assumed (Saint Irenaeus).}        \par \vspace{5pt} \input{psalms/psalm023english}
                 \par \vspace{5pt} \Vbar. Take up my cause and rescue me. \par \Rbar. Be true to your word, give me life. \newpage
 \subsubsection{First Reading}             \input{readings/lectio_prior_Heb.4.1-13--Holy_Saturday.tex}
 \subsubsection{Second Reading}             \input{readings/lectio_altera--ex_antinqua_homilia_in_sancto_et_magno_Sabbato.tex}    \newpage
 \subsubsection{Oratio Ieremiæ}   \index[Oratio Ieremiæ]{Oratio Ieremiæ} \label{Oratio Ieremiæ (Oratio Ieremiæ)}         \input{varia/misc--oratio_ieremiae--translation}
\section{Morning Prayer}
 \subsubsection{Antiphon 1}   \index[Antiphon]{Antiphon 1} \label{Antiphon 1 (Antiphon)}         Though sinless, the Lord has been put to death. The world is in mourning as for an only son.
 \subsubsection{Psalm 64} \paragraph{Prayer for help against enemies}  \index[Psalmus]{Psalm 64} \label{Psalm 64 (Psalmus)} \emph{This psalm commemorates most particularly our Lord’s passion (Saint Augustine).}        \par \vspace{5pt} \input{psalms/psalm063english}
 \subsubsection{Antiphon 2}   \index[Antiphon]{Antiphon 2} \label{Antiphon 2 (Antiphon)}         From the jaws of hell, Lord, rescue my soul.
 \subsubsection{Canticle: Isaiah 38:10-14, 17b-20} \paragraph{Anguish of a dying man and joy in his restoration}  \index[Psalmus]{Canticle: Isaiah 38:10-14, 17b-20} \label{Canticle: Isaiah 38:10-14, 17b-20 (Psalmus)} \emph{I was living, I was dead . . . and I hold the keys of death (Revelation 1:17-18).}        \par \vspace{5pt} \input{psalms/is38_10-14.17b-20english}
 \subsubsection{Antiphon 3}   \index[Antiphon]{Antiphon 3} \label{Antiphon 3 (Antiphon)}         I was dead, but now I live for ever, and I hold the keys of death and of hell.
 \subsubsection{Psalm 150} \paragraph{Praise the Lord}  \index[Psalmus]{Psalm 150} \label{Psalm 150 (Psalmus)} \emph{Let mind and heart be in your song: this is to glorify God with your whole self (Hesychius).}        \par \vspace{5pt} \input{psalms/psalm150english}
 \subsubsection{Reading}     \hfill Hos 5:15b-16:2        \input{readings/lectio_brevis_Hos.5.15b-16.2.tex}
 \subsubsection{Responsory}  \greannotation{VI} \index[Responsory]{For our sake} \label{For our sake (Responsory)} \grecommentary[0pt]{Ph 2:8; \Vbar. 9} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/misc.christus_factus--english--holy_saturday}
 \subsubsection{Gospel Canticle}   \index[Antiphon]{Gospel Canticle} \label{Gospel Canticle (Antiphon)}         Save us, O Savior of the world. On the cross you redeemed us by the shedding of your blood; we cry out for your help, O God.
 \subsubsection{Canticle of Zechariah (Luke 1:68-79)} \paragraph{The Messiah and his forerunner}  \index[Psalmus]{Canticle of Zechariah (Luke 1:68-79)} \label{Canticle of Zechariah (Luke 1:68-79) (Psalmus)}         \par \vspace{5pt} \input{psalms/lc1_68-79english}    
 \subsubsection{Preces} \emph{For the \emph{Preces} all stand facing the altar. Two friars (A) stand by the foot of the high altar, and two friars (B) stand in the middle of the choir.} \par \vspace{5pt} \greannotation{IV} \index[Preces]{Holy Saturday Preces} \label{Holy Saturday Preces (Preces)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/misc.versus_litanici_in_cantu_sabbato_sancto--dominican--english--simple--rubrics}
 \subsubsection{The Lord's Prayer} \emph{When the \emph{Preces} are concluded all remain standing in silence until the Prior begins the Our Father.} \par \vspace{5pt}  \index[Varia]{The Lord's Prayer} \label{The Lord's Prayer (Varia)}         \input{varia/lords-prayer}
 \subsubsection{Concluding Prayer} \emph{When the Our Father is concluded the choir turns and kneels for the concluding collect.} \par \vspace{5pt}  \index[Concluding Prayer]{Good Friday} \label{Good Friday (Concluding Prayer)}         \input{prayers/or-holy-week-7-holy-saturday-morning-prayer}
              \par \vspace{10pt} \emph{All depart in silence.}

 \end{document}
