\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


\usepackage{unicode-math}
\setmathfont{LatinModernMath-Regular}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom



%%Combination

\chapter{Responsories and Gospel Canticles}
\section{Ordinary Time}
 \subsubsection{Responsorium brevis}  \greannotation{IV} \index[Responsorium brevis]{In manus tuas} \label{In manus tuas (Responsorium brevis)} \grecommentary[0pt]{Ps 30:6} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rb--in_manus}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Short responsory}  \greannotation{VI} \index[Short responsory]{Into your hands} \label{Into your hands (Short responsory)} \grecommentary[0pt]{Ps 30:6} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{syllable}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rb--into.your.hands}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}  \newpage
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{III a} \index[Antiphona ad Nunc dimittis]{Salva nos} \label{Salva nos (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--salva_nos--dominican}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{III a} \index[Canticum Evangelicum]{Nunc dimitis 3a} \label{Nunc dimitis 3a (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis3a}
 \subsubsection{Antiphon for the Nunc dimittis}  \greannotation{III a} \index[Antiphon for the Nunc dimittis]{Salva nos} \label{Salva nos (Antiphon for the Nunc dimittis)} \grecommentary[5pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{0pt}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--protect.us.lord}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Canticle of Simeon: Lk 2:29-32} \paragraph{Christ is the light of the nations and the glory of Israel}  \index[Gospel Canticle]{Canticle of Simeon: Lk 2:29-32} \label{Canticle of Simeon: Lk 2:29-32 (Gospel Canticle)}         \vspace{5pt} \par \input{psalms/lc2_29-32english}    \newpage

\section{Christmas}
\subsection{After First Vespers}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{VIII \textsc{g}} \index[Antiphona ad Nunc dimittis]{Ecce completa} \label{Ecce completa (Antiphona ad Nunc dimittis)} \grecommentary[0pt]{Cf. Lc 1:45} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--ecce_completa--dominican}  \vspace{5pt} \emph{Behold, all the things that were spoken by the angel concerning the Virgin Mary have been fulfilled.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{VIII \textsc{g}} \index[Canticum Evangelicum]{Nunc dimitis 8G} \label{Nunc dimitis 8G (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis8G}
\subsection{After Second Vespers and until Epiphany}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{V} \index[Antiphona ad Nunc dimittis]{Alleluia Verbum caro} \label{Alleluia Verbum caro (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Io 1:15} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--alleluia_verbum--dominican}  \vspace{5pt} \emph{Alleluia. The Word became flesh, alleluia, and dwelt among us, alleluia, alleluia.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{V} \index[Canticum Evangelicum]{Nunc dimitis V} \label{Nunc dimitis V (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis5}
\section{Epiphany}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{V} \index[Antiphona ad Nunc dimittis]{Alleluia Omnes de Saba} \label{Alleluia Omnes de Saba (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Is 60:6} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--alleluia_omnes_de_saba--dominican}  \vspace{5pt} \emph{Alleluia. All those from Sheba shall come, alleluia, bringing gold and frankincense, alleluia, alleluia.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{V} \index[Canticum Evangelicum]{Nunc dimitis V} \label{Nunc dimitis V (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis5}
\section{Lent}
 \subsubsection{Responsorium prolixa} \emph{Weekdays of Lent} \greannotation{VIII} \index[Responsorium prolixa]{In pace} \label{In pace (Responsorium prolixa)} \grecommentary[3pt]{Ps 4:9; \Vbar. Ps 131:4} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rp--in_pace--dominican}  \vspace{5pt} \emph{In peace, true peace, I will lie down and rest. \Vbar. If I shall give sleep to my eyes, or slumber to my eyelids. \Rbar. I will lie down and rest. \Vbar. Glory to the Father, and to the Son, and to the Holy Spirit. \Rbar. In peace, true peace, I will lie down and rest.}
 \subsubsection{Responsorium prolixa} \emph{On Saturdays, Sundays, Solemnities, Feasts, and during Holy Week} \vspace{5pt} \greannotation{IV} \index[Responsorium prolixa]{Media vita} \label{Media vita (Responsorium prolixa)} \grecommentary[0pt]{Ecclesia; \Vbar. Cf. Ps 70:9} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rp--media_vita--dominican}  \vspace{5pt} \emph{In the midst of life, we are in death. Whom shall we seek as a helper besides You, Lord, whose anger, with good reason, is enkindled because of our sins? Holy God, holy Mighty One, holy and merciful Savior, give us not over to bitter death. \Vbar. Do not reject us now that we are old; when our strength fails do not forsake us, Lord. \Rbar. Holy God, holy Mighty One, holy and merciful Savior, give us not over to bitter death.}
 \subsubsection{Responsorium} \emph{During the Paschal Triduum} \greannotation{VIII} \index[Responsorium]{Christus factus est} \label{Christus factus est (Responsorium)} \grecommentary[2pt]{Ph 2:8} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.christus_factus}  \vspace{5pt} \emph{Christ for our sake became obedient unto death, even death on a cross.}  \newpage
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{IV \textsc{e}} \index[Antiphona ad Nunc dimittis]{Evigila} \label{Evigila (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--evigila--dominican--compline}  \vspace{5pt} \emph{Watch over us, eternal Savior, that the wily tempter may not lay hold of us, for you have been made our helper for evermore.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{IV \textsc{e}} \index[Canticum Evangelicum]{Nunc dimitis IVE} \label{Nunc dimitis IVE (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis4E}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{III a} \index[Antiphona ad Nunc dimittis]{O Rex} \label{O Rex (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--o_rex--dominican}  \vspace{5pt} \emph{O King, resplendent in the midst of your saints, ever worthy of praise yet surpassing all words: you, O Lord, are in our midst, and we are called by your holy name; do not forsake us, O Lord our God. On that day of judgment, O blessed King, may you deign to place us among your saints and chosen ones.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{III a} \index[Canticum Evangelicum]{Nunc dimitis IVE} \label{Nunc dimitis IVE (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis3a}
\section{Easter}
\subsection{Easter Sunday and throughout the Octave of Easter}
 \subsubsection{Responsorium Prolixa}  \greannotation{II} \index[Responsorium Prolixa]{Haec dies} \label{Haec dies (Responsorium Prolixa)} \grecommentary[0pt]{Ps 117:24} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rp--haec_dies--dominican}  \vspace{5pt} \emph{This is the day the Lord has made; let us rejoice and be glad in it.}
 \subsubsection{Responsorium (Dominican)}  \greannotation{II} \index[Responsorium (Dominican)]{This is the day (Dominican)} \label{This is the day (Dominican) (Responsorium (Dominican))} \grecommentary[0pt]{Ps 117:24} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rp--haec_dies--dominican--english-simple}  \vspace{5pt} \emph{This is the day the Lord has made; let us rejoice and be glad in it.}
 \subsubsection{Responsorium (Gethsemani)}  \greannotation{VIII} \index[Responsorium (Gethsemani)]{This is the day (Gethsemani)} \label{This is the day (Gethsemani) (Responsorium (Gethsemani))} \grecommentary[0pt]{Ps 117:24} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rp--haec_dies--trappist--english-simple}  \vspace{5pt} \emph{This is the day the Lord has made; let us rejoice and be glad in it.}
\subsection{Throughout the season of Easter}
 \subsubsection{Responsorium brevis}  \greannotation{IV} \index[Responsorium brevis]{In manus tuas ... alleluia} \label{In manus tuas ... alleluia (Responsorium brevis)} \grecommentary[0pt]{Cf. Ps 30:6} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rb--in_manus_alleluia}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Short responsory}  \greannotation{VI} \index[Short responsory]{Into your hands ... alleluia} \label{Into your hands ... alleluia (Short responsory)} \grecommentary[0pt]{Cf. Ps 30:6} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{syllable}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/rb--into.your.hands.alleluia}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}  \newpage
\subsection{Easter until the Ascension}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{V} \index[Antiphona ad Nunc dimittis]{Alleluia Resurrexit} \label{Alleluia Resurrexit (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Cf. 1 Cor 15:12} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--alleluia_ascendens--dominican}  \vspace{5pt} \emph{Alleluia. When Christ ascended on high, alleluia, he led captivity captive, alleluia, alleluia.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{V} \index[Canticum Evangelicum]{Nunc dimitis V} \label{Nunc dimitis V (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis5}
\subsection{The Ascension until Pentecost}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{V} \index[Antiphona ad Nunc dimittis]{Alleluia Ascendens} \label{Alleluia Ascendens (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Io 15:26} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--alleluia_spiritus--dominican}  \vspace{5pt} \emph{Alleluia. The Spirit, the Counselor, alleluia, will teach you all things, alleluia, alleluia.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{V} \index[Canticum Evangelicum]{Nunc dimitis V} \label{Nunc dimitis V (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis5}
\section{Solemnities and Feasts}
\subsection{The Presentation of the Lord (February 2)}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{VII a} \index[Antiphona ad Nunc dimittis]{Nunc dimitis} \label{Nunc dimitis (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Lc 2:29-30} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--nunc_dimittis--dominican}  \vspace{5pt} \emph{Now, Lord, you give leave to your servant to go in peace, for my eyes have seen your salvation.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{VII a} \index[Canticum Evangelicum]{Nunc dimitis VIIa} \label{Nunc dimitis VIIa (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis7a}
\subsection{The Annunciation of the Lord (March 25)}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{VIII c} \index[Antiphona ad Nunc dimittis]{Ecce ancilla Domini} \label{Ecce ancilla Domini (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Lc 1:38} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--ecce_ancilla--dominican}  \vspace{5pt} \emph{Behold, I am the handmaid of the Lord; let it be done to me according to your word.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{VIII c} \index[Canticum Evangelicum]{Nunc dimitis VIIIc} \label{Nunc dimitis VIIIc (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis8c}
\subsection{The Most Holy Body and Blood of Christ}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{V} \index[Antiphona ad Nunc dimittis]{Alleluia Panis} \label{Alleluia Panis (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Io 6:52} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--alleluia_panis--dominican}  \vspace{5pt} \emph{Alleluia. The bread which I shall give, alleluia, is my flesh for the life of the world, alleluia, alleluia.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{V} \index[Canticum Evangelicum]{Nunc dimitis V} \label{Nunc dimitis V (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis5}
\subsection{The Most Sacred Heart of Jesus}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{V} \index[Antiphona ad Nunc dimittis]{Alleluia Haurietis} \label{Alleluia Haurietis (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Is 12:3} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--alleluia_haurietis--dominican}  \vspace{5pt} \emph{Alleluia. With joy you will draw, alleluia, from the wells of salvation, alleluia, alleluia.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{V} \index[Canticum Evangelicum]{Nunc dimitis V} \label{Nunc dimitis V (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis5}
\subsection{Solemnities and Feasts of the Blessed Virgin Mary}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{VIII \textsc{g}} \index[Antiphona ad Nunc dimittis]{Corde et animo} \label{Corde et animo (Antiphona ad Nunc dimittis)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--corde_et_animo--dominican}  \vspace{5pt} \emph{With heart and mind let us sing glory to Christ on this sacred festival of the illustrious Mary, mother of God.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{VIII \textsc{g}} \index[Canticum Evangelicum]{Nunc dimitis V} \label{Nunc dimitis V (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis8G}
 \subsubsection{Antiphona ad Nunc dimittis}  \greannotation{VII a} \index[Antiphona ad Nunc dimittis]{Sub tuum} \label{Sub tuum (Antiphona ad Nunc dimittis)} \grecommentary[3pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--sub_tuum--dominican}  \vspace{5pt} \emph{We fly to your protection, holy mother of God. Do not despise our prayers in our needs, but ever deliver us from all dangers, O blessed Virgin.}
 \subsubsection{Canticum Evangelicum} \paragraph{Christus lumen gentium et gloria Israel} \greannotation{VII a} \index[Canticum Evangelicum]{Nunc dimitis VIIa} \label{Nunc dimitis VIIa (Canticum Evangelicum)} \grecommentary[3pt]{Lc 2:29-32} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/nunc_dimitis7a}       


  \end{document}
