\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%\usepackage{unicode-math}
%\setmathfont{LatinModernMath-Regular}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter[The Most Holy Trinity]{The Most Holy Trinity\\(Years A, B, and C)}                  
\section{Second Vespers}                  
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium}   \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen. Alleluia.} 
 \subsubsection{Hymnus}  \greannotation{I} \index[Hymnus]{Adesto sancta Trinitas} \label{Adesto sancta Trinitas (Hymnus)} \grecommentary[10pt]{\emph{Adesto sancta Trinitas}} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}  \grechangedim{spaceabovelines}{0.25 cm}{scalable} \gregorioscore{chants/hy--adesto_sancta_trinitas}    
 \subsubsection{Antiphona}  \greannotation{IV \textsc{e}} \index[Antiphona]{O vera} \label{O vera (Antiphona)} \grecommentary[5pt]{Ecclesia [AR]} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/an--o_vera--solesmes-op}   \vspace{5pt} \emph{O true, complete, sempiternal Trinity, Father, Son, Holy Spirit.} 
 \subsubsection{Psalm 109}   \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm109english3-3}    
 \subsubsection{Antiphona}  \greannotation{VI} \index[Antiphona]{Libera nos} \label{Libera nos (Antiphona)} \grecommentary[5pt]{Ecclesia} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--libera_nos--op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Free us, save us, justify us, O blessed Trinity.} 
 \subsubsection{Psalm 113A}   \index[Psalmus]{Psalm 113A} \label{Psalm 113A (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm113Aenglish3-3}    \newpage
 \subsubsection{Antiphona}  \greannotation{V} \index[Antiphona]{Sanctus sanctus} \label{Sanctus sanctus (Antiphona)} \grecommentary[5pt]{Ap 4:8 [AR]} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel} \emph{The antiphon is sung with the canticle in the mode of a trope, before and after the canticle.} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--sanctus_sanctus_sanctus--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Holy, Holy, Holy, Lord God almighty, who was, and who is, and who is to come.} 
 \subsubsection{Canticum} \paragraph{The wedding of the Lamb} \greannotation{V} \index[Canticum]{Salus et gloria} \label{Salus et gloria (Canticum)} \grecommentary[0pt]{Cf. Ap 19:1-2, 5-7 [AR]} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}  \grechangedim{spaceabovelines}{0.5cm}{scalable} \gregorioscore{chants/canticle--salus-et-honor--5--english}  \grechangedim{spaceabovelines}{0cm}{scalable}  \newpage
 \subsubsection{Lectio brevis}     \hfill Eph 4:3-6        \input{readings/lectio_brevis_Eph.4.3-6.tex}    
 \subsubsection{Responsorium brevis}  \greannotation{VI} \index[Responsorium brevis]{Benedicamus Patrem ... alleluia} \label{Benedicamus Patrem ... alleluia (Responsorium brevis)} \grecommentary[3pt]{Ecclesia} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/rb--benedicamus_patrem__alleluia--op}   \vspace{5pt} \emph{Let us bless the Father and the Son and the Holy Spirit, alleluia, alleluia. \Vbar. Let us praise and exalt him forever.} \newpage
 \subsubsection{Antiphona ad Magnificat}  \greannotation{IV \textsc{e}} \index[Antiphona ad Magnificat]{Te Deum Patrem} \label{Te Deum Patrem (Antiphona ad Magnificat)} \grecommentary[3pt]{Ecclesia} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--te_deum_patrem--dominican--id_6122}   \vspace{5pt} \emph{Unbegotten Father, only-begotten Son, Holy Spirit Comforter, most holy and undivided Trinity: with our whole heart and voice we confess, praise, and bless you, O God; to you be glory for ever.} 
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{IV \textsc{e}} \index[Canticum Evangelicum]{Magnificat 4E} \label{Magnificat 4E (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{spaceabovelines}{0.4 cm}{scalable} \gregorioscore{chants/magnificat4E}  \grechangedim{spaceabovelines}{0 cm}{scalable} \input{chants/magnificat-translation} 
 \subsubsection{Preces}   \index[Preces]{} \label{ (Preces)}         \input{intercessions/intercessions-solemnities-trinity}    
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}  \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/or--pater_noster_a--solesmes}   \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} 
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{} \label{ (Oratio conclusiva)}         \input{prayers/or-solemnities-trinity}    
 \subsubsection{Ritus conclusionis}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.    
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Solemnities} \label{Solemnities (Benedicamus Domino)}         \gregorioscore{chants/misc.benedicamus.dominio.1-T}    
 
  \end{document}
