\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination

\chapter[The Body and Blood of the Lord]{The Body and Blood of the Lord\\(Years A, B, and C)}
\section{Second Vespers}                  \newpage \null\newpage
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium}   \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen. Alleluia.} \newpage
 \subsubsection{Hymnus}  \greannotation{III} \index[Hymnus]{Pange lingua gloriosi, Corporis} \label{Pange lingua gloriosi, Corporis (Hymnus)} \grecommentary[10pt]{\emph{Pange lingua gloriosi, Corporis}} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}  \grechangedim{spaceabovelines}{0.25 cm}{scalable} \gregorioscore{chants/hy--pange_lingua_gloriosi_corporis--english}    \newpage
 \subsubsection{Antiphona}  \greannotation{I g} \index[Antiphona]{Sacerdos in aeternum} \label{Sacerdos in aeternum (Antiphona)} \grecommentary[7pt]{Ps 109:4; cf. Gen 14:18} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/an--sacerdos_in_aeternum--dominican--id_7099}   \vspace{5pt} \emph{A priest for ever according to the Order of Melchisedech, Christ the Lord offered bread and wine.}
 \subsubsection{Psalm 109}   \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm109english3-3}
 \subsubsection{Antiphona}  \greannotation{II} \index[Antiphona]{Calicem salutaris} \label{Calicem salutaris (Antiphona)} \grecommentary[3pt]{Ps 115:4, 8} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--calicem--dominican--id_5506}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{I will take up the chalice of salvation, and I will call upon the name of the Lord.}
 \subsubsection{Psalm 115}   \index[Psalmus]{Psalm 115} \label{Psalm 115 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm115english2-3}
 \subsubsection{Antiphona}  \greannotation{II} \index[Antiphona]{Tu es via} \label{Tu es via (Antiphona)} \grecommentary[5pt]{Cf. Io 14:6 [AR]} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel} \emph{The antiphon is sung with the canticle in the mode of a trope, before and after the canticle.} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--tu_es_via--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{You are the Way, you are the Truth, you are the Life of the World, O Lord.}
 \subsubsection{Canticum} \paragraph{The wedding of the Lamb} \greannotation{II} \index[Canticum]{Salus et gloria} \label{Salus et gloria (Canticum)} \grecommentary[0pt]{Cf. Ap 19:1-2, 5-7} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/canticle--salus-et-honor--2}    \newpage
 \subsubsection{Lectio brevis}     \hfill 1 Cor 11:23-24        \input{readings/lectio_brevis_1.Cor.11.23-25.tex}
 \subsubsection{Responsorium brevis}  \greannotation{VI} \index[Responsorium brevis]{Panem caeli} \label{Panem caeli (Responsorium brevis)} \grecommentary[0pt]{Ps 77:24-25} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/rb--panem_caeli_dedit_eis--dominican--id_5555}   \vspace{5pt} \emph{He gave them bread from heaven, alleluia, alleluia. \Vbar. Man ate the bread of angels.}
 \subsubsection{Antiphona ad Magnificat}  \greannotation{V} \index[Antiphona ad Magnificat]{O sacrum convivium} \label{O sacrum convivium (Antiphona ad Magnificat)} \grecommentary[3pt]{S. Thomas Aquinatis} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--o_sacrum_convivium--dominican--id_7187}   \vspace{5pt} \emph{O Sacred Banquet, in which Christ is received; the memory of his Passion is recalled, the soul is filled with grace, and a pledge of future glory is given to us, alleluia, alleluia.}
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{V} \index[Canticum Evangelicum]{Magnificat 5} \label{Magnificat 5 (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{spaceabovelines}{0.4 cm}{scalable} \gregorioscore{chants/magnificat5}  \grechangedim{spaceabovelines}{0 cm}{scalable} \input{chants/magnificat-translation} \newpage
 \subsubsection{Preces}   \index[Preces]{Second Sunday of Easter} \label{Second Sunday of Easter (Preces)}         \input{intercessions/intercessions-solemnities-corpus_christi}    \newpage
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}  \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/or--pater_noster_a--solesmes}   \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} \newpage
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{Second Sunday of Easter} \label{Second Sunday of Easter (Oratio conclusiva)}         \input{prayers/or-solemnities-corpus_christi}
 \subsubsection{Ritus conclusionis}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Solemnities} \label{Solemnities (Benedicamus Domino)}  \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/misc.benedicamus.dominio.1-T}    

  \end{document}
