\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination

\chapter{The Holy Family of Jesus, Mary and Joseph}
\section{Second Vespers}                  \newpage
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium-T}
 \subsubsection{Hymnus}  \greannotation{I} \index[Hymnus]{O lux beata caelitum} \label{O lux beata caelitum (Hymnus)} \grecommentary[2pt]{\emph{O lux beata caelitum}} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/hy--o_lux_beata_caelitum--english}
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Post triduum} \label{Post triduum (Antiphona)} \grecommentary[5pt]{Lc 2:46} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--post_triduum--dominican--id_4852} \vspace{5pt} \emph{After three days, they found Jesus in the temple, siting in the mist of the teachers, listening to them and asking them questions.} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Psalm 121} \paragraph{Holy city Jerusalem}  \index[Psalmus]{Psalm 121} \label{Psalm 121 (Psalmus)} \emph{You have come to Mount Zion, to the city of the living God, heavenly Jerusalem (Hebrews 12:22).}        \vspace{5pt} \par \input{psalms/psalm121english2-2}    \newpage
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Descendit Iesus} \label{Descendit Iesus (Antiphona)} \grecommentary[5pt]{Lc 2:51} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--descendit_iesus_ii--dominican--id_4798} \vspace{5pt} \emph{Jesus went down with them and came to Nazareth, and was obedient to them.} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Psalm 126} \paragraph{Apart from God our labors are worthless}  \index[Psalmus]{Psalm 126} \label{Psalm 126 (Psalmus)} \emph{You are God’s building (1 Corinthians 3:9).}        \vspace{5pt} \par \input{psalms/psalm126english2-2}    \newpage
 \subsubsection{Antiphona}  \greannotation{VI} \index[Antiphona]{Puer Iesus proficiebat} \label{Puer Iesus proficiebat (Antiphona)} \grecommentary[0pt]{Lc 2:52} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--puer_iesus_proficiebat} \vspace{5pt} \emph{The boy Jesus progressed in age and wisdom in the presence of God and men.} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Eph 1:3-10} \paragraph{God our Savior}  \index[Canticum]{Eph 1:3-10} \label{Eph 1:3-10 (Canticum)}         \vspace{5pt} \par \input{psalms/eph1_3-10english3-3}
 \subsubsection{Lectio brevis}     \hfill Ph 2:6-7        \input{readings/lectio_brevis_Ph.2.6-7.tex}    \newpage
 \subsubsection{Responsorium brevis}  \greannotation{VI} \index[Responsorium brevis]{Verbum caro} \label{Verbum caro (Responsorium brevis)} \grecommentary[0pt]{Heb 2:17; Bar 3:38 [AR]} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/rb--debuit_per_omnia--solesmes-op} \vspace{5pt} \emph{He ought to be like his brothers in all things, that he might show his mercy. \Vbar. He was seen on earth, and conversed with human beings.} \newpage
 \subsubsection{Antiphona ad Magnificat}  \greannotation{VIII \textsc{g}} \index[Antiphona ad Magnificat]{Fili quid fecisti} \label{Fili quid fecisti (Antiphona ad Magnificat)} \grecommentary[5pt]{Cf. Lc 2:10-14; Ps 67:4} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--fili_quid_fecisti--dominican--id_6379} \vspace{5pt} \emph{``Son, why have you done this to us? I and your father were full of sorrow while we sought for you.” ``Why did you seek me? Did you not know that it is fitting for me to be involved with these things that are my Father’s?”} 
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{VIII \textsc{g}} \index[Canticum Evangelicum]{} \label{ (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/magnificat8G} \input{chants/magnificat-translation}   \newpage
 \subsubsection{Preces}   \index[Preces]{Mary, the Holy Mother of God} \label{Mary, the Holy Mother of God (Preces)}         \input{intercessions/intercessions-holy_family-2nd-verspers}    \newpage
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}  \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/or--pater_noster_a--solesmes-T}
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{} \label{ (Oratio conclusiva)}         \input{prayers/or-holy-family}
 \subsubsection{Ritus conclusionis}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Feasts} \label{Feasts (Benedicamus Domino)}         \gregorioscore{chants/misc.benedicamus.dominio.3-T}



  \end{document}
