\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


\usepackage{unicode-math}
\setmathfont{LatinModernMath-Regular}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{4\textsuperscript{th} Sunday of Lent (Year A)}
\section{Second Vespers}
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.25 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium-lent} \grechangedim{spaceabovelines}{0 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen.}
 \subsubsection{Hymnus}  \greannotation{IV} \index[Hymnus]{Audi benigne conditor} \label{Audi benigne conditor (Hymnus)} \grecommentary[3pt]{\emph{Audi benigne conditor}} \gresetinitiallines{1} \gresetlyriccentering{syllable} \grechangedim{spaceabovelines}{0.25 cm}{scalable} \gregorioscore{chants/hy--audi_benigne--english} \grechangedim{spaceabovelines}{0 cm}{scalable}   \newpage
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{De torrente} \label{De torrente (Antiphona)} \grecommentary[5pt]{Ps 109:7 [AR]} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.3 cm}{scalable} \gregorioscore{chants/an--de_torrente--solesmes-op} \grechangedim{spaceabovelines}{0 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{He will drink from the rushing stream on the way, and therefore he shall lift up his head.}
 \subsubsection{Psalm 109}   \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)}     \vspace{5pt} \par \input{psalms/psalm109english2-2}
 \subsubsection{Antiphona}  \greannotation{I \textsc{d}} \index[Antiphona]{Iucundus homo} \label{Iucundus homo (Antiphona)} \grecommentary[0pt]{Ps 111:5, 6 [AR]} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--iucundus_homo--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Happy the man who is merciful in the Lord: he will not be disturbed forever.}
 \subsubsection{Psalm 111}   \index[Psalmus]{Psalm 111} \label{Psalm 111 (Psalmus)}     \vspace{5pt} \par \input{psalms/psalm111english3-3}
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Christus passus} \label{Christus passus (Antiphona)} \grecommentary[0pt]{1 Petr 2:21 [AR]} \gresetinitiallines{1}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--christus_passus--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Christ suffered for you, leaving an example for you, that you might follow in his footsteps.}
 \subsubsection{1 Petr 2:21-24}   \index[Canticum]{1 Petr 2:21-24} \label{1 Petr 2:21-24 (Canticum)}     \vspace{5pt} \par \input{psalms/1petr2_21-24english2-2}
 \subsubsection{Lectio brevis}     \hfill 1 Cor 9:24-25    \input{readings/lectio_brevis_1.Cor.9.24-25.tex}
 \subsubsection{Responsorium brevis}  \greannotation{VI} \index[Responsorium brevis]{Redemisti nos} \label{Redemisti nos (Responsorium brevis)} \grecommentary[0pt]{Apoc 5:9} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/rb--redemisti_nos_lent}   \vspace{5pt} \emph{Redeem us, O Lord, in your blood. \Vbar. From every tribe, and tongue, and people, and nation.} \newpage
 \subsubsection{Antiphona ad Magnificat}  \greannotation{III a} \index[Antiphona ad Magnificat]{Ille homo} \label{Ille homo (Antiphona ad Magnificat)} \grecommentary[0pt]{Io 9:11, 6, 25} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/an--ille_homo--dominican--id_4805}   \vspace{5pt} \emph{That man, who is called Jesus, made clay from saliva, and anointed my eyes, and now I can see.}
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{III a} \index[Canticum Evangelicum]{} \label{ (Canticum Evangelicum)} \grecommentary[5pt]{Lc 1:46-55} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/magnificat3a}   \input{chants/magnificat-translation}
 \subsubsection{Preces}   \index[Preces]{} \label{ (Preces)}     \input{intercessions/intercessions-lent-4-sunday-2nd-vespers}    \newpage
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}   \grechangedim{spaceabovelines}{0.4 cm}{scalable}  \gregorioscore{chants/or--pater_noster_a--solesmes} \grechangedim{spaceabovelines}{0 cm}{scalable}  \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} \newpage
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{Second Sunday of Lent} \label{Second Sunday of Lent (Oratio conclusiva)}     \input{prayers/or-lent-4}
 \subsubsection{Ritus conclusionis}         \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Sundays} \label{Sundays (Benedicamus Domino)}      \gregorioscore{chants/misc.benedicamus.dominio.4-T}

  \end{document}
