\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


\usepackage{unicode-math}
\setmathfont{LatinModernMath-Regular}
\AtBeginDocument{\grelatexsimpledefbarredsymbol{V}{0.1em}{0.12em}{0.14em}{0.18em}}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter[Easter Sunday of the Resurrection of the Lord]{Easter Sunday\\of the Resurrection of the Lord}
\section{Second Vespers}                  \cleardoublepage
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium}   \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen. Alleluia.}
 \subsubsection{Hymnus}  \greannotation{I} \index[Hymnus]{Ad cenam Agni providi} \label{Ad cenam Agni providi (Hymnus)} \grecommentary[10pt]{\emph{Ad cenam Agni providi}} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/hy--ad_cenam_agni--english}    \newpage
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Angelus autem Domini} \label{Angelus autem Domini (Antiphona)} \grecommentary[3pt]{Mt 28:2} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/an--angelus_autem_domini--dominican--id_6988}   \vspace{5pt} \emph{The angel of the Lord descended from heaven; and coming forward he removed the stone, and sat upon it, alleluia, alleluia.}
 \subsubsection{Psalm 109}   \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm109english2-2}    \newpage
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Consilium fecerunt} \label{Consilium fecerunt (Antiphona)} \grecommentary[5pt]{Mt 28:6 [AR]} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--venite_et_videte--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Come, and see the place where the Lord was buried, alleluia, alleluia.}
 \subsubsection{Psalm 113A}   \index[Psalmus]{Psalm 113A} \label{Psalm 113A (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm113Aenglish2-2}    \newpage
 \subsubsection{Antiphona}  \greannotation{IV} \index[Antiphona]{Ite nuntiate} \label{Ite nuntiate (Antiphona)} \grecommentary[0pt]{Mt 28:10 [AR]} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel} \emph{The antiphon is sung with the canticle in the mode of a trope, before and after the canticle.} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--ite_nuntiate--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Go, announce to my brothers, alleluia, that they should go to Galilee; there they will see me, alleluia, alleluia, alleluia.}
 \subsubsection{Canticum} \paragraph{The wedding of the Lamb} \greannotation{IV} \index[Canticum]{Salus et gloria} \label{Salus et gloria (Canticum)} \grecommentary[0pt]{Cf. Ap 19:1-2, 5-7 [AR]} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/canticle--salus-et-honor--4--english}    \newpage
 \subsubsection{Lectio brevis}     \hfill Heb 10:12-14        \input{readings/lectio_brevis_Heb.10.12-14.tex}
 \subsubsection{Responsorium}  \greannotation{II} \index[Responsorium]{Haec dies} \label{Haec dies (Responsorium)} \grecommentary[0pt]{Ps 117:24} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/rp--haec_dies--dominican}   \vspace{5pt} \emph{This is the day the Lord has made; let us rejoice and be glad in it.} \newpage
 \subsubsection{Antiphona ad Magnificat}  \greannotation{I \textsc{d}} \index[Antiphona ad Magnificat]{Cum esset sero} \label{Cum esset sero (Antiphona ad Magnificat)} \grecommentary[3pt]{Io 20:19} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--cum_esset_sero--dominican--id_5636}   \vspace{5pt} \emph{When evening came on that day, the first day of the week, and the doors were locked where the disciples were gathered, Jesus stood in their midst and said to them: ``Peace be with you, alleluia.”}


\newpage

\subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{I \textsc{d}} \index[Canticum Evangelicum]{Magnificat !D} \label{Magnificat !D (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}

\gabcsnippet{(c4)Ma(f)gní(gh)fi(h)cat.(h) (::)}

\newpage \gabcsnippet{(c4) Qui(f)a(gh) re(h)spé(h)xit(h) hu(h)mi(h)li(h)tá(h)tem(h) an(hg)cíl(ixgi)læ(h) su(hg)æ.(gh) <v>$\star$</v>(:)
 Ec(h)ce(h) e(h)nim(h) ex(h) hoc(h) be(h)á(h)tam(h) me(h) di(h)cent(h) om(h)nes(h) ge(h)ne(h)ra(g)ti(f)ó(gh)nes,(gvFED) (::)}

\newpage \gabcsnippet{(c4) Et(f) mi(gh)se(h)ri(h)cór(h)di(h)a(h) e(h)ius(h) a(h) pro(h)gé(h)ni(h)e(hg) in(ixgi) pro(h)gé(h)ni(hg)es(gh) <v>$\star$</v>(:)
 ti(h)mén(h)ti(g)bus(f) e(gh)um.(gvFED) (::)}

\newpage \gabcsnippet{(c4) De(f)pó(gh)su(h)it(h) po(h)tén(hg)tes(ixgi) de(h) se(hg)de(gh) <v>$\star$</v>(:)
 et(h) ex(h)al(h)tá(g)vit(f) hú(gh)mi(g)les;(gvFED) (::)}

\newpage \gabcsnippet{(c4) Sus(f)cé(gh)pit(h) Is(h)ra(h)el(h) pú(hg)e(ixgi)rum(h) su(hg)um,(gh) <v>$\star$</v>(:)
 re(h)cor(h)dá(h)tus(h) mi(h)se(h)ri(h)cór(h)di(g)æ(f) su(gh)æ,(gvFED) (::)}

\newpage \gabcsnippet{(c4) Gló(f)ri(gh)a(h) Pa(hg)tri,(ixgi) et(h) Fí(h)li(hg)o,(gh) <v>$\star$</v>(:)
 et(h) Spi(h)rí(h)tu(g)i(f) San(gh)cto.(gvFED) (::)}

%%  \gregorioscore{chants/magnificat1D-f3}   \input{chants/magnificat-translation}

\newpage



 \subsubsection{Preces}   \index[Preces]{Second Sunday of Easter} \label{Second Sunday of Easter (Preces)}         \input{intercessions/intercessions-easter-1-sunday-second-vespers}    \newpage
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}  \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/or--pater_noster_a--solesmes}   \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} \newpage
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{Second Sunday of Easter} \label{Second Sunday of Easter (Oratio conclusiva)}         \input{prayers/or-easter-1}
 \subsubsection{Ritus conclusionis}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Dismissio}   \index[Dismissio]{Easter Octave} \label{Easter Octave (Dismissio)}  \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/va--ite_in_pace_alleluia--solesmes-op}

  \end{document}
