\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


\usepackage{unicode-math}
\setmathfont{LatinModernMath-Regular}
\AtBeginDocument{\grelatexsimpledefbarredsymbol{V}{0.1em}{0.12em}{0.14em}{0.18em}}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter[6\textsuperscript{th} Sunday of Easter (Year A)]{6\textsuperscript{th} Sunday of Easter (Year A)}
\section{Second Vespers}
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.25 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium} \grechangedim{spaceabovelines}{0 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen. Alleluia.}
 \subsubsection{Hymnus}  \greannotation{I} \index[Hymnus]{Ad cenam Agni providi} \label{Ad cenam Agni providi (Hymnus)} \grecommentary[10pt]{\emph{Ad cenam Agni providi}} \gresetinitiallines{1} \gresetlyriccentering{syllable} \grechangedim{spaceabovelines}{0.25 cm}{scalable} \gregorioscore{chants/hy--ad_cenam_agni--english} \grechangedim{spaceabovelines}{0 cm}{scalable}
 \subsubsection{Antiphona}  \greannotation{IV \textsc{e}} \index[Antiphona]{Sedebit Dominus} \label{Sedebit Dominus (Antiphona)} \grecommentary[3pt]{Ps 28:10 [AR]} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/an--sedebit_dominus--solesmes-op} \grechangedim{spaceabovelines}{0 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{The Lord will reign as King forever, alleluia.}
 \subsubsection{Psalm 109}   \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)}     \vspace{5pt} \par \input{psalms/psalm109english3-3}
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Nomini tuo} \label{Nomini tuo (Antiphona)} \grecommentary[5pt]{Ps 113:9 [AR]} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--nomini_tuo--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{To your Name, O Lord, give the glory, alleluia.}
 \subsubsection{Psalm 113B}   \index[Psalmus]{Psalm 113B} \label{Psalm 113B (Psalmus)}     \vspace{5pt} \par \input{psalms/psalm113Benglish2-2}    \newpage
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Benedictio et claritas} \label{Benedictio et claritas (Antiphona)} \grecommentary[5pt]{Ap 7:12 [AR]} \gresetinitiallines{1} \emph{The antiphon is sung with the canticle in the mode of a trope, before and after the canticle.} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--benedictio_et_claritas--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Benediction and renown and wisdom and thanksgiving, honor, power, and strength to our God forever and ever. Amen. Alleluia.}
 \subsubsection{Canticum} \paragraph{The wedding of the Lamb} \greannotation{VIII \textsc{g}} \index[Canticum]{Salus et gloria} \label{Salus et gloria (Canticum)} \grecommentary[4pt]{Cf. Ap 19:1-2, 5-7 [AR]} \gresetinitiallines{1} \gresetlyriccentering{syllable}  \gregorioscore{chants/canticle--salus-et-honor--8--english}
 \subsubsection{Lectio brevis}     \hfill Heb 10:12-14    \input{readings/lectio_brevis_Heb.10.12-14.tex}    \newpage
 \subsubsection{Responsorium brevis}  \greannotation{VI} \index[Responsorium brevis]{Surrexit Dominus vere} \label{Surrexit Dominus vere (Responsorium brevis)} \grecommentary[0pt]{Lc 24:34} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/rb--surrexit_dominus_vere--op}   \vspace{5pt} \emph{The Lord has truly risen, alleluia, alleluia. \Vbar. He appeared to Simon.}
 \subsubsection{Antiphona ad Magnificat}  \greannotation{V} \index[Antiphona ad Magnificat]{Adhuc modicum} \label{Adhuc modicum (Antiphona ad Magnificat)} \grecommentary[3pt]{Io 14:19 [AR]} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/an--adhuc_modicum--solesmes-op}   \vspace{5pt} \emph{In a little while, the world will no longer see me; but you will see me, because I live, and you will live, alleluia.} \newpage
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{V} \index[Canticum Evangelicum]{Magnificat 5} \label{Magnificat 5 (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{spaceabovelines}{0.4 cm}{scalable} \gregorioscore{chants/magnificat5}  \grechangedim{spaceabovelines}{0 cm}{scalable} \input{chants/magnificat-translation}
 \subsubsection{Preces}   \index[Preces]{Second Sunday of Easter} \label{Second Sunday of Easter (Preces)}     \input{intercessions/intercessions-easter-6-sunday-second-vespers}
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}   \grechangedim{spaceabovelines}{0.4 cm}{scalable}  \gregorioscore{chants/or--pater_noster_a--solesmes} \grechangedim{spaceabovelines}{0 cm}{scalable}  \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.}
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{Second Sunday of Easter} \label{Second Sunday of Easter (Oratio conclusiva)}     \input{prayers/or-easter-6}
 \subsubsection{Ritus conclusionis}         \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Easter Season Sundays} \label{Easter Season Sundays (Benedicamus Domino)}   \grechangestyle{translation}{\textnormal\selectfont}  \gregorioscore{chants/misc.benedicamus.dominio.alleluia.1}  \grechangestyle{translation}{\it\selectfont}  

  \end{document}
