\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


\usepackage{unicode-math}
\setmathfont{LatinModernMath-Regular}



%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2017}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{3\textsuperscript{rd} Sunday of Lent (Year B)}
\section{Second Vespers}
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.25 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium-lent} \grechangedim{spaceabovelines}{0 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen.}
 \subsubsection{Hymnus}  \greannotation{IV} \index[Hymnus]{Audi benigne conditor} \label{Audi benigne conditor (Hymnus)} \grecommentary[0pt]{\emph{Audi benigne conditor}} \gresetinitiallines{1} \gresetlyriccentering{syllable} \grechangedim{spaceabovelines}{0.25 cm}{scalable} \gregorioscore{chants/hy--audi_benigne--english} \grechangedim{spaceabovelines}{0 cm}{scalable}   \newpage
 \subsubsection{Antiphona}  \greannotation{II} \index[Antiphona]{Domine rex omnipotens} \label{Domine rex omnipotens (Antiphona)} \grecommentary[5pt]{Cf. Ps 78:9; Sap 12:19 [AR]} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.3 cm}{scalable} \gregorioscore{chants/an--domine_rex_omipotens_--solesmes-op} \grechangedim{spaceabovelines}{0 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{O Lord, almighty King, free us on account of your name, and give to us a place of penitence.}
 \subsubsection{Psalm 109}   \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)}     \vspace{5pt} \par \input{psalms/psalm109english2-3}
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Salus nostra} \label{Salus nostra (Antiphona)} \grecommentary[7pt]{Ecclesia [AR]} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--salus_nostra_--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Our salvation is in your hands, O Lord: look upon us with your mercy, that we may serve you securely.}
 \subsubsection{Psalm 110}   \index[Psalmus]{Psalm 110} \label{Psalm 110 (Psalmus)}     \vspace{5pt} \par \input{psalms/psalm110english2-2}    \newpage
 \subsubsection{Antiphona}  \greannotation{III a} \index[Antiphona]{Vere languores} \label{Vere languores (Antiphona)} \grecommentary[3pt]{Is 53:4} \gresetinitiallines{1}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--vere_languores--dominican}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Truly he bore our infirmities, and he himself underwent our sufferings.}
 \subsubsection{1 Petr 2:21-24}   \index[Canticum]{1 Petr 2:21-24} \label{1 Petr 2:21-24 (Canticum)}     \vspace{5pt} \par \input{psalms/1petr2_21-24english3-3}
 \subsubsection{Lectio brevis}     \hfill 1 Cor 9:24-25    \input{readings/lectio_brevis_1.Cor.9.24-25.tex}
 \subsubsection{Responsorium brevis}  \greannotation{IV} \index[Responsorium brevis]{Inclina cor meum} \label{Inclina cor meum (Responsorium brevis)} \grecommentary[0pt]{Ps 118:36-37} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/rb--inclina_cor_meum--dominican--id_7105}   \vspace{5pt} \emph{Incline my heart, O Lord, according to your testimony. \Vbar. Turn my eyes lest they see vanities: give me life in your way.} \newpage

  \subsubsection{Antiphona ad Magnificat}  \greannotation{VIII \textsc{g}} \index[Antiphona ad Magnificat]{Scriptum est enim} \label{Scriptum est enim (Antiphona ad Magnificat)} \grecommentary[5pt]{Lc 19:46-47} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--scriptum_est--dominican--id_6862}   \vspace{5pt} \emph{``It is written that my house is a house of prayer for all the nations; but you have made it a den of thieves.” And he was teaching every day in the temple.}

 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{VIII \textsc{g}} \index[Canticum Evangelicum]{Magnificat 3a} \label{Magnificat 8G (Canticum Evangelicum)} \grecommentary[5pt]{Lc 1:46-55} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/magnificat8G}   \input{chants/magnificat-translation}
 \subsubsection{Preces}   \index[Preces]{Lent II - Second Vespers} \label{Lent II - Second Vespers (Preces)}


 \input{intercessions/intercessions-lent-3-sunday-2nd-vespers}    \newpage
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}   \grechangedim{spaceabovelines}{0.4 cm}{scalable}  \gregorioscore{chants/or--pater_noster_a--solesmes} \grechangedim{spaceabovelines}{0 cm}{scalable}  \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} \newpage
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{Second Sunday of Lent} \label{Second Sunday of Lent (Oratio conclusiva)}     \input{prayers/or-lent-3}
 \subsubsection{Ritus conclusionis}         \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Sundays} \label{Sundays (Benedicamus Domino)}      \gregorioscore{chants/misc.benedicamus.dominio.4-T}

  \end{document}
