\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}



%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{1\textsuperscript{st} Sunday of Advent (Years A, B, and C)}
\section{First Vespers}                  \newpage
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium-T}
 \subsubsection{Hymnus}  \greannotation{IV} \index[Hymnus]{Conditor alme siderum} \label{Conditor alme siderum (Hymnus)} \grecommentary[5pt]{\emph{Conditor alme siderum}} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.35cm}{scalable} \gresetlyriccentering{syllable}   \gregorioscore{chants/hy--conditor-alme--english}    \newpage
 \subsubsection{Antiphona}  \greannotation{IV \textsc{a}} \index[Antiphona]{Annuntiate populis} \label{Annuntiate populis (Antiphona)} \grecommentary[3pt]{Cf. Ier 31:10; Is 12:2} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--annuntiate--dominican--id_6886} \vspace{5pt} \emph{Make a proclamation to the people and say: Behold, God our Savior will come.} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Psalm 140} \paragraph{A prayer when in danger}  \index[Psalmus]{Psalm 140} \label{Psalm 140 (Psalmus)} \emph{An angel stood before the face of God, thurible in hand. The fragrant incense soaring aloft was the prayer of God’s people on earth (Revelation 8:4).}        \vspace{5pt} \par \input{psalms/psalm140english3-3}
 \subsubsection{Antiphona}  \greannotation{V} \index[Antiphona]{Ecce Dominus veniet} \label{Ecce Dominus veniet (Antiphona)} \grecommentary[4pt]{Cf. Zac 14:5-6} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--ecce_dominus--dominican} \vspace{5pt} \emph{Behold, the Lord will come, and all His holy ones with Him, and there will be in that day a great light, alleluia.} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Psalm 141} \paragraph{You, Lord, are my refuge}  \index[Psalmus]{Psalm 141} \label{Psalm 141 (Psalmus)} \emph{What is written in this psalm was fulfilled in our Lord’s passion (Saint Hilary).}        \vspace{5pt} \par \input{psalms/psalm141english2-3}
 \subsubsection{Antiphona}  \greannotation{IV \textsc{a}} \index[Antiphona]{Veniet Dominus} \label{Veniet Dominus (Antiphona)} \grecommentary[0pt]{Cf. Lc 21:27; 3:6 [AR]} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--veniet_dominus_in_potestate--solesmes-op} \vspace{5pt} \emph{The Lord will come in great power, and all flesh will see the salvation of God.} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsubsection{Phil 2:6-11} \paragraph{Christ, God’s holy servant}  \index[Canticum]{Phil 2:6-11} \label{Phil 2:6-11 (Canticum)}         \vspace{5pt} \par \input{psalms/phil2_6-11english3-3}    \newpage
 \subsubsection{Lectio brevis}     \hfill 1 Th 5:23-24        \input{readings/lectio_brevis_1.Th.5.23-24.tex}
 \subsubsection{Responsorium prolixa}  \greannotation{VII} \index[Responsorium prolixa]{Missus est} \label{Missus est (Responsorium prolixa)} \grecommentary[5pt]{Cf. Lc 1:26, 27, 29, 30, 31, 32a; \Vbar. 32b} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/rp--missus_est--dominican} \vspace{5pt} \emph{The angel Gabriel was sent to the Virgin Mary who was bethrothed to Joseph, announcing to her a word: and the Virgin became frightened by the light. ``Do not fear, Mary, you have found grace with the Lord; behold, you will conceive, and bear a son, and He will be called the Son of the Most High. \Vbar. The Lord God will give Him the throne of David His father, and He will reign in the house of Jacob forever."}   \newpage
 \subsubsection{Antiphona ad Magnificat}  \greannotation{I g} \index[Antiphona ad Magnificat]{Ecce nomen Domini} \label{Ecce nomen Domini (Antiphona ad Magnificat)} \grecommentary[0pt]{Cf. Is 30:27} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--ecce_nomen_domini--dominican} \vspace{5pt} \emph{Behold, the name of the Lord comes from a long way off, and His brightness fills the whole world.}
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{I g} \index[Canticum Evangelicum]{Magnificat 1g} \label{Magnificat 1g (Canticum Evangelicum)} \grecommentary[0pt]{Lc 1:46-55} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/magnificat1g} \newpage \input{chants/magnificat-translation}   \newpage
 \subsubsection{Preces}   \index[Preces]{Advent I - Second Vespers} \label{Advent I - Second Vespers (Preces)}         \input{intercessions/intercessions-advent-1-sunday-1st-vespers}    \newpage
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}  \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/or--pater_noster_a--solesmes-T}    \newpage
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{First Sunday of Advent} \label{First Sunday of Advent (Oratio conclusiva)}         \input{prayers/or-advent-1}
 \subsubsection{Ritus conclusionis}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Sundays} \label{Sundays (Benedicamus Domino)}         \gregorioscore{chants/misc.benedicamus.dominio.4-T}


   \end{document}
