\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}



%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{1\textsuperscript{st} Sunday of Lent (Years A, B, and C)}
\section{Second Vespers}
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{spaceabovelines}{0.25 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium-lent} \grechangedim{spaceabovelines}{0 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen.}
 \subsubsection{Hymnus}  \greannotation{IV} \index[Hymnus]{Audi benigne conditor} \label{Audi benigne conditor (Hymnus)} \grecommentary[0pt]{\emph{Audi benigne conditor}} \gresetinitiallines{1} \gresetlyriccentering{syllable} \grechangedim{spaceabovelines}{0.25 cm}{scalable} \gregorioscore{chants/hy--audi_benigne--english} \grechangedim{spaceabovelines}{0 cm}{scalable}   \newpage
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Dominum Deum tuum} \label{Dominum Deum tuum (Antiphona)} \grecommentary[3pt]{Mt 4:10 [AR]} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/an--dominum_deum_tuum--solesmes} \grechangedim{spaceabovelines}{0 cm}{scalable} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{The Lord your God you shall adore, and him alone shall you serve.}
 \subsubsection{Psalm 109} \paragraph{The Messiah, king and priest}  \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)} \emph{Christ’s reign will last until all his enemies are made subject to him (1~Cor 15:25).}    \vspace{5pt} \par \input{psalms/psalm109english2-2}
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Ecce nunc tempus} \label{Ecce nunc tempus (Antiphona)} \grecommentary[0pt]{2 Cor 6:2, 4, 5, 6} \gresetinitiallines{1} \gresetlyriccentering{vowel} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--ecce_nunc_tempus_acceptabile--dominican--id_6148}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Behold, now is the acceptable time; behold, now is the day of salvation: therefore in these days we shall show ourselves to be the ministers of God, in much patience, in vigils, in fasts, and in charity without deceit.}
 \subsubsection{Psalm 113A} \paragraph{The Israelites are delivered from the bondage of Egypt}  \index[Psalmus]{Psalm 113A} \label{Psalm 113A (Psalmus)} \emph{You too left Egypt when, at baptism, you renounced that world which is at enmity with God (Saint Augustine).}    \vspace{5pt} \par \input{psalms/psalm113Aenglish2-2}    \newpage
 \subsubsection{Antiphona}  \greannotation{VII a} \index[Antiphona]{Ecce ascendimus Ierosolymam et filius} \label{Ecce ascendimus Ierosolymam et filius (Antiphona)} \grecommentary[0pt]{Mt 20:18, 19} \gresetinitiallines{1}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--ecce_ascendimus_ierosolymam_et_filius--dominican--id_5808}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{Behold, we are going up to Jerusalem: and the Son of man will be handed over to be crucified.}
 \subsubsection{1 Petr 2:21-24} \paragraph{The willing acceptance of his passion by Christ, \\ the servant of God}  \index[Canticum]{1 Petr 2:21-24} \label{1 Petr 2:21-24 (Canticum)} \emph{}    \vspace{5pt} \par \input{psalms/1petr2_21-24english3-3}
 \subsubsection{Lectio brevis}     \hfill 1 Cor 9:24-25    \input{readings/lectio_brevis_1.Cor.9.24-25.tex}
 \subsubsection{Responsorium brevis}  \greannotation{} \index[Responsorium brevis]{Sana animam meam} \label{Sana animam meam (Responsorium brevis)} \grecommentary[0pt]{Ps 40:5} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/rb--sana_animam--dominican--id_7078}   \vspace{5pt} \emph{Heal my soul, for I have sinned against you. \Vbar. I have said: O Lord, have mercy on me.} \newpage
 \subsubsection{Antiphona ad Magnificat}  \greannotation{IV \textsc{e}} \index[Antiphona ad Magnificat]{Evigila super nos} \label{Evigila super nos (Antiphona ad Magnificat)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/an--evigila--dominican--id_5306}   \vspace{5pt} \emph{Watch over us, eternal Savior, lest the wily tempter should apprehend us: for you have been made for us an everlasting helper.}
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{IV \textsc{e}} \index[Canticum Evangelicum]{Magnificat 4E} \label{Magnificat 4E (Canticum Evangelicum)} \grecommentary[0pt]{Lc 1:46-55} \gresetinitiallines{1} \gresetlyriccentering{vowel}  \gregorioscore{chants/magnificat4E}   \input{chants/magnificat-translation}
 \subsubsection{Preces}   \index[Preces]{Lent I - Second Vespers} \label{Lent I - Second Vespers (Preces)}     \input{intercessions/intercessions-lent-1-sunday-2nd-vespers}    \newpage
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}   \grechangedim{spaceabovelines}{0.4 cm}{scalable}  \gregorioscore{chants/or--pater_noster_a--solesmes} \grechangedim{spaceabovelines}{0 cm}{scalable}  \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} \newpage
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{First Sunday of Lent} \label{First Sunday of Lent (Oratio conclusiva)}     \input{prayers/or-lent-1}
 \subsubsection{Ritus conclusionis}         \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Sundays} \label{Sundays (Benedicamus Domino)}      \gregorioscore{chants/misc.benedicamus.dominio.4-T}

  \end{document}
