\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{The Presentation of the Lord}
\section{Second Vespers}

\cleardoublepage

\index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium}   \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen. Alleluia.}
\subsubsection{Hymnus}  \greannotation{I} \index[Hymnus]{Ave Maris stella} \label{Ave Maris stella (Hymnus)} \grecommentary[0pt]{\emph{Ave Maris stella}} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/hy--ave_maris--latin-with-trans}    \newpage
\subsubsection{Antiphona}  \greannotation{VII a} \index[Antiphona]{Responsum accepit} \label{Responsum accepit (Antiphona)} \grecommentary[3pt]{Lc 2:26} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/an--responsum_accepit--dominican--id_7146--mode_7}   \vspace{5pt} \emph{Simeon had received a revelation from the Holy Spirit that he would not see death until he had seen the Lord.}
\subsubsection{Psalm 109}   \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm109english3-3}
\subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Crux benedicta} \label{Crux benedicta (Antiphona)} \grecommentary[2pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--obtulerunt_pro_eo--dominican--id_6302}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{The made an offering for him to the Lord, a turtledove or two young pigeons.}
\subsubsection{Psalm 129}   \index[Psalmus]{Psalm 129} \label{Psalm 129 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm129english2-2}
\subsubsection{Antiphona}  \greannotation{IV \textsc{e}} \index[Antiphona]{Homo erat} \label{Homo erat (Antiphona)} \grecommentary[0pt]{Lc 2:25 [AR]} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--homo_erat_in_ierusalem--solesmes-op}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{There was a man in Jerusalem whose name was Simeon; this man, just and devout, was awaiting the redeption of Israel, and the Holy Spirit was upon him. }
\subsubsection{Phil 2:6-11} \paragraph{Christ, God’s holy servant}  \index[Canticum]{Phil 2:6-11} \label{Phil 2:6-11 (Canticum)}         \vspace{5pt} \par \input{psalms/phil2_6-11english3-3}    \newpage
\subsubsection{Lectio brevis}     \hfill Heb 4:15-16        \input{readings/lectio_brevis_Heb.4.15-16.tex}
\subsubsection{Responsorium brevis}  \greannotation{VI} \index[Responsorium brevis]{Notum fecit Dominus salutare} \label{Notum fecit Dominus salutare (Responsorium brevis)} \grecommentary[0pt]{Ps 97:2; Lc 2:31} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/rb--notum_fecit_dominus_salutare--solesmes-op}   \vspace{5pt} \emph{The Lord has made known his salvation. \Vbar. What he has prepared before the face of all peoples.} \newpage
\subsubsection{Antiphona ad Magnificat}  \greannotation{I \textsc{d}} \index[Antiphona ad Magnificat]{Hodie beata virgo} \label{Hodie beata virgo (Antiphona ad Magnificat)} \grecommentary[3pt]{Cf. Lc 2:28} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--hodie_beata_virgo--dominican--id_5416}   \vspace{5pt} \emph{Today the Blessed Virgin Mary presented the child Jesus in the temple, and Simeon, filled with the Holy Spirit, received him in his arms and blessed God.}
\subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{I \textsc{d}} \index[Canticum Evangelicum]{Magnificat 4E} \label{Magnificat 4E (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/magnificat1D}   \input{chants/magnificat-translation} \newpage
\subsubsection{Preces}   \index[Preces]{Transfiguration} \label{Transfiguration (Preces)}         \input{intercessions/intercessions-sanctorale--02.02--presentation-2nd_vespers}    \newpage
\subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}  \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/or--pater_noster_a--solesmes}   \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} \newpage
\subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{Transfiguration} \label{Transfiguration (Oratio conclusiva)}         \input{prayers/or-sanctorale--02.02--presentation}
\subsubsection{Ritus conclusionis}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
\subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Feasts} \label{Feasts (Benedicamus Domino)}  \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/misc.benedicamus.dominio.3}   \vspace{5pt} \emph{\Vbar. Let us bless the Lord. \Rbar. Thanks be to God.}

 \end{document}
