\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage[normalem]{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter{Saint Patrick, Bishop}
\section{First Vespers}
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium-lent}   \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen.}
 \subsubsection{Hymnus}  \greannotation{I} \index[Hymnus]{Iste Confessor} \label{Iste Confessor (Hymnus)} \grecommentary[3pt]{\emph{Iste confessor}} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}  \grechangedim{spaceabovelines}{0.25 cm}{scalable} \gregorioscore{chants/hy--iste_confessor--english--solemnities}    \newpage
 \subsubsection{Antiphona}  \greannotation{I \textsc{d}} \index[Antiphona]{Iste Sanctus} \label{Iste Sanctus (Antiphona)} \grecommentary[3pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/an--iste_sanctus--dominican--id_5904}   \vspace{5pt} \emph{This saint is worthily held in the memory of men, who has passed to the joy of the angels.}
 \subsubsection{Psalm 112}   \index[Psalmus]{Psalm 112} \label{Psalm 112 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm112english3-3}
 \subsubsection{Antiphona}  \greannotation{III a} \index[Antiphona]{Ego sum pastor} \label{Ego sum pastor (Antiphona)} \grecommentary[0pt]{Cf. Io 10:14, 15} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--ego_sum_pastor_bonus--dominican--no_alleluia}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{I am the good shepherd, I who feed my flock; and for my sheep I lay down my life.}
 \subsubsection{Psalm 145}   \index[Psalmus]{Psalm 145} \label{Psalm 145 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm145english3-3}
 \subsubsection{Antiphona}  \greannotation{III a} \index[Antiphona]{Pastor bonus} \label{Pastor bonus (Antiphona)} \grecommentary[0pt]{Io 10:11} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--pastor_bonus--dominican--no_alleluia}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{The good shepherd lays down his life for his sheep.}
 \subsubsection{Eph 1:3-10}   \index[Canticum]{Eph 1:3-10} \label{Eph 1:3-10 (Canticum)}         \vspace{5pt} \par \input{psalms/eph1_3-10english3-3}
 \subsubsection{Lectio brevis}     \hfill 1 Pt 5:1-4        \input{readings/lectio_brevis_1.Pt.5.1-4.tex}    \newpage
 \subsubsection{Responsorium prolixa} \emph{The long responsory is sung by the cantors alone.} \greannotation{II} \index[Responsorium prolixa]{Sancte Patrici} \label{Sancte Patrici (Responsorium prolixa)} \grecommentary[0pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.4cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/rp--sancte_patrici--dominican}   \vspace{5pt} \emph{Holy Patrick, Confessor of Christ, hear your suppliant servants, and from heaven bring the favor procured. \Vbar. O holy Patrick, golden star, by the favor of the Lord hear with accustomed kindness the pleadings of your servants.} \newpage
 \subsubsection{Antiphona ad Magnificat}  \greannotation{I g} \index[Antiphona ad Magnificat]{Confessor Domini Patricii} \label{Confessor Domini Patricii (Antiphona ad Magnificat)} \grecommentary[3pt]{Ecclesia} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--confessor_domini_patricius--dominican}   \vspace{5pt} \emph{Patrick, Confessor of the Lord, give strength through your holy intercession to the people here present, so that we who are pressed down with the weight of evil may be raised up by the glory of your happiness, and, under your guidance, attain to eternal rewards.}
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{I g} \index[Canticum Evangelicum]{Magnificat 1g} \label{Magnificat 1g (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{spaceabovelines}{0.4 cm}{scalable} \gregorioscore{chants/magnificat1g}  \grechangedim{spaceabovelines}{0 cm}{scalable} \input{chants/magnificat-translation} 
 \subsubsection{Preces}   \index[Preces]{Common of Pastors} \label{Common of Pastors (Preces)}         \input{intercessions/intercessions-common_of_pastors--vespers}
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}  \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/or--pater_noster_a--solesmes}   \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} \newpage
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{Second Sunday of Easter} \label{Second Sunday of Easter (Oratio conclusiva)}         \input{prayers/or-sanctorale--03.17--st_patrick}
 \subsubsection{Ritus conclusionis}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Solemnities} \label{Solemnities (Benedicamus Domino)}  \gresetinitiallines{1} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/misc.benedicamus.dominio.1-T}


 \end{document}
