\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{#1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\leftmark}
\fancyhead[CO]{\rightmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{-30pt}{0pt}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*0}
\titlespacing*{\subsubsubsection}{0pt}{10pt}{*0}
\titleformat{\part} {\normalfont\Huge\sc\center}{\thechapter}{1em}{}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\Large\sc\center}{\thesubsubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\large\sc\center}{\thesubsubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\normalsize\sc\center}{\thesubsubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage[normalem]{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}


%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


\raggedbottom

\newcommand{\lectio}[3]{%
  \makebox[0pt][l]{#1}%
  \makebox[\textwidth][c]{#2}%
  \makebox[0pt][r]{\normalsize{\textnormal{#3}}}}


%%Combination
\chapter[The Exaltation of the Holy Cross]{The Exaltation of the Holy Cross}
\section{Second Vespers}
    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium}   \vspace{5pt} \emph{God, come to my assistance. \Rbar. Lord, make haste to help me. Glory to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, unto the age of ages. Amen. Alleluia.}
 \subsubsection{Hymnus}  \greannotation{I} \index[Hymnus]{Vexilla regis prodeunt} \label{Vexilla regis prodeunt (Hymnus)} \grecommentary[3pt]{\emph{Vexilla regis prodeunt}} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{syllable}  \grechangedim{spaceabovelines}{0.25 cm}{scalable} \gregorioscore{chants/hy--vexilla_regis--english}
 \subsubsection{Antiphona}  \greannotation{VII d} \index[Antiphona]{O magnum pietatis} \label{O magnum pietatis (Antiphona)} \grecommentary[3pt]{Ecclesia} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \grechangedim{spaceabovelines}{0.5 cm}{scalable} \gregorioscore{chants/an--o_magnum_pietatis--dominican--id_5658}   \vspace{5pt} \emph{O great work of love! Death was then dead, when Life had died on the tree.}
 \subsubsection{Psalm 109}   \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm109english3-3}
 \subsubsection{Antiphona}  \greannotation{VIII \textsc{g}} \index[Antiphona]{Crux benedicta} \label{Crux benedicta (Antiphona)} \grecommentary[2pt]{Ecclesia} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--crux_benedicta--dominican--id_5629}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{The blessed cross blooms; the Lord hung upon it in the flesh, and with his blood washed our wounds.}
 \subsubsection{Psalm 115}   \index[Psalmus]{Psalm 115} \label{Psalm 115 (Psalmus)}         \vspace{5pt} \par \input{psalms/psalm115english2-2}
 \subsubsection{Antiphona}  \greannotation{VII d} \index[Antiphona]{Nos autem gloriari} \label{Nos autem gloriari (Antiphona)} \grecommentary[5pt]{Gal 6:14} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/an--nos_autem_gloriari--dominican--id_7037}  \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable} \vspace{5pt} \emph{It is fitting for us to glory in the Cross of our Lord Jesus Christ.}
 \subsubsection{Canticle: Ap 4:11; 5:9-10, 12}   \index[Canticum]{Canticle: Ap 4:11; 5:9-10, 12} \label{Canticle: Ap 4:11; 5:9-10, 12 (Canticum)}         \vspace{5pt} \par \input{psalms/ap4_11etc3-3}    \newpage
 \subsubsection{Lectio brevis}     \hfill 1 Cor 1:23-24        \input{readings/lectio_brevis_1.Cor.1.23-24.tex}
 \subsubsection{Responsorium brevis}  \greannotation{VI} \index[Responsorium brevis]{Magnificentia} \label{Magnificentia (Responsorium brevis)} \grecommentary[0pt]{Ecclesia} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/rb--o_crux_gloriosa--solesmes-op}   \vspace{5pt} \emph{O glorious cross, upon you the King of Angels triumphed. \Vbar. And his blood washed our wounds.}
 \subsubsection{Antiphona ad Magnificat}  \greannotation{I g} \index[Antiphona ad Magnificat]{Et audientes} \label{Et audientes (Antiphona ad Magnificat)} \grecommentary[3pt]{Ecclesia} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/an--super_omnia--dominican}   \vspace{5pt} \emph{You alone are nobler than all cedar woods. On you hung the Life of the world; on you Christ triumphed, and death conquered death, alleluia.}
 \subsubsection{Canticum Evangelicum} \paragraph{The soul rejoices in the Lord} \greannotation{I g} \index[Canticum Evangelicum]{Magnificat 4E} \label{Magnificat 4E (Canticum Evangelicum)} \grecommentary[3pt]{Lc 1:46-55} \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}  \grechangedim{spaceabovelines}{0.4 cm}{scalable} \gregorioscore{chants/magnificat1g}  \grechangedim{spaceabovelines}{0 cm}{scalable} \input{chants/magnificat-translation}
 \subsubsection{Preces}   \index[Preces]{Transfiguration} \label{Transfiguration (Preces)}         \input{intercessions/intercessions-sanctorale--09.14--exaltation}    \newpage
 \subsubsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}  \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/or--pater_noster_a--solesmes}   \vspace{5pt} \emph{Our Father, who art in heaven, hallowed be thy name; thy kingdom come, thy will be done on earth as it is in heaven. Give us this day our daily bread, and forgive us our trespasses as we forgive those who tresspass against us; and lead us not into temptation, but deliver us from evil.} \newpage
 \subsubsection{Oratio conclusiva}   \index[Oratio conclusiva]{Transfiguration} \label{Transfiguration (Oratio conclusiva)}         \input{prayers/or-sanctorale--09.14--exaltation}
 \subsubsection{Ritus conclusionis}             \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsubsection{Benedicamus Domino}   \index[Benedicamus Domino]{Feasts} \label{Feasts (Benedicamus Domino)}  \grechangestyle{initial}{\fontsize{1}{1}\selectfont} \grechangestyle{initial}{\fontsize{36}{36}\selectfont} \grechangedim{maxbaroffsettextleft@nobar}{12 cm}{scalable} \grechangedim{spaceabovelines}{0.5cm}{scalable} \gresetlyriccentering{vowel}   \gregorioscore{chants/misc.benedicamus.dominio.3}   \vspace{5pt} \emph{\Vbar. Let us bless the Lord. \Rbar. Thanks be to God.}
  \end{document}
