\grechangedim{spaceabovelines}{0.6cm}{scalable}

%\emph{A veiled cross is carried to the steps of the altar. Then two priests standing to the right of the altar hold the cross by its arms and turning to the community or the people sing the verse:}

Cantors:
\vspace{5 pt}
\greannotation{VIII}
﻿\gabcsnippet{(c4)Pó(c)pu(df)le(efED) me(cd)us,(d) (;) quid(e!fg) fe(gf)ci(e) ti(fe)bi,(de) (;) aut(c) in(e) quo(ixgv_//hih/ghg) (,4) con(fe)tris(fg)tá(fe)vi(fg) te?(efEDd) (;) Re(c)spón(efeed~)de(dc) mi(ef)hi:(d) (:) Qui(deDC)a(c) e(e!fg)dú(gf)xi(ef) te(d) (;) de(ce) ter(g)ra(ixgv_//hih/ghg) Æ(fe)gýp(fg)ti,(e) (;) pa(ce)rás(ixgv_//hiHGhg)ti(fe) (,4) Cru(fg)cem(ef/gffe) (;) Sal(fe~)va(f)tó(ghg)ri(f) tu(gf)o.(e!fg) (::)}

\vspace{5 pt}

%\emph{When the verse is finished, the two deacons stand at the steps of the sanctuary and sing the ``Hagios." Each time ``Hagios" is sung, both kneel; having finished the word ``Hagios," they immediately rise.}
Priest Cantors:
\vspace{5pt}
\gresetinitiallines{0}
\gabcsnippet{(c4)A<alt>Kneel</alt>(g)gi(fe)os(fgffe) (;) o<alt>Rise</alt>(c) The(d)ós,(fg!hvhg) (:) A<alt>Kneel</alt>(g)gi(fe)os(fgffe) (;) is<alt>Rise</alt>(c)chy(d)rós,(fg!hvhg) (:) (z) A<alt>Kneel</alt>(gh)gi(g)os(ixhg/hiHGg) (;) a<alt>Rise</alt>(f)thá(g)na(h)tos,(iyhj/jvIHih) (:) e(g)lé(h!ijIH)i(g)son(hghg) (,4) i(fvED)más.(fg/hhg) (::)}
\vspace{5 pt}

Choir:
\vspace{5pt}
%\emph{Then the choir and, if possible, all those assembled sing the following in response. Each time ``Sanctus" is sung, all kneel; having finished the word ``Sanctus," all immediately rise. (The priests who hold the cross do not kneel, nor do the two deacons kneel when the community kneels, nor the community when the two deacons kneel.)}
\gabcsnippet{(c4)Sanc<alt>Kneel</alt>(g)tus(fgffe) (;) De<alt>Rise</alt>(cd)us,(fg!hvhg) (:) Sanc<alt>Kneel</alt>(g)tus(fgffe) (;) for<alt>Rise</alt>(cd)tis,(fg!hvhg) (:) Sanc<alt>Kneel</alt>(ghg~)tus(ixhg/hiHGg) (;) et<alt>Rise</alt>(f) im(g)mor(h)tá(iyhj/jvIH)lis,(ih) (:) mi(g)se(h)ré(h!ijIHG)re(hghg) (,4) no(fvED)bis.(fg/hhg) (::)}
\vspace{5 pt}

Cantors:
\vspace{5pt}
%\emph{When the choir has finished the response, the two priests move more towards the middle of the altar and sing the second verse:}}
\gabcsnippet{(c4) <sp>V/</sp>. Qui(deDC)a(c) e(e!fg)dú(gf)xi(ef) te(d) (;) per(c) de(e)sér(ixgv_//hih/ghg)tum(fd) (;) qua(fe)dra(fg)gín(fe~)ta(fg) an(f)nis,(e) (;) et(fe~) man(de)na(d) ci(dc)bá(df)vi(de) te,(eed) (;) et(e) in(g)tro(gh)dú(hhg)xi(e) (,3) in(gf~) ter(ef)ram(e) sa(fe)tis(dc) óp(df)ti(de)mam,(ed) (:) pa(ce)rás(ixgv//hih/ghg)ti(fe) (,4) Cru(fg)cem(ef/gffe) (;) Sal(fe~)va(f)tó(ghg)ri(f) tu(gf)o.(e!fg) (::)}
\vspace{5 pt}

\emph{The ``Hagios" and ``Sanctus" are repeated.}

%\emph{Then the two deacons sing the ``Hagios" again and the choir again responds with ``Sanctus." They kneel and rise as before.}

Cantors:
\vspace{5pt}
%\emph{Then the priests move to the middle of the altar and sing the third verse:}
\gabcsnippet{(c4) <sp>V/</sp>. Quid(c) ul(de)tra(d) dé(e!fg)bu(fe)i(e) (,1) fá(e)ce(e)re(e) ti(e)bi,(dc) (;) et(de) non(de) fe(ed)ci?(cd) (:) E(deDC)go(c) qui(ef)dem(ed) (,1) plan(e!fg)tá(gf)vi(ef) te(d) (;) ví(e)ne(c)am(e) me(gh)am(h) (,3) spe(h)ci(g)o(fe)sí(de)si(dc)mam,(c) (:) et(cd) tu(fg) fac(gf)ta(gh) es(h) (,3) mi(h)hi(g) ni(fe)mis(d) a(fe)má(ddv)ra:(c) (:) a(d)cé(c)to(df) nam(fe~)que(d) (,1) mix(ffe)to(c) cum(df) fel(fe)le(d) (;) si(e)tim(f) me(d)am(e) po(f)tás(ddv)ti,(c) (:) et(cd) lán(ffg)ce(f)a(f) (,3) per(f)fo(gh)rás(h)ti(g) la(fe)tus(df) (;) Sal(fe~)va(f)tó(ghg)ri(f) tu(gf)o.(e!fg) (::)}

\vspace{5pt}

\emph{The ``Hagios" and ``Sanctus" are repeated.}

\vspace{10pt}
\emph{My people, what have I done to you? or in what have I grieved you? Answer me. Because I brought you out of the land of Egypt you have prepared a cross for your savior. \Rbar. O holy God! holy and mighty! holy and eternal! have mercy on us. \Rbar. O holy God! holy and mighty! holy and eternal! have mercy on us.	\Vbar. Because I led you through the desert forty years, and fed you with manna, and brought you into an excellent land, you have prepared a cross for your savior. \Vbar. What more could I do for you, that I have not done? I have planted you my most beautiful vine, and you have proved exceeding bitter to Me; in My thirst you gave Me vinegar to drink, and with a spear you have pierced the side of your Savior.}

\grechangedim{spaceabovelines}{0cm}{scalable}
