\noindent O Lord, I have heard your renown,~\GreStar{}~\nopagebreak

and feared, O Lord, your work.

\noindent In the course of the years revive it,~†~\nopagebreak

in the course of the years make it known;~\GreStar{}~\nopagebreak

in your wrath remember compassion!

\noindent God comes from Teman,~\GreStar{}~\nopagebreak

the Holy One from Mount Paran.

\noindent Covered are the heavens with his glory,~\GreStar{}~\nopagebreak

and with his praise the earth is filled.

\noindent His splendor spreads like the light;~†~\nopagebreak

rays shine forth from beside him,~\GreStar{}~\nopagebreak

where his power is concealed.

\noindent You come forth to save your people,~\GreStar{}~\nopagebreak

to save your anointed one.

\noindent You tread the sea with your steeds~\GreStar{}~\nopagebreak

amid the churning of the deep waters.

\noindent I hear, and my body trembles;~\GreStar{}~\nopagebreak

at the sound, my lips quiver.

\noindent Decay invades my bones,~\GreStar{}~\nopagebreak

my legs tremble beneath me.

\noindent I await the day of distress~\GreStar{}~\nopagebreak

that will come upon the people who attack us.

\noindent For though the fig tree blossom not~\GreStar{}~\nopagebreak

nor fruit be on the vines,

\noindent though the yield of the olive fail~\GreStar{}~\nopagebreak

and the terraces produce no nourishment,

\noindent though the flocks disappear from the fold~\GreStar{}~\nopagebreak

and there be no herd in the stalls,

\noindent yet will I rejoice in the Lord~\GreStar{}~\nopagebreak

and exult in my saving God.

\noindent God, my Lord, is my strength;~†~\nopagebreak

he makes my feet swift as those of hinds~\GreStar{}~\nopagebreak

and enables me to go upon the heights.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
