\noindent Once I said,~\GreStar{}~\nopagebreak

“In the noontime of life I must depart!

\noindent To the gates of the nether world I shall be consigned~\GreStar{}~\nopagebreak

for the rest of my years.”

\noindent I said, “I shall see the Lord no more~\GreStar{}~\nopagebreak

in the land of the living.

\noindent No longer shall I behold my fellow men~\GreStar{}~\nopagebreak

among those who dwell in the world.”

\noindent My dwelling, like a shepherd’s tent,~\GreStar{}~\nopagebreak

is struck down and borne away from me;

\noindent you have folded up my life, like a weaver~\GreStar{}~\nopagebreak

who severs the last thread.

\noindent Day and night you give me over to torment;~\GreStar{}~\nopagebreak

I cry out until the dawn.

\noindent Like a lion he breaks all my bones;~\GreStar{}~\nopagebreak

day and night you give me over to torment.

\noindent Like a swallow I utter shrill cries;~\GreStar{}~\nopagebreak

I moan like a dove.

\noindent My eyes grow weak, gazing heaven-ward:~\GreStar{}~\nopagebreak

O Lord, I am in straits; be my surety!

\noindent You have preserved my life~\GreStar{}~\nopagebreak

from the pit of destruction,

\noindent When you cast behind your back~\GreStar{}~\nopagebreak

all my sins.

\noindent For it is not the nether world that gives you thanks,~\GreStar{}~\nopagebreak

nor death that praises you;

\noindent Neither do those who go down into the pit~\GreStar{}~\nopagebreak

await your kindness.

\noindent The living, the living give you thanks,~\GreStar{}~\nopagebreak

as I do today.

\noindent Fathers declare to their sons,~\GreStar{}~\nopagebreak

O God, your faithfulness.

\noindent The Lord is our savior;~\GreStar{}~\nopagebreak

we shall sing to stringed instruments

\noindent In the house of the Lord~\GreStar{}~\nopagebreak

all the days of our life.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
