\noindent I rejoice heartily in the Lord,~\GreStar{}~\nopagebreak

in my God is the joy of my soul;

\noindent for he has clothed me with a robe of salvation,~\GreStar{}~\nopagebreak

and wrapped me in a mantle of justice,

\noindent like a bridegroom adorned with a diadem,~\GreStar{}~\nopagebreak

like a bride bedecked with her jewels.

\noindent As the earth brings forth its plants,~\GreStar{}~\nopagebreak

and a garden makes its growth spring up,

\noindent so will the Lord God make justice and praise~\GreStar{}~\nopagebreak

spring up before all the nations.

\noindent For Zion’s sake I will not be silent,~\GreStar{}~\nopagebreak

for Jerusalem’s sake I will not be quiet,

\noindent until her vindication shines forth like the dawn~\GreStar{}~\nopagebreak

and her victory like a burning torch.

\noindent Nations shall behold your vindication,~\GreStar{}~\nopagebreak

and all kings your glory;

\noindent you shall be called by a new name~\GreStar{}~\nopagebreak

pronounced by the mouth of the Lord.

\noindent You shall be a glorious crown in the hand of the Lord,~\GreStar{}~\nopagebreak

a royal diadem held by your God.

\noindent No more shall men call you “Forsaken,”~\GreStar{}~\nopagebreak

or your land “Desolate,”

\noindent but you shall be called “My Delight,”~\GreStar{}~\nopagebreak

and your land “Espoused.”

\noindent For the Lord delights in you,~\GreStar{}~\nopagebreak

and makes your land his spouse.

\noindent As a young man marries a virgin,~\GreStar{}~\nopagebreak

your Builder shall marry you;

\noindent and as a bridegroom rejoices in his bride~\GreStar{}~\nopagebreak

so shall your God rejoice in you.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
