\lettrine[loversize=0.15,lines=2]{B}{}lessed be the Lord, the God of Israel; ~\GreStar{}~\nopagebreak

\hspace{2pt} he has come to his people and set them free.

\noindent He has raised up for us a mighty savior,~\GreStar{}~\nopagebreak

born of the house of his servant David.

\noindent Through his holy prophets he promised of old~†~\nopagebreak

  that he would save us from our enemies,~\GreStar{}~\nopagebreak

  from the hands of all who hate us.

\noindent He promised to show mercy to our fathers~\GreStar{}~\nopagebreak


and to remember his holy covenant.

\noindent This was the oath he swore to our father Abraham:~\GreStar{}~\nopagebreak

to set us free from the hands of our enemies,

\noindent free to worship him without fear,~\GreStar{}~\nopagebreak

holy and righteous in his sight all the days of our life.

\noindent You, my child, shall be called the prophet of the Most High;~\GreStar{}~\nopagebreak

for you will go before the Lord to prepare his way,

\noindent to give his people knowledge of salvation~\GreStar{}~\nopagebreak


by the forgiveness of their sins.

\noindent In the tender compassion of our God~\GreStar{}~\nopagebreak


the dawn from on high shall break upon us,

\noindent to shine on those who dwell in darkness and the shadow of death,~\GreStar{}~\nopagebreak

and to guide our feet into the way of peace.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
