\noindent I will give you glory, O God my King,~\GreStar{}~\nopagebreak

I will bless your name for ever.

\noindent I will bless you day after day~\GreStar{}~\nopagebreak

and praise your name for ever.

\noindent The Lord is great, highly to be praised,~\GreStar{}~\nopagebreak

his greatness cannot be measured.

\noindent Age to age shall proclaim your works,~\GreStar{}~\nopagebreak

shall declare your mighty deeds,

\noindent shall speak of your splendor and glory,~\GreStar{}~\nopagebreak

tell the tale of your wonderful works.

\noindent They will speak of your terrible deeds,~\GreStar{}~\nopagebreak

recount your greatness and might.

\noindent They will recall your abundant goodness;~\GreStar{}~\nopagebreak

age to age shall ring out your justice.

\noindent The Lord is kind and full of compassion,~\GreStar{}~\nopagebreak

slow to anger, abounding in love.

\noindent How good is the Lord to all,~\GreStar{}~\nopagebreak

compassionate to all his creatures.

\noindent All your creatures shall thank you, O Lord,~\GreStar{}~\nopagebreak

and your friends shall repeat their blessing.

\noindent They shall speak of the glory of your reign~\GreStar{}~\nopagebreak

and declare your might, O God,

\noindent to make known to men your mighty deeds~\GreStar{}~\nopagebreak

and the glorious splendor of your reign.

\noindent Yours is an everlasting kingdom;~\GreStar{}~\nopagebreak

your rule lasts from age to age.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
