\noindent O Lord, do not rebuke me in your anger;~\GreStar{}~\nopagebreak

do not punish me, Lord, in your rage.

\noindent Your arrows have sunk deep in me;~\GreStar{}~\nopagebreak

your hand has come down upon me.

\noindent Through your anger all my body is sick:~\GreStar{}~\nopagebreak

through my sin, there is no health in my limbs.

\noindent My guilt towers higher than my head;~\GreStar{}~\nopagebreak

it is a weight too heavy to bear.

\noindent My wounds are foul and festering,~\GreStar{}~\nopagebreak

the result of my own folly.

\noindent I am bowed and brought to my knees.~\GreStar{}~\nopagebreak

I go mourning all the day long.

\noindent All my frame burns with fever;~\GreStar{}~\nopagebreak

all my body is sick.

\noindent Spent and utterly crushed,~\GreStar{}~\nopagebreak

I cry aloud in anguish of heart.

\noindent O Lord, you know all my longing:~\GreStar{}~\nopagebreak

my groans are not hidden from you.

\noindent My heart throbs, my strength is spent;~\GreStar{}~\nopagebreak

the very light has gone from my eyes.

\noindent My friends avoid me like a leper;~\GreStar{}~\nopagebreak

those closest to me stand afar off.

\noindent Those who plot against my life lay snares;~†~\nopagebreak

those who seek my ruin speak of harm,~\GreStar{}~\nopagebreak

planning treachery all the day long.

\noindent But I am like the deaf who cannot hear,~\GreStar{}~\nopagebreak

like the dumb unable to speak.

\noindent I am like a man who hears nothing,~\GreStar{}~\nopagebreak

in whose mouth is no defense.

\noindent I count on you, O Lord:~\GreStar{}~\nopagebreak

it is you, Lord God, who will answer.

\noindent I pray: “Do not let them mock me,~\GreStar{}~\nopagebreak

those who triumph if my foot should slip.”

\noindent For I am on the point of falling~\GreStar{}~\nopagebreak

and my pain is always before me.

\noindent I confess that I am guilty~\GreStar{}~\nopagebreak

and my sin fills me with dismay.

\noindent My wanton enemies are numberless~\GreStar{}~\nopagebreak

and my lying foes are many.

\noindent They repay me evil for good~\GreStar{}~\nopagebreak

and attack me for seeking what is right.

\noindent O Lord, do not forsake me!~\GreStar{}~\nopagebreak

My God, do not stay afar off!

\noindent Make haste and come to my help,~\GreStar{}~\nopagebreak

O Lord, my God, my savior!

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
