\noindent Preserve me, God, I take refuge in you.~†~\nopagebreak

I say to the Lord: “You are my God. ~\GreStar{}~\nopagebreak

My happiness lies in you alone.”

\noindent He has put into my heart a marvellous love ~\GreStar{}~\nopagebreak

for the faithful ones who dwell in his land.

\noindent Those who choose other gods increase their sorrows.~†~\nopagebreak

Never will I offer their offerings of blood. ~\GreStar{}~\nopagebreak

Never will I take their name upon my lips.

\noindent O Lord, it is you who are my portion and cup; ~\GreStar{}~\nopagebreak

it is you yourself who are my prize.

\noindent The lot marked out for me is my delight: ~\GreStar{}~\nopagebreak

welcome indeed the heritage that falls to me!

\noindent I will bless the Lord who gives me counsel, ~\GreStar{}~\nopagebreak

who even at night directs my heart.

\noindent I keep the Lord ever in my sight: ~\GreStar{}~\nopagebreak

since he is at my right hand, I shall stand firm.

\noindent And so my heart rejoices, my soul is glad; ~\GreStar{}~\nopagebreak

even my body shall rest in safety.

\noindent For you will not leave my soul among the dead, ~\GreStar{}~\nopagebreak

nor let your beloved know decay.

\noindent You will show me the path of life,~†~\nopagebreak

the fullness of joy in your presence, ~\GreStar{}~\nopagebreak

at your right hand happiness for ever.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
