\noindent Have mercy on me, God, in your kindness.~\GreStar{}~\nopagebreak

In your compassion blot out my offense.

\noindent O wash me more and more from my guilt~\GreStar{}~\nopagebreak

and cleanse me from my sin.

\noindent My offenses truly I know them;~\GreStar{}~\nopagebreak

my sin is always before me

\noindent Against you, you alone, have I sinned;~\GreStar{}~\nopagebreak

what is evil in your sight I have done.

\noindent That you may be justified when you give sentence~\GreStar{}~\nopagebreak

and be without reproach when you judge.

\noindent O see, in guilt I was born,~\GreStar{}~\nopagebreak

a sinner was I conceived.

\noindent Indeed you love truth in the heart;~\GreStar{}~\nopagebreak

then in the secret of my heart teach me wisdom.

\noindent O purify me, then I shall be clean;~\GreStar{}~\nopagebreak

O wash me, I shall be whiter than snow.

\noindent Make me hear rejoicing and gladness,~\GreStar{}~\nopagebreak

that the bones you have crushed may revive.

\noindent From my sins turn away your face~\GreStar{}~\nopagebreak

and blot out all my guilt.

\noindent A pure heart create for me, O God,~\GreStar{}~\nopagebreak

put a steadfast spirit within me.

\noindent Do not cast me away from your presence,~\GreStar{}~\nopagebreak

nor deprive me of your holy spirit.

\noindent Give me again the joy of your help;~\GreStar{}~\nopagebreak

with a spirit of fervor sustain me,

\noindent that I may teach transgressors your ways~\GreStar{}~\nopagebreak

and sinners may return to you.

\noindent O rescue me, God, my helper,~\GreStar{}~\nopagebreak

and my tongue shall ring out your goodness. 

\noindent O Lord, open my lips~\GreStar{}~\nopagebreak

and my mouth shall declare your praise.

\noindent For in sacrifice you take no delight,~\GreStar{}~\nopagebreak

burnt offering from me you would refuse,

\noindent my sacrifice, a contrite spirit.~\GreStar{}~\nopagebreak

A humbled, contrite heart you will not spurn.

\noindent In your goodness, show favor to Zion:~\GreStar{}~\nopagebreak

rebuild the walls of Jerusalem.

\noindent Then you will be pleased with lawful sacrifice,~\GreStar{}~\nopagebreak

holocausts offered on your altar.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
