\noindent I will give you glory, O God \uline{my} King,~\GreStar{}~\nopagebreak

I will bless your name \uline{for} ever.

\noindent I will bless you day af\uline{ter} day~\GreStar{}~\nopagebreak

and praise your name \uline{for} ever.

\noindent The Lord is great, highly to \uline{be} praised,~\GreStar{}~\nopagebreak

his greatness cannot \uline{be} measured.

\noindent Age to age shall proclaim \uline{your} works,~\GreStar{}~\nopagebreak

shall declare your might\uline{y} deeds,

\noindent shall speak of your splendor \uline{and} glory,~\GreStar{}~\nopagebreak

tell the tale of your wonder\uline{ful} works.

\noindent They will speak of your terri\uline{ble} deeds,~\GreStar{}~\nopagebreak

recount your greatness \uline{and} might.

\noindent They will recall your abun\uline{dant} goodness;~\GreStar{}~\nopagebreak

age to age shall ring out \uline{your} justice.

\noindent The Lord is kind and full of \uline{com}passion,~\GreStar{}~\nopagebreak

slow to anger, abounding \uline{in} love.

\noindent How good is the Lord \uline{to} all,~\GreStar{}~\nopagebreak

compassionate to all \uline{his} creatures.

\noindent All your creatures shall thank you, \uline{O} Lord,~\GreStar{}~\nopagebreak

and your friends shall repeat \uline{their} blessing.

\noindent They shall speak of the glory of \uline{your} reign~\GreStar{}~\nopagebreak

and declare your might, \uline{O} God,

\noindent to make known to men your might\uline{y} deeds~\GreStar{}~\nopagebreak

and the glorious splendor of \uline{your} reign.

\noindent Yours is an everlast\uline{ing} kingdom;~\GreStar{}~\nopagebreak

your rule lasts from age \uline{to} age.

\noindent Glory to the Father, and to \uline{the} Son,~\GreStar{}~\nopagebreak

and to the Ho\uline{ly} Spirit:

\noindent as it was in the beginning, \uline{is} now,~\GreStar{}~\nopagebreak

and will be for ever. \uline{A}men.
