\noindent Lord my God, I call for help by day;~\GreStar{}~\nopagebreak

I cry at night before you.

\noindent Let my prayer come into your presence.~\GreStar{}~\nopagebreak

O turn your ear to my cry.

\noindent For my soul is filled with evils;~\GreStar{}~\nopagebreak

my life is on the brink of the grave.

\noindent I am reckoned as one in the tomb:~\GreStar{}~\nopagebreak

I have reached the end of my strength,

\noindent like one alone among the dead;~\GreStar{}~\nopagebreak

like the slain lying in their graves;

\noindent like those you remember no more,~\GreStar{}~\nopagebreak

cut off, as they are, from your hand.

\noindent You have laid me in the depths of the tomb,~\GreStar{}~\nopagebreak

in places that are dark, in the depths.

\noindent Your anger weighs down upon me:~\GreStar{}~\nopagebreak

I am drowned beneath your waves.

\noindent You have taken away my friends~\GreStar{}~\nopagebreak

and made me hateful in their sight.

\noindent Imprisoned, I cannot escape;~\GreStar{}~\nopagebreak

my eyes are sunken with grief.

\noindent I call to you, Lord, all the day long;~\GreStar{}~\nopagebreak

to you I stretch out my hands.

\noindent Will you work your wonders for the dead?~\GreStar{}~\nopagebreak

Will the shades stand and praise you?

\noindent Will your love be told in the grave~\GreStar{}~\nopagebreak

or your faithfulness among the dead?

\noindent Will your wonders be known in the dark~\GreStar{}~\nopagebreak

or your justice in the land of oblivion?

\noindent As for me, Lord, I call to you for help:~\GreStar{}~\nopagebreak

in the morning my prayer comes before you.

\noindent Lord, why do you reject me?~\GreStar{}~\nopagebreak

Why do you hide your face?

\noindent Wretched, close to death from my youth,~\GreStar{}~\nopagebreak

I have borne your trials; I am numb.

\noindent Your fury has swept down upon me;~\GreStar{}~\nopagebreak

your terrors have utterly destroyed me.

\noindent They surround me all the day like a flood,~\GreStar{}~\nopagebreak

they assail me all together.

\noindent Friend and neighbor you have taken away:~\GreStar{}~\nopagebreak

my one companion is darkness.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
