\noindent Lord, listen to my prayer:~†~\nopagebreak

turn your ear to my appeal.~\GreStar{}~\nopagebreak

You are faithful, you are just; give answer.

\noindent Do not call your servant to judgment~\GreStar{}~\nopagebreak

for no one is just in your sight.

\noindent The enemy pursues my soul;~\GreStar{}~\nopagebreak

he has crushed my life to the ground;

\noindent he has made me dwell in darkness~\GreStar{}~\nopagebreak

like the dead, long forgotten.

\noindent Therefore my spirit fails;~\GreStar{}~\nopagebreak

my heart is numb within me.

\noindent I remember the days that are past:~\GreStar{}~\nopagebreak

I ponder all your works.

\noindent I muse on what your hand has wrought~†~\nopagebreak

and to you I stretch out my hands.~\GreStar{}~\nopagebreak

Like a parched land my soul thirsts for you.

\noindent Lord, make haste and answer;~\GreStar{}~\nopagebreak

for my spirit fails within me.

\noindent Do not hide your face~\GreStar{}~\nopagebreak

lest I become like those in the grave.

\noindent In the morning let me know your love~\GreStar{}~\nopagebreak

for I put my trust in you.

\noindent Make me know the way I should walk:~\GreStar{}~\nopagebreak

to you I lift up my soul.

\noindent Rescue me, Lord, from my enemies;~\GreStar{}~\nopagebreak

I have fled to you for refuge.

\noindent Teach me to do your will~\GreStar{}~\nopagebreak

for you, O Lord, are my God.

\noindent Let your good spirit guide me~\GreStar{}~\nopagebreak

in ways that are level and smooth.

\noindent For your name’s sake, Lord, save my life;~\GreStar{}~\nopagebreak

in your justice save my soul from distress.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
