\noindent My God, my God, why have you forsaken me?~\GreStar{}~\nopagebreak

You are far from my plea and the cry of my distress.

\noindent O my God, I call by day and you give no reply;~\GreStar{}~\nopagebreak

I call by night and I find no peace.

\noindent Yet you, O God, are holy,~\GreStar{}~\nopagebreak

enthroned on the praises of Israel.

\noindent In you our fathers put their trust;~\GreStar{}~\nopagebreak

they trusted and you set them free.

\noindent When they cried to you, they escaped.~\GreStar{}~\nopagebreak

In you they trusted and never in vain.

\noindent But I am a worm and no man,~\GreStar{}~\nopagebreak

scorned by men, despised by the people.

\noindent All who see me deride me.~\GreStar{}~\nopagebreak

They curl their lips, they toss their heads.

\noindent “He trusted in the Lord, let him save him;~\GreStar{}~\nopagebreak

let him release him if this is his friend.”

\noindent Yes, it was you who took me from the womb,~\GreStar{}~\nopagebreak

entrusted me to my mother’s breast.

\noindent To you I was committed from my birth,~\GreStar{}~\nopagebreak

from my mother’s womb you have been my God.

\noindent Do not leave me alone in my distress;~\GreStar{}~\nopagebreak

come close, there is none else to help.

\noindent Many bulls have surrounded me,~\GreStar{}~\nopagebreak

fierce bulls of Bashan close me in.

\noindent Against me they open wide their jaws,~\GreStar{}~\nopagebreak

like lions, rending and roaring.

\noindent Like water I am poured out,~\GreStar{}~\nopagebreak

disjointed are all my bones.

\noindent My heart has become like wax,~\GreStar{}~\nopagebreak

it is melted within my breast.

\noindent Parched as burnt clay is my throat,~\GreStar{}~\nopagebreak

my tongue cleaves to my jaws.

\noindent Many dogs have surrounded me,~\GreStar{}~\nopagebreak

a band of the wicked beset me.

\noindent They tear holes in my hands and my feet~\GreStar{}~\nopagebreak

and lay me in the dust of death.

\noindent I can count every one of my bones.~\GreStar{}~\nopagebreak

These people stare at me and gloat; 

\noindent they divide my clothing among them.~\GreStar{}~\nopagebreak

They cast lots for my robe.

\noindent O Lord, do not leave me alone,~\GreStar{}~\nopagebreak

my strength, make haste to help me!

\noindent Rescue my soul from the sword,~\GreStar{}~\nopagebreak

my life from the grip of these dogs.

\noindent Save my life from the jaws of these lions,~\GreStar{}~\nopagebreak

my poor soul from the horns of these oxen.

\noindent I will tell of your name to my brethren~\GreStar{}~\nopagebreak

and praise you where they are assembled.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
