\noindent Ring out your joy to God our strength,~\GreStar{}~\nopagebreak

shout in triumph to the God of Jacob.

\noindent Raise a song and sound the timbrel,~\GreStar{}~\nopagebreak

the sweet-sounding harp and the lute,

\noindent blow the trumpet at the new moon,~\GreStar{}~\nopagebreak

when the moon is full, on our feast.

\noindent For this is Israel’s law,~\GreStar{}~\nopagebreak

a command of the God of Jacob.

\noindent He imposed it as a rule on Joseph,~\GreStar{}~\nopagebreak

when he went out against the land of Egypt.

\noindent A voice I did not know said to me:~\GreStar{}~\nopagebreak

“I freed your shoulder from the burden;

\noindent your hands were freed from the load.~\GreStar{}~\nopagebreak

You called in distress and I saved you.

\noindent I answered, concealed in the storm cloud,~\GreStar{}~\nopagebreak

at the waters of Meribah I tested you.

\noindent Listen, my people, to my warning,~\GreStar{}~\nopagebreak

O Israel, if only you would heed!

\noindent Let there be no foreign god among you,~\GreStar{}~\nopagebreak

no worship of an alien god.

\noindent I am the Lord your God,~†~\nopagebreak

who brought you from the land of Egypt.~\GreStar{}~\nopagebreak

Open wide your mouth and I will fill it.

\noindent But my people did not heed my voice~\GreStar{}~\nopagebreak

and Israel would not obey,

\noindent so I left them in their stubbornness of heart~\GreStar{}~\nopagebreak

to follow their own designs.

\noindent O that my people would heed me,~\GreStar{}~\nopagebreak

that Israel would walk in my ways!

\noindent At once I would subdue their foes,~\GreStar{}~\nopagebreak

turn my hand against their enemies.

\noindent The Lord’s enemies would cringe at their feet~\GreStar{}~\nopagebreak

and their subjection would last for ever.

\noindent But Israel I would feed with finest wheat~\GreStar{}~\nopagebreak

and fill them with honey from the rock.”

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
