\noindent Preserve me, God, I take refuge in \uline{you}.~†~\nopagebreak

I say to the Lord: “You are \uline{my} God. ~\GreStar{}~\nopagebreak

My happiness lies in you \uline{a}lone.”

\noindent He has put into my heart a marvel\uline{lous} love ~\GreStar{}~\nopagebreak

for the faithful ones who dwell in \uline{his} land.

\noindent Those who choose other gods increase their \uline{sorrows}.~†~\nopagebreak

Never will I offer their offerings \uline{of} blood. ~\GreStar{}~\nopagebreak

Never will I take their name upon \uline{my} lips.

\noindent O Lord, it is you who are my portion \uline{and} cup; ~\GreStar{}~\nopagebreak

it is you yourself who are \uline{my} prize.

\noindent The lot marked out for me is my \uline{de}light: ~\GreStar{}~\nopagebreak

welcome indeed the heritage that falls \uline{to} me!

\noindent I will bless the Lord who gives \uline{me} counsel, ~\GreStar{}~\nopagebreak

who even at night directs \uline{my} heart.

\noindent I keep the Lord ever in \uline{my} sight: ~\GreStar{}~\nopagebreak

since he is at my right hand, I shall \uline{stand} firm.

\noindent And so my heart rejoices, my soul \uline{is} glad; ~\GreStar{}~\nopagebreak

even my body shall rest \uline{in} safety.

\noindent For you will not leave my soul among \uline{the} dead, ~\GreStar{}~\nopagebreak

nor let your beloved know \uline{de}cay.

\noindent You will show me the path of \uline{life},~†~\nopagebreak

the fullness of joy in \uline{your} presence, ~\GreStar{}~\nopagebreak

at your right hand happiness \uline{for} ever.

\noindent Glory to the Father, and to \uline{the} Son,~\GreStar{}~\nopagebreak

and to the Ho\uline{ly} Spirit:

\noindent as it was in the beginning, \uline{is} now,~\GreStar{}~\nopagebreak

and will be for ever. \uline{A}men.
