\noindent My heart is ready, O God;~\GreStar{}~\nopagebreak

I will sing, sing your praise.

\noindent Awake, my soul;~†~\nopagebreak

awake, lyre and harp.~\GreStar{}~\nopagebreak

I will awake the dawn.

\noindent I will thank you, Lord, among the peoples,~\GreStar{}~\nopagebreak

among the nations I will praise you,

\noindent for your love reaches to the heavens~\GreStar{}~\nopagebreak

and your truth to the skies.

\noindent O God, arise above the heavens;~\GreStar{}~\nopagebreak

may your glory shine on earth!

\noindent O come and deliver your friends;~\GreStar{}~\nopagebreak

help with your right hand and reply.

\noindent From his holy place God has made this promise:~†~\nopagebreak

“I will triumph and divide the land of Shechem;~\GreStar{}~\nopagebreak

I will measure out the valley of Succoth.

\noindent Gilead is mine and Manasseh.~†~\nopagebreak

Ephraim I take for my helmet,~\GreStar{}~\nopagebreak

Judah for my commander’s staff.~\GreStar{}~\nopagebreak

\noindent Moab I will use for my washbowl,~†~\nopagebreak

on Edom I will plant my shoe.~\GreStar{}~\nopagebreak

Over the Philistines I will shout in triumph.”

\noindent But who will lead me to conquer the fortress?~\GreStar{}~\nopagebreak

Who will bring me face to face with Edom?

\noindent Will you utterly reject us, O God,~\GreStar{}~\nopagebreak

and no longer march with our armies?

\noindent Give us help against the foe:~\GreStar{}~\nopagebreak

for the help of man is vain.

\noindent With God we shall do bravely~\GreStar{}~\nopagebreak

and he will trample down our foes.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
