\noindent Not to us, Lord, not \uline{to} us,~\GreStar{}~\nopagebreak

but to your name give \uline{the} glory

\noindent for the sake of your love and \uline{your} truth,~\GreStar{}~\nopagebreak

lest the heathen say: “Where is \uline{their} God?”



\noindent But our God is in \uline{the} heavens;~\GreStar{}~\nopagebreak

he does whatever \uline{he} wills.

\noindent Their idols are silver \uline{and} gold,~\GreStar{}~\nopagebreak

the work of hu\uline{man} hands.



\noindent They have mouths but they can\uline{not} speak;~\GreStar{}~\nopagebreak

they have eyes but they can\uline{not} see;

\noindent they have ears but they can\uline{not} hear;~\GreStar{}~\nopagebreak

they have nostrils but they can\uline{not} smell.



\noindent With their hands they cannot \uline{feel};~†~\nopagebreak

with their feet they can\uline{not} walk.~\GreStar{}~\nopagebreak

No sound comes from \uline{their} throats.



\noindent Their makers will come to be \uline{like} them~\GreStar{}~\nopagebreak

and so will all who trust \uline{in} them.



\noindent Sons of Israel, trust in \uline{the} Lord;~\GreStar{}~\nopagebreak

he is their help and \uline{their} shield.

\noindent Sons of Aaron, trust in \uline{the} Lord;~\GreStar{}~\nopagebreak

he is their help and \uline{their} shield.



\noindent You who fear him, trust in \uline{the} Lord;~\GreStar{}~\nopagebreak

he is their help and \uline{their} shield.

\noindent He remembers us, and he will \uline{bless us};~†~\nopagebreak

he will bless the sons \uline{of} Israel.~\GreStar{}~\nopagebreak

He will bless the sons \uline{of} Aaron.



\noindent The Lord will bless those \uline{who} fear him,~\GreStar{}~\nopagebreak

the little no less than \uline{the} great:

\noindent to you may the Lord \uline{grant} increase,~\GreStar{}~\nopagebreak

to you and all \uline{your} children.



\noindent May you be blessed by \uline{the} Lord,~\GreStar{}~\nopagebreak

the maker of heaven \uline{and} earth.

\noindent The heavens belong to \uline{the} Lord~\GreStar{}~\nopagebreak

but the earth he has given \uline{to} men.



\noindent The dead shall not praise \uline{the} Lord,~\GreStar{}~\nopagebreak

nor those who go down into \uline{the} silence.

\noindent But we who live bless \uline{the} Lord~\GreStar{}~\nopagebreak

now and for ever. \uline{A}men.


\noindent Glory to the Father, and to \uline{the} Son,~\GreStar{}~\nopagebreak

and to the Ho\uline{ly} Spirit:

\noindent as it was in the beginning, \uline{is} now,~\GreStar{}~\nopagebreak

and will be for ever. \uline{A}men.
