\noindent He who dwells in the shelter of the Most High~\GreStar{}~\nopagebreak

and abides in the shade of the Almighty

\noindent says to the Lord: ``My refuge,~\GreStar{}~\nopagebreak

my stronghold, my God in whom I trust!"

\noindent It is he who will free you from the snare~\GreStar{}~\nopagebreak

of the fowler who seeks to destroy you;

\noindent he will conceal you with his pinions~\GreStar{}~\nopagebreak

and under his wings you will find refuge.

\noindent You will not fear the terror of the night~\GreStar{}~\nopagebreak

nor the arrow that flies by day,

\noindent nor the plague that prowls in the darkness~\GreStar{}~\nopagebreak

nor the scourge that lays waste at noon.

\noindent A thousand may fall at your side,~\GreStar{}~\nopagebreak

ten thousand fall at your right,

\noindent you, it will never approach;~\GreStar{}~\nopagebreak

his faithfulness is buckler and shield.

\noindent Your eyes have only to look~\GreStar{}~\nopagebreak

to see how the wicked are repaid,

\noindent you who have said: ``Lord, my refuge!"~\GreStar{}~\nopagebreak

and have made the Most High your dwelling.

\noindent Upon you no evil shall fall,~\GreStar{}~\nopagebreak

no plague approach where you dwell.

\noindent For you has he commanded his angels,~\GreStar{}~\nopagebreak

to keep you in all your ways.

\noindent They shall bear you upon their hands~\GreStar{}~\nopagebreak

lest you strike your foot against a stone.

\noindent On the lion and the viper you will tread~\GreStar{}~\nopagebreak

and trample the young lion and the dragon.

\noindent Since he clings to me in love, I will free him;~\GreStar{}~\nopagebreak

protect him for he knows my name.

\noindent When he calls I shall answer: ``I am with you,"~\GreStar{}~\nopagebreak

I will save him in distress and give him glory.

\noindent With length of life I will content him;~\GreStar{}~\nopagebreak

I shall let him see my saving power.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
