\noindent Not to us, Lord, not to us,~\GreStar{}~\nopagebreak

but to your name give the glory

\noindent for the sake of your love and your truth,~\GreStar{}~\nopagebreak

lest the heathen say: “Where is their God?”



\noindent But our God is in the heavens;~\GreStar{}~\nopagebreak

he does whatever he wills.

\noindent Their idols are silver and gold,~\GreStar{}~\nopagebreak

the work of human hands.



\noindent They have mouths but they cannot speak;~\GreStar{}~\nopagebreak

they have eyes but they cannot see;

\noindent they have ears but they cannot hear;~\GreStar{}~\nopagebreak

they have nostrils but they cannot smell.



\noindent With their hands they cannot feel;~†~\nopagebreak

with their feet they cannot walk.~\GreStar{}~\nopagebreak

No sound comes from their throats.



\noindent Their makers will come to be like them~\GreStar{}~\nopagebreak

and so will all who trust in them.



\noindent Sons of Israel, trust in the Lord;~\GreStar{}~\nopagebreak

he is their help and their shield.

\noindent Sons of Aaron, trust in the Lord;~\GreStar{}~\nopagebreak

he is their help and their shield.



\noindent You who fear him, trust in the Lord;~\GreStar{}~\nopagebreak

he is their help and their shield.

\noindent He remembers us, and he will bless us;~†~\nopagebreak

he will bless the sons of Israel.~\GreStar{}~\nopagebreak

He will bless the sons of Aaron.



\noindent The Lord will bless those who fear him,~\GreStar{}~\nopagebreak

the little no less than the great:

\noindent to you may the Lord grant increase,~\GreStar{}~\nopagebreak

to you and all your children.



\noindent May you be blessed by the Lord,~\GreStar{}~\nopagebreak

the maker of heaven and earth.

\noindent The heavens belong to the Lord~\GreStar{}~\nopagebreak

but the earth he has given to men.



\noindent The dead shall not praise the Lord,~\GreStar{}~\nopagebreak

nor those who go down into the silence.

\noindent But we who live bless the Lord~\GreStar{}~\nopagebreak

now and for ever. Amen.



\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
