\noindent O shepherd of Israel, hear us,~$\star$~\nopagebreak

you who lead Joseph’s flock,

\noindent shine forth from your cherubim throne~$\star$~\nopagebreak

upon Ephraim, Benjamin, Manasseh.

\noindent O Lord, rouse up your might,~$\star$~\nopagebreak

O Lord, come to our help.

\noindent God of hosts, bring us back;~$\star$~\nopagebreak

let your face shine on us and we shall be saved.

\noindent Lord God of hosts, how long~$\star$~\nopagebreak

will you frown on your people’s plea?

\noindent You have fed them with tears for their bread,~$\star$~\nopagebreak

an abundance of tears for their drink.

\noindent You have made us the taunt of our neighbors,~$\star$~\nopagebreak

our enemies laugh us to scorn.

\noindent God of hosts, bring us back;~$\star$~\nopagebreak

let your face shine on us and we shall be saved.

\noindent You brought a vine out of Egypt;~$\star$~\nopagebreak

to plant it you drove out the nations.

\noindent Before it you cleared the ground;~$\star$~\nopagebreak

it took root and spread through the land.

\noindent The mountains were covered with its shadow,~$\star$~\nopagebreak

the cedars of God with its boughs.

\noindent It stretched out its branches to the sea,~$\star$~\nopagebreak

to the Great River it stretched out its shoots.

\noindent Then why have you broken down its walls?~$\star$~\nopagebreak

It is plucked by all who pass by.

\noindent It is ravaged by the boar of the forest,~$\star$~\nopagebreak

devoured by the beasts of the field.

\noindent God of hosts, turn again, we implore,~$\star$~\nopagebreak

look down from heaven and see.

\noindent Visit this vine and protect it,~$\star$~\nopagebreak

the vine your right hand has planted.

\noindent Men have burnt it with fire and destroyed it.~$\star$~\nopagebreak

May they perish at the frown of your face.

\noindent May your hand be on the man you have chosen,~$\star$~\nopagebreak

the man you have given your strength.

\noindent And we shall never forsake you again:~$\star$~\nopagebreak

give us life that we may call upon your name.

\noindent God of hosts, bring us back;~$\star$~\nopagebreak

let your face shine on us and we shall be saved.

\noindent Glory to the Father, and to the Son,~$\star$~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~$\star$~\nopagebreak

and will be for ever. Amen.
