\noindent The Lord is my light and my help;~\GreStar{}~\nopagebreak

whom shall I fear?

\noindent The Lord is the stronghold of my life;~\GreStar{}~\nopagebreak

before whom shall I shrink?

\noindent When evil-doers draw near~\GreStar{}~\nopagebreak

to devour my flesh,

\noindent it is they, my enemies and foes,~\GreStar{}~\nopagebreak

who stumble and fall.

\noindent Though an army encamp against me~\GreStar{}~\nopagebreak

my heart would not fear.

\noindent Though war break out against me~\GreStar{}~\nopagebreak

even then would I trust.

\noindent There is one thing I ask of the Lord,~\GreStar{}~\nopagebreak

for this I long,

\noindent to live in the house of the Lord,~\GreStar{}~\nopagebreak

all the days of my life,

\noindent to savor the sweetness of the Lord,~\GreStar{}~\nopagebreak

to behold his temple.

\noindent For there he keeps me safe in his tent~\GreStar{}~\nopagebreak

in the day of evil.

\noindent He hides me in the shelter of his tent,~\GreStar{}~\nopagebreak

on a rock he sets me safe.

\noindent And now my head shall be raised~\GreStar{}~\nopagebreak

above my foes who surround me,

\noindent and I shall offer within his tent~~†~\nopagebreak

a sacrifice of joy.~\GreStar{}~\nopagebreak

I will sing and make music for the Lord.

\noindent O Lord, hear my voice when I call;~\GreStar{}~\nopagebreak

have mercy and answer.

\noindent Of you my heart has spoken:~\GreStar{}~\nopagebreak

“Seek his face.”

\noindent It is your face, O Lord, that I seek;~\GreStar{}~\nopagebreak

hide not your face.

\noindent Dismiss not your servant in anger;~\GreStar{}~\nopagebreak

you have been my help.

\noindent Do not abandon or forsake me,~\GreStar{}~\nopagebreak

O God my help~

\noindent Though father and mother forsake me,~\GreStar{}~\nopagebreak

the Lord will receive me.

\noindent Instruct me, Lord, in your way;~\GreStar{}~\nopagebreak

on an even path lead me.

\noindent When they lie in ambush, protect me~\GreStar{}~\nopagebreak

from my enemy’s greed.

\noindent False witnesses rise against me,~\GreStar{}~\nopagebreak

breathing out fury.

\noindent I am sure I shall see the Lord’s goodness~\GreStar{}~\nopagebreak

in the land of the living.

\noindent Hope in him, hold firm and take heart.~\GreStar{}~\nopagebreak

Hope in the Lord~

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
