\noindent Why this tumult among nations,~\GreStar{}~\nopagebreak

among peoples this useless murmuring?

\noindent They arise, the kings of the earth,~\GreStar{}~\nopagebreak

princes plot against the Lord and his Anointed.

\noindent “Come let us break their fetters,~\GreStar{}~\nopagebreak

come, let us cast off their yoke.”

\noindent He who sits in the heavens laughs;~\GreStar{}~\nopagebreak

the Lord is laughing them to scorn.

\noindent Then he will speak in his anger,~\GreStar{}~\nopagebreak

his rage will strike them with terror.

\noindent “It is I who have set up my king~\GreStar{}~\nopagebreak

on Zion, my holy mountain.”

\noindent I will announce the decree of the Lord: ~†~\nopagebreak

The Lord said to me: “You are my Son.~\GreStar{}~\nopagebreak

It is I who have begotten you this day.

\noindent Ask and I shall bequeath you the nations,~\GreStar{}~\nopagebreak

put the ends of the earth in your possession.

\noindent With a rod of iron you will break them,~\GreStar{}~\nopagebreak

shatter them like a potter’s jar.”

\noindent Now, O kings, understand,~\GreStar{}~\nopagebreak

take warning, rulers of the earth;

\noindent serve the Lord with awe~\GreStar{}~\nopagebreak

and trembling, pay him your homage

\noindent lest he be angry and you perish;~†~\nopagebreak

for suddenly his anger will blaze.~\GreStar{}~\nopagebreak

Blessed are they who put their trust in God.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
