\noindent I waited, I waited for the Lord~†~\nopagebreak

and he stooped down to me;~\GreStar{}~\nopagebreak

he heard my cry.

\noindent He drew me from the deadly pit,~\GreStar{}~\nopagebreak

from the miry clay.

\noindent He set my feet upon a rock~\GreStar{}~\nopagebreak

and made my footsteps firm.

\noindent He put a new song into my mouth,~\GreStar{}~\nopagebreak

praise of our God.

\noindent Many shall see and fear~\GreStar{}~\nopagebreak

and shall trust in the Lord.

\noindent Happy the man who has placed~\GreStar{}~\nopagebreak

his trust in the Lord

\noindent and has not gone over to the rebels~\GreStar{}~\nopagebreak

who follow false gods.

\noindent How many, O Lord my God,~\GreStar{}~\nopagebreak

are the wonders and designs 

\noindent that you have worked for us;~\GreStar{}~\nopagebreak

you have no equal.

\noindent Should I proclaim and speak of them,~\GreStar{}~\nopagebreak

they are more than I can tell!

\noindent You do not ask for sacrifice and offerings,~\GreStar{}~\nopagebreak

but an open ear.

\noindent You do not ask for holocaust and victim.~\GreStar{}~\nopagebreak

Instead, here am I.

\noindent In the scroll of the book it stands written~\GreStar{}~\nopagebreak

that I should do your will.

\noindent My God, I delight in your law~\GreStar{}~\nopagebreak

in the depth of my heart.

\noindent Your justice I have proclaimed~\GreStar{}~\nopagebreak

in the great assembly.

\noindent My lips I have not sealed;~\GreStar{}~\nopagebreak

you know it, O Lord.

\noindent I have not hidden your justice in my heart~\GreStar{}~\nopagebreak

but declared your faithful help.

\noindent I have not hidden your love and your truth~\GreStar{}~\nopagebreak

from the great assembly.

\noindent O Lord, you will not withhold~\GreStar{}~\nopagebreak

your compassion from me.

\noindent Your merciful love and your truth~\GreStar{}~\nopagebreak

will always guard me.

\noindent For I am beset with evils~\GreStar{}~\nopagebreak

too many to be counted.

\noindent My sins have fallen upon me~\GreStar{}~\nopagebreak

and my sight fails me.

\noindent They are more than the hairs of my head~\GreStar{}~\nopagebreak

and my heart sinks.

\noindent O Lord, come to my rescue,~\GreStar{}~\nopagebreak

Lord, come to my aid.

\noindent O let there be rejoicing and gladness~\GreStar{}~\nopagebreak

for all who seek you.

\noindent Let them ever say: “The Lord is great,”~\GreStar{}~\nopagebreak

who love your saving help.

\noindent As for me, wretched and poor,~\GreStar{}~\nopagebreak

the Lord thinks of me.

\noindent You are my rescuer, my help,~\GreStar{}~\nopagebreak

O God, do not delay.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.