\noindent Turn your ear, O Lord, and give answer~\GreStar{}~\nopagebreak

for I am poor and needy.

\noindent Preserve my life, for I am faithful:~\GreStar{}~\nopagebreak

save the servant who trusts in you.

\noindent You are my God; have mercy on me, Lord,~\GreStar{}~\nopagebreak

for I cry to you all the day long.

\noindent Give joy to your servant, O Lord,~\GreStar{}~\nopagebreak

for to you I lift up my soul.

\noindent O Lord, you are good and forgiving,~\GreStar{}~\nopagebreak

full of love to all who call.

\noindent Give heed, O Lord, to my prayer~\GreStar{}~\nopagebreak

and attend to the sound of my voice.

\noindent In the day of distress I will call~\GreStar{}~\nopagebreak

and surely you will reply.

\noindent Among the gods there is none like you, O Lord;~\GreStar{}~\nopagebreak

nor work to compare with yours.

\noindent All the nations shall come to adore you~\GreStar{}~\nopagebreak

and glorify your name, O Lord:

\noindent for you are great and do marvelous deeds,~\GreStar{}~\nopagebreak

you who alone are God.

\noindent Show me, Lord, your way~†~\nopagebreak

so that I may walk in your truth.~\GreStar{}~\nopagebreak

Guide my heart to fear your name.

\noindent I will praise you, Lord my God, with all my heart~\GreStar{}~\nopagebreak

and glorify your name for ever;

\noindent for your love to me has been great:~\GreStar{}~\nopagebreak

you have saved me from the depths of the grave.

\noindent The proud have risen against me;~†~\nopagebreak

ruthless men seek my life:~\GreStar{}~\nopagebreak

to you they pay no heed.

\noindent But you, God of mercy and compassion,~\GreStar{}~\nopagebreak

slow to anger, O Lord,

\noindent abounding in love and truth,~\GreStar{}~\nopagebreak

turn and take pity on me.

\noindent O give your strength to your servant~\GreStar{}~\nopagebreak

and save your handmaid’s son.

\noindent Show me the sign of your favor~†~\nopagebreak

that my foes may see to their shame~\GreStar{}~\nopagebreak

that you console me and give me your help.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
