\noindent Save me, O God,~\GreStar{}~\nopagebreak

for the waters have risen to my neck.

\noindent I have sunk into the mud of the deep~\GreStar{}~\nopagebreak

and there is no foothold.

\noindent I have entered the waters of the deep~\GreStar{}~\nopagebreak

and the waves overwhelm me.

\noindent I am wearied with all my crying,~\GreStar{}~\nopagebreak

my throat is parched.

\noindent My eyes are wasted away~\GreStar{}~\nopagebreak

from looking for my God.

\noindent More numerous than the hairs on my head~\GreStar{}~\nopagebreak

are those who hate me without cause.

\noindent Those who attack me with lies~\GreStar{}~\nopagebreak

are too much for my strength.

\noindent How can I restore~\GreStar{}~\nopagebreak

what I have never stolen?

\noindent O God, you know my sinful folly;~\GreStar{}~\nopagebreak

my sins you can see.

\noindent Let those who hope in you not be put to shame~\GreStar{}~\nopagebreak

through me, Lord of hosts:

\noindent let not those who seek you be dismayed~\GreStar{}~\nopagebreak

through me, God of Israel.

\noindent It is for you that I suffer taunts,~\GreStar{}~\nopagebreak

that shame covers my face,

\noindent that I have become a stranger to my brothers,~\GreStar{}~\nopagebreak

an alien to my own mother’s sons.

\noindent I burn with zeal for your house~\GreStar{}~\nopagebreak

and taunts against you fall on me.

\noindent When I afflict my soul with fasting~\GreStar{}~\nopagebreak

they make it a taunt against me.

\noindent When I put on sackcloth in mourning~\GreStar{}~\nopagebreak

then they make me a byword,

\noindent the gossip of men at the gates,~\GreStar{}~\nopagebreak

the subject of drunkards’ songs.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
