\noindent I will praise you, Lord, you have rescued me~\GreStar{}~\nopagebreak

and have not let my enemies rejoice over me.

\noindent O Lord, I cried to you for help,~\GreStar{}~\nopagebreak

and you, my God, have healed me.

\noindent O Lord, you have raised my soul from the dead,~\GreStar{}~\nopagebreak

restored me to life from those who sink into the grave.

\noindent Sing psalms to the Lord, you who love him,~\GreStar{}~\nopagebreak

give thanks to his holy name.

\noindent His anger lasts a moment; his favor through life.~\GreStar{}~\nopagebreak

At night there are tears, but joy comes with dawn.

\noindent I said to myself in my good fortune:~\GreStar{}~\nopagebreak

“Nothing will ever disturb me.”

\noindent Your favor had set me on a mountain fastness,~\GreStar{}~\nopagebreak

then you hid your face and I was put to confusion.

\noindent To you, Lord, I cried,~\GreStar{}~\nopagebreak

to my God I made appeal:

\noindent ``What profit would my death be, my going to the grave?~\GreStar{}~\nopagebreak

Can dust give you praise or proclaim your truth?”

\noindent The Lord listened and had pity.~\GreStar{}~\nopagebreak

The Lord came to my help.

\noindent For me you have changed my mourning into dancing,~\GreStar{}~\nopagebreak

you removed my sackcloth and clothed me with joy.

\noindent So my soul sings psalms to you unceasingly.~\GreStar{}~\nopagebreak

O Lord my God, I will thank you for ever.

\noindent Glory to the Father, and to the Son,~\GreStar{}~\nopagebreak

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~\GreStar{}~\nopagebreak

and will be for ever. Amen.
