\emph{Ant.} Come, let us worship Christ, the Son of God, who redeemed us with his blood.

\subsubsection{Psalm 95}	\paragraph{A call to praise God}




\vspace{5pt}
\emph{Encourage each other daily while it is still today (Hebrews 3:13).}
\vspace{5pt}

Come, let us sing to the Lord 

 \noindent  and shout with joy to the Rock who saves us.

\noindent Let us approach him with praise and thanksgiving 

\noindent   and sing joyful songs to the Lord.

\vspace{5pt}
\emph{Ant.} Come, let us worship Christ, the Son of God, who redeemed us with his blood.
\vspace{5pt}

The Lord is God, the mighty God, 

\noindent   the great king over all the gods.

\noindent He holds in his hands the depths of the earth 

\noindent   and the highest mountains as well.

\noindent He made the sea; it belongs to him, 

\noindent   the dry land, too, for it was formed by his hands.

\vspace{5pt}
\emph{Ant.} Come, let us worship Christ, the Son of God, who redeemed us with his blood.
\vspace{5pt}

Come, then, let us bow down and worship, 

\noindent   bending the knee before the Lord, our maker.

\noindent For he is our God and we are his people, 

\noindent   the flock he shepherds.

\vspace{5pt}
\emph{Ant.} Come, let us worship Christ, the Son of God, who redeemed us with his blood.
\vspace{5pt}

Today, listen to the voice of the Lord:

\noindent Do not grow stubborn, as your fathers did in the wilderness, 

\noindent when at Meriba and Massah they challenged me and provoked me, 

\noindent Although they had seen all of my works.

\vspace{5pt}
\emph{Ant.} Come, let us worship Christ, the Son of God, who redeemed us with his blood.
\vspace{5pt}

Forty years I endured that generation. 

\noindent I said, “They are a people whose hearts go astray

\noindent   and they do not know my ways.”

\noindent So I swore in my anger, 

\noindent   “They shall not enter into my rest.”

\vspace{5pt}
\emph{Ant.} Come, let us worship Christ, the Son of God, who redeemed us with his blood.
\vspace{5pt}

Glory to the Father, and to the Son, 

\noindent and to the Holy Spirit:

\noindent as it was in the beginning, is now, 

\noindent and will be for ever. Amen.

\vspace{5pt}
\emph{Ant.} Come, let us worship Christ, the Son of God, who redeemed us with his blood.