\noindent Not to us, Lord, \uline{not} to us,~\GreStar{}~\nopagebreak

but to your name \uline{give} the glory

\noindent for the sake of your love \uline{and} your truth,~\GreStar{}~\nopagebreak

lest the heathen say: “Where \uline{is} their God?”



\noindent But our God is \uline{in} the heavens;~\GreStar{}~\nopagebreak

he does whatev\uline{er} he wills.

\noindent Their idols are sil\uline{ver} and gold,~\GreStar{}~\nopagebreak

the work of \uline{hu}man hands.



\noindent They have mouths but they \uline{can}not speak;~\GreStar{}~\nopagebreak

they have eyes but they \uline{can}not see;

\noindent they have ears but they \uline{can}not hear;~\GreStar{}~\nopagebreak

they have nostrils but they \uline{can}not smell.



\noindent With their hands they cannot \uline{feel};~†~\nopagebreak

with their feet they \uline{can}not walk.~\GreStar{}~\nopagebreak

No sound comes \uline{from} their throats.



\noindent Their makers will come to \uline{be} like them~\GreStar{}~\nopagebreak

and so will all who \uline{trust} in them.



\noindent Sons of Israel, trust \uline{in} the Lord;~\GreStar{}~\nopagebreak

he is their help \uline{and} their shield.

\noindent Sons of Aaron, trust \uline{in} the Lord;~\GreStar{}~\nopagebreak

he is their help \uline{and} their shield.



\noindent You who fear him, trust \uline{in} the Lord;~\GreStar{}~\nopagebreak

he is their help \uline{and} their shield.

\noindent He remembers us, and he will \uline{bless us;}~†~\nopagebreak

he will bless the \uline{sons} of Israel.~\GreStar{}~\nopagebreak

He will bless the \uline{sons} of Aaron.



\noindent The Lord will bless \uline{those} who fear him,~\GreStar{}~\nopagebreak

the little no less \uline{than} the great:

\noindent to you may the \uline{Lord} grant increase,~\GreStar{}~\nopagebreak

to you and \uline{all} your children.



\noindent May you be blessed \uline{by} the Lord,~\GreStar{}~\nopagebreak

the maker of hea\uline{ven} and earth.

\noindent The heavens belong \uline{to} the Lord~\GreStar{}~\nopagebreak

but the earth he has gi\uline{ven} to men.



\noindent The dead shall not \uline{praise} the Lord,~\GreStar{}~\nopagebreak

nor those who go down in\uline{to} the silence.

\noindent But we who live \uline{bless} the Lord~\GreStar{}~\nopagebreak

now and for ev\uline{er}. Amen.



\noindent Glory to the Father, and \uline{to} the Son,~\GreStar{}~\nopagebreak

and to the \uline{Ho}ly Spirit:

\noindent as it was in the begin\uline{ning}, is now,~\GreStar{}~\nopagebreak

and will be for ev\uline{er}. Amen.
