\textbf{From the letter to the Hebrews} \hfill 4:14-5:10

\paragraph{Jesus Christ, the great high priest}

\lettrine[lines=3]{S}{}ince we have a great high priest who has passed through the heavens, Jesus, the Son of God, let us hold fast to our profession of faith. For we do not have a high priest who is unable to sympathize with our weakness, but one who was tempted in every way that we are, yet never sinned. So let us confidently approach the throne of grace to receive mercy and favor and to find help in time of need.

Every high priest is taken from among men and made their representative before God, to offer gifts and sacrifices for sins. He is able to deal patiently with erring sinners, for he himself is beset by weakness and so must make sin offerings for himself as well as for the people. One does not take this honor on his own initiative, but only when called by God as Aaron was.

Even Christ did not glorify himself with the office of high priest; he received it from the One who said to him,

\vspace{5pt}
   “You are my Son; \par
      today I have begotten you”;

\vspace{5pt}

just as he says in another place,

\vspace{5pt}

   “You are a priest forever,\par
      according to the order of Melchizedek.”

\vspace{5pt}

In the days when he was in the flesh, he offered prayers and supplications with loud cries and tears to God, who was able to save him from death, and he was heard because of his reverence. Son though he was, he learned obedience from what he suffered; and when perfected, he became the source of eternal salvation for all who obey him, designated by God as high priest according to the order of Melchizedek.

\subsubsection{Responsory}
\hfill \emph{Hebrews 5:8, 9, 7}

Though he was the Son of God,\par
Christ learned obedience through what he suffered;\par
– and now, for all who obey him,\par
he has become the source of eternal life.\par
\vspace{5pt}
In the days of his earthly life he prayed, crying aloud,\par
and he submitted so humbly that his prayer was heard.\par
– And now, for all who obey him,\par
he has become the source of eternal life.\par