Thirty years among us dwelling,

\noindent His appointed time fulfilled,

\noindent Born for this he meets his passion,

\noindent This indeed he freely willed;

\noindent On the cross the Lamb is lifted

\noindent Where his lifeblood shall be spilled.

\noindent 

2. He endured the nails, the spitting,

\noindent Vinegar and spear and reed;

\noindent From that holy body broken,

\noindent Blood and water forth proceed:

\noindent Earth and stars and sky and ocean,

\noindent By that flood from stain are freed.

\noindent 

3. Faithful Cross! Above all others,

\noindent One and only noble tree!

\noindent None in foliage, none in blossom,

\noindent None in fruit, your peer may be;

\noindent Precious wood and precious fast'ning,

\noindent Precious weight upheld in plea.

\noindent 

4. Bend your boughs, O Tree of glory!

\noindent Your relaxing sinews bend;

\noindent For a while the ancient rigor,

\noindent That your birth bestowed, suspend;

\noindent And the King of heav'nly beauty

\noindent On your bosom gently tend.

\noindent 

5. You alone were counted worthy

\noindent This world's ransom to sustain,

\noindent That a shipwrecked race forever

\noindent Might the port of refuge gain;

\noindent With the sacred blood anointed

\noindent Of the Lamb for sinners slain.

\noindent 

6. Praise and honor to the Father;

\noindent Praise and honor to the Son,

\noindent Praise and honor to the Spirit,

\noindent Ever three and ever one;

\noindent Consubstantial, coeternal,

\noindent While unending ages run. Amen.