\hfill Lamentations 5:1–22
\par\vspace{5pt}
\textit{For Latin text with musical notation, see p. \pageref{Oratio Ieremiæ}. For English text with musical notation, see p. \pageref{Prayer of Jeremiah}.}
\par\vspace{5pt}

The Prayer of the Prophet Jeremiah. Remember, Lord, what has happened to us,
    pay attention, and see our disgrace:
Our heritage is turned over to strangers,
    our homes, to foreigners.
We have become orphans, without fathers;
    our mothers are like widows.
We pay money to drink our own water,
    our own wood comes at a price.
With a yoke on our necks, we are driven;
    we are worn out, but allowed no rest.

We extended a hand to Egypt and Assyria,
    to satisfy our need of bread.
Our ancestors, who sinned, are no more;
    but now we bear their guilt.
Servants rule over us,
    with no one to tear us from their hands.
We risk our lives just to get bread,
    exposed to the desert heat;
Our skin heats up like an oven,
    from the searing blasts of famine.

The wives in Zion were ravished by the enemy,
    the maidens in the cities of Judah;
Princes have been hanged by them,
    elders shown no respect.
Young men carry millstones,
    boys stagger under loads of wood;
The elders have abandoned the gate,
    the young men their music.

The joy of our hearts has ceased,
    dancing has turned into mourning;
The crown has fallen from our head:
    woe to us that we sinned!
Because of this our hearts grow sick,
    at this our eyes grow dim:
Because of Mount Zion, lying desolate,
    and the jackals roaming there!

But you, Lord, are enthroned forever;
    your throne stands from age to age.
Why have you utterly forgotten us,
    forsaken us for so long?
Bring us back to you, Lord, that we may return:
    renew our days as of old.
For now you have indeed rejected us
    and utterly turned your wrath against us.
    
    Jerusalem, Jerusalem, return to the Lord your God!
